### 2020-03-20 analyses/analyses.Rmd
- set-up of github - novel analyses using newly merged data

---
title: "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
shorttitle : "Online Supplementary Material: Analyses"
output: 
  html_document:
    self_contained: yes
    mode: selfcontained
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

```{r setup, include=F}
knitr::opts_chunk$set(
  cache=T, comment=NA, warning=F, echo=F, error=F, 
  message=F, prompt=F, tidy=T, fig.height=4
  )
options(digits = 3, width = 120)
```

```{r r-setup, include=F}
# define packages
packages <- c("cowplot", "devtools", "GGally", "knitr", "lavaan", "magrittr", 
              "MVN", "psych", "pwr", "quanteda", "semTools", "tidyverse")

# install packages
# devtools::install_github("tdienlin/td@v.0.0.2.3")
# lapply(packages, install.packages, character.only = T, quietly = TRUE)

# load packages
lapply(packages, library, character.only = TRUE, quietly = TRUE)
library(td)
```

```{r Data-Wrangling, include=F}
# load data
d_raw <- read_csv("data/data_raw.csv")

# recode variables
d <- d_raw %>% 
  dplyr::rename(
    "male" = "SD01", 
    "age" = "SD02_01", 
    "state" = "SD03", 
    "edu_fac" = "SD04"
    ) %>% 
  mutate(

    #general
    version = factor(.$VE01_01, labels = c("Control", "Like", "Like & Dislike")),
    version_no = recode(version, "Control" = 1, "Like" = 2, "Like & Dislike" = 3),
    male = replace_na(.$male, "[3]") %>% dplyr::recode(., "männlich [1]" = 1, "weiblich [2]" = 0),
    age_grp = cut(.$age, 
                  breaks = c(0, 29, 39, 49, 59, 100), 
                  labels = c("<30", "30-39", "40-49", "50-59", ">59")),

    # contrasts
    lik_ctrl = recode(version, "Control" = 0, "Like" = 1),
    lik_ctrl = na_if(lik_ctrl, "Like & Dislike"),
    likdis_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
    likdis_ctrl = na_if(likdis_ctrl, "Like"),
    likdis_lik = recode(version, "Like" = 0, "Like & Dislike" = 1),
    likdis_lik = na_if(likdis_lik, "Control"),
    likdislik_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
    likdislik_ctrl = na_if(likdislik_ctrl, "Like"),

    # recode
    edu = recode(edu_fac, 
                 "Hauptschulabschluss/Volksschulabschluss" = 1, 
                 "Noch Schüler" = 1,
                 "Realschulabschluss (Mittlere Reife)" = 1,
                 "Abschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = 1,
                 "Anderer Schulabschluss:" = 1,
                 "Fachhochschulreife (Abschluss einer Fachoberschule)" = 2,
                 "Abitur, allgemeine oder fachgebundene Hochschulreife (Gymnasium bzw. EOS)" = 2,
                 "Hochschulabschluss" = 3),
    PC01_03 = 8 - PC01_03, 
    SE01_05 = 8 - SE01_05, 
    SE01_06 = 8 - SE01_06,
    PL01 = recode(PL01, "2" = 1, .default = 0),
    PL02 = recode(PL02, "3" = 1, .default = 0),
    PL03 = recode(PL03, "4" = 1, .default = 0),
    PL04 = recode(PL04, "2" = 1, .default = 0),
    IF01_01 = recode(IF01_01, "1" = 1, .default = 0),
    IF01_02 = recode(IF01_02, "1" = 1, .default = 0),

    # behavioral data
    words = replace_na(.$words, 0),
    self_dis = words + (reactions * 2),
    time_read_MIN = time_read / 60,
    time_sum_min_t2 = TIME_SUM_t2 / 60,

    # take logarithm
    posts_log = log1p(.$post_count),
    time_log = log1p(.$time_read), 
    posts_read_count_log = log1p(.$posts_read_count),
    words_log = log1p(.$words),
    self_dis_log = log1p(self_dis)
  )
```

```{r defaults, include=F}
# variable labels
var_names <- c("Privacy concerns", 
               "General gratifications", 
               "Specific gratifications",
               "Privacy deliberation", 
               "Self-efficacy", 
               "General trust", 
               "Specific trust",
               "Self-disclosure")

var_names_breaks <- c("Privacy\nconcerns", 
                      "General\ngratifications", 
                      "Specific\ngratifications",
                      "Privacy\ndeliberation", 
                      "Self-\nefficacy", 
                      "General\ntrust", 
                      "Specific\ntrust",
                      "Self-\ndisclosure")
```

```{r sample-descriptives, include=F}
# sample descriptives t1
n_t1 <- nrow(d)
age_t1_m <- mean(d$age)
male_t1_m <- mean(d$male, na.rm = TRUE)
college_t1_m <- table(d$edu)[3] / n_t1

# sample descriptives t2
n_t2 <- filter(d, !is.na(id_survey_t2)) %>% nrow()
age_t2_m <- filter(d, !is.na(id_survey_t2))$age %>% mean()
male_t2_m <- filter(d, !is.na(id_survey_t2))$male %>% mean(na.rm = TRUE)
college_t2_m <- filter(d, !is.na(id_survey_t2))$edu %>% table() %>% .[3] / n_t2

# characteristics of posts
n_comments <- sum(d$post_count, na.rm = TRUE)
n_words <- sum(d$words_sum, na.rm = TRUE)
n_time <- sum(d$time_read_MIN, na.rm = TRUE)
n_posts <- sum(d$post_count, na.rm = TRUE)

# speeding
time_crit <- 3 # minimum time on survey
n_speeding <- nrow(filter(d, time_sum_min_t2 < time_crit))

# filter data
d <- filter(d, time_sum_min_t2 > time_crit) # Deletion of fast respondents
d <- filter(d, !is.na(username) & !is.na(id_survey_t2))  # Use only completes

# sample descriptives final data set
n_final <- nrow(d)
age_final_m <- mean(d$age)
male_final_m <- mean(d$male, na.rm = TRUE)
college_final_m <- table(d$edu)[3] / n_final
```

# Measures
## Privacy Concerns
### Items

Using the participation platform I had ...

 1. ... concerns about what happens to my data.
 2. ... concerns about disclosing information about myself.
 3. ... no concerns.
 4. ... concerns that others could discover my real identity (i.e. my last and first name).
 5. ... concerns that information about myself could fall into wrong hands.
 6. ... concerns that others could discover what my political views are.
 7. ... concerns about my privacy.

### Distributions

```{r}
ggplot(gather(select(d, starts_with("PC01"))), 
                      mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_pricon <- select(d, starts_with("PC01")) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_03 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

Shows that PC01_03 doesn't load well. As it's an inverted item that's not surprising. Also from a theoretic perspective it's suboptional, because it doesn't explicitly focus on privacy, but just concerns in general. Will be deleted.

### CFA updated

```{r}
name <- "pricon"
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

## Gratifications general
### Items

Using the participation platform ...

 1.	... had many benefits for me.
 2.	... has paid off for me.
 3.	... was useful for me.
 4.	... was fun.
 5.	... has brought me further regarding content.

### Distributions

```{r}
ggplot(gather(select(d, starts_with("GR02"))), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_grats_gen <- select(d, starts_with("GR02")) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "grats_general"
model <- "
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

## Gratifications specific
### Items

Using the participation platform it has been possible for me ...

_Information_

 1.	... to learn things I would not otherwise have noticed.
 2.	... to hear the opinion of others.
 3.	... to learn how other people tick.

_Relevance_

 4.	... to react to a subject that is very dear to me.
 5.	... to react to a subject that is important to me.
 6.	... to react to a subject that I am affected by.

_Political participation_

 7.	... to engage politically.
 8.	... to discuss political issues.
 9.	... to pursue my political interest.

_Idealism_

 10. ... to try to improve society.
 11. ... to advocate to something meaningful.
 12. ... to serve a good purpose.

_Extrinsic benefits_

 13. ... to do the responsible persons a favor.
 14. ... to soothe my bad consciences.
 15. ... to fulfil my civic duty.

### Distributions

```{r fig.height=6}
ggplot(gather(select(d, starts_with("GR01"))), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=2) + 
  theme_bw()

des_grats_spec <- select(d, starts_with("GR01")) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "grats_specific"
model <- "
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

## Privacy Deliberation
### Items

Using the participation platform ...

 1. ... I have considered whether I could be disadvantaged by writing a comment.
 2. ... I have considered whether I could be advantaged by writing a comment.
 3. ... I have weighed up the advantages and disadvantages of writing a comment.
 4. ... I have thought about consequences of a possible comment.
 5. ... I have considered whether I should write a comment or not.

### Distributions

```{r}
ggplot(gather(select(d, starts_with("PD01"))), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_pridel <- select(d, starts_with("PD01")) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "pridel"
model <- "
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

## Trust general
### Items

 1. The other users seemed trustworthy.
 5. The operators of the participation platform seemed trustworthy.
 9. The website seemed trustworthy.

### Distributions

```{r}
ggplot(gather(select(d, TR01_01, TR01_05, TR01_09)), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_trust_gen <- select(d, TR01_01, TR01_05, TR01_09) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "trust_gen"
model <- "
trust =~ TR01_01 + a*TR01_05 + a*TR01_09
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

Note that we constrained Items 5 and Item 9 to be equal. Explanation: First, they are theoretically related. Second, not constraining would yield to just-identified model, for which model fit cannot be interpreted meaningfully.

## Trust specific
### Items

_Community_

 2.	The comments of other users were useful.
 3.	The other users had good intentions.
 4.	I could rely on the statements of other users.

_Provider_

 6.	The operators of the participation platform have done a good job.
 7.	It was important to the operators that the users are satisfied with the participation platform.
 8.	I could rely on the statements of the operators of the participation platform.

_Information System_

 10.	The website worked well.
 11.	I had the impression that my data was necessary for the use of the website.
 12.	I found the website useful.

### Distributions

```{r}
ggplot(gather(select(d, TR01_02:TR01_04, TR01_06:TR01_08, TR01_10:TR01_12)), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_trust_spec <- select(d, TR01_02:TR01_04, TR01_06:TR01_08, TR01_10:TR01_12) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "trust_spec"
model <- "
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08
trust_system =~ TR01_10 + TR01_11 + TR01_12

trust =~ trust_community + trust_provider + trust_system
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

## Self-Efficacy
### Items

 1. In principle, I felt able to write a comment.
 2. I have felt technically competent enough to write a comment.
 3. Regarding content I have felt competent enough to express my opinion.
 4. I found the subject too difficult to express my opinion.
 5. I found it complicated to write a comment.
 6. I was overburdened to write a comment.

### Distributions

```{r}
ggplot(gather(select(d, starts_with("SE01"))), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_selfeff <- select(d, starts_with("SE01")) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "self-eff"
model <- "
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04 + SE01_05 + SE01_06
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

Shows significant misfit. We will run exploratory factor analyses to determine factorial structure.

### EFA

```{r}
fa.parallel(select(d, SE01_01 : SE01_06))
fa(r = select(d, SE01_01 : SE01_06), 
   nfactors = 2, fm = "ml", rotate = "promax")
```

Implies latent structure with two factors.

### CFA updated

```{r}
name <- "selfeff"
model <- "
self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
self_eff_neg =~ SE01_05 + SE01_06
self_eff =~ a*self_eff_pos + a*self_eff_neg
"
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

Adapted version shows better and adequate fit.

## Self-Disclosure
### Items

Let us assume that the participation platform would continue to exist in the future. Please indicate to what extent you agree with the following statements:

In the future, I am willing to ...

 1. ... discuss political issues on the participation platform.
 2. ... express my personal opinion on the participation platform.
 3. ... write comments on the participation platform.
 4. ... disclose concerns and fears on the participation platform.
 5. ... share personal experience on the participation platform.

### Distributions

```{r}
ggplot(gather(select(d, starts_with("WS01"))), 
       mapping = aes(x = value)) +
  geom_bar() +
  facet_wrap(~key, nrow=1) + 
  theme_bw()

des_futuse <- select(d, starts_with("WS01")) %>% 
  apply(1, mean, na.rm = TRUE) %>% 
  as.data.frame() %>% 
  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
```

### CFA

```{r}
name <- "futuse"
model <- "
fut_use =~ WS01_01 + WS01_02 + WS01_03 + WS01_04 + WS01_05
"
sem(model = model, data = d)
fit <- sem(model = model, data = d, estimator = "MLM")
```

#### Model fit

```{r}
(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
assign(paste0(name, "_factor_val"), factor_val)
```

#### Factor loadingss

```{r}
inspect(fit,what="std")$lambda
```

## Baseline Model

In what follows, please find the results of all variables combined in one model. This model will be used to extract factor scores.

```{r}
model <- "
  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
  grats_par =~ GR01_07 + GR01_08 + GR01_09
  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
  grats_ext =~ GR01_13 + GR01_14 + GR01_15
  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
  trust_gen =~ TR01_01 + TR01_05 + TR01_09
  trust_community =~ TR01_02 + TR01_03 + TR01_04
  trust_provider =~ TR01_06 + TR01_07 + TR01_08
  trust_system =~ TR01_10 + TR01_11 + TR01_12
  trust_spec =~ trust_community + trust_provider + trust_system
  self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  self_eff_neg =~ SE01_05 + SE01_06
  self_eff =~ a*self_eff_pos + a*self_eff_neg
  self_dis_lg =~ self_dis_log
"
fit_baseline <- sem(model, data = d, missing = "ML")
summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)

# extract model predicted values for items & calc means
d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
  as.data.frame() %>% 
  mutate(grats_gen = rowMeans(select(., starts_with("GR02")))) %>% 
  mutate(grats_spec = rowMeans(select(., starts_with("GR01")))) %>% 
  mutate(pricon = rowMeans(select(., starts_with("PC01")))) %>% 
  mutate(trust_gen = rowMeans(select(., TR01_01, TR01_05, TR01_09))) %>%
  mutate(trust_spec = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12))) %>% 
  mutate(pridel = rowMeans(select(., starts_with("PD01")))) %>% 
  mutate(selfeff = rowMeans(select(., starts_with("SE01")))) %>%
  select(pricon, grats_gen, grats_spec, pridel, selfeff, trust_gen, trust_spec, self_dis_log) %>% 
  set_names(var_names_breaks) %>% 
  mutate(version = d$version)
```

# Descriptive analyses

We first report the factor validity of all variables combined.

```{r}
# means of model predicted values
des <- rbind(des_pricon,
             des_grats_gen,
             des_grats_spec,
             des_pridel,
             des_selfeff,
             des_trust_gen,
             des_trust_spec,
             des_futuse)

factor_val_tab <- rbind(pricon_factor_val,
                        grats_general_factor_val,
                        grats_specific_factor_val,
                        pridel_factor_val,
                        selfeff_factor_val,
                        trust_gen_factor_val,
                        trust_spec_factor_val) %$%
  cbind(des[-8, ], .) %>%
  set_rownames(var_names[-8]) %T>%
  print()
# factor_val_tab %>% kable(digits = 2)
```

In what follows, we report zero-order correlations, distributions, and scatterplots of the variables' factor scores.

```{r zds, fig.height=8, fig.width=8}
plot_fs_cor <- ggpairs(
  select(d_fs, -version),
  upper = list(continuous = "cor"),
  lower = list(continuous = scat_plot)) +
  theme_bw()
print(plot_fs_cor)
```

# Power analyses

```{r pwr-criteria, include=F}
z_crit <- 1.96
alpha <- .05
power_desired <- .95
r_sesoi <- .10
```

We first estimate the sample size necessary to find small effects in 95% of all cases.

```{r pwr-samplesize}
pwr.r.test(r = r_sesoi, sig.level = alpha, power = power_desired, alternative = "greater") %T>%
  print %$% 
  n %>% 
  round(0) ->
  n_desired
```

We then compute the power we have achieved with our finale sample size to detect small effects.

```{r pwr-achieved}
pwr.r.test(n = n_final, r = r_sesoi, sig.level = alpha, alternative = "greater") %T>%
  print %$% 
  power %>% 
  round(2) ->
  power_achieved
```

We finally compute what effect size we are likely to find in 95% of all cases given our final sample size.

```{r pwr-sensitivity}
pwr.r.test(n = n_final, power = power_desired, sig.level = alpha, alternative = "greater") %T>%
  print %$% 
  r %>% 
  round(2) ->
  r_sensitive
```

# Results
## Privacy calculus
### Preregistered
#### Model "Peregistered"

We first test for multivariate normal distribution.

```{r}
# create subset of data with all items that were used
d_sub <- d[, c("self_dis_log", "GR02_01", "GR02_02", "GR02_03", "GR02_04", "GR02_05", "PC01_01", "PC01_02", "PC01_04", "PC01_05", "PC01_06", "PC01_07", "TR01_02", "TR01_03", "TR01_04", "TR01_06", "TR01_07", "TR01_08", "TR01_10", "TR01_11", "TR01_12", "PD01_01", "PD01_02", "PD01_03", "PD01_04", "PD01_05", "SE01_01", "SE01_02", "SE01_03", "SE01_04", "male", "age", "edu")]

# test multivariate normal distribution
mvn_result <- mvn(d_sub, mvnTest = "mardia")
mvn_result$multivariateNormality
```

Shows that multivariate normal distribution is violated. We hence use maximum likelihood estimation with robust standard errors and a Satorra-Bentler scaled test statistic.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 # + PC01_03 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d, estimator = "MLM")
summary(fit_prereg, fit = TRUE, std = TRUE)
fit_tab(fit_prereg, scaled = TRUE)

d_coeffs_prereg <- coeffs_tab(fit_prereg, c("a1", "b1", "c1", "d1", "e1")) %>% 
  mutate(Outcome = rep("Preregistered\nmodel", 5)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Trust\nspecific", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\ngeneral", "Privacy\nconcern"))))

plot_coeffs_prereg <- ggplot(d_coeffs_prereg, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

### Exploratory
#### Model "adapted"

We now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d, estimator = "MLM")
summary(fit_adapted, fit = TRUE, std = TRUE)
fit_tab(fit_adapted, scaled = TRUE)

d_coeffs_adapted <- coeffs_tab(fit_adapted, c("a1", "b1", "c1", "d1", "e1")) %>% 
  mutate(Outcome = rep("Adapted\nmodel", 5)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific", "Privacy\ndelib.", "Self-\nefficacy", "Trust\ngeneral")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Trust\ngeneral", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\nspecific", "Privacy\nconcern"))))

plot_coeffs_adapted <- ggplot(d_coeffs_adapted, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

#### Model "simple"

We now use only variables, that is specific gratifications and privacy concerns.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

self_dis_log ~ a1*pri_con + b1*grats_spec

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d, estimator = "MLM")
summary(fit_simple, fit = TRUE, std = TRUE)
fit_tab(fit_simple, scaled = TRUE)

d_coeffs_simple <- coeffs_tab(fit_simple, c("a1", "b1")) %>% 
  mutate(Outcome = rep("Simple\nmodel", 2)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Grats.\nspecific", "Privacy\nconcern"))))

plot_coeffs_simple <- ggplot(d_coeffs_simple, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

### Model Comparison

```{r}
plot_pc <- plot_grid(plot_coeffs_prereg, 
                     plot_coeffs_adapted, 
                     plot_coeffs_simple, 
                     nrow = 1)
```

```{r}
model_comp_tab <- data.frame(
  preregistered = fitmeasures(fit_prereg, c("BIC", "AIC")),
  adapted = fitmeasures(fit_adapted, c("BIC", "AIC")),
  simple = fitmeasures(fit_simple, c("BIC", "AIC"))) %>% 
  t() %T>%
  print()
```

## Effects of popularity cues
### Visualisation

The easiest way to assess the effect of the experimental manipulation on the variables is by visualizing their means. If 95% confidence intervals don't overlap, the variables differ significantly across the conditions. One can quickly see that there aren't any major effects.

```{r}
plot_fs_m <- ggplot(
  gather(d_fs, variable, value, -version) %>% 
    mutate(variable = factor(variable, levels = var_names_breaks)),
  aes(x = version, y = value, fill = version)) +
  stat_summary(fun.y = mean, geom = "bar") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
  facet_wrap(~ variable, nrow = 2) + 
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust = .5),
        panel.spacing = unit(.9, "lines"),
        text = element_text(size = 12),
        legend.position="bottom",
        legend.title = element_blank()) +
  scale_fill_brewer(palette="Greys")
plot_fs_m
```

### Preregistered

In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts. However, please note that several models did not converge. This is likely because the models remain complex, while the sample size significantly decreases (i.e., only 2/3 of prior models).

#### Like vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Like

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"

fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
summary(fit_likdis_lik, fit = TRUE, std = TRUE)
```

### Exploratory
#### Like vs. control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con ~ a1*lik_ctrl
grats_spec ~ a2*lik_ctrl
self_dis_log ~ b1*pri_con + b2*grats_spec + c1*lik_ctrl

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_lik_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
summary(fit_lik_ctrl_simple, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con + grats_spec ~ likdis_ctrl
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_ctrl

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_likdis_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
summary(fit_likdis_ctrl_simple, std = TRUE)
```

#### Like & Dislike vs. Like

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con + grats_spec ~ likdis_lik
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_lik

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
summary(fit_likdis_lik, std = TRUE, fit = TRUE)
```

# Results without Covariates

As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain the same.

## Privacy calculus
### Preregistered
#### Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 # + PC01_03 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
"
fit_nocovs_prereg <- sem(model, data = d, estimator = "MLM")
summary(fit_nocovs_prereg, fit = TRUE, std = TRUE)
fit_tab(fit_nocovs_prereg)

d_coeffs_prereg <- coeffs_tab(fit_nocovs_prereg, c("a1", "b1", "c1", "d1", "e1")) %>% 
  mutate(Outcome = rep("Preregistered\nmodel", 5)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Trust\nspecific", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\ngeneral", "Privacy\nconcern"))))

plot_coeffs_prereg <- ggplot(d_coeffs_prereg, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

### Exploratory
#### Model "better"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
"
fit_nocovs_adapted <- sem(model, data = d, estimator = "MLM")
summary(fit_nocovs_adapted, fit = TRUE, std = TRUE)
fit_tab(fit_nocovs_adapted)

d_coeffs_adapted <- coeffs_tab(fit_nocovs_adapted, c("a1", "b1", "c1", "d1", "e1")) %>% 
  mutate(Outcome = rep("Adapted\nmodel", 5)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific", "Privacy\ndelib.", "Self-\nefficacy", "Trust\ngeneral")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Trust\ngeneral", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\nspecific", "Privacy\nconcern"))))

plot_coeffs_adapted <- ggplot(d_coeffs_adapted, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

#### Model "simple"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

self_dis_log ~ a1*pri_con + b1*grats_spec
"
fit_nocovs_simple <- sem(model, data = d, estimator = "MLM")
summary(fit_nocovs_simple, fit = TRUE, std = TRUE)
fit_tab(fit_nocovs_simple)

d_coeffs_simple <- coeffs_tab(fit_nocovs_simple, c("a1", "b1")) %>% 
  mutate(Outcome = rep("Simple\nmodel", 2)) %>%  
  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific")) %>% 
  mutate_at(vars(Predictor), funs(factor(., c("Grats.\nspecific", "Privacy\nconcern"))))

plot_coeffs_simple <- ggplot(d_coeffs_simple, aes(x = b, y = Predictor)) + 
  theme_bw() +
  theme(axis.title.x=element_blank()) + 
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = ll, xmax = ul), 
                lwd = .75, colour = "grey", height = .2) +
  geom_errorbarh(aes(xmin = ll, xmax = ul),
                lwd = .75, colour = "black", height = .2) +
  geom_point(size = 2) +
  guides(color = FALSE, shape = FALSE) + 
  facet_grid(~ Outcome) +
  theme(axis.title.y = element_blank()) +
  theme(plot.title = element_text(hjust = .5)) + 
  theme(panel.spacing = unit(.9, "lines")) + 
  theme(text = element_text(size = 12))
```

## Effects of popularity cues
### Preregisterd
#### Like vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
"
fit_nocovs_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
summary(fit_nocovs_lik_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
"
fit_nocovs_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
summary(fit_nocovs_likdis_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Like

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
"

fit_nocovs_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
summary(fit_nocovs_likdis_lik, fit = TRUE, std = TRUE)
```

### Exploratory
#### Like vs. control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con ~ a1*lik_ctrl
grats_spec ~ a2*lik_ctrl
self_dis_log ~ b1*pri_con + b2*grats_spec + c1*lik_ctrl
"
fit_nocovs_lik_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
summary(fit_nocovs_lik_ctrl_simple, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con + grats_spec ~ likdis_ctrl
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_ctrl
"
fit_nocovs_likdis_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
summary(fit_nocovs_likdis_ctrl_simple, std = TRUE)
```

#### Like & Dislike vs. Like

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con + grats_spec ~ likdis_lik
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_lik
"
fit_nocovs_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
summary(fit_nocovs_likdis_lik, std = TRUE, fit = TRUE)
```

```{r remove-large-objects, include=F}
obj_keep <- c("d", "d_fs", 
              "fit_baseline", "fit_adapted", "fit_prereg", "fit_simple",
              "plot_fs_m", "plot_fs_cor", "plot_pc",
              "des_pridel",
              "model_comp_tab", "factor_val_tab",
              "n_comments", "n_desired", "n_posts", "n_speeding", "n_time", "n_words",
              "n_comments", "n_words", "n_time", "n_posts", "n_speeding",
              "n_t1", "age_t1_m", "male_t1_m", "college_t1_m",
              "n_t2", "age_t2_m", "male_t2_m", "college_t2_m",
              "n_final", "age_final_m", "male_final_m", "college_final_m",
              "r_sesoi", "r_sensitive", "power_achieved")
# rm(list=setdiff(ls(), obj_keep))
```

```{r SaveData, include = FALSE, cache=F}
write.csv(d, file = "data/data.csv", row.names = FALSE)
save(d, d_fs,
     fit_baseline,
     fit_adapted, 
     fit_prereg,
     fit_simple,
     plot_fs_m, plot_fs_cor, plot_pc,
     des_pridel,
     model_comp_tab, factor_val_tab,
     n_comments, n_desired, n_posts, n_speeding, n_time, n_words,
     n_comments, n_words, n_time, n_posts, n_speeding,
     n_t1, age_t1_m, male_t1_m, college_t1_m,
     n_t2, age_t2_m, male_t2_m, college_t2_m,
     n_final, age_final_m, male_final_m, college_final_m,
     r_sesoi, r_sensitive, power_achieved,
     file = "data/workspace.RData"
     )
```

### 2020-03-20 manuscript/manuscript.RmD
- set-up of github - novel analyses using newly merged data

---
title             : "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
shorttitle        : "Popularity cues and the privacy calculus"
author: 
  - name          : "Author"
    affiliation   : "1"
    corresponding : yes
    address       : "Postal address"
    email         : "my@email.com"
affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
authornote: |
abstract: |
    Äccording to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online. So far, little is known about whether the privacy calculus can be used to predict observations of actual authentic behavior, and whether the privacy calculus can be influenced by the design of online websites---for example, by implementing popularity cues such as like and dislike buttons. To answer this question, we ran a preregistered one-week field experiment, in which participants were randomly distributed to three different websites where they could discuss a current political topic. First, the results showed that privacy calculus variables predicted a considerable share of actual self-disclosure. Second, we found that the impact of implementing popularity cues was negligible. In conclusion, the results demonstrate that self-disclosure online can be explained by, for example, privacy concerns and psychological gratifications. This finding has several implications---for example, it provides further evidence against the privacy paradox.
keywords          : "privacy calculus, self-disclosure, popularity cues, structural equation modeling, preregistration"
bibliography      : 
  - [../bibliography/r-references.bib]
  - [../bibliography/references.bib]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes
wordcount         : "`r wordcountaddin::word_count('../manuscript/manuscript.Rmd')`"
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
---

```{r include=F}
# knitr::opts_knit$set(root.dir = "../")
knitr::opts_chunk$set(cache=F)
```

```{r setup, include=F}
# load packages
pcks <- c("devtools", "jpeg", "knitr", "lavaan", "magrittr", "papaja", "png", "pwr", "semTools", "tidyverse")
invisible(lapply(pcks, library, character.only = TRUE))
# install_github("tdienlin/td@v.0.0.2.3")
library(td)

# create bib with r-packages
r_refs(file = "../bibliography/r-references.bib")

# load bib
r_citations <- cite_r("../bibliography/r-references.bib"
                      , footnote = FALSE
                      , withhold = FALSE
                      , pkgs = c("tidyverse", "lavaan", "papaja", "pwr", "quanteda", "semTools")
                      )
load("../data/workspace.RData")
```

Understanding why people disclose personal information online remains a critical question for both society and academic research. Originally, self-disclosure online was thought to be mostly erratic---for example, it was assumed that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints. Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].

Somewhat surprisingly, despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018] the privacy paradox has garnered little empirical support. A recent meta-analysis revealed that the correlation between privacy concerns and self-disclosure on SNS is *r* = -.13 [@baruhOnlinePrivacyConcerns2017], indicating that privacy concerns are indeed related to self-disclosure online.

Rather than further pursuing the privacy paradox, a large share of current day research posits that self-disclosure online can be explained---at least partly---by means of the so-called _privacy-calculus_ [@krasnovaOnlineSocialNetworks2010]. The privacy calculus builds on the work of @lauferPrivacyConceptSocial1977 and claims that both expected risks *and* expected benefits explain self-disclosure. Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information [e.g., @heirmanPredictingAdolescentsDisclosure2013].

However, although the privacy calculus has gained some momentum several important questions remain unanswered. First, we still know comparatively little about whether the privacy calculus can be replicated with actual behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020]. However, all three of these approaches significantly hamper external validity.

Second, current research on the privacy calculus is often criticized for not explicitly focusing on the deliberation process of self-disclosure. According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that concerns and gratifications both correlate with self-disclosure is not evidence for any substantial or explicit weighing of pros and cons. We agree and consider it necessary to now explicitly focus on the privacy deliberation process itself. Moreover, and on a more general level, we aim to gauge the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-disclosure self-efficacy.

Finally, we want to determine whether the privacy calculus can be affected by the design of a website. Specifically, we analyze whether *popularity cues* such as like and dislike buttons affect self-disclosure and the privacy calculus.

To test our research questions, we conducted a preregistered online field experiment, drawing from a representative sample of the German population. Participants were randomly distributed to one of three different websites, which either featured only a like button, both a like and a dislike button, or no buttons at all. Over the course of one week participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany). Afterward, they answered our follow-up questionnaire with items pertaining to the privacy calculus variables.

## The Privacy Calculus

Being a primary means of regulating privacy [e.g., @masurSituationalPrivacySelfdisclosure2018], self-disclosure is our key variable of interest. There are two different understandings of self-disclosure in the literature: The first defines self-disclosure as _deliberate_ acts of sharing truthful information about the self with others [@jourardTransparentSelf1964]. The second considers _all_ acts of sharing information---whether active or passive, deliberate or unwitting---as self-disclosure, because each piece of information shared allows meaningful inferences to be made about a person [e.g., @watzlawickPragmaticsHumanCommunication2011]. In this paper we follow the latter approach, not least because recent years have vividly illustrated how it is possible to derive a plethora of insights about a person simply by analyzing his or her written communication [e.g., @kosinskiPrivateTraitsAttributes2013]. Moreover, independently from which position one chooses to adopt, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [e.g., @omarzuDisclosureDecisionModel2000]. In this study we mainly focus on communication quantity, as we consider communication quantity to be a necessary precondition and hence valid proxy for self-disclosure.

Privacy concerns have been defined as follows: "Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [AUTHOR]. Previous research has found that people who are more concerned about their privacy than others are less inclined to share personal information [e.g., @baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013].

H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.

Although privacy concerns are related to self-disclosure, one can make the case that since most studies in the literature report only small effects, there should also be additional meaningful factors that contribute to explaining self-disclosure. Most prominently, it has been argued that people trade a loss of privacy for a gain in gratifications such as social capital, entertainment, information, or self-presentation [@ellisonNegotiatingPrivacyConcerns2011; @taddickenUsesPrivacyOnline2011]. By now, a large body of research has found support for this hypothesis [e.g., @krasnovaOnlineSocialNetworks2010; @minHowArePeople2015; @trepteCrossculturalPerspectivePrivacy2017].

H2: People are more likely to self-disclose on a website when they obtain more gratifications from using the website.

In the current literature on the privacy calculus there still seems to be a shortage of studies that explicitly analyze the process of actively comparing the pros and cons of disclosing information, even though this point of criticism has been levelled several times [e.g., @knijnenburgDeathPrivacyCalculus2017] and even though other fields such as behavioral economics have long focused on the underlying problem [e.g., @zhuPrivacyCalculusIts2017]. The criticism is justified, because showing that experiencing privacy concerns and expecting gratifications are related to self-disclosure does not necessarily imply that an explicit weighing took place. Hence, we argue that research on the privacy calculus would benefit significantly from addressing a novel concept that might best be termed _privacy deliberation_, which we define as the extent to which individual people explicitly compare positive and negative potential outcomes before communicating with others.

On the one hand, it seems plausible to suggest that deliberating about one's privacy would dampen subsequent self-disclosure, because refraining from regular communication---the primary means of connecting with others---requires at least a minimum of active and hence deliberate restraint. On the other hand, deliberating about one's privacy might also increase self-disclosure, as after having actively deliberated about the potential consequences, a person concerned about his or her privacy might arrive at the conclusion that in this situation self-disclosure is not only appropriate but expedient. In light of the paucity of studies and the plausibility of both effects, we formulate the following research question:

RQ1: Are people more or less likely to self-disclose on a website when they more actively deliberate about whether they should self-disclose?

Several attempts have already been made to expand the privacy calculus [e.g., @dinevExtendedPrivacyCalculus2006]. Additional variables such as privacy self-efficacy or trust have been introduced. Building on @dienlinExtendedPrivacyCalculus2016, self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future that foster either self-withdrawal (e.g., deleting inappropriate content) or self-disclosure (e.g., publishing a blog post). Thus far, several studies have found that people who report more privacy self-efficacy also self-withdraw more online than others [e.g., @chenRevisitingPrivacyParadox2018].

Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: It either captures "specific beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p. 55] or a "general belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55]. @gefenTrustTAMOnline2003 prioritize specific trust beliefs (p. 60). In the online context, it is important to differentiate among several targets of trust [@sollnerWhyDifferentTrust2016]. For example, one can differentiate between (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. Trust plays a key role in online communication [e.g., @metzgerPrivacyTrustDisclosure2004]. For example, it has been demonstrated that people who put more trust in the providers of networks also disclose more personal information [see, e.g., @liEmpiricalStudiesOnline2011].

In conclusion, while we expect to find these relations as well, we would also like to determine whether the inclusion of all the other variables mentioned above, including the not yet researched concept of privacy deliberation, might potentially attenuate or even obviate the predictive capacity of self-efficacy and trust.

H3: People are more likely to self-disclose on a website when their self-efficacy about self-disclosing on the website is higher.

H4: People are more likely to self-disclose on a website when they have greater trust in the provider, the website, and the other users.

## The Effect of Popularity Cues

What is the effect of the communication context on the privacy calculus and on self-disclosure? First, it has often been noted that researchers should not exclusively focus on specific features of particular websites, for features are prone to change and quickly become obsolete [@foxDistinguishingTechnologiesSocial2017]. Instead, it has been suggested that researchers prioritize underlying latent structures, for example by analyzing what are know as affordances [e.g., @ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. The concept of affordances was developed by @gibsonEcologicalApproachVisual2015, who argued that it is not the objective features of objects that determine behavior but rather subjective perceptions. Affordances are a mental representation of how a given entity might be used; as such, they are by definition subjective. There is much debate in the literature concerning what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017]. For example, whereas @evansExplicatingAffordancesConceptual2017 propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), @foxDistinguishingTechnologiesSocial2017 suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).

As the privacy calculus states that both benefits and costs determine behavior, we suggest that popularity cues such as like and dislike buttons, which are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p. 142], perfectly epitomize benefits and costs. The like button is positive; it expresses an endorsement, a compliment, a reward [e.g., @sumnerFunctionalApproachFacebook2017]. However, communication online is also often characterized by negative and critical debates [e.g., @ziegeleDynamicsOnlineNews2017]. As the dislike button is a major means of downgrading content it represents the cost and risk factor of the privacy calculus well---in fact, its stark negative effect might also explain why only a handful of major websites have implemented a dislike button (e.g., reddit.com or stackexchange.com).

Popularity cues have been shown to impact behavior. For example, a large-scale field experiment in which 101,281 comments were analyzed found that comments with dislikes were more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. @stroudRecommendRespectAltering2017 demonstrated that when users had a different opinion than the one that was communicated in a post, they were more likely to click on a button labelled _respect_ compared to a button labelled _like_.

In this vein it seems plausible to suggest that popularity cues might also impact the privacy calculus. First, on a very primordial level, popularity cues should serve as a means of reward and punishment, as a mechanism of instrumental conditioning [@skinnerScienceHumanBehavior2014]. Specifically, we argue that being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit future disclosure. Similarly, like buttons should be associated with being able to garner positive feedback, so implementing a like-button---similar to a compliment in the offline world---might leverage gratifications. Implementing a like or a dislike button might also bring people to more actively deliberate about whether or not it is actually worthwhile to disclose information. If both like and dislike buttons are present, privacy deliberation should increase even further. Finally, because people who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017], implementation of the dislike button should both stir privacy concerns and stifle self-disclosure. For a simplified overview of our theoretical model, see Figure \@ref(fig:model).

H5.	Compared to people who use a website without like or dislike buttons, people who use a website with like buttons (a) self-disclose more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.

H6.	Compared to people who use a website without like or dislike buttons, people who use a website with like and dislike buttons (a) self-disclose more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.

H7.	Compared to people who use a website with only like buttons, people who use a website with like and dislike buttons (a) are more concerned about their privacy, and (b) deliberate more about whether they should communicate online.

```{r model, fig.cap="Overview of theoretical model.", fig.align='center', out.width=".8\\textwidth"}
knitr::include_graphics("../figures/design/model.pdf")
# knitr::include_graphics("figures/design/model.png")
```

# Methods
## Open Science

We preregistered the study's hypotheses, sample size, materials, analyses, and exclusion criteria (https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859 [^prereg]). We needed to change our pre-defined plan in some cases. For a full account of all changes, see online supplementary material (OSM), https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0. New analyses that were not preregistered appear in the section on exploratory analyses. For example, we also measured additional variables that were not included in the preregistration (e.g., specific gratifications and general trust; see below), whose results we report as exploratory analyses.

[^prereg]: To find the actual preregistration on the website, click _View Registration Form_ (blue button on the right hand side).

## Procedure

The study was designed as an online field experiment with three different groups. The first group interacted with a website without like/dislike buttons, the second with a website with only like buttons, and the third with a website with both like and dislike buttons. Participants were randomly distributed to one of the three websites in a between-subject design.

We collaborated with a professional panel agency to recruit participants. As an incentive, participants were awarded digital points, which they could use to get special offers from other companies. In order to be able to take part, participants needed to be above the age of 18 and had to live in Germany. In a first step, the agency sent their panel members an invitation to participate in the study (_invitation_). In this invitation, panel members were asked whether they would be interested in taking part in a study analyzing the threat posed by current terrorist attacks in Germany.[^1] If panel members decided to take part, they were subsequently sent the first questionnaire (_T1_) in which we asked about the participants’ sociodemographics, provided more details about the study, and included a registration link for the website. Afterward, the participants were randomly assigned to one of the three websites. After registration participants had the chance to discuss the topic of the terrorism threat in Germany over the course of one week (_field_). Afterward, participants received a follow-up questionnaire in which we collected the self-reported measures (_T2_). Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.

[^1]: Although the terror attack was not of primary interest for this study, the data can and will also be used to analyze perceptions of the terrorism threat. Hence, no deception took place, and in the debriefing participants were informed about our additional research interest in privacy.

We programmed an online website based on the open-source software discourse (https://www.discourse.org/). We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). Participants used the website actively: Overall, users spent `r sum(d$time_read/60) %>% round(digit = 0)` minutes online and wrote `r sum(d$post_count)` comments (for an example of communication that took place, see Figure \@ref(fig:comments)).

```{r website, fig.cap="The website's homepage. (Translated to English; university logos pixelated for peer review.)", fig.align='center', out.width=".9\\textwidth"}
knitr::include_graphics("../figures/website/website_translated.jpg")
```

```{r comments, fig.align='center', fig.cap="Communication that took place on the website with like and dislike buttons. (Translated to English.)", out.width=".9\\textwidth"}
knitr::include_graphics("../figures/website/comments_translated.png")
```

## Participants

We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. Thus, we defined an effect size that we would consider enough to support our hypotheses. Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be r = `r r_sesoi`. Our aim was to be able to detect this SESOI with a probability of at least 95%. Using the regular alpha level of 5%, this leads to a minimum sample size of _n_ = `r n_desired`. In the end, we were able to include n = `r n_final` in our analyses (see below). This means that our study had a probability (power) of `r power_achieved * 100`% of finding an effect at least as large as _r_ = `r r_sesoi`. Put differently, we were able to make reliable inferences about effects at least as big as _r_ = `r r_sensitive`.

We collected a representative sample of the German population in terms of age, sex, and federal state. T1 was completed by _N_ = `r n_t1` participants and T2 by _n_ = `r n_t2` participants. We connected the data from T1, participants' behavior on the platform, and T2 by means of objective and automated processes (e.g., participants were matched via tokens or IP addresses). So far, we have been able to match the data for _n_ = `r n_final` participants. The matching process is not yet finished, and we will try to match the remaining cases manually. We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less then three minutes, which we considered to be unreasonably fast. The sample characteristics at T1 were as follows: 
Age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
The characteristics of the final sample were as follows: 
Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m, 2)*100`%.
Hence, despite dropout, T2 can also be considered a largely representative sample of the German population.

## Measures

In what follows, we present the materials we used to measure our variables. To gauge the variables' factor validity, we ran confirmatory factor analyses (CFA). If the CFAs revealed insufficient fit, we deleted individual items. All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale. Answer options were as follows: -3 (_strongly disagree_), -2 (_disagree_), -1 (_slightly disagree_), 0 (_neutral_), +1 (_slightly agree_), +2 (_agree_), +3 (_strongly agree_). In the questionnaire, all items measuring a variable were presented on the same page in a randomized order.

For an overview of the means, standard deviations, factorial validity, and reliability, see Table \@ref(tab:CFA). For an overview of the variables' distributions, see Figure \@ref(fig:corrplot). For the exact wording of all items and their individual distributions, see the OSM.

```{r CFA, results = "asis"}
apa_table(select(factor_val_tab, -alpha), font_size = "footnotesize",
          caption = "Psychometric Properties, Factorial Validity, and Reliability of Measures",
          note = "omega = Raykov's composite reliability coefficient omega; avevar = average variance extracted.")
```

```{r corrplot, fig.cap="Above diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below diagonal: bivariate scatter plots for zero-order correlations. Solid regression lines represent linear regressions, dotted regression lines represent quadratic regressions. Calculated with the model predicted values for each variable (baseline model).", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
print(plot_fs_cor)
```

### Privacy concerns

Privacy concerns were measured with seven items based on @buchananDevelopmentMeasuresOnline2007 One example item was "When using the participation platform, I had concerns about my privacy". One item had to be deleted due to poor psychometric properties.

### Gratifications

Next, we differentiated between two separate types of gratification. _General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015 One example item was "Using the participation platform has paid off for me". _Specific gratifications_ were measured with 15 items on five different subdimensions with three items each. The scaled was loosely based on @schererGratifikationMinuteZeitnahe2002 Example items were: "Using the participation platform made it possible for me to" ... "learn things I would not otherwise have noticed" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).

### Self-disclosure self-efficacy

Self-disclosure self-efficacy was captured with six self-designed items, which captured whether participants felt that they had sufficient self-efficacy to write a comment on the platform. For example, we asked "I felt technically competent enough to write a comment." Two items, which were inverted, had to be deleted due to poor psychometric properties.

### Trust

Next, we differentiated between two separate types of trust. _General trust_ was operationalized based on @sollnerWhyDifferentTrust2016 for three targets (i.e., provider, website, and other users) with one item each. One example items was "The operators of the participation platform seemed trustworthy."
_Specific trust_ was operationalized for the same three targets with three subdimensions each (i.e., ability, benevolence/integrity, and reliability), which were measured with one item each. Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability). The results showed that the provider and website targets were not sufficiently distinctive, as was evidenced by the existence of a Heywood case. We hence adapted the scale to combine these two targets. The updated scale exhibited adequate fit.

### Privacy deliberation

Privacy deliberation was measured with 5 self-designed items. One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."

### Self-disclosure

Self-disclosure was calculated by taking the natural logarithm of the number of comments each participant posted.

## Data analysis

We tested all hypotheses and research questions using structural equation modeling (SEM). We tested the influence of the three websites using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework using latent variables [e.g., @klinePrinciplesPracticeStructural2016]. As the dependent variable (self-disclosure) was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. As recommended by @klinePrinciplesPracticeStructural2016, we report the following global fit indices: $\chi^2$, RMSEA (90% CI), CFI, and SRMR. As sociodemagraphic variables are often related to self-disclosure and other privacy-related variables [e.g., @dindiaSexDifferencesSelfdisclosure1992], we controlled all variables for the influence of sex and age. Preregistered hypotheses were tested with a one-sided significance level of 5%. Research questions and exploratory analyses were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction. We used `r r_citations` for all our analyses.

# Results

## Descriptive Analyses

```{r PriDel}
# calc participants who actively deliberated
pridel_active <- select(d, starts_with("PD01")) %>% 
  as.data.frame %>% 
  mutate(m = apply(., 1, mean, na.rm = T) %>% round(0)) %>% 
  select(m) %$% 
  nrow(filter(., m > 4)) / n_final * 100
```

First, we measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). The results did not reveal any relationships to be particularly curvilinear. Furthermore, all variables making up the privacy calculus demonstrated the expected relationships with self-disclosure. For example, people who were more concerned about their privacy had written fewer posts (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`). Worth noting is that specific gratifications and general trust predicted self-disclosure better than general gratifications and specific trust. The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. Altogether, `r pridel_active %>% round(0)`% of participants reported having actively deliberated about their privacy.

It is important to note that the bivariate results showed three very large correlations: First, between specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% round(2) %>% .[2, 1]`); second, between privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% round(2) %>% .[2, 1]`); third, between specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% round(2) %>% .[2, 1]`). As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.

## Privacy Calculus
### Preregistered analyses

First, we ran a model as specified in the preregistration. The model fit our data comparatively well, `r fit_txt(fit_prereg, scaled = TRUE)`. Regarding H1, we did not find that general gratifications predicted self-disclosure (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`). Regarding H2, neither did we find that privacy concerns predicted self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`). The analyses for RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`). With regard to H3, however, we found that experiencing self-efficacy substantially predicted self-disclosure (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`). Concerning H4, the results showed that trust was not associated with self-disclosure (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`).

However, these results should be treated with utmost caution. As mentioned above, we indeed detected problems suggesting multicollinearity. Most prominently, in this multiple regression trust had a negative relation with self-disclosure, even though when analyzed bivariately the relation was positive---which is a sign of multicollinearity [@klinePrinciplesPracticeStructural2016]. As a result, specific trust and general gratifications should not be analyzed within the same model, as the two concepts are empirically too close to one another.

### Exploratory analyses

Thus, we slightly adapted our preregistered model on the basis of the insights described above. First, instead of specific trust and general gratifications we now included general trust and specific gratifications (which were also correlated slightly less strongly with one another). The adapted model fit our data comparatively well, `r fit_txt(fit_adapted)`.

In the adapted privacy calculus model, we found two additional significant effects. For example, specific gratifications predicted self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`). Furthermore, in this model people who engaged in more privacy deliberation did not disclose less information (`r coeffs_txt(fit_adapted, "c1")`). However, note that the effect was only marginally not significant. Self-efficacy remained substantially correlated with self-disclosure (`r coeffs_txt(fit_adapted, "d1")`). We again found a negative correlation between trust and self-disclosure (`r coeffs_txt(fit_adapted, "e1")`), which, as a sign of multicollinearity, suggests that also general trust and specific gratifications should not be analyzed within the same model either.

Given that we observed several instances of multicollinearity, we also fitted a simple privacy calculus model containing only privacy concerns and specific gratifications. The simple model fit our data well, `r fit_txt(fit_simple)`. First, we found that people who experienced more privacy concerns than others also disclosed less information (`r coeffs_txt(fit_simple, "a1")`). Second, people who reported more specific gratifications than others also self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`). Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi`, implying that the effects were sufficiently large to qualify as support our the hypotheses. All effects labelled as significant were below their individual Bonferroni-Holm corrected significance level. For a visual overview of all results, see Figure \@ref(fig:plot-pc).

```{r plot-pc, fig.cap="Predictors of self-disclosure. Black lines indicate 90\\% CIs (for one-sided hypotheses), grey lines 95\\% CIs (for two-sided hypotheses). Displayed are unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=3}
print(plot_pc)
```

When comparing the three models with one another, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"]`, AIC = `r model_comp_tab["simple", "aic"]`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"]`, AIC = `r model_comp_tab["preregistered", "aic"]`) and the adapted model (BIC = `r model_comp_tab["adapted", "bic"]`, AIC = `r model_comp_tab["adapted", "aic"]`).

## Popularity Cues
### Preregistered analyses

Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables. For an illustration, see Figure \@ref(fig:popularitycues), which displays the model-predicted values for each variable (using the baseline model) and shows that the confidence intervals of all preregistered variables overlap. For the results of the specific inference tests using contrasts, see the OSM.

### Exploratory analyses

The picture remained mostly the same also when analyzing variables that we did not include in the preregistration. Note that some differences missed statistical significance only marginally (e.g., specific gratifications for the comparison between the website with like buttons and the control website without like and dislike buttons). Nevertheless, we refrain from reading too much into the differences between the three websites and conclude that they were mostly similar with regard to the privacy calculus variables and the amount of self-disclosure.

```{r popularitycues, fig.cap="Overview of the variables for the three websites. Control: Website without buttons. Like: Website with like buttons. Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
# knitr::include_graphics("figures/results/plot_pop.pdf")
print(plot_fs_m)
```

# Discussion

In this study, we analyzed theg e privacy calculus using actual observed behavior in a preregistered field experiment with data from a representative sample of the German population. We additionally sought to determine whether the privacy calculus is dependent on popularity cues such as like and dislike buttons. The data were analyzed using structural equation modeling. In the bivariate analyses, all privacy calculus variables were shown to significantly predict self-disclosure. In the preregistered analyses using multiple regression, in which several variables were analyzed together, self-efficacy turned out to be the strongest predictor of self-disclosure. However, this preregistered model exhibited significant problems with regard to multicollinearity, which is why we also computed a more basal privacy calculus model consisting of only privacy concerns and specific gratifications. In this model, both variables significantly and meaningfully predicted self-disclosure. Taken together, the results add further support to the privacy calculus framework, suggesting that self-disclosure online is not erratic (as for example posited by the privacy paradox, for example) but---at least somewhat---considered.

Our results suggest that in new communication contexts roughly one third of all Internet users actively deliberates about their privacy. Determining whether this figure is large or small is a normative question---for example, one can convincingly argue that this number sould be higher and that we as society should still more actively deliberate about our self-disclosure practices online. Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar---evidenced by their strong correlation with one another and their similar correlations with other variables. This either implies that thinking about one's privacy increases one's concern or, conversely, that being concerned about one's privacy leads one to think about one's options more actively. Future research might tell.

The next major implication is that popularity cues do not seem to have an overly strong influence on the privacy calculus and self-disclosure. Although some studies have found that popularity cues substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], our results suggest the opposite: Users still disclose the same amount of personal information regardless of whether a website includes like or dislike buttons, potentially highlighting the agency of users.

The results also have several more fine-grained implications. First, we question the tendency to further increase the complexity of the privacy calculus model by adding additional variables [e.g., @dienlinExtendedPrivacyCalculus2016]. "Since all models are wrong the scientist cannot obtain a "correct"it one by excessive elaboration. [...] Just as the ability to devise simple but evocative models is the signature of the great scientist so overelaboration and overparameterization is often the mark of mediocrity" [@boxScienceStatistics1976, p. 792]. Although adding variables can increase the amount of explained variance, it might also introduce spurious results due to multicollinearity---a problem that we think deserves more attention in general. Specifically, we have come to believe that adding self-efficacy to privacy calculus models is of limited value, for self-efficacy is mostly a proxy of behavior and does not offer much epistemic insight. Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to self-disclose whereas others do not.

<!-- Explaining self-disclosure online by means of a basal privacy calculus model instead has the charm of offering a more parsimonious model while still being capable of explaining a substantial part of self-disclosure online. -->

Furthermore, we found a remarkably strong correlation between trust and expected gratifications (i.e., _r_ = .77), which at first glance seemed somewhat peculiar to us. On closer inspection, however, we realized that the way trust is routinely operationalized in the literature is very close to expected gratifications. To illustrate, one subdimension explicitly measures _ability_ via items such as “The comments of other users were useful”. In fact, the literature often operationalizes trust as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016]. In conclusion, our results suggest that we should not confuse _causes_ of trust with _measures_ of trust, for this might introduce problems of both homogeneity and/or multicollinearity.

<!-- As suggested in literature (), we operationalized trust by measuring how much expertise, benevolence, and reliability participants associated with users, the website, and the providers. It seems that these three measures do not measure trust per se, but rather those aspects that cause trust. In other words, not trust but antecedents of trust. We hence recommend to use measures than focus on the actual psychological experience of trust.  -->

<!-- Finally, this study offers some implications on a meta-level. At a time when the social sciences are experiencing an excruciating replication crisis [e.g., @Camerer.2018; @Camerer.2016; @McEwan.2018], it has become increasingly important to further improve the way we go about doing science. In this preregistration, we have tried to implement several mechanisms proposed by @Munafo.2017. In doing so, we had the chance to learn several important aspects: For example, in the future we will be more hesitant to formulate concrete hypotheses when treading on novel ground. Moreover, instead of selling model adaptions as a priori rationales (a practice known as harking; i.e., hypothesizing after results are known), we reported them as additional analyses; we hope to have shown that this does not decrease a paper's value, but instead offers several interesting insights (e.g., that it might be expedient to formulate gratifications specifically rather than generally, or that gratifications and trust are highly correlated).  -->

## Limitations

The results do not allow for causal interpretation on the within-person level. First, all results are based on analyses of between-person variance. However, between-person relations often do not translate well to within-person effects [e.g. @hamakerCritiqueCrosslaggedPanel2015]. While some studies on privacy concerns online have begun to examine both sources of variance [e.g., @dietvorstAdolescentPerceptionsParental2017], finding that intrapersonal changes in privacy concerns are indeed related to intrapersonal changes in self-disclosure, similar analyses are still lacking for the privacy calculus. Second, the self-reported measures were collected _after_ the field phase in which the dependent variable was measured. As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior to reduce dissonance. Nevertheless, we deliberately decided to measure the self-reported variables afterward in order to not bias participants and not prime our specific research interest. Third, experiments should only manipulate the experimental variable while holding all others constant. In this study, we explicitly manipulated the popularity cues. However, as the experiment was conducted in the field, several other variables could not be held constant; for example, the content of communication by other users, the unfolding communication dynamics, or the characteristics of other users.

It is important to note that our not having found significant effects of like and dislike buttons does not necessarily mean that like and dislike buttons do indeed have no effect on self-disclosure and the privacy calculus. As always, with null-findings one is confronted with the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely--- states that null findings can either be due to the actual non-existence of effects or, instead, a poor operationalization of the research question. In this case, we were not able send participants notifications when their comments were liked/disliked, significantly decreasing the popularity cues' salience.

<!-- One can make the case that gratifications should not be measured as reflective constructs but rather as formative constructs. However, we have not been able to specify a formative model with adequate fit as of yet.  -->

This paper analyzes self-disclosure in the context of political participation. Our focus was on understanding self-disclosure, which is why we deliberately excluded variables pertaining to political participation, such as informational self-efficacy [@loyPsychologicalPredictorsPolitical2018]. Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.[^3] It is worth noting that we did not find any instances of people providing meaningless text and, as mentioned above, in times of big data, every piece of communication allows increasingly accurate inferences about one's personality to be made.

[^3]: Somewhat fittingly, in the German language there is a saying: 'He spoke a lot but didn't say a thing'.

Finally, there are several interesting research questions that one could address with the data. Most prominently, one could analyze the actual content of the posts to detect whether the three websites might have differed with regard to communication quality. In addition, one can make the case that privacy deliberation rather as a moderator---such that deliberating more actively about one's privacy strengthens the relation between privacy concerns or gratifications and self-disclosure. Upon publication, the data will be made publicly available and we invite researchers from all disciplines to investigate the aforementioned and other interesting research questions.

## Conclusion

While some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p. 1], in our opinion the privacy calculus is alive and kicking. This study adds to the growing confirmation of observation that people who are more concerned about their privacy than others disclose less information online, whereas people who receive more gratifications from using a website than others disclose more information online. The results of this study suggest that a substantial share of internet users, approximately 30%, consciously engage in a privacy calculus by actively deliberating about whether or not to disclose information. Popularity cues seem to play a minor role in this process, especially if no means are implemented to guarantee that users are notified about others liking or disliking their communication. In conclusion, our results indicate that internet users are at least somewhat proactive and reasonable---probably no more or less proactive or reasonable than in any other regular everyday situation.

\newpage

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

### 2020-04-07 analyses/analyses.Rmd
- major updates on theory, analyses, and osm

@@
 ---
-title: "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
-shorttitle : "Online Supplementary Material: Analyses"
+title: "How Do Like and Dislike Buttons Affect Communication?"
+shorttitle : "Analyses"
 output: 
   html_document:
-    self_contained: yes
-    mode: selfcontained
     toc: TRUE
@@
 # define packages
-packages <- c("cowplot", "devtools", "GGally", "knitr", "lavaan", "magrittr", 
-              "MVN", "psych", "pwr", "quanteda", "semTools", "tidyverse")
-
-# install packages
+packages <- c("cowplot", "devtools", "faoutlier", "GGally", "gganimate",
+              "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
+              "quanteda", "semTools", "tidyverse")
+
+# install packages # uncomment lines to install packages
 # devtools::install_github("tdienlin/td@v.0.0.2.3")
@@
 # load data
+# please note that in a prior step several different data sets were merged using information such as case_taken or IP-addresses.
+To guarantee the privacy of the participants, these data were deleted after merging.
 d_raw <- read_csv("data/data_raw.csv")
@@
     SE01_06 = 8 - SE01_06,
-    PL01 = recode(PL01, "2" = 1, .default = 0),
-    PL02 = recode(PL02, "3" = 1, .default = 0),
-    PL03 = recode(PL03, "4" = 1, .default = 0),
-    PL04 = recode(PL04, "2" = 1, .default = 0),
-    IF01_01 = recode(IF01_01, "1" = 1, .default = 0),
-    IF01_02 = recode(IF01_02, "1" = 1, .default = 0),
 
@@
 
-```{r defaults, include=F}
+```{r include=F}
+# sample descriptives t1
+n_t1 <- nrow(d)
+age_t1_m <- mean(d$age, na.rm = TRUE)
+male_t1_m <- mean(d$male, na.rm = TRUE)
+college_t1_m <- table(d$edu)[3] / n_t1
+
+# sample descriptives t2
+n_t2 <- filter(d, !is.na(id_survey_t2)) %>% nrow()
+age_t2_m <- filter(d, !is.na(id_survey_t2))$age %>% mean()
+male_t2_m <- filter(d, !is.na(id_survey_t2))$male %>% mean(na.rm = TRUE)
+college_t2_m <- filter(d, !is.na(id_survey_t2))$edu %>% table() %>% .[3] / n_t2
+
+# descriptives users
+n_users <- filter(d, !is.na(post_count)) %>% nrow()
+
+# characteristics of posts
+n_comments <- sum(d$post_count, na.rm = TRUE)
+n_words <- sum(d$words, na.rm = TRUE)
+n_time <- sum(d$time_read_MIN, na.rm = TRUE)
+n_posts <- sum(d$post_count, na.rm = TRUE)
+
+# filter unmatched cases
+d <- filter(d, !is.na(post_count) & !is.na(id_survey_t2))  # Use only completes
+n_matched <- nrow(d)
+
+# save data file with all participants to compare results
+d_all <- d
+
 # variable labels
@@
 
-```{r sample-descriptives, include=F}
-# sample descriptives t1
-n_t1 <- nrow(d)
-age_t1_m <- mean(d$age)
-male_t1_m <- mean(d$male, na.rm = TRUE)
-college_t1_m <- table(d$edu)[3] / n_t1
-
-# sample descriptives t2
-n_t2 <- filter(d, !is.na(id_survey_t2)) %>% nrow()
-age_t2_m <- filter(d, !is.na(id_survey_t2))$age %>% mean()
-male_t2_m <- filter(d, !is.na(id_survey_t2))$male %>% mean(na.rm = TRUE)
-college_t2_m <- filter(d, !is.na(id_survey_t2))$edu %>% table() %>% .[3] / n_t2
-
-# characteristics of posts
-n_comments <- sum(d$post_count, na.rm = TRUE)
-n_words <- sum(d$words_sum, na.rm = TRUE)
-n_time <- sum(d$time_read_MIN, na.rm = TRUE)
-n_posts <- sum(d$post_count, na.rm = TRUE)
-
-# speeding
+# Filter Participants
+
+```{r include=F}
+# filter speeders
 time_crit <- 3 # minimum time on survey
 n_speeding <- nrow(filter(d, time_sum_min_t2 < time_crit))
-
-# filter data
-d <- filter(d, time_sum_min_t2 > time_crit) # Deletion of fast respondents
-d <- filter(d, !is.na(username) & !is.na(id_survey_t2))  # Use only completes
+d <- filter(d, time_sum_min_t2 >= time_crit) # Deletion of fast respondents
+```
+
+We've also inspected the data manually for cases with clear response patterns. The following cases show extreme response patterns, fast response times, and were hence removed.
+
+```{r include=F}
+# identify response patterns
+resp_pattern <- c(
+  "ANIEVLK9F2SW", "BN4MAOWZO7W2"  # clear response pattern
+  )
+n_resp_pattern <- length(resp_pattern)
+# infl_cases_tokens <- infl_cases_tokens[!infl_cases_tokens %in% resp_pattern]
+
+d %>% 
+  filter(case_token %in% resp_pattern) %>% 
+  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
+  kable() %>% 
+  kable_styling("striped") %>% 
+  scroll_box(width = "100%")
+d %<>% filter(!case_token %in% resp_pattern)
 
@@
 male_final_m <- mean(d$male, na.rm = TRUE)
-college_final_m <- table(d$edu)[3] / n_final
+college_final_m <- table(d$edu)[[3]] / n_final
 ```
@@
 # Measures
-## Privacy Concerns
+## Privacy concerns
 ### Items
@@
 "
-fit <- sem(model = model, data = d, estimator = "MLM")
-```
-
-#### Model fit
+fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
+```
+
+Model fit:
 
@@
 
-#### Factor loadingss
+Factor loadings:
 
@@
 
-### CFA updated
+### CFA 2
 
@@
  2.	... has paid off for me.
- 3.	... was useful for me.
+ 3.	... was worthwhile.
  4.	... was fun.
@@
  13. ... to do the responsible persons a favor.
- 14. ... to soothe my bad consciences.
+ 14. ... to soothe my guilty consciences.
  15. ... to fulfil my civic duty.
@@
 
-## Privacy Deliberation
+## Privacy deliberation
 ### Items
@@
 
- 1. The other users seemed trustworthy.
- 5. The operators of the participation platform seemed trustworthy.
- 9. The website seemed trustworthy.
+&nbsp;&nbsp;&nbsp;1. The other users seemed trustworthy.  
+&nbsp;&nbsp;&nbsp;5. The operators of the participation platform seemed trustworthy.  
+&nbsp;&nbsp;&nbsp;9. The website seemed trustworthy.
 
@@
 "
-fit <- sem(model = model, data = d, estimator = "MLM")
-```
-
-#### Model fit
-
-```{r}
+fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
+```
+
+Model fit:
+
+```{r warning=T}
 (factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
@@
 
-## Self-Efficacy
+### CFA 2
+
+Because there was Heywoodcase, we now also run a model in which the subdimensions `provider` and `system` are combined.
+
+```{r}
+name <- "trust_spec"
+model <- "
+trust_community =~ TR01_02 + TR01_03 + TR01_04
+trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+trust =~ b*trust_community + b*trust_provider
+"
+fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
+```
+
+Model fit:
+
+```{r}
+(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
+assign(paste0(name, "_factor_val"), factor_val)
+```
+
+Factor loadings:
+
+```{r}
+inspect(fit,what="std")$lambda
+```
+Warning disappears, results show adequate fit.
+
+## Self-efficacy
 ### Items
@@
  1. In principle, I felt able to write a comment.
- 2. I have felt technically competent enough to write a comment.
- 3. Regarding content I have felt competent enough to express my opinion.
- 4. I found the subject too difficult to express my opinion.
+ 2. I felt technically competent enough to write a comment.
+ 3. In terms of the topic, I felt competent enough to express my opinion.
+ 4. I found it easy to express my opinion regarding the topic.
  5. I found it complicated to write a comment.
@@
 
-Shows significant misfit. We will run exploratory factor analyses to determine factorial structure.
-
-### EFA
-
-```{r}
-fa.parallel(select(d, SE01_01 : SE01_06))
-fa(r = select(d, SE01_01 : SE01_06), 
-   nfactors = 2, fm = "ml", rotate = "promax")
-```
-
-Implies latent structure with two factors.
-
-### CFA updated
+Shows significant misfit. We will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).
+
+### CFA 2
 
@@
 self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-self_eff_neg =~ SE01_05 + SE01_06
-self_eff =~ a*self_eff_pos + a*self_eff_neg
-"
-fit <- sem(model = model, data = d, estimator = "MLM")
-```
-
-#### Model fit
+SE01_01 ~~ x*SE01_02
+SE01_03 ~~ x*SE01_04
+"
+fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
+```
+
+Model fit:
 
@@
 
-## Self-Disclosure
-### Items
-
-Let us assume that the participation platform would continue to exist in the future. Please indicate to what extent you agree with the following statements:
-
-In the future, I am willing to ...
-
- 1. ... discuss political issues on the participation platform.
- 2. ... express my personal opinion on the participation platform.
- 3. ... write comments on the participation platform.
- 4. ... disclose concerns and fears on the participation platform.
- 5. ... share personal experience on the participation platform.
-
-### Distributions
-
-```{r}
-ggplot(gather(select(d, starts_with("WS01"))), 
-       mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=1) + 
-  theme_bw()
-
-des_futuse <- select(d, starts_with("WS01")) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
-
-### CFA
-
-```{r}
-name <- "futuse"
-model <- "
-fut_use =~ WS01_01 + WS01_02 + WS01_03 + WS01_04 + WS01_05
-"
-sem(model = model, data = d)
-fit <- sem(model = model, data = d, estimator = "MLM")
-```
-
-#### Model fit
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-#### Factor loadingss
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-## Baseline Model
+## Baseline model
 
@@
 ```{r}
-model <- "
+model_baseline <- "
   pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
@@
   trust_community =~ TR01_02 + TR01_03 + TR01_04
-  trust_provider =~ TR01_06 + TR01_07 + TR01_08
-  trust_system =~ TR01_10 + TR01_11 + TR01_12
-  trust_spec =~ trust_community + trust_provider + trust_system
-  self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  self_eff_neg =~ SE01_05 + SE01_06
-  self_eff =~ a*self_eff_pos + a*self_eff_neg
+  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+  trust_spec =~ trust_community + trust_provider
+  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+    SE01_01 ~~ x*SE01_02
+    SE01_03 ~~ x*SE01_04
   self_dis_lg =~ self_dis_log
-"
-fit_baseline <- sem(model, data = d, missing = "ML")
+
+  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
+"
+fit_baseline <- sem(model_baseline, data = d, missing = "ML")
 summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
-
+```
+
+# Descriptive analyses
+
+We first report the factor validity of all variables combined.
+
+```{r}
 # extract model predicted values for items & calc means
@@
   as.data.frame() %>% 
-  mutate(grats_gen = rowMeans(select(., starts_with("GR02")))) %>% 
-  mutate(grats_spec = rowMeans(select(., starts_with("GR01")))) %>% 
-  mutate(pricon = rowMeans(select(., starts_with("PC01")))) %>% 
-  mutate(trust_gen = rowMeans(select(., TR01_01, TR01_05, TR01_09))) %>%
-  mutate(trust_spec = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12))) %>% 
-  mutate(pridel = rowMeans(select(., starts_with("PD01")))) %>% 
-  mutate(selfeff = rowMeans(select(., starts_with("SE01")))) %>%
-  select(pricon, grats_gen, grats_spec, pridel, selfeff, trust_gen, trust_spec, self_dis_log) %>% 
-  set_names(var_names_breaks) %>% 
-  mutate(version = d$version)
-```
-
-# Descriptive analyses
-
-We first report the factor validity of all variables combined.
-
-```{r}
+  mutate(version = d$version, 
+         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
+         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
+         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
+         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
+         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
+         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
+         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
+  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)
+
+# combine d with d factor scores
+d %<>% cbind(select(d_fs, -version, -self_dis_log))
+
+# rename for plotting
+d_fs %<>% set_names(c("version", var_names_breaks))
+
 # means of model predicted values
@@
              des_trust_gen,
-             des_trust_spec,
-             des_futuse)
+             des_trust_spec)
 
@@
   print()
-# factor_val_tab %>% kable(digits = 2)
 ```
@@
 ```{r zds, fig.height=8, fig.width=8}
-plot_fs_cor <- ggpairs(
+fig_fs_cor <- ggpairs(
   select(d_fs, -version),
   upper = list(continuous = "cor"),
-  lower = list(continuous = scat_plot)) +
+  lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) +
   theme_bw()
-print(plot_fs_cor)
+print(fig_fs_cor)
 ```
@@
 
-# Results
-## Privacy calculus
-### Preregistered
-#### Model "Peregistered"
-
-We first test for multivariate normal distribution.
+# Assumptions
+## Multivariate normal distribution
 
@@
 
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 # + PC01_03 
+## Influential cases
+
+In what follows we test for influential cases in baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.
+
+```{r}
+cooks_dis <- gCD(d, model_baseline)
+plot(cooks_dis)
+```
+
+The following ten cases have a particularly strong influence on the baseline model.
+
+```{r}
+infl_cases <- invisible(rownames(print(cooks_dis)))
+```
+
+Let's inspect these cases.
+
+```{r}
+infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
+d %>% 
+  filter(case_token %in% infl_cases_tokens) %>% 
+  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
+  kable() %>% 
+  kable_styling("striped") %>% 
+  scroll_box(width = "100%")
+```
+
+These data do not reveal potential cases of response patterns. Indeed, answer times suggest that respondents were diligent.
+
+# Results
+## Privacy calculus
+### Model "Peregistered"
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
 grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
@@
 self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
 trust_community =~ TR01_02 + TR01_03 + TR01_04
@@
 "
-fit_prereg <- sem(model, data = d, estimator = "MLM")
+fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
 summary(fit_prereg, fit = TRUE, std = TRUE)
-fit_tab(fit_prereg, scaled = TRUE)
-
-d_coeffs_prereg <- coeffs_tab(fit_prereg, c("a1", "b1", "c1", "d1", "e1")) %>% 
-  mutate(Outcome = rep("Preregistered\nmodel", 5)) %>%  
-  mutate(Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific")) %>% 
-  mutate_at(vars(Predictor), funs(factor(., c("Trust\nspecific", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\ngeneral", "Privacy\nconcern"))))
-
-plot_coeffs_prereg <- ggplot(d_coeffs_prereg, aes(x = b, y = Predictor)) + 
-  theme_bw() +
-  theme(axis.title.x=element_blank()) + 
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_errorbarh(aes(xmin = ll, xmax = ul), 
-                lwd = .75, colour = "grey", height = .2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul),
-                lwd = .75, colour = "black", height = .2) +
-  geom_point(size = 2) +
-  guides(color = FALSE, shape = FALSE) + 
-  facet_grid(~ Outcome) +
-  theme(axis.title.y = element_blank()) +
-  theme(plot.title = element_text(hjust = .5)) + 
-  theme(panel.spacing = unit(.9, "lines")) + 
-  theme(text = element_text(size = 12))
-```
-
-### Exploratory
-#### Model "adapted"
-
-We now use specific gratifications and general trust.
+rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
+```
+
+### Model "Adapted"
+
+Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.
 
@@
 self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
 trust_gen =~ TR01_01 + TR01_05 + TR01_09
@@
 "
-fit_adapted <- sem(model, data = d, estimator = "MLM")
+fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
 summary(fit_adapted, fit = TRUE, std = TRUE)
-fit_tab(fit_adapted, scaled = TRUE)
-
-d_coeffs_adapted <- coeffs_tab(fit_adapted, c("a1", "b1", "c1", "d1", "e1")) %>% 
-  mutate(Outcome = rep("Adapted\nmodel", 5)) %>%  
-  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific", "Privacy\ndelib.", "Self-\nefficacy", "Trust\ngeneral")) %>% 
-  mutate_at(vars(Predictor), funs(factor(., c("Trust\ngeneral", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\nspecific", "Privacy\nconcern"))))
-
-plot_coeffs_adapted <- ggplot(d_coeffs_adapted, aes(x = b, y = Predictor)) + 
-  theme_bw() +
-  theme(axis.title.x=element_blank()) + 
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_errorbarh(aes(xmin = ll, xmax = ul), 
-                lwd = .75, colour = "grey", height = .2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul),
-                lwd = .75, colour = "black", height = .2) +
-  geom_point(size = 2) +
-  guides(color = FALSE, shape = FALSE) + 
-  facet_grid(~ Outcome) +
-  theme(axis.title.y = element_blank()) +
-  theme(plot.title = element_text(hjust = .5)) + 
-  theme(panel.spacing = unit(.9, "lines")) + 
-  theme(text = element_text(size = 12))
-```
-
-#### Model "simple"
+```
+
+### Model "Simple"
 
@@
 "
-fit_simple <- sem(model, data = d, estimator = "MLM")
+fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
 summary(fit_simple, fit = TRUE, std = TRUE)
-fit_tab(fit_simple, scaled = TRUE)
-
-d_coeffs_simple <- coeffs_tab(fit_simple, c("a1", "b1")) %>% 
-  mutate(Outcome = rep("Simple\nmodel", 2)) %>%  
-  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific")) %>% 
-  mutate_at(vars(Predictor), funs(factor(., c("Grats.\nspecific", "Privacy\nconcern"))))
-
-plot_coeffs_simple <- ggplot(d_coeffs_simple, aes(x = b, y = Predictor)) + 
-  theme_bw() +
-  theme(axis.title.x=element_blank()) + 
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_errorbarh(aes(xmin = ll, xmax = ul), 
-                lwd = .75, colour = "grey", height = .2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul),
-                lwd = .75, colour = "black", height = .2) +
-  geom_point(size = 2) +
-  guides(color = FALSE, shape = FALSE) + 
-  facet_grid(~ Outcome) +
-  theme(axis.title.y = element_blank()) +
-  theme(plot.title = element_text(hjust = .5)) + 
-  theme(panel.spacing = unit(.9, "lines")) + 
-  theme(text = element_text(size = 12))
-```
-
-### Model Comparison
-
-```{r}
-plot_pc <- plot_grid(plot_coeffs_prereg, 
-                     plot_coeffs_adapted, 
-                     plot_coeffs_simple, 
-                     nrow = 1)
-```
+rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
+```
+
+### Comparison
 
@@
 
+### Visualization
+
+```{r}
+# extract coeffs
+d_coeffs_baseline <- coeffs_tab(fit_baseline, c("a1", "b1", "c1", "d1", "e1", "f1", "g1")) %>% 
+  mutate(Model = rep("Bivariate\nrelations", 7),
+         Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific", "Trust\ngeneral", "Grats.\nspecific"))
+
+d_coeffs_prereg <- coeffs_tab(fit_prereg, c("a1", "b1", "c1", "d1", "e1")) %>% 
+  mutate(Model = rep("Preregistered\nmodel", 5),
+         Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific"))
+
+d_coeffs_adapted <- coeffs_tab(fit_adapted, c("a1", "b1", "c1", "d1", "e1")) %>% 
+  mutate(Model = rep("Adapted\nmodel", 5),
+         Predictor = c("Privacy\nconcern", "Grats.\nspecific", "Privacy\ndelib.", "Self-\nefficacy", "Trust\ngeneral"))
+
+d_coeffs_simple <- coeffs_tab(fit_simple, c("a1", "b1")) %>% 
+  mutate(Model = rep("Simple\nmodel", 2),
+         Predictor = c("Privacy\nconcern", "Grats.\nspecific"))
+
+d_coeffs <- rbind(d_coeffs_baseline, d_coeffs_prereg, d_coeffs_adapted, d_coeffs_simple) %>% 
+  mutate(Predictor = factor(Predictor, c("Trust\ngeneral", "Trust\nspecific", "Self-\nefficacy", "Privacy\ndelib.", "Privacy\nconcern", "Grats.\nspecific", "Grats.\ngeneral")),
+         Model = factor(Model, c("Bivariate\nrelations", "Preregistered\nmodel", "Adapted\nmodel", "Simple\nmodel"))
+  )
+
+# plot coeffs
+fig_coeffs <- ggplot(d_coeffs, aes(x = b, y = Predictor)) + 
+  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
+  geom_point(size = 2) +
+  geom_errorbarh(aes(xmin = ll, xmax = ul), 
+                lwd = .75, colour = "grey", height = .2) +
+  geom_errorbarh(aes(xmin = ll, xmax = ul),
+                lwd = .75, colour = "black", height = .2) +
+  facet_grid(~ Model) +
+  guides(color = FALSE, shape = FALSE) + 
+  theme_bw() +
+  theme(axis.title.x=element_blank(),
+        axis.title.y = element_blank(),
+        plot.title = element_text(hjust = .5),
+        panel.spacing = unit(.9, "lines"),
+        text = element_text(size = 12)) +
+  coord_cartesian(xlim = c(-1.5, 1.5))
+
+fig_coeffs
+```
+
 ## Effects of popularity cues
@@
 ```{r}
-plot_fs_m <- ggplot(
+fig_fs_m <- ggplot(
   gather(d_fs, variable, value, -version) %>% 
@@
   scale_fill_brewer(palette="Greys")
-plot_fs_m
+fig_fs_m
 ```
@@
 "
-fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
+fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
 summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
@@
 
-#### Like & Dislike vs. Control
+Model did not converge. It's likely too complex given the reduced number of participants. The trust subdimension "provider" seems to cause trouble. Will hence be substituted with factor score.
 
@@
 self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_spec =~ trust_spec_fs
+
+pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
+self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
 
 # Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
-summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
+self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
+summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
+```
+
+#### Like & Dislike vs. Control
 
@@
 
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
+pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
+self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
 
@@
 "
-
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
-summary(fit_likdis_lik, fit = TRUE, std = TRUE)
-```
-
-### Exploratory
-#### Like vs. control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con ~ a1*lik_ctrl
-grats_spec ~ a2*lik_ctrl
-self_dis_log ~ b1*pri_con + b2*grats_spec + c1*lik_ctrl
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_lik_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
-summary(fit_lik_ctrl_simple, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con + grats_spec ~ likdis_ctrl
-self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_ctrl
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_likdis_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
-summary(fit_likdis_ctrl_simple, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con + grats_spec ~ likdis_lik
-self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_lik
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
-summary(fit_likdis_lik, std = TRUE, fit = TRUE)
-```
-
-# Results without Covariates
-
-As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain the same.
-
-## Privacy calculus
-### Preregistered
-#### Model "Peregistered"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 # + PC01_03 
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
-"
-fit_nocovs_prereg <- sem(model, data = d, estimator = "MLM")
-summary(fit_nocovs_prereg, fit = TRUE, std = TRUE)
-fit_tab(fit_nocovs_prereg)
-
-d_coeffs_prereg <- coeffs_tab(fit_nocovs_prereg, c("a1", "b1", "c1", "d1", "e1")) %>% 
-  mutate(Outcome = rep("Preregistered\nmodel", 5)) %>%  
-  mutate(Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific")) %>% 
-  mutate_at(vars(Predictor), funs(factor(., c("Trust\nspecific", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\ngeneral", "Privacy\nconcern"))))
-
-plot_coeffs_prereg <- ggplot(d_coeffs_prereg, aes(x = b, y = Predictor)) + 
-  theme_bw() +
-  theme(axis.title.x=element_blank()) + 
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_errorbarh(aes(xmin = ll, xmax = ul), 
-                lwd = .75, colour = "grey", height = .2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul),
-                lwd = .75, colour = "black", height = .2) +
-  geom_point(size = 2) +
-  guides(color = FALSE, shape = FALSE) + 
-  facet_grid(~ Outcome) +
-  theme(axis.title.y = element_blank()) +
-  theme(plot.title = element_text(hjust = .5)) + 
-  theme(panel.spacing = unit(.9, "lines")) + 
-  theme(text = element_text(size = 12))
-```
-
-### Exploratory
-#### Model "better"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-trust_gen =~ TR01_01 + TR01_05 + TR01_09
-
-self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
-"
-fit_nocovs_adapted <- sem(model, data = d, estimator = "MLM")
-summary(fit_nocovs_adapted, fit = TRUE, std = TRUE)
-fit_tab(fit_nocovs_adapted)
-
-d_coeffs_adapted <- coeffs_tab(fit_nocovs_adapted, c("a1", "b1", "c1", "d1", "e1")) %>% 
-  mutate(Outcome = rep("Adapted\nmodel", 5)) %>%  
-  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific", "Privacy\ndelib.", "Self-\nefficacy", "Trust\ngeneral")) %>% 
-  mutate_at(vars(Predictor), funs(factor(., c("Trust\ngeneral", "Self-\nefficacy", "Privacy\ndelib.", "Grats.\nspecific", "Privacy\nconcern"))))
-
-plot_coeffs_adapted <- ggplot(d_coeffs_adapted, aes(x = b, y = Predictor)) + 
-  theme_bw() +
-  theme(axis.title.x=element_blank()) + 
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_errorbarh(aes(xmin = ll, xmax = ul), 
-                lwd = .75, colour = "grey", height = .2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul),
-                lwd = .75, colour = "black", height = .2) +
-  geom_point(size = 2) +
-  guides(color = FALSE, shape = FALSE) + 
-  facet_grid(~ Outcome) +
-  theme(axis.title.y = element_blank()) +
-  theme(plot.title = element_text(hjust = .5)) + 
-  theme(panel.spacing = unit(.9, "lines")) + 
-  theme(text = element_text(size = 12))
-```
-
-#### Model "simple"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-self_dis_log ~ a1*pri_con + b1*grats_spec
-"
-fit_nocovs_simple <- sem(model, data = d, estimator = "MLM")
-summary(fit_nocovs_simple, fit = TRUE, std = TRUE)
-fit_tab(fit_nocovs_simple)
-
-d_coeffs_simple <- coeffs_tab(fit_nocovs_simple, c("a1", "b1")) %>% 
-  mutate(Outcome = rep("Simple\nmodel", 2)) %>%  
-  mutate(Predictor = c("Privacy\nconcern", "Grats.\nspecific")) %>% 
-  mutate_at(vars(Predictor), funs(factor(., c("Grats.\nspecific", "Privacy\nconcern"))))
-
-plot_coeffs_simple <- ggplot(d_coeffs_simple, aes(x = b, y = Predictor)) + 
-  theme_bw() +
-  theme(axis.title.x=element_blank()) + 
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_errorbarh(aes(xmin = ll, xmax = ul), 
-                lwd = .75, colour = "grey", height = .2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul),
-                lwd = .75, colour = "black", height = .2) +
-  geom_point(size = 2) +
-  guides(color = FALSE, shape = FALSE) + 
-  facet_grid(~ Outcome) +
-  theme(axis.title.y = element_blank()) +
-  theme(plot.title = element_text(hjust = .5)) + 
-  theme(panel.spacing = unit(.9, "lines")) + 
-  theme(text = element_text(size = 12))
-```
-
-## Effects of popularity cues
-### Preregisterd
-#### Like vs. Control
+fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
+summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
+```
+
+Again, does not converge; will use `Trust Specific` as factor score.
 
@@
 self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
-"
-fit_nocovs_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
-summary(fit_nocovs_lik_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Control
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_spec =~ trust_spec_fs
+
+pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
+self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
+
+# Covariates
+self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
+summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
+```
+
+#### Like & Dislike vs. Like
 
@@
 
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
-"
-fit_nocovs_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
-summary(fit_nocovs_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
 pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
 self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
-"
-
-fit_nocovs_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
-summary(fit_nocovs_likdis_lik, fit = TRUE, std = TRUE)
-```
-
-### Exploratory
-#### Like vs. control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con ~ a1*lik_ctrl
-grats_spec ~ a2*lik_ctrl
-self_dis_log ~ b1*pri_con + b2*grats_spec + c1*lik_ctrl
-"
-fit_nocovs_lik_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLM")
-summary(fit_nocovs_lik_ctrl_simple, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con + grats_spec ~ likdis_ctrl
-self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_ctrl
-"
-fit_nocovs_likdis_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLM")
-summary(fit_nocovs_likdis_ctrl_simple, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con + grats_spec ~ likdis_lik
-self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_lik
-"
-fit_nocovs_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLM")
-summary(fit_nocovs_likdis_lik, std = TRUE, fit = TRUE)
-```
-
-```{r remove-large-objects, include=F}
-obj_keep <- c("d", "d_fs", 
-              "fit_baseline", "fit_adapted", "fit_prereg", "fit_simple",
-              "plot_fs_m", "plot_fs_cor", "plot_pc",
-              "des_pridel",
-              "model_comp_tab", "factor_val_tab",
-              "n_comments", "n_desired", "n_posts", "n_speeding", "n_time", "n_words",
-              "n_comments", "n_words", "n_time", "n_posts", "n_speeding",
-              "n_t1", "age_t1_m", "male_t1_m", "college_t1_m",
-              "n_t2", "age_t2_m", "male_t2_m", "college_t2_m",
-              "n_final", "age_final_m", "male_final_m", "college_final_m",
-              "r_sesoi", "r_sensitive", "power_achieved")
-# rm(list=setdiff(ls(), obj_keep))
-```
-
-```{r SaveData, include = FALSE, cache=F}
+
+# Covariates
+self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+
+fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
+summary(fit_likdis_lik, fit = TRUE, std = TRUE)
+```
+
+This time, does converge, no need to change model.
+
+```{r SaveData, include=F, cache=F}
 write.csv(d, file = "data/data.csv", row.names = FALSE)
-save(d, d_fs,
-     fit_baseline,
-     fit_adapted, 
-     fit_prereg,
-     fit_simple,
-     plot_fs_m, plot_fs_cor, plot_pc,
+save(d, d_raw, d_all, d_fs,
+     fit_baseline, fit_prereg, fit_adapted, fit_simple,
+     fig_fs_m, fig_fs_cor, fig_coeffs,
      des_pridel,
@@
      n_comments, n_words, n_time, n_posts, n_speeding,
+     n_users, n_final,
+     infl_cases, infl_cases_tokens, resp_pattern, n_resp_pattern,
      n_t1, age_t1_m, male_t1_m, college_t1_m,
      n_t2, age_t2_m, male_t2_m, college_t2_m,
-     n_final, age_final_m, male_final_m, college_final_m,
+     n_matched, n_final, age_final_m, male_final_m, college_final_m,
      r_sesoi, r_sensitive, power_achieved,

### 2020-04-07 manuscript/manuscript.RmD
- major updates on theory, analyses, and osm

@@
 abstract: |
-    Äccording to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
-So far, little is known about whether the privacy calculus can be used to predict observations of actual authentic behavior, and whether the privacy calculus can be influenced by the design of online websites---for example, by implementing popularity cues such as like and dislike buttons.
-To answer this question, we ran a preregistered one-week field experiment, in which participants were randomly distributed to three different websites where they could discuss a current political topic.
-First, the results showed that privacy calculus variables predicted a considerable share of actual self-disclosure.
-Second, we found that the impact of implementing popularity cues was negligible.
-In conclusion, the results demonstrate that self-disclosure online can be explained by, for example, privacy concerns and psychological gratifications.
-This finding has several implications---for example, it provides further evidence against the privacy paradox.
+    According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
+So far, most findings are based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual authentic behavior.
+Likewise, we still know comparatively little whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
+To answer these questions, we ran a preregistered one-week field experiment.
+Participants were randomly distributed to three different websites where they could discuss a current political topic.
+The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
+The results showed that privacy calculus variables predicted a considerable share of actual self-disclosure.
+The impact of popularity cues was negligible.
+In conclusion, the results demonstrate that self-disclosure online can be explained by privacy concerns and specific gratifications.
+This finding has several implications.
+For example, it provides further evidence against the privacy paradox.
 keywords          : "privacy calculus, self-disclosure, popularity cues, structural equation modeling, preregistration"
@@
 ```{r include=F}
-# knitr::opts_knit$set(root.dir = "../")
 knitr::opts_chunk$set(cache=F)
@@
                       )
-load("../data/workspace.RData")
+```
+
+```{r load-data, cache=T, include=F}
+load("../data/workspace.rData")
 ```
@@
 The privacy calculus builds on the work of @lauferPrivacyConceptSocial1977 and claims that both expected risks *and* expected benefits explain self-disclosure.
-Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information [e.g., @heirmanPredictingAdolescentsDisclosure2013].
+Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information [@heirmanPredictingAdolescentsDisclosure2013; koohikamaliInvestigationDynamicModel2019].
 
@@
 According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that concerns and gratifications both correlate with self-disclosure is not evidence for any substantial or explicit weighing of pros and cons.
+
 We agree and consider it necessary to now explicitly focus on the privacy deliberation process itself. 
@@
 To test our research questions, we conducted a preregistered online field experiment, drawing from a representative sample of the German population.
-Participants were randomly distributed to one of three different websites, which either featured only a like button, both a like and a dislike button, or no buttons at all.
+Participants were randomly distributed to one of three different websites, which either included only a like button, both a like and a dislike button, or no buttons at all.
 Over the course of one week participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany).
@@
 In this paper we follow the latter approach, not least because recent years have vividly illustrated how it is possible to derive a plethora of insights about a person simply by analyzing his or her written communication [e.g., @kosinskiPrivateTraitsAttributes2013].
-Moreover, independently from which position one chooses to adopt, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [e.g., @omarzuDisclosureDecisionModel2000].
+Moreover, independent from which position one chooses to adopt, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [e.g., @omarzuDisclosureDecisionModel2000].
 In this study we mainly focus on communication quantity, as we consider communication quantity to be a necessary precondition and hence valid proxy for self-disclosure.
 
-Privacy concerns have been defined as follows: "Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [AUTHOR].
-Previous research has found that people who are more concerned about their privacy than others are less inclined to share personal information [e.g., @baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013].
+Privacy concerns have been defined as follows: 
+"Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [AUTHOR].
+Previous research has found that people who are more concerned about their privacy than others are less inclined to share personal information [@baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
@@
 
-In the current literature on the privacy calculus there still seems to be a shortage of studies that explicitly analyze the process of actively comparing the pros and cons of disclosing information, even though this point of criticism has been levelled several times [e.g., @knijnenburgDeathPrivacyCalculus2017] and even though other fields such as behavioral economics have long focused on the underlying problem [e.g., @zhuPrivacyCalculusIts2017].
-The criticism is justified, because showing that experiencing privacy concerns and expecting gratifications are related to self-disclosure does not necessarily imply that an explicit weighing took place.
-Hence, we argue that research on the privacy calculus would benefit significantly from addressing a novel concept that might best be termed _privacy deliberation_, which we define as the extent to which individual people explicitly compare positive and negative potential outcomes before communicating with others.
+In the current literature on the privacy calculus there still seems to be a shortage of studies that explicitly analyze the decision process of actively comparing the pros and cons of disclosing information, although this point of criticism has been leveled several times [e.g., @knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [e.g., @zhuPrivacyCalculusIts2017].
+This criticism is justified.
+The observation that both experiencing privacy concerns and expecting gratifications are related to self-disclosure does not bit itself necessitate an explicit weighing process 
+Hence, we argue that the research on the privacy calculus would benefit significantly from analyzing this decision process explicitly. 
+Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which we define as the extent to which individual people explicitly compare positive and negative potential outcomes before communicating with others.
 
-On the one hand, it seems plausible to suggest that deliberating about one's privacy would dampen subsequent self-disclosure, because refraining from regular communication---the primary means of connecting with others---requires at least a minimum of active and hence deliberate restraint.
+On the one hand, it seems plausible that deliberating about one's privacy would dampen subsequent self-disclosure, because refraining from regular communication---the primary means of connecting with others---requires at least a minimum of active and hence deliberate restraint.
 On the other hand, deliberating about one's privacy might also increase self-disclosure, as after having actively deliberated about the potential consequences, a person concerned about his or her privacy might arrive at the conclusion that in this situation self-disclosure is not only appropriate but expedient.
-In light of the paucity of studies and the plausibility of both effects, we formulate the following research question:
+In light of the paucity of empirical studies and the plausibility of both effects, we formulate the following research question:
 
@@
 Several attempts have already been made to expand the privacy calculus [e.g., @dinevExtendedPrivacyCalculus2006]. 
-Additional variables such as privacy self-efficacy or trust have been introduced.
-Building on @dienlinExtendedPrivacyCalculus2016, self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future that foster either self-withdrawal (e.g., deleting inappropriate content) or self-disclosure (e.g., publishing a blog post).
+Additional variables such as self-efficacy or trust have been introduced. 
+Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
+These privacy behaviors can either refer to self-withdrawal (e.g., deleting inappropriate content) or self-disclosure (e.g., publishing a blog post).
 Thus far, several studies have found that people who report more privacy self-efficacy also self-withdraw more online than others [e.g., @chenRevisitingPrivacyParadox2018].
+In light of our focus on self-disclosure, in this study we investigate the influence of self-disclosure self-efficacy.
 
-Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: It either captures "specific beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
-55] or a "general belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55].
-@gefenTrustTAMOnline2003 prioritize specific trust beliefs (p.
-60).
+Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
+55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added].
+Whereas specific trust beliefs focus on the causes of trust, general trust beliefs focus on the experience of trust.
+@gefenTrustTAMOnline2003 prioritize specific trust beliefs (p. 60). 
 In the online context, it is important to differentiate among several targets of trust [@sollnerWhyDifferentTrust2016]. 
-For example, one can differentiate between (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016].
-Trust plays a key role in online communication [e.g., @metzgerPrivacyTrustDisclosure2004].
-For example, it has been demonstrated that people who put more trust in the providers of networks also disclose more personal information [see, e.g., @liEmpiricalStudiesOnline2011].
+Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
+Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
+For example, it has been demonstrated that people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].
 
@@
 142], perfectly epitomize benefits and costs.
-The like button is positive; it expresses an endorsement, a compliment, a reward [e.g., @sumnerFunctionalApproachFacebook2017].
-However, communication online is also often characterized by negative and critical debates [e.g., @ziegeleDynamicsOnlineNews2017].
-As the dislike button is a major means of downgrading content it represents the cost and risk factor of the privacy calculus well---in fact, its stark negative effect might also explain why only a handful of major websites have implemented a dislike button (e.g., reddit.com or stackexchange.com).
+The like button is positive; it expresses an endorsement, a compliment, a reward [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017]. 
+However, communication online is also often characterized by negative and critical debates [@ziegeleDynamicsOnlineNews2017]. 
+As the dislike button is a major means of downgrading content it represents the cost and risk factor of the privacy calculus well. 
+In fact, its stark negative effect might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit or stackexchange).
 
-Popularity cues have been shown to impact behavior.
+Paralinguistic digital affordances and/or popularity cues have been shown to impact behavior [@kramerMasteringChallengeBalancing2020; @treptePrivacyCalculusContextualized2020].
 For example, a large-scale field experiment in which 101,281 comments were analyzed found that comments with dislikes were more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
@@
 
-In this vein it seems plausible to suggest that popularity cues might also impact the privacy calculus.
-First, on a very primordial level, popularity cues should serve as a means of reward and punishment, as a mechanism of instrumental conditioning [@skinnerScienceHumanBehavior2014].
-Specifically, we argue that being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit future disclosure.
+In this vein it seems plausible that popularity cues might also impact the privacy calculus [kramerMasteringChallengeBalancing2020].
+First, on a primordial level, popularity cues serve as a means of reward and punishment, affecting behavior via instrumental conditioning [@skinnerScienceHumanBehavior2014]. 
+Specifically, being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit future disclosure. 
 Similarly, like buttons should be associated with being able to garner positive feedback, so implementing a like-button---similar to a compliment in the offline world---might leverage gratifications.
@@
 
-We preregistered the study's hypotheses, sample size, materials, analyses, and exclusion criteria (https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859 [^prereg]).
+The online supplementary material (OSM) of this study include the data, research material, analyses scripts, and a reproducible version of this manuscript (see https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0)
+We preregistered the study using the registration form _OSF Prereg_, which includes hypotheses, sample size, materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
 We needed to change our pre-defined plan in some cases. 
-For a full account of all changes, see online supplementary material (OSM), https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0.
+For a full account of all changes, see OSM. 
 New analyses that were not preregistered appear in the section on exploratory analyses. 
-For example, we also measured additional variables that were not included in the preregistration (e.g., specific gratifications and general trust; see below), whose results we report as exploratory analyses.
-
-[^prereg]: To find the actual preregistration on the website, click _View Registration Form_ (blue button on the right hand side).
+For example, we also measured two additional variables that were not included in the preregistration (e.g., _specific_ gratifications and _general_ trust; see below), which are included in the exploratory analyses.
 
@@
 We collaborated with a professional panel agency to recruit participants. 
-As an incentive, participants were awarded digital points, which they could use to get special offers from other companies.
-In order to be able to take part, participants needed to be above the age of 18 and had to live in Germany.
+As incentive, participants were awarded digital points, which they could use to get special offers from other companies. 
+Participants were above the age of 18 and lived in Germany. 
 In a first step, the agency sent their panel members an invitation to participate in the study (_invitation_). 
-In this invitation, panel members were asked whether they would be interested in taking part in a study analyzing the threat posed by current terrorist attacks in Germany.[^1] If panel members decided to take part, they were subsequently sent the first questionnaire (_T1_) in which we asked about the participants’ sociodemographics, provided more details about the study, and included a registration link for the website.
-Afterward, the participants were randomly assigned to one of the three websites.
+In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.[^1] 
+Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which we asked about their sociodemographics, provided more details about the study, and included a registration link for the website.
+Afterward, participants were randomly assigned to one of the three websites. 
 After registration participants had the chance to discuss the topic of the terrorism threat in Germany over the course of one week (_field_). 
-Afterward, participants received a follow-up questionnaire in which we collected the self-reported measures (_T2_).
+Subsequently, participants received a follow-up questionnaire in which we collected the self-reported measures (_T2_). 
 Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.
@@
 We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). 
-Participants used the website actively: Overall, users spent `r sum(d$time_read/60) %>% round(digit = 0)` minutes online and wrote `r sum(d$post_count)` comments (for an example of communication that took place, see Figure \@ref(fig:comments)).
+Participants used the website actively: Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(60) %>% round(0) %>% format(big.mark = ",")` minutes online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and left `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
+For an example of communication that took place, see Figure \@ref(fig:comments).
 
@@
 
-We ran a priori power analyses to determine how many participants to recruit.
-The power analysis was based on the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018].
+We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
 Thus, we defined an effect size that we would consider enough to support our hypotheses. 
-Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be r = `r r_sesoi`.
+Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be r = `r r_sesoi %>% my_round("std")`.
 Our aim was to be able to detect this SESOI with a probability of at least 95%.
-Using the regular alpha level of 5%, this leads to a minimum sample size of _n_ = `r n_desired`.
+Using the regular alpha level of 5%, this leads to a minimum sample size of _n_ = `r n_desired %>% format(big.mark = ",")`.
 In the end, we were able to include n = `r n_final` in our analyses (see below). 
-This means that our study had a probability (power) of `r power_achieved * 100`% of finding an effect at least as large as _r_ = `r r_sesoi`.
-Put differently, we were able to make reliable inferences about effects at least as big as _r_ = `r r_sensitive`.
+This means that our study had a probability (power) of `r power_achieved * 100`% of finding an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
+Put differently, we were able to make reliable inferences about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
 
 We collected a representative sample of the German population in terms of age, sex, and federal state. 
-T1 was completed by _N_ = `r n_t1` participants and T2 by _n_ = `r n_t2` participants.
-We connected the data from T1, participants' behavior on the platform, and T2 by means of objective and automated processes (e.g., participants were matched via tokens or IP addresses).
-So far, we have been able to match the data for _n_ = `r n_final` participants.
-The matching process is not yet finished, and we will try to match the remaining cases manually.
+`r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1, `r n_users` participants created a user account on the website,  and `r n_t2` participants completed the survey at T2. 
+Using tokens and IP addresses, we connected the data from T1, participants' behavior on the platform, and T2 by means of objective and automated processes.
+The data for _n_ = `r n_matched` participants could be matched successfully across all three platforms. 
 We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less then three minutes, which we considered to be unreasonably fast. 
-The sample characteristics at T1 were as follows:
-Age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
-The characteristics of the final sample were as follows: 
-Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m, 2)*100`%.
-Hence, despite dropout, T2 can also be considered a largely representative sample of the German population.
+To detect corrupt data, we calculated Cook's distance. 
+We excluded `r n_resp_pattern` participants because they provided clear response patterns. 
+The final sample included `r n_final` participants.
+The sample characteristics at T1 and T2 were as follows: 
+T1: Age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
+T2: Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m, 2)*100`%.
+(One participant did not report his or her sex.) 
+<!-- Despite the dropout and although somewhat higher-educated, also T2 can hence be considered a largely representative sample of the German population. -->
 
@@
 In what follows, we present the materials we used to measure our variables. 
+Wherever possible, we operationalized our variables using established measures.
+Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items that were pretested in terms of legibility and/or understandability.
 To gauge the variables' factor validity, we ran confirmatory factor analyses (CFA). 
@@
 For an overview of the variables' distributions, see Figure \@ref(fig:corrplot). 
-For the exact wording of all items and their individual distributions, see the OSM.
+For the exact wording of all items and their individual distributions, see OSM.
 
@@
 Calculated with the model predicted values for each variable (baseline model).", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
-print(plot_fs_cor)
+print(fig_fs_cor)
 ```
@@
 
-Privacy concerns were measured with seven items based on @buchananDevelopmentMeasuresOnline2007 One example item was "When using the participation platform, I had concerns about my privacy".
+Privacy concerns were measured with seven items based on @buchananDevelopmentMeasuresOnline2007.
+One example item was "When using the participation platform, I had concerns about my privacy". 
 One item had to be deleted due to poor psychometric properties.
@@
 Next, we differentiated between two separate types of gratification. 
-_General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015 One example item was "Using the participation platform has paid off for me".
+_General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
+One example item was "Using the participation platform has paid off for me". 
 _Specific gratifications_ were measured with 15 items on five different subdimensions with three items each. 
-The scaled was loosely based on @schererGratifikationMinuteZeitnahe2002 Example items were: "Using the participation platform made it possible for me to" ...
+The scaled was loosely based on @schererGratifikationMinuteZeitnahe2002.
+Example items were: "Using the participation platform made it possible for me to" ...
 "learn things I would not otherwise have noticed" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).
 
-### Self-disclosure self-efficacy
+### Privacy deliberation
 
-Self-disclosure self-efficacy was captured with six self-designed items, which captured whether participants felt that they had sufficient self-efficacy to write a comment on the platform.
-For example, we asked "I felt technically competent enough to write a comment." Two items, which were inverted, had to be deleted due to poor psychometric properties.
+Privacy deliberation was measured with 5 self-designed items. One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."
+
+### Self-efficacy
+
+Self-efficacy was captured with six self-designed items, which captured whether participants felt that they had sufficient self-efficacy to write a comment on the platform. 
+For example, we asked "I felt technically competent enough to write a comment." 
+Two items, which were inverted, had to be deleted due to poor psychometric properties.
 
@@
 Next, we differentiated between two separate types of trust. 
-_General trust_ was operationalized based on @sollnerWhyDifferentTrust2016 for three targets (i.e., provider, website, and other users) with one item each.
+_General trust_ was operationalized based on @sollnerWhyDifferentTrust2016 for three targets (i.e., provider, website, and other users), with one item each. 
 One example items was "The operators of the participation platform seemed trustworthy."
@@
 
-### Privacy deliberation
-
-Privacy deliberation was measured with 5 self-designed items. One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."
-
 ### Self-disclosure
 
-Self-disclosure was calculated by taking the natural logarithm of the number of comments each participant posted.
+Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment plus the number of likes and dislikes, with likes and dislikes being multiplied by two.
+Like and dislike buttons were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons the sentence “I dislike”.
+The sum of words and likes/likes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already said.
 
@@
 
-We tested all hypotheses and research questions using structural equation modeling (SEM).
-We tested the influence of the three websites using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework using latent variables [e.g., @klinePrinciplesPracticeStructural2016].
-As the dependent variable (self-disclosure) was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016].
+All hypotheses and research questions were tested using structural equation modeling (SEM). 
+The influence of the three websites was analyzed using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework using latent variables [e.g., @klinePrinciplesPracticeStructural2016].
+Because the dependent variable (self-disclosure) was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
 As recommended by @klinePrinciplesPracticeStructural2016, we report the following global fit indices: $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
-As sociodemagraphic variables are often related to self-disclosure and other privacy-related variables [e.g., @dindiaSexDifferencesSelfdisclosure1992], we controlled all variables for the influence of sex and age.
+Because sociodemographic variables are often related to self-disclosure and other privacy-related variables [e.g., @dindiaSexDifferencesSelfdisclosure1992], we controlled all variables for the influence of sex, age, and education.
 Preregistered hypotheses were tested with a one-sided significance level of 5%. 
-Research questions and exploratory analyses were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction.
+Research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction. 
+Exploratory analyses were conducted from a descriptive perspective, and the reported p-values/CIs should not be overinterpreted.
+
 We used `r r_citations` for all our analyses.
@@
 
-It is important to note that the bivariate results showed three very large correlations: First, between specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% round(2) %>% .[2, 1]`); second, between privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% round(2) %>% .[2, 1]`); third, between specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% round(2) %>% .[2, 1]`).
+It is important to note that the bivariate results showed three very large correlations: First, between specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% .[2, 1] %>% my_round("std")`); second, between privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`); third, between specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`).
 As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.
@@
 The model fit our data comparatively well, `r fit_txt(fit_prereg, scaled = TRUE)`.
-Regarding H1, we did not find that general gratifications predicted self-disclosure (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`).
-Regarding H2, neither did we find that privacy concerns predicted self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`).
-The analyses for RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`).
-With regard to H3, however, we found that experiencing self-efficacy substantially predicted self-disclosure (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`).
-Concerning H4, the results showed that trust was not associated with self-disclosure (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`).
+Regarding H1, we did not find that general gratifications predicted self-disclosure (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided).
+Regarding H2, neither did we find that privacy concerns predicted self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided).
+The analyses for RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`; two-sided).
+With regard to H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided).
+Concerning H4, the results showed that trust was not associated with self-disclosure (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).
 
-However, these results should be treated with utmost caution.
-As mentioned above, we indeed detected problems suggesting multicollinearity.
-Most prominently, in this multiple regression trust had a negative relation with self-disclosure, even though when analyzed bivariately the relation was positive---which is a sign of multicollinearity [@klinePrinciplesPracticeStructural2016].
-As a result, specific trust and general gratifications should not be analyzed within the same model, as the two concepts are empirically too close to one another.
+However, these results should be treated with caution. 
+As mentioned above, we indeed detected problems related to multicollinearity. 
+For example, in this multiple regression trust had a _negative_ relation with self-disclosure, whereas in the bivariate analysis the relation was _positive_.
+"Wrong" signs are a typical indicator of multicollinearity [@grewalMulticollinearityMeasurementError2004].
+
+<!-- As a result, specific trust and general gratifications should not be analyzed within the same model, as the two concepts are empirically too close to one another. -->
 
@@
 Thus, we slightly adapted our preregistered model on the basis of the insights described above. 
-First, instead of specific trust and general gratifications we now included general trust and specific gratifications (which were also correlated slightly less strongly with one another).
+First, instead of specific trust and general gratifications we now included general trust and specific gratifications, which were correlated slightly less strongly with one another. 
 The adapted model fit our data comparatively well, `r fit_txt(fit_adapted)`.
 
-In the adapted privacy calculus model, we found two additional significant effects.
-For example, specific gratifications predicted self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`).
-Furthermore, in this model people who engaged in more privacy deliberation did not disclose less information (`r coeffs_txt(fit_adapted, "c1")`).
-However, note that the effect was only marginally not significant.
+In the adapted privacy calculus model, we found that specific gratifications were positively related to self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`). 
+Furthermore, people who deliberated more about their privacy disclosed less information (`r coeffs_txt(fit_adapted, "c1")`). 
 Self-efficacy remained substantially correlated with self-disclosure (`r coeffs_txt(fit_adapted, "d1")`). 
-We again found a negative correlation between trust and self-disclosure (`r coeffs_txt(fit_adapted, "e1")`), which, as a sign of multicollinearity, suggests that also general trust and specific gratifications should not be analyzed within the same model either.
+However, we again found a negative correlation between trust and self-disclosure (`r coeffs_txt(fit_adapted, "e1")`), which again implies multicollinearity.
 
-Given that we observed several instances of multicollinearity, we also fitted a simple privacy calculus model containing only privacy concerns and specific gratifications.
+When confronted with multicollinearity, two responses are typically recommended [@grewalMulticollinearityMeasurementError2004]:
+(a) combining collinear variables into a single measure, or (b) keeping only one of the collinear variables.
+Combining variables was not an option in our case, because both trust and expected benefits are theoretically distinct constructs.
+Because several variables were closely related to one another, in the end we therefore decided to fit a simple privacy calculus model, which contains only privacy concerns and specific gratifications.
+
 The simple model fit our data well, `r fit_txt(fit_simple)`. 
-First, we found that people who experienced more privacy concerns than others also disclosed less information (`r coeffs_txt(fit_simple, "a1")`).
-Second, people who reported more specific gratifications than others also self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`).
-Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi`, implying that the effects were sufficiently large to qualify as support our the hypotheses.
-All effects labelled as significant were below their individual Bonferroni-Holm corrected significance level.
+First, we found that people who experienced more privacy concerns than others disclosed less information (`r coeffs_txt(fit_simple, "a1")`). 
+Second, people who reported more specific gratifications than others self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`). 
+Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, implying that the effects were sufficiently large to be relevant. 
 For a visual overview of all results, see Figure \@ref(fig:plot-pc).
 
-```{r plot-pc, fig.cap="Predictors of self-disclosure.
-Black lines indicate 90\\% CIs (for one-sided hypotheses), grey lines 95\\% CIs (for two-sided hypotheses).
-Displayed are unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=3}
-print(plot_pc)
+```{r plot-pc, fig.cap="Predictors of self-disclosure. Displayed are the 95% CIs of the unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=4}
+print(fig_coeffs)
 ```
 
-When comparing the three models with one another, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"]`, AIC = `r model_comp_tab["simple", "aic"]`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"]`, AIC = `r model_comp_tab["preregistered", "aic"]`) and the adapted model (BIC = `r model_comp_tab["adapted", "bic"]`, AIC = `r model_comp_tab["adapted", "aic"]`).
+When comparing the three models with one another, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
 
@@
 
+In a next step, we analyzed the potential effects of the popularity cues on the privacy calculus. 
 Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables. 
@@
 Note that some differences missed statistical significance only marginally (e.g., specific gratifications for the comparison between the website with like buttons and the control website without like and dislike buttons).
-Nevertheless, we refrain from reading too much into the differences between the three websites and conclude that they were mostly similar with regard to the privacy calculus variables and the amount of self-disclosure.
+Nevertheless, we refrain from reading too much into the differences between the three websites and conclude that they were mostly similar regarding the privacy calculus variables and the amount of self-disclosure.
 
@@
 Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
-# knitr::include_graphics("figures/results/plot_pop.pdf")
-print(plot_fs_m)
+# knitr::include_graphics("figures/results/fig_pop.pdf")
+print(fig_fs_m)
 ```
@@
 
-In this study, we analyzed theg e privacy calculus using actual observed behavior in a preregistered field experiment with data from a representative sample of the German population.
-We additionally sought to determine whether the privacy calculus is dependent on popularity cues such as like and dislike buttons.
-The data were analyzed using structural equation modeling.
+In this study, we analyzed the privacy calculus using actual observed behavior in a preregistered field experiment. 
+We additionally asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons. 
+The data came from a representative sample of the German population and were analyzed using structural equation modeling.
+
 In the bivariate analyses, all privacy calculus variables were shown to significantly predict self-disclosure. 
-In the preregistered analyses using multiple regression, in which several variables were analyzed together, self-efficacy turned out to be the strongest predictor of self-disclosure.
-However, this preregistered model exhibited significant problems with regard to multicollinearity, which is why we also computed a more basal privacy calculus model consisting of only privacy concerns and specific gratifications.
-In this model, both variables significantly and meaningfully predicted self-disclosure.
-Taken together, the results add further support to the privacy calculus framework, suggesting that self-disclosure online is not erratic (as for example posited by the privacy paradox, for example) but---at least somewhat---considered.
+In the preregistered analyses using multiple regression, in which several variables were analyzed together, self-efficacy was the strongest predictor of self-disclosure.
+All other variables were not significant, which is why the originally postulated extended privacy calculus model was not supported by the data.
+However, this preregistered model exhibited significant problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a more basal privacy calculus model, which included only privacy concerns and specific gratifications.
 
-Our results suggest that in new communication contexts roughly one third of all Internet users actively deliberates about their privacy.
-Determining whether this figure is large or small is a normative question---for example, one can convincingly argue that this number sould be higher and that we as society should still more actively deliberate about our self-disclosure practices online.
-Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar---evidenced by their strong correlation with one another and their similar correlations with other variables.
+The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy share less, people who expect more specific gratifications disclose more, and people who feel more self-efficacious disclose more.
+However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases, which seems implausible. 
+As a result, we also fit the above-mentioned simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure.
+Taken together, the results support the privacy calculus framework and suggest that self-disclosure online is not erratic and that it can be explained by various psychological variables.
+
+Relatedly, the results suggest that in new communication contexts roughly one third of all Internet users actively deliberates about their privacy. 
+Determining whether this figure is large or small is a normative question.
+For example, one can convincingly argue that this number should be higher and that we as society should still more actively deliberate about our self-disclosure practices online. 
+Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables.
 This either implies that thinking about one's privacy increases one's concern or, conversely, that being concerned about one's privacy leads one to think about one's options more actively. 
@@
 
-The next major implication is that popularity cues do not seem to have an overly strong influence on the privacy calculus and self-disclosure.
-Although some studies have found that popularity cues substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], our results suggest the opposite: Users still disclose the same amount of personal information regardless of whether a website includes like or dislike buttons, potentially highlighting the agency of users.
+The next major implication is that several scenarios and uses cases exist in which popularity cues do not seem to have an overly strong influence on the privacy calculus and self-disclosure. 
+Although some studies have found that popularity cues substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], in our study we found the opposite: 
+Users still disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons, potentially highlighting the agency of users.
 
@@
 First, we question the tendency to further increase the complexity of the privacy calculus model by adding additional variables [e.g., @dienlinExtendedPrivacyCalculus2016]. 
-"Since all models are wrong the scientist cannot obtain a "correct"it one by excessive elaboration.
+"Since all models are wrong the scientist cannot obtain a "correct" one by excessive elaboration.
 [...] Just as the ability to devise simple but evocative models is the signature of the great scientist so overelaboration and overparameterization is often the mark of mediocrity" [@boxScienceStatistics1976, p.
 792].
-Although adding variables can increase the amount of explained variance, it might also introduce spurious results due to multicollinearity---a problem that we think deserves more attention in general.
-Specifically, we have come to believe that adding self-efficacy to privacy calculus models is of limited value, for self-efficacy is mostly a proxy of behavior and does not offer much epistemic insight.
+Specifically, we have come to believe that adding self-efficacy to privacy calculus models is of limited value, for self-efficacy is mostly a self-reported proxy of behavior and offers little epistemic insight.
 Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to self-disclose whereas others do not. 
+In addition, although adding variables increases the amount of explained variance, it introduces further problems, for example spurious results due to multicollinearity.
+
+In general, we think that the topic of multicollinearity should receive more scholarly attention. 
+Interestingly, one can rightfully argue that multicollinearity is not actually a problem, but rather a warning sign. 
+From a _statistical_ perspective, when predictors are strongly correlated this only means that standard errors increase [@vanhoveCollinearityIsnDisease2019]. 
+In other words, when predictors are strongly correlated we can be less certain about the effects we obtain, because there is less variance [@vanhoveCollinearityIsnDisease2019]. 
+So to increase certainty researchers could compensate by collecting larger samples, which would allow to achieve sufficient statistical power. 
+Fortunately, using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated/collinear predictors [@wangPowerAnalysisParameter2020].
+
+From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
+It is our understanding that multiple regression is often used with the aim to isolate effects, to make sure that effects are not simply caused by another third variable.
+However, in cases of highly correlated measures this often does not make much sense theoretically.
+For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure, _while holding trust constant_.
+Theoretically, however, it is more plausible to assume that increasing gratifications also fosters trust [@sollnerWhyDifferentTrust2016].
+In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant several variables such as gratifications, privacy concerns, privacy deliberations, and self-efficacy, measures which are all strongly correlated.
+In short, the effects we found could even be correct, but the interpretation is much more difficult, artificial, and thereby of little theoretical and practical value.
 
@@
 
-Furthermore, we found a remarkably strong correlation between trust and expected gratifications (i.e., _r_ = .77), which at first glance seemed somewhat peculiar to us.
+Furthermore, we found a remarkably strong correlation between specific trust and expected gratifications (i.e., _r_ = .79).
+At first glance, this strong relation seemed somewhat peculiar to us. 
 On closer inspection, however, we realized that the way trust is routinely operationalized in the literature is very close to expected gratifications. 
-To illustrate, one subdimension explicitly measures _ability_ via items such as “The comments of other users were useful”.
-In fact, the literature often operationalizes trust as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016].
+To illustrate, the trust subdimension _ability_ includes items such as “The comments of other users were useful”. 
+In fact, in the literature trust is often operationalized as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016]. 
 In conclusion, our results suggest that we should not confuse _causes_ of trust with _measures_ of trust, for this might introduce problems of both homogeneity and/or multicollinearity.
+Instead, we recommend to measures general and reflective measures of trust, which are less closely related to expected gratifications.
 
@@
 First, all results are based on analyses of between-person variance. 
-However, between-person relations often do not translate well to within-person effects [e.g.
-@hamakerCritiqueCrosslaggedPanel2015].
+However, between-person relations often do not translate well to within-person effects [e.g. @hamakerCritiqueCrosslaggedPanel2015]. 
 While some studies on privacy concerns online have begun to examine both sources of variance [e.g., @dietvorstAdolescentPerceptionsParental2017], finding that intrapersonal changes in privacy concerns are indeed related to intrapersonal changes in self-disclosure, similar analyses are still lacking for the privacy calculus.
+
 Second, the self-reported measures were collected _after_ the field phase in which the dependent variable was measured. 
@@
 Nevertheless, we deliberately decided to measure the self-reported variables afterward in order to not bias participants and not prime our specific research interest.
-Third, experiments should only manipulate the experimental variable while holding all others constant.
+
+Third, in experiments we should manipulate only the experimental variable while holding all others constant. 
 In this study, we explicitly manipulated the popularity cues. 
 However, as the experiment was conducted in the field, several other variables could not be held constant; for example, the content of communication by other users, the unfolding communication dynamics, or the characteristics of other users.
+As a result, the assumption of stable unit treatment was violated [@klinePrinciplesPracticeStructural2016].
 
 It is important to note that our not having found significant effects of like and dislike buttons does not necessarily mean that like and dislike buttons do indeed have no effect on self-disclosure and the privacy calculus.
-As always, with null-findings one is confronted with the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely--- states that null findings can either be due to the actual non-existence of effects or, instead, a poor operationalization of the research question.
-In this case, we were not able send participants notifications when their comments were liked/disliked, significantly decreasing the popularity cues' salience.
+As always, with null-findings one is confronted with the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely---states that null findings can either be due to an actual non-existence of effects or, instead, to a poor operationalization of the research question.
+In this case, we were not able send participants notifications when their comments were liked/disliked, which significantly decreases the popularity cues' salience.
 
@@
 Our focus was on understanding self-disclosure, which is why we deliberately excluded variables pertaining to political participation, such as informational self-efficacy [@loyPsychologicalPredictorsPolitical2018].
-Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.[^3] It is worth noting that we did not find any instances of people providing meaningless text and, as mentioned above, in times of big data, every piece of communication allows increasingly accurate inferences about one's personality to be made.
-
-[^3]: Somewhat fittingly, in the German language there is a saying: 'He spoke a lot but didn't say a thing'.
-
-Finally, there are several interesting research questions that one could address with the data.
-Most prominently, one could analyze the actual content of the posts to detect whether the three websites might have differed with regard to communication quality.
-In addition, one can make the case that privacy deliberation rather as a moderator---such that deliberating more actively about one's privacy strengthens the relation between privacy concerns or gratifications and self-disclosure.
-Upon publication, the data will be made publicly available and we invite researchers from all disciplines to investigate the aforementioned and other interesting research questions.
+Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.
+Notably, we did not find any instances of people providing meaningless text and, as mentioned above, in times of big data, every piece of communication allows for increasingly accurate inferences about one's personality.
 
@@
 
-While some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p.
-1], in our opinion the privacy calculus is alive and kicking.
+While some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p. 1], in our opinion the privacy calculus is alive and kicking. 
 This study adds to the growing confirmation of observation that people who are more concerned about their privacy than others disclose less information online, whereas people who receive more gratifications from using a website than others disclose more information online.
 The results of this study suggest that a substantial share of internet users, approximately 30%, consciously engage in a privacy calculus by actively deliberating about whether or not to disclose information.
-Popularity cues seem to play a minor role in this process, especially if no means are implemented to guarantee that users are notified about others liking or disliking their communication.
+The results thereby provide further evidence against the privacy paradox.
+Popularity cues such as like and dislike buttons seem to play only a minor role in this process, especially if no means are implemented to guarantee that users are notified about others liking or disliking their communication.
 In conclusion, our results indicate that internet users are at least somewhat proactive and reasonable---probably no more or less proactive or reasonable than in any other regular everyday situation.

### 2020-04-07 manuscript/manuscript.RmD
- small update in abstract

@@
     According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
-So far, most findings are based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual authentic behavior.
+So far, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual authentic behavior.
 Likewise, we still know comparatively little whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.

### 2020-04-07 manuscript/manuscript.RmD
- updated introduction

--- 2020-04-07 manuscript/manuscript.RmD
@@
     According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
-So far, most findings are based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual authentic behavior.
-Likewise, we still know comparatively little whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
+So far, most findings were based on self-reports, and little is known about whether the privacy calculus can explain also observations of authentic behavior.
+Likewise, we still know comparatively little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
 To answer these questions, we ran a preregistered one-week field experiment.
-Participants were randomly distributed to three different websites where they could discuss a current political topic.
+Participants were randomly distributed to three different websites, on which they could discuss a current political topic.
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
-The results showed that privacy calculus variables predicted a considerable share of actual self-disclosure.
+Although the originally preregistered model could not be confirmed, the results showed that the privacy calculus variables predicted a considerable share of actual self-disclosure.
 The impact of popularity cues was negligible.
-In conclusion, the results demonstrate that self-disclosure online can be explained by privacy concerns and specific gratifications.
+In conclusion, the results indicate that self-disclosure online can be explained by privacy concerns and specific gratifications.
 This finding has several implications.
 For example, it provides further evidence against the privacy paradox.
-keywords          : "privacy calculus, self-disclosure, popularity cues, structural equation modeling, preregistration"
+keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
 bibliography      : 
@@
 Somewhat surprisingly, despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018] the privacy paradox has garnered little empirical support.
-A recent meta-analysis revealed that the correlation between privacy concerns and self-disclosure on SNS is *r* = -.13 [@baruhOnlinePrivacyConcerns2017], indicating that privacy concerns are indeed related to self-disclosure online.
+A recent meta-analysis revealed that the correlation between privacy concerns and self-disclosure on SNS is *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which indicates that privacy concerns are indeed related to self-disclosure online.
 
-Rather than further pursuing the privacy paradox, a large share of current day research posits that self-disclosure online can be explained---at least partly---by means of the so-called _privacy-calculus_ [@krasnovaOnlineSocialNetworks2010].
-The privacy calculus builds on the work of @lauferPrivacyConceptSocial1977 and claims that both expected risks *and* expected benefits explain self-disclosure.
-Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information [@heirmanPredictingAdolescentsDisclosure2013; koohikamaliInvestigationDynamicModel2019].
+Rather than further pursuing the privacy paradox, a large share of current day research hence posits that self-disclosure online can be explained---at least partly---by means of the so-called _privacy-calculus_ [@krasnovaOnlineSocialNetworks2010].
+Building on the work of @lauferPrivacyConceptSocial1977, the privacy calculus  claims that both expected risks *and* expected benefits explain self-disclosure.
+Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
-However, although the privacy calculus has gained some momentum several important questions remain unanswered. 
+However, although the privacy calculus has gained some momentum in academic research several important questions remain unanswered. 
 First, we still know comparatively little about whether the privacy calculus can be replicated with actual behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
 Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020].
-However, all three of these approaches significantly hamper external validity.
+However, all three of these approaches have reduced external validity.
+As a result, in this study we analyze actual information sharing behavior in an authentic online setting.
 
@@
 According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that concerns and gratifications both correlate with self-disclosure is not evidence for any substantial or explicit weighing of pros and cons.
-
-We agree and consider it necessary to now explicitly focus on the privacy deliberation process itself. 
+We agree and in this study hence explicitly focus on the privacy deliberation process itself. 
 Moreover, and on a more general level, we aim to gauge the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-disclosure self-efficacy.
 
-Finally, we want to determine whether the privacy calculus can be affected by the design of a website.
-Specifically, we analyze whether *popularity cues* such as like and dislike buttons affect self-disclosure and the privacy calculus.
+Finally, because the privacy calculus does not take place in a vacuum, and because it is often argued that self-disclosure can be easilty triggered by external circumstances, we analyze whether the privacy calculus can be affected by the design of a website.
+Specifically, in this study we investigate whether *popularity cues* such as like and dislike buttons have the power to affect the privacy calculus and to foster self-disclosure.
 

### 2020-04-08 manuscript/manuscript.RmD
- ms: updates on methods, results, and discussion section

@@
     According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
-So far, most findings were based on self-reports, and little is known about whether the privacy calculus can explain also observations of authentic behavior.
+So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual authentic behavior.
 Likewise, we still know comparatively little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
 To answer these questions, we ran a preregistered one-week field experiment.
-Participants were randomly distributed to three different websites, on which they could discuss a current political topic.
+Participants were randomly distributed to three different websites, on which they discussed a current political topic.
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
@@
 Understanding why people disclose personal information online remains a critical question for both society and academic research. 
-Originally, self-disclosure online was thought to be mostly erratic---for example, it was assumed that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints.
+Originally, self-disclosure online was thought to be mostly erratic.
+For example, it was assumed that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints. 
 Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
 
-Somewhat surprisingly, despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018] the privacy paradox has garnered little empirical support.
-A recent meta-analysis revealed that the correlation between privacy concerns and self-disclosure on SNS is *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which indicates that privacy concerns are indeed related to self-disclosure online.
+Somewhat surprisingly, and despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018], the privacy paradox has garnered little empirical support. 
+A recent meta-analysis revealed that the correlation between privacy concerns and self-disclosure on SNS is *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which shows that privacy concerns are indeed related to self-disclosure online.
 
-Rather than further pursuing the privacy paradox, a large share of current day research hence posits that self-disclosure online can be explained---at least partly---by means of the so-called _privacy-calculus_ [@krasnovaOnlineSocialNetworks2010].
-Building on the work of @lauferPrivacyConceptSocial1977, the privacy calculus  claims that both expected risks *and* expected benefits explain self-disclosure.
-Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
+Hence, rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called _privacy-calculus_ [@lauferPrivacyConceptSocial1977], which states that self-disclosure online can be explained---at least partly---by means of expected risks *and* expected benefits [@krasnovaOnlineSocialNetworks2010].
+Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
@@
 Second, current research on the privacy calculus is often criticized for not explicitly focusing on the deliberation process of self-disclosure. 
-According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that concerns and gratifications both correlate with self-disclosure is not evidence for any substantial or explicit weighing of pros and cons.
-We agree and in this study hence explicitly focus on the privacy deliberation process itself. 
-Moreover, and on a more general level, we aim to gauge the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-disclosure self-efficacy.
+According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that concerns and gratifications both correlate with self-disclosure is not evidence for an explicit weighing process of pros and cons.
+We agree.
+In this study, we hence explicitly focus on the privacy deliberation process itself. 
+Moreover, and on a more general level, we explore the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-efficacy.
 
-Finally, because the privacy calculus does not take place in a vacuum, and because it is often argued that self-disclosure can be easilty triggered by external circumstances, we analyze whether the privacy calculus can be affected by the design of a website.
-Specifically, in this study we investigate whether *popularity cues* such as like and dislike buttons have the power to affect the privacy calculus and to foster self-disclosure.
+Finally, because the privacy calculus does not take place in a vacuum, and because it is often argued that self-disclosure can be easily triggered by external circumstances, we analyze whether the privacy calculus can be affected by the design of a website.
+Specifically, we investigate whether *popularity cues* such as like and dislike buttons have the power to affect the privacy calculus and to foster self-disclosure.
 
-To test our research questions, we conducted a preregistered online field experiment, drawing from a representative sample of the German population.
-Participants were randomly distributed to one of three different websites, which either included only a like button, both a like and a dislike button, or no buttons at all.
+To test our research questions, drawing from a representative sample of the German population we conducted a preregistered online field experiment.
+Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all. 
 Over the course of one week participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany). 
-Afterward, they answered our follow-up questionnaire with items pertaining to the privacy calculus variables.
+Afterward, they answered a follow-up questionnaire with items measuring the privacy calculus variables.
 
@@
 There are two different understandings of self-disclosure in the literature: The first defines self-disclosure as _deliberate_ acts of sharing truthful information about the self with others [@jourardTransparentSelf1964].
-The second considers _all_ acts of sharing information---whether active or passive, deliberate or unwitting---as self-disclosure, because each piece of information shared allows meaningful inferences to be made about a person [e.g., @watzlawickPragmaticsHumanCommunication2011].
-In this paper we follow the latter approach, not least because recent years have vividly illustrated how it is possible to derive a plethora of insights about a person simply by analyzing his or her written communication [e.g., @kosinskiPrivateTraitsAttributes2013].
-Moreover, independent from which position one chooses to adopt, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [e.g., @omarzuDisclosureDecisionModel2000].
+The second considers _all_ acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information shared allows for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011].
+In this paper we follow the latter approach, not least because the recent years have vividly illustrated how easy it is to derive personal insights simply by analyzing exchanged communication [@kosinskiPrivateTraitsAttributes2013].
+Moreover, independent from which position one chooses to adopt, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000].
 In this study we mainly focus on communication quantity, as we consider communication quantity to be a necessary precondition and hence valid proxy for self-disclosure.
@@
 "Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [AUTHOR].
-Previous research has found that people who are more concerned about their privacy than others are less inclined to share personal information [@baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
+Previous research has found that people who are more concerned about their privacy than others are less likely to share personal information [@baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
@@
 
-Although privacy concerns are related to self-disclosure, one can make the case that since most studies in the literature report only small effects, there should also be additional meaningful factors that contribute to explaining self-disclosure.
+Although privacy concerns are related to self-disclosure, one can make the case that since most studies in the literature report only small effects there should also be additional meaningful factors that contribute to explaining self-disclosure.
 Most prominently, it has been argued that people trade a loss of privacy for a gain in gratifications such as social capital, entertainment, information, or self-presentation [@ellisonNegotiatingPrivacyConcerns2011; @taddickenUsesPrivacyOnline2011].
@@
 
-In the current literature on the privacy calculus there still seems to be a shortage of studies that explicitly analyze the decision process of actively comparing the pros and cons of disclosing information, although this point of criticism has been leveled several times [e.g., @knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [e.g., @zhuPrivacyCalculusIts2017].
+As mentioned above, there is still a shortage of studies that explicitly analyze the decision process behind the disclosing of information, although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017].
 This criticism is justified.
-The observation that both experiencing privacy concerns and expecting gratifications are related to self-disclosure does not bit itself necessitate an explicit weighing process 
-Hence, we argue that the research on the privacy calculus would benefit significantly from analyzing this decision process explicitly. 
-Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which we define as the extent to which individual people explicitly compare positive and negative potential outcomes before communicating with others.
+The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not a sufficient condition for an explicit weighing process.
+Hence, research on the privacy calculus would benefit significantly from analyzing this decision process explicitly. 
+Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which captures the extent to which individual people explicitly compare positive and negative potential outcomes before communicating with others.
 
 On the one hand, it seems plausible that deliberating about one's privacy would dampen subsequent self-disclosure, because refraining from regular communication---the primary means of connecting with others---requires at least a minimum of active and hence deliberate restraint.
-On the other hand, deliberating about one's privacy might also increase self-disclosure, as after having actively deliberated about the potential consequences, a person concerned about his or her privacy might arrive at the conclusion that in this situation self-disclosure is not only appropriate but expedient.
-In light of the paucity of empirical studies and the plausibility of both effects, we formulate the following research question:
+On the other hand, deliberating about one's privacy might also increase self-disclosure, because a person concerned about his or her privacy might arrive at the conclusion that in this situation self-disclosure is not only appropriate but expedient.
+In light of the lack of empirical studies and the plausibility of both effects, we formulate the following research question:
 
@@
 
-Several attempts have already been made to expand the privacy calculus [e.g., @dinevExtendedPrivacyCalculus2006]. 
-Additional variables such as self-efficacy or trust have been introduced. 
+Several attempts have already been made to expand the privacy calculus [@dinevExtendedPrivacyCalculus2006], introducing additional variables such as self-efficacy or trust. 
 Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
-These privacy behaviors can either refer to self-withdrawal (e.g., deleting inappropriate content) or self-disclosure (e.g., publishing a blog post).
-Thus far, several studies have found that people who report more privacy self-efficacy also self-withdraw more online than others [e.g., @chenRevisitingPrivacyParadox2018].
-In light of our focus on self-disclosure, in this study we investigate the influence of self-disclosure self-efficacy.
+These privacy behaviors refer to either self-_disclosure_ (e.g., publishing a blog post) or self-_withdrawal_ (e.g., deleting inappropriate content).
+People who report more privacy self-efficacy also engage in more self-withdrawal  [@chenRevisitingPrivacyParadox2018].
+In light of our focus on active communication, in this study we investigate the influence of self-_disclosure_ self-efficacy.
 
-Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
+H3: People are more likely to self-disclose on a website when their self-efficacy about self-disclosing on the website is higher.
+
+Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
+It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added].
-Whereas specific trust beliefs focus on the causes of trust, general trust beliefs focus on the experience of trust.
-@gefenTrustTAMOnline2003 prioritize specific trust beliefs (p. 60). 
-In the online context, it is important to differentiate among several targets of trust [@sollnerWhyDifferentTrust2016]. 
+Whereas specific trust focuses on the causes of trust, general trust emphasized the experience of trust.
+@gefenTrustTAMOnline2003 prioritize specific trust (p. 60). 
+In the online context, it is also important to differentiate among several _targets_ of trust [@sollnerWhyDifferentTrust2016]. 
 Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
 Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
-For example, it has been demonstrated that people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].
-
-In conclusion, while we expect to find these relations as well, we would also like to determine whether the inclusion of all the other variables mentioned above, including the not yet researched concept of privacy deliberation, might potentially attenuate or even obviate the predictive capacity of self-efficacy and trust.
-
-H3: People are more likely to self-disclose on a website when their self-efficacy about self-disclosing on the website is higher.
+For example, people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].
 
@@
 First, it has often been noted that researchers should not exclusively focus on specific features of particular websites, for features are prone to change and quickly become obsolete [@foxDistinguishingTechnologiesSocial2017].
-Instead, it has been suggested that researchers prioritize underlying latent structures, for example by analyzing what are know as affordances [e.g., @ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017].
-The concept of affordances was developed by @gibsonEcologicalApproachVisual2015, who argued that it is not the objective features of objects that determine behavior but rather subjective perceptions. 
+Instead, it has been suggested to prioritize underlying latent structures, for example by analyzing so-called affordances [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. 
+The concept of affordances was developed by @gibsonEcologicalApproachVisual2015, who argued that it is not the _objective features_ of objects that determine behavior.
+Instead, more important are the _subjective perceptions_. 
 Affordances are a mental representation of how a given entity might be used; as such, they are by definition subjective. 
-There is much debate in the literature concerning what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017]. 
+There is an ongoing debate on what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017]. 
 For example, whereas @evansExplicatingAffordancesConceptual2017 propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), @foxDistinguishingTechnologiesSocial2017 suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).
@@
 As the privacy calculus states that both benefits and costs determine behavior, we suggest that popularity cues such as like and dislike buttons, which are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p.
-142], perfectly epitomize benefits and costs.
-The like button is positive; it expresses an endorsement, a compliment, a reward [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017]. 
+142], perfectly capture potential benefits and costs.
+The like button is positive. 
+It expresses an endorsement, a compliment, a reward [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017]. 
 However, communication online is also often characterized by negative and critical debates [@ziegeleDynamicsOnlineNews2017]. 
-As the dislike button is a major means of downgrading content it represents the cost and risk factor of the privacy calculus well. 
-In fact, its stark negative effect might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit or stackexchange).
+As the dislike button is a major means of downgrading content it is negative and represents the risk factor of the privacy calculus well. 
+In fact, its stark negative effect might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit, or stackexchange).
 
-Paralinguistic digital affordances and/or popularity cues have been shown to impact behavior [@kramerMasteringChallengeBalancing2020; @treptePrivacyCalculusContextualized2020].
+Paralinguistic digital affordances and specifically popularity cues have been shown to impact behavior [@kramerMasteringChallengeBalancing2020; @treptePrivacyCalculusContextualized2020].
 For example, a large-scale field experiment in which 101,281 comments were analyzed found that comments with dislikes were more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
-@stroudRecommendRespectAltering2017 demonstrated that when users had a different opinion than the one that was communicated in a post, they were more likely to click on a button labelled _respect_ compared to a button labelled _like_.
+@stroudRecommendRespectAltering2017 demonstrated that when users disagreed with a post, they were more likely to click on a button labeled _respect_ compared to a button labeled _like_.
 
-In this vein it seems plausible that popularity cues might also impact the privacy calculus [kramerMasteringChallengeBalancing2020].
-First, on a primordial level, popularity cues serve as a means of reward and punishment, affecting behavior via instrumental conditioning [@skinnerScienceHumanBehavior2014]. 
-Specifically, being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit future disclosure. 
-Similarly, like buttons should be associated with being able to garner positive feedback, so implementing a like-button---similar to a compliment in the offline world---might leverage gratifications.
-Implementing a like or a dislike button might also bring people to more actively deliberate about whether or not it is actually worthwhile to disclose information.
+In this vein, it seems plausible that popularity cues might also impact the privacy calculus [@kramerMasteringChallengeBalancing2020].
+First, popularity cues could serve as a means of reward and punishment, affecting behavior via instrumental conditioning [@skinnerScienceHumanBehavior2014]. 
+Being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit disclosure. 
+Similarly, like buttons imply being able to garner positive feedback, so implementing a like-button---similar to a compliment in the offline world---might leverage gratifications. 
+Implementing popularity cues might also bring people to more actively deliberate about whether or not it is actually worthwhile to disclose information. 
 If both like and dislike buttons are present, privacy deliberation should increase even further. 
 Finally, because people who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017], implementation of the dislike button should both stir privacy concerns and stifle self-disclosure.
-For a simplified overview of our theoretical model, see Figure \@ref(fig:model).
 
@@
 H7.	Compared to people who use a website with only like buttons, people who use a website with like and dislike buttons (a) are more concerned about their privacy, and (b) deliberate more about whether they should communicate online.
+
+For a simplified overview of our theoretical model, see Figure \@ref(fig:model).
 
@@
 
-The online supplementary material (OSM) of this study include the data, research material, analyses scripts, and a reproducible version of this manuscript (see https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0)
-We preregistered the study using the registration form _OSF Prereg_, which includes hypotheses, sample size, materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
+The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript (see https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0).
+We preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
 We needed to change our pre-defined plan in some cases. 
@@
 New analyses that were not preregistered appear in the section on exploratory analyses.
-For example, we also measured two additional variables that were not included in the preregistration (e.g., _specific_ gratifications and _general_ trust; see below), which are included in the exploratory analyses.
 
@@
 The study was designed as an online field experiment with three different groups. 
-The first group interacted with a website without like/dislike buttons, the second with a website with only like buttons, and the third with a website with both like and dislike buttons. 
+The first group used a website without like/dislike buttons, the second a website with only like buttons, and the third a website with both like and dislike buttons. 
 Participants were randomly distributed to one of the three websites in a between-subject design.
@@
 Participants were above the age of 18 and lived in Germany. 
-In a first step, the agency sent their panel members an invitation to participate in the study (_invitation_). 
+In a first step, the agency sent its panel members an invitation to participate in the study (_invitation_). 
 In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.[^1] 
@@
 Afterward, participants were randomly assigned to one of the three websites. 
-After registration participants had the chance to discuss the topic of the terrorism threat in Germany over the course of one week (_field_). 
-Subsequently, participants received a follow-up questionnaire in which we collected the self-reported measures (_T2_). 
+After registration was completed, participants could discuss the topic of the terrorism threat in Germany over the course of one week (_field_). 
+Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (_T2_). 
 Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.
@@
 
-We programmed an online website based on the open-source software discourse (https://www.discourse.org/). 
+We programmed an online website based on the open-source software _discourse_ (https://www.discourse.org/). 
 We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). 
@@
 
-We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
-Thus, we defined an effect size that we would consider enough to support our hypotheses. 
-Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be r = `r r_sesoi %>% my_round("std")`.
+We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on a smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
+In other words, we defined a minimum effect size that we would consider sufficiently large enough to support our hypotheses. 
+Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be _r_ = `r r_sesoi %>% my_round("std")`.
 Our aim was to be able to detect this SESOI with a probability of at least 95%.
@@
 In the end, we were able to include n = `r n_final` in our analyses (see below). 
-This means that our study had a probability (power) of `r power_achieved * 100`% of finding an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
+This means that our study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
 Put differently, we were able to make reliable inferences about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
@@
 T1: Age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
-T2: Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m, 2)*100`%.
-(One participant did not report his or her sex.) 
+T2: Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m * 100, 0)`%.
+One participant did not report his or her sex.
 <!-- Despite the dropout and although somewhat higher-educated, also T2 can hence be considered a largely representative sample of the German population. -->
@@
 In what follows, we present the materials we used to measure our variables. 
-Wherever possible, we operationalized our variables using established measures.
-Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items that were pretested in terms of legibility and/or understandability.
-To gauge the variables' factor validity, we ran confirmatory factor analyses (CFA). 
-If the CFAs revealed insufficient fit, we deleted individual items. 
+Wherever possible, we operationalized the variables using established measures.
+Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which we pretested concerning their legibility and understandability.
+To assess factor validity we ran confirmatory factor analyses (CFA). 
+If the CFAs revealed insufficient fit, we deleted malfunctioning items. 
 All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale. 
 Answer options were as follows: -3 (_strongly disagree_), -2 (_disagree_), -1 (_slightly disagree_), 0 (_neutral_), +1 (_slightly agree_), +2 (_agree_), +3 (_strongly agree_). 
-In the questionnaire, all items measuring a variable were presented on the same page in a randomized order.
+In the questionnaire, all items measuring a variable were presented on the same page in randomized order.
 
@@
 
-Next, we differentiated between two separate types of gratification. 
+We differentiated between two separate types of gratification. 
 _General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
@@
 Example items were: "Using the participation platform made it possible for me to" ...
-"learn things I would not otherwise have noticed" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).
+"learn things I would not have noticed otherwise" (information), "react to a subject that is important to me" (relevance), "engage politically" (political participation), "try to improve society" (idealism), and "soothe my guilty consciences" (extrinsic benefits).
 
@@
 
-Privacy deliberation was measured with 5 self-designed items. One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."
+Privacy deliberation was measured with five self-designed items. One example item was "While using the participation platform I have weighed the advantages and disadvantages of writing a comment."
 
@@
 
-Self-efficacy was captured with six self-designed items, which captured whether participants felt that they had sufficient self-efficacy to write a comment on the platform. 
+Self-efficacy was captured with six self-designed items, which measured whether participants felt that they had sufficient self-efficacy to write a comment on the platform. 
 For example, we asked "I felt technically competent enough to write a comment." 
-Two items, which were inverted, had to be deleted due to poor psychometric properties.
+Two inverted items were deleted due to poor psychometric properties.
 
@@
 
-Next, we differentiated between two separate types of trust. 
-_General trust_ was operationalized based on @sollnerWhyDifferentTrust2016 for three targets (i.e., provider, website, and other users), with one item each. 
+We differentiated between two types of trust. 
+_General trust_ was operationalized based on @sollnerWhyDifferentTrust2016, addressing three targets (i.e., provider, website, and other users) with one item each. 
 One example items was "The operators of the participation platform seemed trustworthy."
@@
 Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability).
-The results showed that the provider and website targets were not sufficiently distinctive, as was evidenced by the existence of a Heywood case. 
+The results showed that the provider and website targets were not sufficiently distinct, as was evidenced a Heywood case. 
 We hence adapted the scale to combine these two targets. 
@@
 
-Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment plus the number of likes and dislikes, with likes and dislikes being multiplied by two.
-Like and dislike buttons were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons the sentence “I dislike”.
+Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two. 
+The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
 The sum of words and likes/likes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already said.
@@
 
-All hypotheses and research questions were tested using structural equation modeling (SEM). 
-The influence of the three websites was analyzed using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework using latent variables [e.g., @klinePrinciplesPracticeStructural2016].
-Because the dependent variable (self-disclosure) was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
+All hypotheses and research questions were tested using structural equation modeling. 
+The influence of the three websites was analyzed using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016].
+Because the dependent variable self-disclosure was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
 As recommended by @klinePrinciplesPracticeStructural2016, we report the following global fit indices: $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
-Because sociodemographic variables are often related to self-disclosure and other privacy-related variables [e.g., @dindiaSexDifferencesSelfdisclosure1992], we controlled all variables for the influence of sex, age, and education.
+Because sociodemographic variables are often related to self-disclosure and other privacy-related variables [@dindiaSexDifferencesSelfdisclosure1992], we controlled all variables for the influence of sex, age, and education.
 Preregistered hypotheses were tested with a one-sided significance level of 5%. 
 Research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction. 
-Exploratory analyses were conducted from a descriptive perspective, and the reported p-values/CIs should not be overinterpreted.
+Exploratory analyses were conducted from a descriptive perspective, which is why the reported p-values and confidence intervals should not be overinterpreted.
 
@@
 
-First, we measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)).
+We first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
 The results did not reveal any relationships to be particularly curvilinear. 
-Furthermore, all variables making up the privacy calculus demonstrated the expected relationships with self-disclosure.
-For example, people who were more concerned about their privacy had written fewer posts (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
-Worth noting is that specific gratifications and general trust predicted self-disclosure better than general gratifications and specific trust.
-The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`.
-Altogether, `r pridel_active %>% round(0)`% of participants reported having actively deliberated about their privacy.
+Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with self-disclosure. 
+For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
+Worth noting, specific gratifications and general trust predicted self-disclosure better than general gratifications and specific trust (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
+_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
+The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. Altogether, `r pridel_active %>% round(0)`% of participants reported having actively deliberated about their privacy.
 
@@
 
-First, we ran a model as specified in the preregistration.
-The model fit our data comparatively well, `r fit_txt(fit_prereg, scaled = TRUE)`.
+First, we ran a model as specified in the preregistration. The model fit our data comparatively well, `r fit_txt(fit_prereg, scaled = TRUE)`. 
 Regarding H1, we did not find that general gratifications predicted self-disclosure (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
-Regarding H2, neither did we find that privacy concerns predicted self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided).
-The analyses for RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`; two-sided).
-With regard to H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided).
-Concerning H4, the results showed that trust was not associated with self-disclosure (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).
+With regard to H2, privacy concerns did not predict self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
+RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`). 
+Regarding H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided). 
+Concerning H4, results showed that trust was not associated with self-disclosure (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).
 
-However, these results should be treated with caution. 
-As mentioned above, we indeed detected problems related to multicollinearity. 
-For example, in this multiple regression trust had a _negative_ relation with self-disclosure, whereas in the bivariate analysis the relation was _positive_.
-"Wrong" signs are a typical indicator of multicollinearity [@grewalMulticollinearityMeasurementError2004].
+However, these results should be treated with caution, because they indeed exhibit problems typical of multicollinearity, such as "wrong" signs of the predictors [@grewalMulticollinearityMeasurementError2004].
+For example, in the multiple regression trust had a _negative_ relation with self-disclosure, whereas in the bivariate analysis it was _positive_.
 
@@
 Thus, we slightly adapted our preregistered model on the basis of the insights described above. 
-First, instead of specific trust and general gratifications we now included general trust and specific gratifications, which were correlated slightly less strongly with one another. 
+First, instead of specific trust and general gratifications we now included _general_ trust and _specific_ gratifications, which were correlated slightly less strongly. 
 The adapted model fit our data comparatively well, `r fit_txt(fit_adapted)`.
 
-In the adapted privacy calculus model, we found that specific gratifications were positively related to self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`). 
+In the adapted privacy calculus model, specific gratifications were positively related to self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`). 
 Furthermore, people who deliberated more about their privacy disclosed less information (`r coeffs_txt(fit_adapted, "c1")`). 
@@
 Combining variables was not an option in our case, because both trust and expected benefits are theoretically distinct constructs.
-Because several variables were closely related to one another, in the end we therefore decided to fit a simple privacy calculus model, which contains only privacy concerns and specific gratifications.
+Because several variables were closely related to one another, we therefore decided to fit a simple privacy calculus model, which contains only privacy concerns and specific gratifications.
 
@@
 Second, people who reported more specific gratifications than others self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`). 
-Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, implying that the effects were sufficiently large to be relevant. 
-For a visual overview of all results, see Figure \@ref(fig:plot-pc).
+Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, which implies that the they were large enough to be theoretically relevant.
 
-```{r plot-pc, fig.cap="Predictors of self-disclosure. Displayed are the 95% CIs of the unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=4}
+When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (`r rsquare_fit_adapted * 100` %), followed by the preregistered model (`r rsquare_fit_prereg * 100` %), and the simple privacy calculus model (`r rsquare_fit_simple * 100` %).
+At the same time, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
+For a visual overview of all results, see Figure \@ref(fig:plotpc).
+
+```{r plotpc, fig.cap="Predictors of self-disclosure. Displayed are the 95\\% CIs of unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=4}
 print(fig_coeffs)
+# print(fig_fs_m)
 ```
-
-When comparing the three models with one another, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
 
@@
 
-In a next step, we analyzed the potential effects of the popularity cues on the privacy calculus. 
+In a next step, we analyzed the potential effects of the popularity cues. 
 Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables. 
@@
 
-The picture remained mostly the same also when analyzing variables that we did not include in the preregistration. 
+The picture remained the same also when analyzing variables not included in the preregistration. 
 Note that some differences missed statistical significance only marginally (e.g., specific gratifications for the comparison between the website with like buttons and the control website without like and dislike buttons).
-Nevertheless, we refrain from reading too much into the differences between the three websites and conclude that they were mostly similar regarding the privacy calculus variables and the amount of self-disclosure.
+Nevertheless, we refrain from reading too much into these differences and conclude that the three websites were comparable regarding the privacy calculus variables and the amount of self-disclosure.
 
@@
 
-In the bivariate analyses, all privacy calculus variables were shown to significantly predict self-disclosure. 
-In the preregistered analyses using multiple regression, in which several variables were analyzed together, self-efficacy was the strongest predictor of self-disclosure.
-All other variables were not significant, which is why the originally postulated extended privacy calculus model was not supported by the data.
-However, this preregistered model exhibited significant problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a more basal privacy calculus model, which included only privacy concerns and specific gratifications.
+In the bivariate analyses, all privacy calculus variables significantly predicted self-disclosure. 
+In the preregistered analyses using multiple regression, however, only self-efficacy significantly predicted self-disclosure.
+All other variables were not significant.
+The preregistered extended privacy calculus model was therefore not supported by the data.
+However, the model showed problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a more basal privacy calculus model, which included only privacy concerns and specific gratifications.
 
-The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy share less, people who expect more specific gratifications disclose more, and people who feel more self-efficacious disclose more.
-However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases, which seems implausible. 
+The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy disclose less, and that people who expect more specific gratifications and who feel more self-efficacious disclose more.
+However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases.
+This is theoretically implausible. 
 As a result, we also fit the above-mentioned simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure.
-Taken together, the results support the privacy calculus framework and suggest that self-disclosure online is not erratic and that it can be explained by various psychological variables.
+Taken together, the results support the privacy calculus framework and suggest that self-disclosure online is not erratic and that it can be explained by several psychological variables.
 
-Relatedly, the results suggest that in new communication contexts roughly one third of all Internet users actively deliberates about their privacy. 
+Aligned with this observation, the results also suggest that in new communication contexts at least one third of all Internet users _actively deliberates_ about their privacy. 
 Determining whether this figure is large or small is a normative question.
-For example, one can convincingly argue that this number should be higher and that we as society should still more actively deliberate about our self-disclosure practices online. 
+Because although substantial, one could argue that it should be higher and that we as society should still more actively deliberate about our self-disclosure practices online. 
 Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables.
@@
 
-The next major implication is that several scenarios and uses cases exist in which popularity cues do not seem to have an overly strong influence on the privacy calculus and self-disclosure. 
-Although some studies have found that popularity cues substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], in our study we found the opposite: 
+The next major implication is that popularity cues do not always seem to have a strong influence on the privacy calculus and self-disclosure.
+Although some studies have found that popularity cues can substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], in our study we found the opposite.
 Users still disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons, potentially highlighting the agency of users.
@@
 The results also have several more fine-grained implications. 
-First, we question the tendency to further increase the complexity of the privacy calculus model by adding additional variables [e.g., @dienlinExtendedPrivacyCalculus2016]. 
+First, one can question the tendency to further increase the complexity of the privacy calculus model by adding additional variables [e.g., @dienlinExtendedPrivacyCalculus2016]. 
 "Since all models are wrong the scientist cannot obtain a "correct" one by excessive elaboration.
@@
 792].
-Specifically, we have come to believe that adding self-efficacy to privacy calculus models is of limited value, for self-efficacy is mostly a self-reported proxy of behavior and offers little epistemic insight.
+Specifically, we have come to believe that adding self-efficacy to privacy calculus models is of limited value, because self-efficacy is often only a self-reported proxy of behavior offering little epistemic insight.
 Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to self-disclose whereas others do not. 
@@
 In general, we think that the topic of multicollinearity should receive more scholarly attention. 
-Interestingly, one can rightfully argue that multicollinearity is not actually a problem, but rather a warning sign. 
-From a _statistical_ perspective, when predictors are strongly correlated this only means that standard errors increase [@vanhoveCollinearityIsnDisease2019]. 
-In other words, when predictors are strongly correlated we can be less certain about the effects we obtain, because there is less variance [@vanhoveCollinearityIsnDisease2019]. 
-So to increase certainty researchers could compensate by collecting larger samples, which would allow to achieve sufficient statistical power. 
+Interestingly, multicollinearity might not even be a problem per se, but rather a helpful warning sign. 
+Because from a _statistical_ perspective, strongly correlated predictors only means increased standard errors [@vanhoveCollinearityIsnDisease2019]. 
+In other words, when predictors are strongly correlated we can be less certain about the effects we obtain, because there is less unique variance [@vanhoveCollinearityIsnDisease2019]. 
+As a remedy, researchers could simply collect larger samples, which would allow to achieve sufficient statistical power. 
 Fortunately, using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated/collinear predictors [@wangPowerAnalysisParameter2020].
@@
 From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
-It is our understanding that multiple regression is often used with the aim to isolate effects, to make sure that effects are not simply caused by another third variable.
+It is our understanding that multiple regression is often used with the aim to isolate effects, to make sure that they are not simply caused by another third variable.
 However, in cases of highly correlated measures this often does not make much sense theoretically.
-For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure, _while holding trust constant_.
+For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure _while holding trust constant_.
 Theoretically, however, it is more plausible to assume that increasing gratifications also fosters trust [@sollnerWhyDifferentTrust2016].
-In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant several variables such as gratifications, privacy concerns, privacy deliberations, and self-efficacy, measures which are all strongly correlated.
+In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy, measures which are all strongly correlated.
 In short, the effects we found could even be correct, but the interpretation is much more difficult, artificial, and thereby of little theoretical and practical value.
@@
 At first glance, this strong relation seemed somewhat peculiar to us. 
-On closer inspection, however, we realized that the way trust is routinely operationalized in the literature is very close to expected gratifications. 
+On closer inspection, however, we realized that the way trust is typically operationalized is remarkably close to expected gratifications. 
 To illustrate, the trust subdimension _ability_ includes items such as “The comments of other users were useful”. 
 In fact, in the literature trust is often operationalized as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016]. 
-In conclusion, our results suggest that we should not confuse _causes_ of trust with _measures_ of trust, for this might introduce problems of both homogeneity and/or multicollinearity.
-Instead, we recommend to measures general and reflective measures of trust, which are less closely related to expected gratifications.
+In conclusion, our results suggest that _causes_ of trust should not be confused with _measures_ of trust, for this might introduce problems of both homogeneity and/or multicollinearity.
+Instead, we recommend to use general and reflective measures of trust.
+<!-- , which are less closely related to expected gratifications. -->
 
@@
 First, all results are based on analyses of between-person variance. 
-However, between-person relations often do not translate well to within-person effects [e.g. @hamakerCritiqueCrosslaggedPanel2015]. 
-While some studies on privacy concerns online have begun to examine both sources of variance [e.g., @dietvorstAdolescentPerceptionsParental2017], finding that intrapersonal changes in privacy concerns are indeed related to intrapersonal changes in self-disclosure, similar analyses are still lacking for the privacy calculus.
+However, between-person relations often do not translate well to within-person effects [@hamakerCritiqueCrosslaggedPanel2015]. 
+While some studies on privacy concerns online have begun to examine both sources of variance, finding that intrapersonal changes in privacy concerns are indeed related to intrapersonal changes in self-disclosure [@dietvorstAdolescentPerceptionsParental2017], similar analyses are still lacking for the privacy calculus.
 
 Second, the self-reported measures were collected _after_ the field phase in which the dependent variable was measured. 
-As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior to reduce dissonance.
-Nevertheless, we deliberately decided to measure the self-reported variables afterward in order to not bias participants and not prime our specific research interest.
+As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.
+Nevertheless, we deliberately decided to measure the self-reported variables afterward in order not to bias participants or prime our research interest.
 
@@
 In this study, we explicitly manipulated the popularity cues. 
-However, as the experiment was conducted in the field, several other variables could not be held constant; for example, the content of communication by other users, the unfolding communication dynamics, or the characteristics of other users.
+However, because the experiment was conducted in the field several other variables could not be held constant.
+This includes the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
 As a result, the assumption of stable unit treatment was violated [@klinePrinciplesPracticeStructural2016].
@@
 It is important to note that our not having found significant effects of like and dislike buttons does not necessarily mean that like and dislike buttons do indeed have no effect on self-disclosure and the privacy calculus.
-As always, with null-findings one is confronted with the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely---states that null findings can either be due to an actual non-existence of effects or, instead, to a poor operationalization of the research question.
+Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely---states that null findings can either results from an actual non-existence of effects or, instead, from a poor operationalization of the research question.
 In this case, we were not able send participants notifications when their comments were liked/disliked, which significantly decreases the popularity cues' salience.
@@
 Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.
-Notably, we did not find any instances of people providing meaningless text and, as mentioned above, in times of big data, every piece of communication allows for increasingly accurate inferences about one's personality.
+Notably, we did not find any instances of people providing meaningless text.
+<!-- and, as mentioned above, in times of big data, every piece of communication allows for increasingly accurate inferences about one's personality. -->
 
@@
 
-While some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p. 1], in our opinion the privacy calculus is alive and kicking. 
-This study adds to the growing confirmation of observation that people who are more concerned about their privacy than others disclose less information online, whereas people who receive more gratifications from using a website than others disclose more information online.
-The results of this study suggest that a substantial share of internet users, approximately 30%, consciously engage in a privacy calculus by actively deliberating about whether or not to disclose information.
-The results thereby provide further evidence against the privacy paradox.
+While some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p. 1], we think that the privacy calculus is alive and kicking. 
+In this study, people who were more concerned about their privacy than others disclosed less information online, whereas people who received more gratifications from using a website than others disclosed more information online.
+In addition, the results suggest that a substantial share of internet users, approximately 30%, consciously engage in a privacy calculus by actively deliberating about whether or not to disclose information.
 Popularity cues such as like and dislike buttons seem to play only a minor role in this process, especially if no means are implemented to guarantee that users are notified about others liking or disliking their communication.
-In conclusion, our results indicate that internet users are at least somewhat proactive and reasonable---probably no more or less proactive or reasonable than in any other regular everyday situation.
+In conclusion, the results thereby provide further evidence against the privacy paradox.
+Internet users are at least somewhat proactive and reasonable---probably no more or less proactive or reasonable than in other everyday situations.
 

### 2020-04-08 analyses/analyses.Rmd
- ms: updates on methods, results, and discussion section

@@
 summary(fit_adapted, fit = TRUE, std = TRUE)
+rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
 ```
@@
      r_sesoi, r_sensitive, power_achieved,
+     rsquare_fit_prereg, rsquare_fit_adapted, rsquare_fit_simple,
      file = "data/workspace.RData"

### 2020-04-08 analyses/analyses.Rmd
- analyses: updated sec. "filter participants"

@@
 
-```{r include=F}
+```{r}
 # filter speeders
@@
 
-We've also inspected the data manually for cases with clear response patterns. The following cases show extreme response patterns, fast response times, and were hence removed.
-
-```{r include=F}
+We first inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.
+
+```{r}
 # identify response patterns

### 2020-04-09 manuscript/manuscript.RmD
- implementation of feedback from Niklas

@@
 author:            
-  - name          : "Author"
+  - name          : "Dienlin, Tobias"
+    email         : "tobias.dienlin@uni-hohenheim.de"
     affiliation   : "1"
     corresponding : yes
-    address       : "Postal address"
-    email         : "my@email.com"
+    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
+  - name          : "Braeunlich, Katharina"
+    email         : "braeunlich@uni-koblenz.de"
+    affiliation   : "2"
+  - name          : "Trepte, Sabine"
+    email         : "sabine.trepte@uni-hohenheim.de"
+    affiliation   : "1"
 affiliation:
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
-authornote: |
+    institution   : "University of Hohenheim"
+  - id            : "2"
+    institution   : "University of Koblenz-Landau"
+author_note: |
+  All authors contributed extensively to the work presented in this paper.
+TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.
+  The authors declare no competing interests.
+
+  This research was funded by the Volkswagen Foundation, project "Transformations of privacy", which was awarded to Sandra Seubert, Sabine Trepte, Ruediger Grimm, & Christoph Gusy.
+We would like to thank all our colleagues from the project and Niklas Johannes for valuable feedback.
+
+  This manuscript features online supplementary material, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0).
 abstract: |
     According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
-So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual authentic behavior.
-Likewise, we still know comparatively little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
+So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior.
+Likewise, we still know little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
 To answer these questions, we ran a preregistered one-week field experiment.
@@
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
-Although the originally preregistered model could not be confirmed, the results showed that the privacy calculus variables predicted a considerable share of actual self-disclosure.
-The impact of popularity cues was negligible.
-In conclusion, the results indicate that self-disclosure online can be explained by privacy concerns and specific gratifications.
-This finding has several implications.
-For example, it provides further evidence against the privacy paradox.
+Although the originally preregistered model could not be confirmed, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
+The impact of the popularity cues on self-disclosure and the privacy calculus was negligible.
+In conclusion, the results suggest that privacy concerns and expected benefits are relevant when it comes to understanding self-disclosure, which together provides further evidence against the privacy paradox.
 keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
@@
 linenumbers       : yes
-mask              : yes
+mask              : no
 wordcount         : "`r wordcountaddin::word_count('../manuscript/manuscript.Rmd')`"
@@
 
-Understanding why people disclose personal information online remains a critical question for both society and academic research. 
-Originally, self-disclosure online was thought to be mostly erratic.
-For example, it was assumed that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints. 
+Understanding why people disclose personal information online remains a critical question for both society and research. 
+Originally, it was claimed that self-disclosure is mostly erratic, and that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints. 
 Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
@@
 Hence, rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called _privacy-calculus_ [@lauferPrivacyConceptSocial1977], which states that self-disclosure online can be explained---at least partly---by means of expected risks *and* expected benefits [@krasnovaOnlineSocialNetworks2010].
-Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
+Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information online, whereas expecting benefits is related to disclosing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
-However, although the privacy calculus has gained some momentum in academic research several important questions remain unanswered. 
-First, we still know comparatively little about whether the privacy calculus can be replicated with actual behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
+However, although the privacy calculus has gained some momentum in academic research, several important questions remain unanswered. 
+First, we still know little about whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
 Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020].
-However, all three of these approaches have reduced external validity.
+However, all three of these approaches have low external validity.
 As a result, in this study we analyze actual information sharing behavior in an authentic online setting.
@@
 We agree.
-In this study, we hence explicitly focus on the privacy deliberation process itself. 
-Moreover, and on a more general level, we explore the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-efficacy.
+In this study, we therefore explicitly focus on the privacy deliberation process. 
+Related, and on a more general level, we explore the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-efficacy.
 
@@
 
-Being a primary means of regulating privacy [e.g., @masurSituationalPrivacySelfdisclosure2018], self-disclosure is our key variable of interest. 
-There are two different understandings of self-disclosure in the literature: The first defines self-disclosure as _deliberate_ acts of sharing truthful information about the self with others [@jourardTransparentSelf1964].
-The second considers _all_ acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information shared allows for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011].
-In this paper we follow the latter approach, not least because the recent years have vividly illustrated how easy it is to derive personal insights simply by analyzing exchanged communication [@kosinskiPrivateTraitsAttributes2013].
-Moreover, independent from which position one chooses to adopt, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000].
+Self-disclosure is a primary means of regulating privacy [e.g., @masurSituationalPrivacySelfdisclosure2018].
+It is our key variable of interest.
+There are two different understandings of self-disclosure in the literature: 
+The first defines self-disclosure as _deliberate_ acts of sharing truthful information about the self with others [@jourardTransparentSelf1964]. 
+The second considers _all_ acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information allows for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011].
+In this paper we follow the latter approach, not least because the recent years have illustrated how easy it is to derive personal insights simply by analyzing exchanged communication [@kosinskiPrivateTraitsAttributes2013].
+Moreover, independent from which position one adopts, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000].
 In this study we mainly focus on communication quantity, as we consider communication quantity to be a necessary precondition and hence valid proxy for self-disclosure.
@@
 Privacy concerns have been defined as follows: 
-"Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [AUTHOR].
-Previous research has found that people who are more concerned about their privacy than others are less likely to share personal information [@baruhOnlinePrivacyConcerns2017; @dienlinPrivacyParadoxRelic2015; @heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
+"Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [@dienlinLongitudinalAnalysisPrivacy2019, p.
+6].
+Previous research has found that people who are more concerned about their privacy than others are less likely to share personal information [@baruhOnlinePrivacyConcerns2017; @heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
@@
 
-Although privacy concerns are related to self-disclosure, one can make the case that since most studies in the literature report only small effects there should also be additional meaningful factors that contribute to explaining self-disclosure.
+Although privacy concerns are related to self-disclosure, one can argue that most studies report only small effects, and that there should be additional factors that also contribute to explaining self-disclosure.
 Most prominently, it has been argued that people trade a loss of privacy for a gain in gratifications such as social capital, entertainment, information, or self-presentation [@ellisonNegotiatingPrivacyConcerns2011; @taddickenUsesPrivacyOnline2011].
@@
 
-As mentioned above, there is still a shortage of studies that explicitly analyze the decision process behind the disclosing of information, although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017].
+As mentioned above, there is still a shortage of studies that explicitly analyze the decision process behind the disclosing of information---although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017].
 This criticism is justified.
-The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not a sufficient condition for an explicit weighing process.
+The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient evidence for an explicit weighing process.
 Hence, research on the privacy calculus would benefit significantly from analyzing this decision process explicitly. 
@@
 In this vein, it seems plausible that popularity cues might also impact the privacy calculus [@kramerMasteringChallengeBalancing2020].
-First, popularity cues could serve as a means of reward and punishment, affecting behavior via instrumental conditioning [@skinnerScienceHumanBehavior2014]. 
+First, popularity cues could serve as a means of reward and punishment. 
 Being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit disclosure. 
@@
 Participants used the website actively: Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(60) %>% round(0) %>% format(big.mark = ",")` minutes online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and left `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
+Notably, we did not find any instances of people providing meaningless text. 
 For an example of communication that took place, see Figure \@ref(fig:comments).
@@
 This means that our study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
-Put differently, we were able to make reliable inferences about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
+Put differently, we were able to make reliable inferences (i.e., power = 95%) about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
 
@@
 We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less then three minutes, which we considered to be unreasonably fast. 
-To detect corrupt data, we calculated Cook's distance. 
-We excluded `r n_resp_pattern` participants because they provided clear response patterns. 
+To detect potentially corrupt data, we calculated Cook's distance.[^note]
+We excluded `r n_resp_pattern` participants because they provided clear response patterns (i.e., straight-lining). 
 The final sample included `r n_final` participants.
@@
 <!-- Despite the dropout and although somewhat higher-educated, also T2 can hence be considered a largely representative sample of the German population. -->
+
+[^note]: We preregistered to delete participants with less than 6 minutes answer time.
+However, this led to the exclusion of too many data points of high quality, which is why we relaxed this criterion.
+In the OSM, we report the results using all participants.
 
@@
 _Specific gratifications_ were measured with 15 items on five different subdimensions with three items each. 
-The scaled was loosely based on @schererGratifikationMinuteZeitnahe2002.
+The scaled was based on @schererGratifikationMinuteZeitnahe2002.
 Example items were: "Using the participation platform made it possible for me to" ...
@@
 Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability).
-The results showed that the provider and website targets were not sufficiently distinct, as was evidenced a Heywood case. 
+The results showed that the provider and website targets were not sufficiently distinct, as was evidenced by a Heywood case. 
 We hence adapted the scale to combine these two targets. 
@@
 The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
-The sum of words and likes/likes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already said.
+The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already said.
 
@@
 
-All hypotheses and research questions were tested using structural equation modeling. 
+All hypotheses and research questions were tested using structural equation modeling with latent variables. 
 The influence of the three websites was analyzed using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016].
@@
 
-First, we ran a model as specified in the preregistration. The model fit our data comparatively well, `r fit_txt(fit_prereg, scaled = TRUE)`. 
+First, we ran a model as specified in the preregistration. The model fit our data okay, `r fit_txt(fit_prereg, scaled = TRUE)`. 
 Regarding H1, we did not find that general gratifications predicted self-disclosure (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
-With regard to H2, privacy concerns did not predict self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
-RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`). 
+With regard to H2, privacy concerns did not significantly predict self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
+RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`; two-sided). 
 Regarding H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided). 
@@
 In the adapted privacy calculus model, specific gratifications were positively related to self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`). 
-Furthermore, people who deliberated more about their privacy disclosed less information (`r coeffs_txt(fit_adapted, "c1")`). 
-Self-efficacy remained substantially correlated with self-disclosure (`r coeffs_txt(fit_adapted, "d1")`). 
-However, we again found a negative correlation between trust and self-disclosure (`r coeffs_txt(fit_adapted, "e1")`), which again implies multicollinearity.
+Furthermore, people who deliberated more about their privacy disclosed less information (`r coeffs_txt(fit_adapted, "c1")`; two-sided). 
+Self-efficacy remained substantially correlated with self-disclosure (`r coeffs_txt(fit_adapted, "d1")`; two-sided). 
+However, we again found a negative correlation between trust and self-disclosure (`r coeffs_txt(fit_adapted, "e1")`; two-sided), which again implies multicollinearity.
 
@@
 The simple model fit our data well, `r fit_txt(fit_simple)`. 
-First, we found that people who experienced more privacy concerns than others disclosed less information (`r coeffs_txt(fit_simple, "a1")`). 
-Second, people who reported more specific gratifications than others self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`). 
+First, we found that people who experienced more privacy concerns than others disclosed less information (`r coeffs_txt(fit_simple, "a1")`; two-sided). 
+Second, people who reported more specific gratifications than others self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`; two-sided). 
 Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, which implies that the they were large enough to be theoretically relevant.
@@
 We additionally asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons. 
-The data came from a representative sample of the German population and were analyzed using structural equation modeling.
+The data came from a representative sample of the German population and were analyzed using structural equation modeling with latent variables.
 
@@
 Determining whether this figure is large or small is a normative question.
-Because although substantial, one could argue that it should be higher and that we as society should still more actively deliberate about our self-disclosure practices online. 
+Because although the effect is substantial, one could argue that it should be higher and that we as society should still more actively deliberate about our self-disclosure practices online. 
 Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables.
@@
 
-In general, we think that the topic of multicollinearity should receive more scholarly attention. 
 Interestingly, multicollinearity might not even be a problem per se, but rather a helpful warning sign. 
-Because from a _statistical_ perspective, strongly correlated predictors only means increased standard errors [@vanhoveCollinearityIsnDisease2019]. 
+Because from a _statistical_ perspective, strongly correlated predictors only mean that standard errors become larger [@vanhoveCollinearityIsnDisease2019]. 
 In other words, when predictors are strongly correlated we can be less certain about the effects we obtain, because there is less unique variance [@vanhoveCollinearityIsnDisease2019]. 
@@
 
-Third, in experiments we should manipulate only the experimental variable while holding all others constant. 
+Third, the assumption of stable unit treatment states that in experiments we should manipulate only the experimental variable while holding all others constant [@klinePrinciplesPracticeStructural2016].
 In this study, we explicitly manipulated the popularity cues. 
@@
 This includes the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
-As a result, the assumption of stable unit treatment was violated [@klinePrinciplesPracticeStructural2016].
+As a result, the assumption of stable unit treatment was violated.
 
-It is important to note that our not having found significant effects of like and dislike buttons does not necessarily mean that like and dislike buttons do indeed have no effect on self-disclosure and the privacy calculus.
-Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely---states that null findings can either results from an actual non-existence of effects or, instead, from a poor operationalization of the research question.
+Although we did not find significant effects of like and dislike buttons in this study, this does not necessarily mean that they have no effect on self-disclosure and the privacy calculus in general.
+Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely---states that null findings can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question.
 In this case, we were not able send participants notifications when their comments were liked/disliked, which significantly decreases the popularity cues' salience.
@@
 Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.
-Notably, we did not find any instances of people providing meaningless text.
 <!-- and, as mentioned above, in times of big data, every piece of communication allows for increasingly accurate inferences about one's personality. -->
@@
 
-While some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p. 1], we think that the privacy calculus is alive and kicking. 
+Whereas some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p. 1], we think that the privacy calculus is alive and kicking. 
 In this study, people who were more concerned about their privacy than others disclosed less information online, whereas people who received more gratifications from using a website than others disclosed more information online.
@@
 In conclusion, the results thereby provide further evidence against the privacy paradox.
-Internet users are at least somewhat proactive and reasonable---probably no more or less proactive or reasonable than in other everyday situations.
+Internet users are at least somewhat proactive and reasonable---maybe no more or less proactive or reasonable than in other everyday situations.
 

### 2020-04-17 docs/analyses/analyses.Rmd
- initalize GitHubPages

--- 2020-04-08 analyses/analyses.Rmd
@@
     toc_depth: 2
+    keep_md: true
 ---
@@
 
-```{r}
+```{r eval=F}
 cooks_dis <- gCD(d, model_baseline)
@@
 
-```{r}
+```{r eval=F}
 infl_cases <- invisible(rownames(print(cooks_dis)))
@@
 
-```{r}
+```{r eval=F}
 infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
@@
      n_users, n_final,
-     infl_cases, infl_cases_tokens, resp_pattern, n_resp_pattern,
+     # infl_cases, infl_cases_tokens, 
+     resp_pattern, n_resp_pattern,
      n_t1, age_t1_m, male_t1_m, college_t1_m,

### 2020-04-17 docs/analyses/analyses_additional.Rmd
- initalize GitHubPages

---
title: "How Do Like and Dislike Buttons Affect Communication?"
shorttitle : "Additional Analyses"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
---

```{r setup, include=F}
knitr::opts_chunk$set(
  cache=T, comment=NA, warning=F, echo=F, error=F, 
  message=F, prompt=F, tidy=T, fig.height=4
  )
options(digits = 3, width = 120)
```

```{r r-setup, include=F}
# define packages
packages <- c("cowplot", "devtools", "faoutlier", "GGally", "kableExtra",
              "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", "quanteda",
              "semTools", "tidyverse")

# load packages
lapply(packages, library, character.only = TRUE, quietly = TRUE)
```

```{r Data-Wrangling, include=F}
# load workspace
load("data/workspace.rdata")
```

# VIF

In what follows, you can find estimations of variance inflation factors to gauge multicollinearity. Generally, values above 5 or even 10 are considered problematic. However, these are only rules of thumb, and multcollinearity can occour with lower values. Indeed, although the values reported below are not above 5, they are increased, suggesting that multicollinearity might be at play here, which the regular analyses also confirm.

```{r vif, include=F}
# Self-Efficacy
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

self_eff ~ pri_con + grats_gen + pri_delib + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_self_eff <- inspect(fit, what = "rsquare")["self_eff"] # extract rsquare
vif_self_eff <- 1 / (1 - r_self_eff) # compute vif

# Privacy Deliberation
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_delib ~ self_eff + pri_con + grats_gen + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_pri_delib <- inspect(fit, what = "rsquare")["pri_delib"]
vif_pri_delib <- 1 / (1 - r_pri_delib)

## Privacy Concerns
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con ~ self_eff + pri_delib + grats_gen + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_pri_con <- inspect(fit, what = "rsquare")["pri_con"]
vif_pri_con <- 1 / (1 - r_pri_con)

# Gratifications
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

grats_gen ~ self_eff + pri_con + pri_delib + trust_spec

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_grats_gen <- inspect(fit, what = "rsquare")["grats_gen"]
vif_grats_gen <- 1 / (1 - r_grats_gen)

# Trust
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
SE01_01 ~~ a*SE01_02
SE01_03 ~~ a*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

trust_spec ~ self_eff + pri_con + grats_gen + pri_delib

# Covariates
GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
r_trust_spec <- inspect(fit, what = "rsquare")["trust_spec"]
vif_trust_spec <- 1 / (1 - r_trust_spec)
```

```{r}
# Table
tibble("Gratifications" = vif_grats_gen, "Trust Specific" = vif_trust_spec, "Privacy Concerns" = vif_pri_con, "Privacy Deliberation" = vif_pri_delib, "Self-Efficacy" = vif_self_eff) %>% 
  kable() %>% 
  kable_styling("striped")
```

# Additional analyses

In what follows, you can find slightly different models that were also run.

## Privacy calculus
### Model 1

Building on the Model "Adapted", we now remove the variable `Trust General`.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

Interestingly, now almost all effects disappear.

### Model 2

Here, we combine both privacy measures into a single one. Likewise, we combine both gratifications and trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
pri_cau =~ pri_con + pri_delib
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
grats_meta =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext + trust_community + trust_provider
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
self_dis_log ~ a1*pri_cau + b1*grats_meta + c1*self_eff

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

### Model 3

Here, we combine both privacy measures into a single one. Likewise, we combine both gratifications and trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
pri_cau =~ pri_con + pri_delib
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
grats_meta =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext + trust_community + trust_provider
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
self_dis_log ~ a1*pri_cau + b1*grats_meta + c1*self_eff

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

### Model 4

We now use also delete self-efficacy.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
pri_cau =~ pri_con + pri_delib
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
grats_meta =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext + trust_community + trust_provider
self_dis_log ~ a1*pri_cau + b1*grats_meta

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

### Model 5

Here, we exchange specific gratitudes for general gratitudes.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05

self_dis_log ~ a1*pri_con + b1*grats_gen

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit, fit = TRUE, std = TRUE)
```

## Effect of popularity cues
### Like vs. control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con ~ a1*lik_ctrl
grats_spec ~ a2*lik_ctrl
self_dis_log ~ b1*pri_con + b2*grats_spec + c1*lik_ctrl

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_lik_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_lik_ctrl_simple, fit = TRUE, std = TRUE)
```

### Like & dislike vs. control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con + grats_spec ~ likdis_ctrl
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_ctrl

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_likdis_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_likdis_ctrl_simple, std = TRUE)
```

### Like & dislike vs. like

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

pri_con + grats_spec ~ likdis_lik
self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_lik

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
summary(fit_likdis_lik, std = TRUE, fit = TRUE)
```

# Results without covariates

As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain the same.

## Privacy calculus
### Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
"
fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
```

### Model "Adapted"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
"
fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

### Model "Simple"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

self_dis_log ~ a1*pri_con + b1*grats_spec
"
fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
```

## Effects of popularity cues
### Preregistered
#### Like vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
"
fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
"
fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Like

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
"

fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
summary(fit_likdis_lik, fit = TRUE, std = TRUE)
```

# Results including removed participants

As stated in the preregistration, we also report the analyses including the deleted participants. Results don't change meaningfully.

## Privacy calculus
### Model "Peregistered"

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_prereg <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_prereg, fit = TRUE, std = TRUE)
```

### Model "Adapted"

Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_gen =~ TR01_01 + TR01_05 + TR01_09

self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_adapted <- sem(model, data = d_all, estimator = "MLR", missing = "ML", missing = "ML")
summary(fit_adapted, fit = TRUE, std = TRUE)
```

### Model "Simple"

We now use only variables, that is specific gratifications and privacy concerns.

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
grats_inf =~ GR01_01 + GR01_02 + GR01_03 
grats_rel =~ GR01_04 + GR01_05 + GR01_06 
grats_par =~ GR01_07 + GR01_08 + GR01_09
grats_ide =~ GR01_10 + GR01_11 + GR01_12 
grats_ext =~ GR01_13 + GR01_14 + GR01_15
grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext

self_dis_log ~ a1*pri_con + b1*grats_spec

# Covariates
self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
"
fit_simple <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
summary(fit_simple, fit = TRUE, std = TRUE)
```

## Effects of popularity cues
### Preregistered

#### Like vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*lik_ctrl

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d_all, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Control

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_spec =~ trust_spec_fs

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*likdis_ctrl

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"
fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
```

#### Like & Dislike vs. Like

```{r}
model <- "
pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
  SE01_01 ~~ x*SE01_02
  SE01_03 ~~ x*SE01_04
trust_community =~ TR01_02 + TR01_03 + TR01_04
trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
trust_spec =~ trust_community + trust_provider

pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*likdis_lik

# Covariates
self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
"

fit_likdis_lik <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
summary(fit_likdis_lik, fit = TRUE, std = TRUE)
```

### 2020-04-17 docs/data/items.rmd
- initalize GitHubPages

--- 2020-04-08 analyses/analyses.Rmd
@@
 title: "How Do Like and Dislike Buttons Affect Communication?"
-shorttitle : "Analyses"
+subtitle: "List of Items"
 output: 
-  html_document:
+  pdf_document:
     toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+    toc_depth: 3
 ---
 
-```{r setup, include=F}
-knitr::opts_chunk$set(
-  cache=T, comment=NA, warning=F, echo=F, error=F, 
-  message=F, prompt=F, tidy=T, fig.height=4
-  )
-options(digits = 3, width = 120)
-```
+\newpage
 
-```{r r-setup, include=F}
-# define packages
-packages <- c("cowplot", "devtools", "faoutlier", "GGally", "gganimate",
-              "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
-              "quanteda", "semTools", "tidyverse")
+# Response format
 
-# install packages # uncomment lines to install packages
-# devtools::install_github("tdienlin/td@v.0.0.2.3")
-# lapply(packages, install.packages, character.only = T, quietly = TRUE)
+All items were measured on a 7-point scale with Likert-response format. Answers ranged between:
 
-# load packages
-lapply(packages, library, character.only = TRUE, quietly = TRUE)
-library(td)
-```
+ - &nbsp;-3   completely disagree
+ - &nbsp;-2   disagree
+ - &nbsp;-1   slightly disagree
+ - &nbsp;&nbsp;0   neutral
+ - +1   slightly agree
+ - +2   agree
+ - +3   strongly agree
 
-```{r Data-Wrangling, include=F}
-# load data
-# please note that in a prior step several different data sets were merged using information such as case_taken or IP-addresses.
-To guarantee the privacy of the participants, these data were deleted after merging.
-d_raw <- read_csv("data/data_raw.csv")
+All items were translated from German.
 
-# recode variables
-d <- d_raw %>% 
-  dplyr::rename(
-    "male" = "SD01", 
-    "age" = "SD02_01", 
-    "state" = "SD03", 
-    "edu_fac" = "SD04"
-    ) %>% 
-  mutate(
-
-    #general
-    version = factor(.$VE01_01, labels = c("Control", "Like", "Like & Dislike")),
-    version_no = recode(version, "Control" = 1, "Like" = 2, "Like & Dislike" = 3),
-    male = replace_na(.$male, "[3]") %>% dplyr::recode(., "männlich [1]" = 1, "weiblich [2]" = 0),
-    age_grp = cut(.$age, 
-                  breaks = c(0, 29, 39, 49, 59, 100), 
-                  labels = c("<30", "30-39", "40-49", "50-59", ">59")),
-
-    # contrasts
-    lik_ctrl = recode(version, "Control" = 0, "Like" = 1),
-    lik_ctrl = na_if(lik_ctrl, "Like & Dislike"),
-    likdis_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
-    likdis_ctrl = na_if(likdis_ctrl, "Like"),
-    likdis_lik = recode(version, "Like" = 0, "Like & Dislike" = 1),
-    likdis_lik = na_if(likdis_lik, "Control"),
-    likdislik_ctrl = recode(version, "Control" = 0, "Like & Dislike" = 1),
-    likdislik_ctrl = na_if(likdislik_ctrl, "Like"),
-
-    # recode
-    edu = recode(edu_fac, 
-                 "Hauptschulabschluss/Volksschulabschluss" = 1, 
-                 "Noch Schüler" = 1,
-                 "Realschulabschluss (Mittlere Reife)" = 1,
-                 "Abschluss Polytechnische Oberschule 10. Klasse (vor 1965: 8. Klasse)" = 1,
-                 "Anderer Schulabschluss:" = 1,
-                 "Fachhochschulreife (Abschluss einer Fachoberschule)" = 2,
-                 "Abitur, allgemeine oder fachgebundene Hochschulreife (Gymnasium bzw. EOS)" = 2,
-                 "Hochschulabschluss" = 3),
-    PC01_03 = 8 - PC01_03, 
-    SE01_05 = 8 - SE01_05, 
-    SE01_06 = 8 - SE01_06,
-
-    # behavioral data
-    words = replace_na(.$words, 0),
-    self_dis = words + (reactions * 2),
-    time_read_MIN = time_read / 60,
-    time_sum_min_t2 = TIME_SUM_t2 / 60,
-
-    # take logarithm
-    posts_log = log1p(.$post_count),
-    time_log = log1p(.$time_read), 
-    posts_read_count_log = log1p(.$posts_read_count),
-    words_log = log1p(.$words),
-    self_dis_log = log1p(self_dis)
-  )
-```
-
-```{r include=F}
-# sample descriptives t1
-n_t1 <- nrow(d)
-age_t1_m <- mean(d$age, na.rm = TRUE)
-male_t1_m <- mean(d$male, na.rm = TRUE)
-college_t1_m <- table(d$edu)[3] / n_t1
-
-# sample descriptives t2
-n_t2 <- filter(d, !is.na(id_survey_t2)) %>% nrow()
-age_t2_m <- filter(d, !is.na(id_survey_t2))$age %>% mean()
-male_t2_m <- filter(d, !is.na(id_survey_t2))$male %>% mean(na.rm = TRUE)
-college_t2_m <- filter(d, !is.na(id_survey_t2))$edu %>% table() %>% .[3] / n_t2
-
-# descriptives users
-n_users <- filter(d, !is.na(post_count)) %>% nrow()
-
-# characteristics of posts
-n_comments <- sum(d$post_count, na.rm = TRUE)
-n_words <- sum(d$words, na.rm = TRUE)
-n_time <- sum(d$time_read_MIN, na.rm = TRUE)
-n_posts <- sum(d$post_count, na.rm = TRUE)
-
-# filter unmatched cases
-d <- filter(d, !is.na(post_count) & !is.na(id_survey_t2))  # Use only completes
-n_matched <- nrow(d)
-
-# save data file with all participants to compare results
-d_all <- d
-
-# variable labels
-var_names <- c("Privacy concerns", 
-               "General gratifications", 
-               "Specific gratifications",
-               "Privacy deliberation", 
-               "Self-efficacy", 
-               "General trust", 
-               "Specific trust",
-               "Self-disclosure")
-
-var_names_breaks <- c("Privacy\nconcerns", 
-                      "General\ngratifications", 
-                      "Specific\ngratifications",
-                      "Privacy\ndeliberation", 
-                      "Self-\nefficacy", 
-                      "General\ntrust", 
-                      "Specific\ntrust",
-                      "Self-\ndisclosure")
-```
-
-# Filter Participants
-
-```{r}
-# filter speeders
-time_crit <- 3 # minimum time on survey
-n_speeding <- nrow(filter(d, time_sum_min_t2 < time_crit))
-d <- filter(d, time_sum_min_t2 >= time_crit) # Deletion of fast respondents
-```
-
-We first inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.
-
-```{r}
-# identify response patterns
-resp_pattern <- c(
-  "ANIEVLK9F2SW", "BN4MAOWZO7W2"  # clear response pattern
-  )
-n_resp_pattern <- length(resp_pattern)
-# infl_cases_tokens <- infl_cases_tokens[!infl_cases_tokens %in% resp_pattern]
-
-d %>% 
-  filter(case_token %in% resp_pattern) %>% 
-  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
-  kable() %>% 
-  kable_styling("striped") %>% 
-  scroll_box(width = "100%")
-d %<>% filter(!case_token %in% resp_pattern)
-
-# sample descriptives final data set
-n_final <- nrow(d)
-age_final_m <- mean(d$age)
-male_final_m <- mean(d$male, na.rm = TRUE)
-college_final_m <- table(d$edu)[[3]] / n_final
-```
-
-# Measures
-## Privacy concerns
-### Items
+# Privacy concerns
 
@@
 
-### Distributions
-
-```{r}
-ggplot(gather(select(d, starts_with("PC01"))), 
-                      mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=1) + 
-  theme_bw()
-
-des_pricon <- select(d, starts_with("PC01")) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
-
-### CFA
-
-```{r}
-name <- "pricon"
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_03 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-Shows that PC01_03 doesn't load well.
-As it's an inverted item that's not surprising.
-Also from a theoretic perspective it's suboptional, because it doesn't explicitly focus on privacy, but just concerns in general.
-Will be deleted.
-
-### CFA 2
-
-```{r}
-name <- "pricon"
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-## Gratifications general
-### Items
+# Gratifications general
 
@@
 
-### Distributions
-
-```{r}
-ggplot(gather(select(d, starts_with("GR02"))), 
-       mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=1) + 
-  theme_bw()
-
-des_grats_gen <- select(d, starts_with("GR02")) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
-
-### CFA
-
-```{r}
-name <- "grats_general"
-model <- "
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-## Gratifications specific
-### Items
+# Gratifications specific
 
@@
 
-### Distributions
-
-```{r fig.height=6}
-ggplot(gather(select(d, starts_with("GR01"))), 
-       mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=2) + 
-  theme_bw()
-
-des_grats_spec <- select(d, starts_with("GR01")) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
-
-### CFA
-
-```{r}
-name <- "grats_specific"
-model <- "
-  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-  grats_par =~ GR01_07 + GR01_08 + GR01_09
-  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-  grats_ext =~ GR01_13 + GR01_14 + GR01_15
-  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-## Privacy deliberation
-### Items
+# Privacy deliberation
 
@@
 
-### Distributions
-
-```{r}
-ggplot(gather(select(d, starts_with("PD01"))), 
-       mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=1) + 
-  theme_bw()
-
-des_pridel <- select(d, starts_with("PD01")) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
-
-### CFA
-
-```{r}
-name <- "pridel"
-model <- "
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-## Trust general
-### Items
+# Trust general
 
@@
 
-### Distributions
-
-```{r}
-ggplot(gather(select(d, TR01_01, TR01_05, TR01_09)), 
-       mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=1) + 
-  theme_bw()
-
-des_trust_gen <- select(d, TR01_01, TR01_05, TR01_09) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
-
-### CFA
-
-```{r}
-name <- "trust_gen"
-model <- "
-trust =~ TR01_01 + a*TR01_05 + a*TR01_09
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-Note that we constrained Items 5 and Item 9 to be equal.
-Explanation: First, they are theoretically related.
-Second, not constraining would yield to just-identified model, for which model fit cannot be interpreted meaningfully.
-
-## Trust specific
-### Items
+# Trust specific
 
@@
 
-### Distributions
-
-```{r}
-ggplot(gather(select(d, TR01_02:TR01_04, TR01_06:TR01_08, TR01_10:TR01_12)), 
-       mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=1) + 
-  theme_bw()
-
-des_trust_spec <- select(d, TR01_02:TR01_04, TR01_06:TR01_08, TR01_10:TR01_12) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
-
-### CFA
-
-```{r}
-name <- "trust_spec"
-model <- "
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08
-trust_system =~ TR01_10 + TR01_11 + TR01_12
-
-trust =~ trust_community + trust_provider + trust_system
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r warning=T}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-### CFA 2
-
-Because there was Heywoodcase, we now also run a model in which the subdimensions `provider` and `system` are combined.
-
-```{r}
-name <- "trust_spec"
-model <- "
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust =~ b*trust_community + b*trust_provider
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-Warning disappears, results show adequate fit.
-
-## Self-efficacy
-### Items
+# Self-efficacy
 
@@
  3. In terms of the topic, I felt competent enough to express my opinion.
- 4. I found it easy to express my opinion regarding the topic.
+ 4. I found the topic too difficult to express my opinion.
  5. I found it complicated to write a comment.
@@
 
-### Distributions
+# Self-disclosure
 
-```{r}
-ggplot(gather(select(d, starts_with("SE01"))), 
-       mapping = aes(x = value)) +
-  geom_bar() +
-  facet_wrap(~key, nrow=1) + 
-  theme_bw()
+Let us assume that the participation platform would continue to exist in the future. Please indicate to what extent you agree with the following statements:
 
-des_selfeff <- select(d, starts_with("SE01")) %>% 
-  apply(1, mean, na.rm = TRUE) %>% 
-  as.data.frame() %>% 
-  summarise(m = mean(., na.rm = TRUE), sd = sd(., na.rm = TRUE))
-```
+In the future, I am willing to ...
 
-### CFA
-
-```{r}
-name <- "self-eff"
-model <- "
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04 + SE01_05 + SE01_06
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-Shows significant misfit. We will delete inverted items, while allowing covariations between Items 1 and 2 (tech-oriented) and Items 3 and 4 (topic-oriented).
-
-### CFA 2
-
-```{r}
-name <- "selfeff"
-model <- "
-self_eff_pos =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-SE01_01 ~~ x*SE01_02
-SE01_03 ~~ x*SE01_04
-"
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
-```
-
-Model fit:
-
-```{r}
-(factor_val <- fit_tab(fit, reliability = TRUE, scaled = TRUE))
-assign(paste0(name, "_factor_val"), factor_val)
-```
-
-Factor loadings:
-
-```{r}
-inspect(fit,what="std")$lambda
-```
-
-Adapted version shows better and adequate fit.
-
-## Baseline model
-
-In what follows, please find the results of all variables combined in one model. This model will be used to extract factor scores.
-
-```{r}
-model_baseline <- "
-  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-  grats_par =~ GR01_07 + GR01_08 + GR01_09
-  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-  grats_ext =~ GR01_13 + GR01_14 + GR01_15
-  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-  trust_gen =~ TR01_01 + TR01_05 + TR01_09
-  trust_community =~ TR01_02 + TR01_03 + TR01_04
-  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-  trust_spec =~ trust_community + trust_provider
-  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-    SE01_01 ~~ x*SE01_02
-    SE01_03 ~~ x*SE01_04
-  self_dis_lg =~ self_dis_log
-
-  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
-"
-fit_baseline <- sem(model_baseline, data = d, missing = "ML")
-summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
-```
-
-# Descriptive analyses
-
-We first report the factor validity of all variables combined.
-
-```{r}
-# extract model predicted values for items & calc means
-d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
-  as.data.frame() %>% 
-  mutate(version = d$version, 
-         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
-         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
-         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
-         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
-         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
-         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
-         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
-  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)
-
-# combine d with d factor scores
-d %<>% cbind(select(d_fs, -version, -self_dis_log))
-
-# rename for plotting
-d_fs %<>% set_names(c("version", var_names_breaks))
-
-# means of model predicted values
-des <- rbind(des_pricon,
-             des_grats_gen,
-             des_grats_spec,
-             des_pridel,
-             des_selfeff,
-             des_trust_gen,
-             des_trust_spec)
-
-factor_val_tab <- rbind(pricon_factor_val,
-                        grats_general_factor_val,
-                        grats_specific_factor_val,
-                        pridel_factor_val,
-                        selfeff_factor_val,
-                        trust_gen_factor_val,
-                        trust_spec_factor_val) %$%
-  cbind(des[-8, ], .) %>%
-  set_rownames(var_names[-8]) %T>%
-  print()
-```
-
-In what follows, we report zero-order correlations, distributions, and scatterplots of the variables' factor scores.
-
-```{r zds, fig.height=8, fig.width=8}
-fig_fs_cor <- ggpairs(
-  select(d_fs, -version),
-  upper = list(continuous = "cor"),
-  lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) +
-  theme_bw()
-print(fig_fs_cor)
-```
-
-# Power analyses
-
-```{r pwr-criteria, include=F}
-z_crit <- 1.96
-alpha <- .05
-power_desired <- .95
-r_sesoi <- .10
-```
-
-We first estimate the sample size necessary to find small effects in 95% of all cases.
-
-```{r pwr-samplesize}
-pwr.r.test(r = r_sesoi, sig.level = alpha, power = power_desired, alternative = "greater") %T>%
-  print %$% 
-  n %>% 
-  round(0) ->
-  n_desired
-```
-
-We then compute the power we have achieved with our finale sample size to detect small effects.
-
-```{r pwr-achieved}
-pwr.r.test(n = n_final, r = r_sesoi, sig.level = alpha, alternative = "greater") %T>%
-  print %$% 
-  power %>% 
-  round(2) ->
-  power_achieved
-```
-
-We finally compute what effect size we are likely to find in 95% of all cases given our final sample size.
-
-```{r pwr-sensitivity}
-pwr.r.test(n = n_final, power = power_desired, sig.level = alpha, alternative = "greater") %T>%
-  print %$% 
-  r %>% 
-  round(2) ->
-  r_sensitive
-```
-
-# Assumptions
-## Multivariate normal distribution
-
-```{r}
-# create subset of data with all items that were used
-d_sub <- d[, c("self_dis_log", "GR02_01", "GR02_02", "GR02_03", "GR02_04", "GR02_05", "PC01_01", "PC01_02", "PC01_04", "PC01_05", "PC01_06", "PC01_07", "TR01_02", "TR01_03", "TR01_04", "TR01_06", "TR01_07", "TR01_08", "TR01_10", "TR01_11", "TR01_12", "PD01_01", "PD01_02", "PD01_03", "PD01_04", "PD01_05", "SE01_01", "SE01_02", "SE01_03", "SE01_04", "male", "age", "edu")]
-
-# test multivariate normal distribution
-mvn_result <- mvn(d_sub, mvnTest = "mardia")
-mvn_result$multivariateNormality
-```
-
-Shows that multivariate normal distribution is violated. We hence use maximum likelihood estimation with robust standard errors and a Satorra-Bentler scaled test statistic.
-
-## Influential cases
-
-In what follows we test for influential cases in baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.
-
-```{r}
-cooks_dis <- gCD(d, model_baseline)
-plot(cooks_dis)
-```
-
-The following ten cases have a particularly strong influence on the baseline model.
-
-```{r}
-infl_cases <- invisible(rownames(print(cooks_dis)))
-```
-
-Let's inspect these cases.
-
-```{r}
-infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
-d %>% 
-  filter(case_token %in% infl_cases_tokens) %>% 
-  select(case_token, GR01_01:SE01_06, topics_entered:reactions, -SO01_01, TIME_SUM_t1, TIME_SUM_t2) %>% 
-  kable() %>% 
-  kable_styling("striped") %>% 
-  scroll_box(width = "100%")
-```
-
-These data do not reveal potential cases of response patterns. Indeed, answer times suggest that respondents were diligent.
-
-# Results
-## Privacy calculus
-### Model "Peregistered"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
-summary(fit_prereg, fit = TRUE, std = TRUE)
-rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
-```
-
-### Model "Adapted"
-
-Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_gen =~ TR01_01 + TR01_05 + TR01_09
-
-self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
-summary(fit_adapted, fit = TRUE, std = TRUE)
-rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
-```
-
-### Model "Simple"
-
-We now use only variables, that is specific gratifications and privacy concerns.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-self_dis_log ~ a1*pri_con + b1*grats_spec
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
-summary(fit_simple, fit = TRUE, std = TRUE)
-rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
-```
-
-### Comparison
-
-```{r}
-model_comp_tab <- data.frame(
-  preregistered = fitmeasures(fit_prereg, c("BIC", "AIC")),
-  adapted = fitmeasures(fit_adapted, c("BIC", "AIC")),
-  simple = fitmeasures(fit_simple, c("BIC", "AIC"))) %>% 
-  t() %T>%
-  print()
-```
-
-### Visualization
-
-```{r}
-# extract coeffs
-d_coeffs_baseline <- coeffs_tab(fit_baseline, c("a1", "b1", "c1", "d1", "e1", "f1", "g1")) %>% 
-  mutate(Model = rep("Bivariate\nrelations", 7),
-         Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific", "Trust\ngeneral", "Grats.\nspecific"))
-
-d_coeffs_prereg <- coeffs_tab(fit_prereg, c("a1", "b1", "c1", "d1", "e1")) %>% 
-  mutate(Model = rep("Preregistered\nmodel", 5),
-         Predictor = c("Privacy\nconcern", "Grats.\ngeneral", "Privacy\ndelib.", "Self-\nefficacy", "Trust\nspecific"))
-
-d_coeffs_adapted <- coeffs_tab(fit_adapted, c("a1", "b1", "c1", "d1", "e1")) %>% 
-  mutate(Model = rep("Adapted\nmodel", 5),
-         Predictor = c("Privacy\nconcern", "Grats.\nspecific", "Privacy\ndelib.", "Self-\nefficacy", "Trust\ngeneral"))
-
-d_coeffs_simple <- coeffs_tab(fit_simple, c("a1", "b1")) %>% 
-  mutate(Model = rep("Simple\nmodel", 2),
-         Predictor = c("Privacy\nconcern", "Grats.\nspecific"))
-
-d_coeffs <- rbind(d_coeffs_baseline, d_coeffs_prereg, d_coeffs_adapted, d_coeffs_simple) %>% 
-  mutate(Predictor = factor(Predictor, c("Trust\ngeneral", "Trust\nspecific", "Self-\nefficacy", "Privacy\ndelib.", "Privacy\nconcern", "Grats.\nspecific", "Grats.\ngeneral")),
-         Model = factor(Model, c("Bivariate\nrelations", "Preregistered\nmodel", "Adapted\nmodel", "Simple\nmodel"))
-  )
-
-# plot coeffs
-fig_coeffs <- ggplot(d_coeffs, aes(x = b, y = Predictor)) + 
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_point(size = 2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul), 
-                lwd = .75, colour = "grey", height = .2) +
-  geom_errorbarh(aes(xmin = ll, xmax = ul),
-                lwd = .75, colour = "black", height = .2) +
-  facet_grid(~ Model) +
-  guides(color = FALSE, shape = FALSE) + 
-  theme_bw() +
-  theme(axis.title.x=element_blank(),
-        axis.title.y = element_blank(),
-        plot.title = element_text(hjust = .5),
-        panel.spacing = unit(.9, "lines"),
-        text = element_text(size = 12)) +
-  coord_cartesian(xlim = c(-1.5, 1.5))
-
-fig_coeffs
-```
-
-## Effects of popularity cues
-### Visualisation
-
-The easiest way to assess the effect of the experimental manipulation on the variables is by visualizing their means.
-If 95% confidence intervals don't overlap, the variables differ significantly across the conditions.
-One can quickly see that there aren't any major effects.
-
-```{r}
-fig_fs_m <- ggplot(
-  gather(d_fs, variable, value, -version) %>% 
-    mutate(variable = factor(variable, levels = var_names_breaks)),
-  aes(x = version, y = value, fill = version)) +
-  stat_summary(fun.y = mean, geom = "bar") +
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
-  facet_wrap(~ variable, nrow = 2) + 
-  theme_bw() +
-  theme(axis.title.y = element_blank(),
-        axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
-        plot.title = element_text(hjust = .5),
-        panel.spacing = unit(.9, "lines"),
-        text = element_text(size = 12),
-        legend.position="bottom",
-        legend.title = element_blank()) +
-  scale_fill_brewer(palette="Greys")
-fig_fs_m
-```
-
-### Preregistered
-
-In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts.
-However, please note that several models did not converge.
-This is likely because the models remain complex, while the sample size significantly decreases (i.e., only 2/3 of prior models).
-
-#### Like vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
-```
-
-Model did not converge. It's likely too complex given the reduced number of participants. The trust subdimension "provider" seems to cause trouble. Will hence be substituted with factor score.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-Again, does not converge; will use `Trust Specific` as factor score.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_lik, fit = TRUE, std = TRUE)
-```
-
-This time, does converge, no need to change model.
-
-```{r SaveData, include=F, cache=F}
-write.csv(d, file = "data/data.csv", row.names = FALSE)
-save(d, d_raw, d_all, d_fs,
-     fit_baseline, fit_prereg, fit_adapted, fit_simple,
-     fig_fs_m, fig_fs_cor, fig_coeffs,
-     des_pridel,
-     model_comp_tab, factor_val_tab,
-     n_comments, n_desired, n_posts, n_speeding, n_time, n_words,
-     n_comments, n_words, n_time, n_posts, n_speeding,
-     n_users, n_final,
-     infl_cases, infl_cases_tokens, resp_pattern, n_resp_pattern,
-     n_t1, age_t1_m, male_t1_m, college_t1_m,
-     n_t2, age_t2_m, male_t2_m, college_t2_m,
-     n_matched, n_final, age_final_m, male_final_m, college_final_m,
-     r_sesoi, r_sensitive, power_achieved,
-     rsquare_fit_prereg, rsquare_fit_adapted, rsquare_fit_simple,
-     file = "data/workspace.RData"
-     )
-```
+ 1. ... discuss political issues on the participation platform.
+ 2. ... express my personal opinion on the participation platform.
+ 3. ... write comments on the participation platform.
+ 4. ... disclose concerns and fears on the participation platform.
+ 5. ... share personal experience on the participation platform.

### 2020-04-17 docs/manuscript/manuscript.tex
- initalize GitHubPages

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment},
  pdflang={en-EN},
  pdfkeywords={privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Popularity cues and the privacy calculus}
\author{Dienlin, Tobias\textsuperscript{1}, Braeunlich, Katharina\textsuperscript{2}, \& Trepte, Sabine\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of Koblenz-Landau}
\authornote{All authors contributed extensively to the work presented in this paper. TD, KB, \& ST designed the study; KB \& TD designed the online website; TD \& KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project. 
The authors declare no competing interests.

This research was funded by the Volkswagen Foundation, project "Transformations of privacy", which was awarded to Sandra Seubert, Sabine Trepte, Ruediger Grimm, \& Christoph Gusy. We would like to thank all our colleagues from the project and Niklas Johannes for valuable feedback.

This manuscript features online supplementary material, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://osf.io/hcqat/?view\_only=5db35868738d40609b11e58cc343a9b0).

Correspondence concerning this article should be addressed to Dienlin, Tobias, University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany. E-mail: tobias.dienlin@uni-hohenheim.de}
\keywords{privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration\newline\indent Word count: 6296}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\setlength{\parskip}{0em}
\raggedbottom
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment}

\date{}

\abstract{
According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online. So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior. Likewise, we still know little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons. To answer these questions, we ran a preregistered one-week field experiment. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The final sample consisted of 590 participants. Although the originally preregistered model could not be confirmed, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy. The impact of the popularity cues on self-disclosure and the privacy calculus was negligible. In conclusion, the results suggest that privacy concerns and expected benefits are relevant when it comes to understanding self-disclosure, which together provides further evidence against the privacy paradox.
}

\begin{document}
\maketitle

Understanding why people disclose personal information online remains a critical question for both society and research.
Originally, it was claimed that self-disclosure is mostly erratic, and that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints.
Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online \emph{despite} having substantial concerns about their privacy (Barnes, 2006; Taddicken \& Jers, 2011).

Somewhat surprisingly, and despite its popularity in the media (Radio, 2018), the privacy paradox has garnered little empirical support.
A recent meta-analysis revealed that the correlation between privacy concerns and self-disclosure on SNS is \emph{r} = -.13 (Baruh, Secinti, \& Cemalcilar, 2017), which shows that privacy concerns are indeed related to self-disclosure online.

Hence, rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called \emph{privacy-calculus} (Laufer \& Wolfe, 1977), which states that self-disclosure online can be explained---at least partly---by means of expected risks \emph{and} expected benefits (Krasnova, Spiekermann, Koroleva, \& Hildebrand, 2010).
Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information online, whereas expecting benefits is related to disclosing more information online (Heirman, Walrave, \& Ponnet, 2013; Koohikamali, French, \& Kim, 2019).

However, although the privacy calculus has gained some momentum in academic research, several important questions remain unanswered.
First, we still know little about whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting (Kokolakis, 2017).
Thus far, most research supporting the privacy calculus has used either self-reports of behavior (e.g., Krasnova et al., 2010), vignette approaches (e.g., Bol et al., 2018), or one-shot experiments in the lab (e.g., Trepte, Scharkow, \& Dienlin, 2020).
However, all three of these approaches have low external validity.
As a result, in this study we analyze actual information sharing behavior in an authentic online setting.

Second, current research on the privacy calculus is often criticized for not explicitly focusing on the deliberation process of self-disclosure.
According to critics (e.g., Knijnenburg et al., 2017), showing that concerns and gratifications both correlate with self-disclosure is not evidence for an explicit weighing process of pros and cons.
We agree.
In this study, we therefore explicitly focus on the privacy deliberation process.
Related, and on a more general level, we explore the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-efficacy.

Finally, because the privacy calculus does not take place in a vacuum, and because it is often argued that self-disclosure can be easily triggered by external circumstances, we analyze whether the privacy calculus can be affected by the design of a website.
Specifically, we investigate whether \emph{popularity cues} such as like and dislike buttons have the power to affect the privacy calculus and to foster self-disclosure.

To test our research questions, drawing from a representative sample of the German population we conducted a preregistered online field experiment.
Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all.
Over the course of one week participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany).
Afterward, they answered a follow-up questionnaire with items measuring the privacy calculus variables.

\hypertarget{the-privacy-calculus}{%
\subsection{The Privacy Calculus}\label{the-privacy-calculus}}

Self-disclosure is a primary means of regulating privacy (e.g., Masur, 2018).
It is our key variable of interest.
There are two different understandings of self-disclosure in the literature:
The first defines self-disclosure as \emph{deliberate} acts of sharing truthful information about the self with others (Jourard, 1964).
The second considers \emph{all} acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information allows for meaningful inferences about a person (Watzlawick, Bavelas, Jackson, \& O'Hanlon, 2011).
In this paper we follow the latter approach, not least because the recent years have illustrated how easy it is to derive personal insights simply by analyzing exchanged communication (Kosinski, Stillwell, \& Graepel, 2013).
Moreover, independent from which position one adopts, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) (Omarzu, 2000).
In this study we mainly focus on communication quantity, as we consider communication quantity to be a necessary precondition and hence valid proxy for self-disclosure.

Privacy concerns have been defined as follows:
\enquote{Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened} (Dienlin, Masur, \& Trepte, 2019, p. 6).
Previous research has found that people who are more concerned about their privacy than others are less likely to share personal information (Baruh et al., 2017; Heirman et al., 2013; Koohikamali et al., 2019).

H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.

Although privacy concerns are related to self-disclosure, one can argue that most studies report only small effects, and that there should be additional factors that also contribute to explaining self-disclosure.
Most prominently, it has been argued that people trade a loss of privacy for a gain in gratifications such as social capital, entertainment, information, or self-presentation (Ellison, Vitak, Steinfield, Gray, \& Lampe, 2011; Taddicken \& Jers, 2011).
By now, a large body of research has found support for this hypothesis (e.g., Krasnova et al., 2010; Min \& Kim, 2015; Trepte et al., 2017).

H2: People are more likely to self-disclose on a website when they obtain more gratifications from using the website.

As mentioned above, there is still a shortage of studies that explicitly analyze the decision process behind the disclosing of information---although this point of criticism has been leveled several times (Knijnenburg et al., 2017) and although other fields such as behavioral economics have long focused on the underlying problem (Zhu, Ou, van den Heuvel, \& Liu, 2017).
This criticism is justified.
The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient evidence for an explicit weighing process.
Hence, research on the privacy calculus would benefit significantly from analyzing this decision process explicitly.
Building on Omarzu (2000) and Altman (1976), we hence address a novel concept that might best be termed \emph{privacy deliberation}, which captures the extent to which individual people explicitly compare positive and negative potential outcomes before communicating with others.

On the one hand, it seems plausible that deliberating about one's privacy would dampen subsequent self-disclosure, because refraining from regular communication---the primary means of connecting with others---requires at least a minimum of active and hence deliberate restraint.
On the other hand, deliberating about one's privacy might also increase self-disclosure, because a person concerned about his or her privacy might arrive at the conclusion that in this situation self-disclosure is not only appropriate but expedient.
In light of the lack of empirical studies and the plausibility of both effects, we formulate the following research question:

RQ1: Are people more or less likely to self-disclose on a website when they more actively deliberate about whether they should self-disclose?

Several attempts have already been made to expand the privacy calculus (Dinev \& Hart, 2006), introducing additional variables such as self-efficacy or trust.
Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future (Dienlin \& Metzger, 2016).
These privacy behaviors refer to either self-\emph{disclosure} (e.g., publishing a blog post) or self-\emph{withdrawal} (e.g., deleting inappropriate content).
People who report more privacy self-efficacy also engage in more self-withdrawal (Chen, 2018).
In light of our focus on active communication, in this study we investigate the influence of self-\emph{disclosure} self-efficacy.

H3: People are more likely to self-disclose on a website when their self-efficacy about self-disclosing on the website is higher.

Trust can be conceptualized in two different ways (Gefen, Karahanna, \& Straub, 2003):
It either captures \enquote{\emph{specific} beliefs dealing primarily with the integrity, benevolence, and ability of another party} (Gefen et al., 2003, p. 55, emphasis added) or a \enquote{\emph{general} belief that another party can be trusted} (Gefen et al., 2003, p. 55, emphasis added).
Whereas specific trust focuses on the causes of trust, general trust emphasized the experience of trust.
Gefen et al. (2003) prioritize specific trust (p.~60).
In the online context, it is also important to differentiate among several \emph{targets} of trust (Söllner, Hoffmann, \& Leimeister, 2016).
Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users (Söllner et al., 2016).
Trust plays a key role in online communication (Metzger, 2004).
For example, people who put more trust in the providers of networks also disclose more personal information (Li, 2011).

H4: People are more likely to self-disclose on a website when they have greater trust in the provider, the website, and the other users.

\hypertarget{the-effect-of-popularity-cues}{%
\subsection{The Effect of Popularity Cues}\label{the-effect-of-popularity-cues}}

What is the effect of the communication context on the privacy calculus and on self-disclosure?
First, it has often been noted that researchers should not exclusively focus on specific features of particular websites, for features are prone to change and quickly become obsolete (Fox \& McEwan, 2017).
Instead, it has been suggested to prioritize underlying latent structures, for example by analyzing so-called affordances (Ellison \& Vitak, 2015; Fox \& McEwan, 2017).
The concept of affordances was developed by Gibson (2015), who argued that it is not the \emph{objective features} of objects that determine behavior.
Instead, more important are the \emph{subjective perceptions}.
Affordances are a mental representation of how a given entity might be used; as such, they are by definition subjective.
There is an ongoing debate on what exactly defines an affordance (Evans, Pearce, Vitak, \& Treem, 2017).
For example, whereas Evans et al. (2017) propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), Fox and McEwan (2017) suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).

As the privacy calculus states that both benefits and costs determine behavior, we suggest that popularity cues such as like and dislike buttons, which are categorized as \enquote{paralinguistic digital affordances} (Carr, Hayes, \& Sumner, 2018, p. 142), perfectly capture potential benefits and costs.
The like button is positive.
It expresses an endorsement, a compliment, a reward (Carr et al., 2018; Sumner, Ruge-Jones, \& Alcorn, 2017).
However, communication online is also often characterized by negative and critical debates (Ziegele, Weber, Quiring, \& Breiner, 2017).
As the dislike button is a major means of downgrading content it is negative and represents the risk factor of the privacy calculus well.
In fact, its stark negative effect might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit, or stackexchange).

Paralinguistic digital affordances and specifically popularity cues have been shown to impact behavior (Krämer \& Schäwel, 2020; Trepte et al., 2020).
For example, a large-scale field experiment in which 101,281 comments were analyzed found that comments with dislikes were more likely to receive further dislikes (Muchnik, Aral, \& Taylor, 2013).
Stroud, Muddiman, and Scacco (2017) demonstrated that when users disagreed with a post, they were more likely to click on a button labeled \emph{respect} compared to a button labeled \emph{like}.

In this vein, it seems plausible that popularity cues might also impact the privacy calculus (Krämer \& Schäwel, 2020).
First, popularity cues could serve as a means of reward and punishment.
Being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit disclosure.
Similarly, like buttons imply being able to garner positive feedback, so implementing a like-button---similar to a compliment in the offline world---might leverage gratifications.
Implementing popularity cues might also bring people to more actively deliberate about whether or not it is actually worthwhile to disclose information.
If both like and dislike buttons are present, privacy deliberation should increase even further.
Finally, because people who are more concerned about their privacy are also more shy and risk averse (Dienlin, 2017), implementation of the dislike button should both stir privacy concerns and stifle self-disclosure.

H5. Compared to people who use a website without like or dislike buttons, people who use a website with like buttons (a) self-disclose more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.

H6. Compared to people who use a website without like or dislike buttons, people who use a website with like and dislike buttons (a) self-disclose more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.

H7. Compared to people who use a website with only like buttons, people who use a website with like and dislike buttons (a) are more concerned about their privacy, and (b) deliberate more about whether they should communicate online.

For a simplified overview of our theoretical model, see Figure \ref{fig:model}.

\begin{figure}

{\centering \includegraphics[width=.8\textwidth]{../figures/design/model}

}

\caption{Overview of theoretical model.}\label{fig:model}
\end{figure}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{open-science}{%
\subsection{Open Science}\label{open-science}}

The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript (see \url{https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0}).
We preregistered the study using the registration form \emph{OSF Prereg}, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see \url{https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859}).
We needed to change our pre-defined plan in some cases.
For a full account of all changes, see OSM.
New analyses that were not preregistered appear in the section on exploratory analyses.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

The study was designed as an online field experiment with three different groups.
The first group used a website without like/dislike buttons, the second a website with only like buttons, and the third a website with both like and dislike buttons.
Participants were randomly distributed to one of the three websites in a between-subject design.

We collaborated with a professional panel agency to recruit participants.
As incentive, participants were awarded digital points, which they could use to get special offers from other companies.
Participants were above the age of 18 and lived in Germany.
In a first step, the agency sent its panel members an invitation to participate in the study (\emph{invitation}).
In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.\footnote{Although the terror attack was not of primary interest for this study, the data can and will also be used to analyze perceptions of the terrorism threat. Hence, no deception took place, and in the debriefing participants were informed about our additional research interest in privacy.}
Members who decided to take part were subsequently sent the first questionnaire (\emph{T1}), in which we asked about their sociodemographics, provided more details about the study, and included a registration link for the website.
Afterward, participants were randomly assigned to one of the three websites.
After registration was completed, participants could discuss the topic of the terrorism threat in Germany over the course of one week (\emph{field}).
Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (\emph{T2}).
Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.

We programmed an online website based on the open-source software \emph{discourse} (\url{https://www.discourse.org/}).
We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \ref{fig:website}).
Participants used the website actively: Overall, they spent 9,694 minutes online, wrote 1,171 comments, and left 560 popularity cues.
Notably, we did not find any instances of people providing meaningless text.
For an example of communication that took place, see Figure \ref{fig:comments}.

\begin{figure}

{\centering \includegraphics[width=.9\textwidth]{../figures/website/website_translated}

}

\caption{The website's homepage. (Translated to English; university logos pixelated for peer review.)}\label{fig:website}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=.9\textwidth]{../figures/website/comments_translated}

}

\caption{Communication that took place on the website with like and dislike buttons. (Translated to English.)}\label{fig:comments}
\end{figure}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on a smallest effect size of interest (SESOI; Lakens, Scheel, \& Isager, 2018).
In other words, we defined a minimum effect size that we would consider sufficiently large enough to support our hypotheses.
Because small effects should be expected when researching aspects of privacy online (e.g., Baruh et al., 2017), with small effects beginning at an effect size of \emph{r} = .10 (Cohen, 1992), we set our SESOI to be \emph{r} = .10.
Our aim was to be able to detect this SESOI with a probability of at least 95\%. Using the regular alpha level of 5\%, this leads to a minimum sample size of \emph{n} = 1,077.
In the end, we were able to include n = 559 in our analyses (see below).
This means that our study had a probability (power) of 77\% to find an effect at least as large as \emph{r} = .10.
Put differently, we were able to make reliable inferences (i.e., power = 95\%) about effects at least as big as \emph{r} = .14.

We collected a representative sample of the German population in terms of age, sex, and federal state.
1,619 participants completed the survey at T1, 960 participants created a user account on the website, and 982 participants completed the survey at T2.
Using tokens and IP addresses, we connected the data from T1, participants' behavior on the platform, and T2 by means of objective and automated processes.
The data for \emph{n} = 590 participants could be matched successfully across all three platforms.
We excluded \emph{n} = 29 participants who finished the questionnaire at T2 in less then three minutes, which we considered to be unreasonably fast.
To detect potentially corrupt data, we calculated Cook's distance.\footnote{We preregistered to delete participants with less than 6 minutes answer time. However, this led to the exclusion of too many data points of high quality, which is why we relaxed this criterion. In the OSM, we report the results using all participants.}
We excluded 2 participants because they provided clear response patterns (i.e., straight-lining).
The final sample included 559 participants.
The sample characteristics at T1 and T2 were as follows:
T1: Age = 45 years, sex = 49\% male, college degree = 22\%.
T2: Age = 46 years, sex = 49\% male, college degree = 29\%.
One participant did not report his or her sex.

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

In what follows, we present the materials we used to measure our variables.
Wherever possible, we operationalized the variables using established measures.
Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which we pretested concerning their legibility and understandability.
To assess factor validity we ran confirmatory factor analyses (CFA).
If the CFAs revealed insufficient fit, we deleted malfunctioning items.
All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale.
Answer options were as follows: -3 (\emph{strongly disagree}), -2 (\emph{disagree}), -1 (\emph{slightly disagree}), 0 (\emph{neutral}), +1 (\emph{slightly agree}), +2 (\emph{agree}), +3 (\emph{strongly agree}).
In the questionnaire, all items measuring a variable were presented on the same page in randomized order.

For an overview of the means, standard deviations, factorial validity, and reliability, see Table \ref{tab:CFA}.
For an overview of the variables' distributions, see Figure \ref{fig:corrplot}.
For the exact wording of all items and their individual distributions, see OSM.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:CFA}Psychometric Properties, Factorial Validity, and Reliability of Measures}

\footnotesize{

\begin{tabular}{llllllllllll}
\toprule
 & \multicolumn{1}{c}{m} & \multicolumn{1}{c}{sd} & \multicolumn{1}{c}{chisq} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{pvalue} & \multicolumn{1}{c}{cfi} & \multicolumn{1}{c}{tli} & \multicolumn{1}{c}{rmsea} & \multicolumn{1}{c}{srmr} & \multicolumn{1}{c}{omega} & \multicolumn{1}{c}{ave}\\
\midrule
Privacy concerns & 3.21 & 1.51 & 11.04 & 9.00 & 0.27 & 1.00 & 1.00 & 0.02 & 0.01 & 0.96 & 0.80\\
General gratifications & 4.76 & 1.22 & 34.03 & 5.00 & 0.00 & 0.98 & 0.95 & 0.10 & 0.02 & 0.93 & 0.74\\
Specific gratifications & 4.71 & 1.02 & 269.77 & 85.00 & 0.00 & 0.94 & 0.93 & 0.06 & 0.05 & 0.93 & 0.59\\
Privacy deliberation & 3.93 & 1.29 & 15.55 & 5.00 & 0.01 & 0.98 & 0.96 & 0.06 & 0.02 & 0.84 & 0.53\\
Self-efficacy & 5.25 & 1.12 & 3.23 & 1.00 & 0.07 & 0.99 & 0.96 & 0.06 & 0.01 & 0.86 & 0.59\\
General trust & 5.21 & 1.04 & 2.07 & 1.00 & 0.15 & 1.00 & 0.99 & 0.04 & 0.01 & 0.86 & 0.70\\
Specific trust & 5.08 & 0.94 & 99.48 & 26.00 & 0.00 & 0.96 & 0.94 & 0.07 & 0.04 & 0.92 & 0.62\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} omega = Raykov's composite reliability coefficient omega; avevar = average variance extracted.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}[!h]

{\centering \includegraphics[width=.9\textwidth]{manuscript_files/figure-latex/corrplot-1}

}

\caption{Above diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below diagonal: bivariate scatter plots for zero-order correlations. Solid regression lines represent linear regressions, dotted regression lines represent quadratic regressions. Calculated with the model predicted values for each variable (baseline model).}\label{fig:corrplot}
\end{figure}

\hypertarget{privacy-concerns}{%
\subsubsection{Privacy concerns}\label{privacy-concerns}}

Privacy concerns were measured with seven items based on Buchanan, Paine, Joinson, and Reips (2007).
One example item was \enquote{When using the participation platform, I had concerns about my privacy}.
One item had to be deleted due to poor psychometric properties.

\hypertarget{gratifications}{%
\subsubsection{Gratifications}\label{gratifications}}

We differentiated between two separate types of gratification.
\emph{General gratifications} were measured with five items based on Sun, Wang, Shen, and Zhang (2015).
One example item was \enquote{Using the participation platform has paid off for me}.
\emph{Specific gratifications} were measured with 15 items on five different subdimensions with three items each.
The scaled was based on Scherer and Schlütz (2002).
Example items were: \enquote{Using the participation platform made it possible for me to} \ldots{} \enquote{learn things I would not have noticed otherwise} (information), \enquote{react to a subject that is important to me} (relevance), \enquote{engage politically} (political participation), \enquote{try to improve society} (idealism), and \enquote{soothe my guilty consciences} (extrinsic benefits).

\hypertarget{privacy-deliberation}{%
\subsubsection{Privacy deliberation}\label{privacy-deliberation}}

Privacy deliberation was measured with five self-designed items. One example item was \enquote{While using the participation platform I have weighed the advantages and disadvantages of writing a comment.}

\hypertarget{self-efficacy}{%
\subsubsection{Self-efficacy}\label{self-efficacy}}

Self-efficacy was captured with six self-designed items, which measured whether participants felt that they had sufficient self-efficacy to write a comment on the platform.
For example, we asked \enquote{I felt technically competent enough to write a comment.}
Two inverted items were deleted due to poor psychometric properties.

\hypertarget{trust}{%
\subsubsection{Trust}\label{trust}}

We differentiated between two types of trust.
\emph{General trust} was operationalized based on Söllner et al. (2016), addressing three targets (i.e., provider, website, and other users) with one item each.
One example items was \enquote{The operators of the participation platform seemed trustworthy.}
\emph{Specific trust} was operationalized for the same three targets with three subdimensions each (i.e., ability, benevolence/integrity, and reliability), which were measured with one item each.
Example items were \enquote{The operators of the participation platform have done a good job} (ability), \enquote{The other users had good intentions} (benevolence/integrity), \enquote{The website worked well} (reliability).
The results showed that the provider and website targets were not sufficiently distinct, as was evidenced by a Heywood case.
We hence adapted the scale to combine these two targets.
The updated scale exhibited adequate fit.

\hypertarget{self-disclosure}{%
\subsubsection{Self-disclosure}\label{self-disclosure}}

Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two.
The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence \enquote{I like} and dislike buttons \enquote{I dislike}.
The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already said.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

All hypotheses and research questions were tested using structural equation modeling with latent variables.
The influence of the three websites was analyzed using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework while using latent variables (Kline, 2016).
Because the dependent variable self-disclosure was not normally distributed, we estimated the model using robust maximum likelihood (Kline, 2016).
As recommended by Kline (2016), we report the following global fit indices: \(\chi^2\), RMSEA (90\% CI), CFI, and SRMR.
Because sociodemographic variables are often related to self-disclosure and other privacy-related variables (Dindia \& Allen, 1992), we controlled all variables for the influence of sex, age, and education.
Preregistered hypotheses were tested with a one-sided significance level of 5\%.
Research questions were tested with a two-sided 5\% significance level using family-wise Bonferroni-Holm correction.
Exploratory analyses were conducted from a descriptive perspective, which is why the reported p-values and confidence intervals should not be overinterpreted.

We used R (Version 3.6.1; R Core Team, 2018) and the R-packages \emph{lavaan} (Version 0.6.5; Rosseel, 2012), \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2018), \emph{pwr} (Version 1.2.2; Champely, 2018), \emph{quanteda} (Version 1.5.2; Benoit, 2018), \emph{semTools} (Version 0.5.2; Jorgensen et al., 2018), and \emph{tidyverse} (Version 1.3.0; Wickham, 2017) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{descriptive-analyses}{%
\subsection{Descriptive Analyses}\label{descriptive-analyses}}

We first measured and plotted all bivariate relations between the study variables (see Figure \ref{fig:corrplot}).
The results did not reveal any relationships to be particularly curvilinear.
Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with self-disclosure.
For example, people who were more concerned about their privacy disclosed less information (\emph{r} = -.16).
Worth noting, specific gratifications and general trust predicted self-disclosure better than general gratifications and specific trust (\emph{r} = .13 vs.~\emph{r} = .23).
The mean of privacy deliberation was \emph{m} = 3.93. Altogether, 32\% of participants reported having actively deliberated about their privacy.

It is important to note that the bivariate results showed three very large correlations: First, between specific trust and general gratifications (\emph{r} = .79); second, between privacy concerns and privacy deliberation (\emph{r} = .61); third, between specific gratifications and self-efficacy (\emph{r} = .55). As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.

\hypertarget{privacy-calculus}{%
\subsection{Privacy Calculus}\label{privacy-calculus}}

\hypertarget{preregistered-analyses}{%
\subsubsection{Preregistered analyses}\label{preregistered-analyses}}

First, we ran a model as specified in the preregistration. The model fit our data okay, \(\chi^2\)(388) = 953.45, \textit{p} \textless{} .001, cfi = .94, rmsea = .05, 90\% CI {[}.05, .05{]}, srmr = .05.
Regarding H1, we did not find that general gratifications predicted self-disclosure (\(\beta\) = -.04, \textit{b} = -0.06, 95\% CI {[}-0.22, 0.09{]}, \textit{z} = -0.78, \textit{p} = .217; one-sided).
With regard to H2, privacy concerns did not significantly predict self-disclosure (\(\beta\) = .07, \textit{b} = 0.14, 95\% CI {[}-0.19, 0.47{]}, \textit{z} = 0.84, \textit{p} = .199; one-sided).
RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (\(\beta\) = -.10, \textit{b} = -0.16, 95\% CI {[}-0.34, 0.02{]}, \textit{z} = -1.72, \textit{p} = .085; two-sided).
Regarding H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (\(\beta\) = .38, \textit{b} = 0.78, 95\% CI {[}0.49, 1.07{]}, \textit{z} = 5.29, \textit{p} \textless{} .001; one-sided).
Concerning H4, results showed that trust was not associated with self-disclosure (\(\beta\) = -.12, \textit{b} = -0.30, 95\% CI {[}-0.83, 0.22{]}, \textit{z} = -1.13, \textit{p} = .129; one-sided).

However, these results should be treated with caution, because they indeed exhibit problems typical of multicollinearity, such as \enquote{wrong} signs of the predictors (Grewal, Cote, \& Baumgartner, 2004).
For example, in the multiple regression trust had a \emph{negative} relation with self-disclosure, whereas in the bivariate analysis it was \emph{positive}.

\hypertarget{exploratory-analyses}{%
\subsubsection{Exploratory analyses}\label{exploratory-analyses}}

Thus, we slightly adapted our preregistered model on the basis of the insights described above.
First, instead of specific trust and general gratifications we now included \emph{general} trust and \emph{specific} gratifications, which were correlated slightly less strongly.
The adapted model fit our data comparatively well, \(\chi^2\)(507) = 1502.61, \textit{p} \textless{} .001, cfi = .93, rmsea = .06, 90\% CI {[}.06, .06{]}, srmr = .06.

In the adapted privacy calculus model, specific gratifications were positively related to self-disclosure online (\(\beta\) = .17, \textit{b} = 0.49, 95\% CI {[}0.09, 0.88{]}, \textit{z} = 2.41, \textit{p} = .016).
Furthermore, people who deliberated more about their privacy disclosed less information (\(\beta\) = -.13, \textit{b} = -0.20, 95\% CI {[}-0.39, -0.02{]}, \textit{z} = -2.17, \textit{p} = .030; two-sided).
Self-efficacy remained substantially correlated with self-disclosure (\(\beta\) = .33, \textit{b} = 0.67, 95\% CI {[}0.40, 0.94{]}, \textit{z} = 4.86, \textit{p} \textless{} .001; two-sided).
However, we again found a negative correlation between trust and self-disclosure (\(\beta\) = -.19, \textit{b} = -0.55, 95\% CI {[}-0.96, -0.13{]}, \textit{z} = -2.57, \textit{p} = .010; two-sided), which again implies multicollinearity.

When confronted with multicollinearity, two responses are typically recommended (Grewal et al., 2004):
(a) combining collinear variables into a single measure, or (b) keeping only one of the collinear variables.
Combining variables was not an option in our case, because both trust and expected benefits are theoretically distinct constructs.
Because several variables were closely related to one another, we therefore decided to fit a simple privacy calculus model, which contains only privacy concerns and specific gratifications.

The simple model fit our data well, \(\chi^2\)(202) = 712.53, \textit{p} \textless{} .001, cfi = .95, rmsea = .07, 90\% CI {[}.06, .07{]}, srmr = .05.
First, we found that people who experienced more privacy concerns than others disclosed less information (\(\beta\) = -.14, \textit{b} = -0.20, 95\% CI {[}-0.32, -0.08{]}, \textit{z} = -3.26, \textit{p} = .001; two-sided).
Second, people who reported more specific gratifications than others self-disclosed more information (\(\beta\) = .22, \textit{b} = 0.64, 95\% CI {[}0.36, 0.93{]}, \textit{z} = 4.45, \textit{p} \textless{} .001; two-sided).
Both effect sizes were above our predefined SESOI of \emph{r} = .10, which implies that the they were large enough to be theoretically relevant.

When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (17.52 \%), followed by the preregistered model (16.34 \%), and the simple privacy calculus model (8.03 \%).
At the same time, the simple privacy calculus model was the most parsimonious one (BIC = 37,168, AIC = 36,567), followed by the preregistered model (BIC = 48,949, AIC = 48,097), and the adapted model (BIC = 57,409, AIC = 56,441).
For a visual overview of all results, see Figure \ref{fig:plotpc}.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{manuscript_files/figure-latex/plotpc-1} \caption{Predictors of self-disclosure. Displayed are the 95\% CIs of unstandardized effects.}\label{fig:plotpc}
\end{figure}

\hypertarget{popularity-cues}{%
\subsection{Popularity Cues}\label{popularity-cues}}

\hypertarget{preregistered-analyses-1}{%
\subsubsection{Preregistered analyses}\label{preregistered-analyses-1}}

In a next step, we analyzed the potential effects of the popularity cues.
Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables.
For an illustration, see Figure \ref{fig:popularitycues}, which displays the model-predicted values for each variable (using the baseline model) and shows that the confidence intervals of all preregistered variables overlap.
For the results of the specific inference tests using contrasts, see the OSM.

\hypertarget{exploratory-analyses-1}{%
\subsubsection{Exploratory analyses}\label{exploratory-analyses-1}}

The picture remained the same also when analyzing variables not included in the preregistration.
Note that some differences missed statistical significance only marginally (e.g., specific gratifications for the comparison between the website with like buttons and the control website without like and dislike buttons).
Nevertheless, we refrain from reading too much into these differences and conclude that the three websites were comparable regarding the privacy calculus variables and the amount of self-disclosure.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{manuscript_files/figure-latex/popularitycues-1} \caption{Overview of the variables for the three websites. Control: Website without buttons. Like: Website with like buttons. Like \& Dislike: Website with like and dislike buttons.}\label{fig:popularitycues}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

In this study, we analyzed the privacy calculus using actual observed behavior in a preregistered field experiment.
We additionally asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons.
The data came from a representative sample of the German population and were analyzed using structural equation modeling with latent variables.

In the bivariate analyses, all privacy calculus variables significantly predicted self-disclosure.
In the preregistered analyses using multiple regression, however, only self-efficacy significantly predicted self-disclosure.
All other variables were not significant.
The preregistered extended privacy calculus model was therefore not supported by the data.
However, the model showed problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a more basal privacy calculus model, which included only privacy concerns and specific gratifications.

The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy disclose less, and that people who expect more specific gratifications and who feel more self-efficacious disclose more.
However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases.
This is theoretically implausible.
As a result, we also fit the above-mentioned simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure.
Taken together, the results support the privacy calculus framework and suggest that self-disclosure online is not erratic and that it can be explained by several psychological variables.

Aligned with this observation, the results also suggest that in new communication contexts at least one third of all Internet users \emph{actively deliberates} about their privacy.
Determining whether this figure is large or small is a normative question.
Because although the effect is substantial, one could argue that it should be higher and that we as society should still more actively deliberate about our self-disclosure practices online.
Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables.
This either implies that thinking about one's privacy increases one's concern or, conversely, that being concerned about one's privacy leads one to think about one's options more actively.
Future research might tell.

The next major implication is that popularity cues do not always seem to have a strong influence on the privacy calculus and self-disclosure.
Although some studies have found that popularity cues can substantially impact behavior (e.g., Muchnik et al., 2013), in our study we found the opposite.
Users still disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons, potentially highlighting the agency of users.

The results also have several more fine-grained implications.
First, one can question the tendency to further increase the complexity of the privacy calculus model by adding additional variables (e.g., Dienlin \& Metzger, 2016).
\enquote{Since all models are wrong the scientist cannot obtain a}correct" one by excessive elaboration. {[}\ldots{]} Just as the ability to devise simple but evocative models is the signature of the great scientist so overelaboration and overparameterization is often the mark of mediocrity" (Box, 1976, p. 792).
Specifically, we have come to believe that adding self-efficacy to privacy calculus models is of limited value, because self-efficacy is often only a self-reported proxy of behavior offering little epistemic insight.
Instead, it might be more interesting to find out \emph{why} some people feel sufficiently efficacious to self-disclose whereas others do not.
In addition, although adding variables increases the amount of explained variance, it introduces further problems, for example spurious results due to multicollinearity.

Interestingly, multicollinearity might not even be a problem per se, but rather a helpful warning sign.
Because from a \emph{statistical} perspective, strongly correlated predictors only mean that standard errors become larger (Vanhove, 2019).
In other words, when predictors are strongly correlated we can be less certain about the effects we obtain, because there is less unique variance (Vanhove, 2019).
As a remedy, researchers could simply collect larger samples, which would allow to achieve sufficient statistical power.
Fortunately, using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated/collinear predictors (Wang \& Rhemtulla, 2020).

From a \emph{theoretical} perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
It is our understanding that multiple regression is often used with the aim to isolate effects, to make sure that they are not simply caused by another third variable.
However, in cases of highly correlated measures this often does not make much sense theoretically.
For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure \emph{while holding trust constant}.
Theoretically, however, it is more plausible to assume that increasing gratifications also fosters trust (Söllner et al., 2016).
In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy, measures which are all strongly correlated.
In short, the effects we found could even be correct, but the interpretation is much more difficult, artificial, and thereby of little theoretical and practical value.

Furthermore, we found a remarkably strong correlation between specific trust and expected gratifications (i.e., \emph{r} = .79).
At first glance, this strong relation seemed somewhat peculiar to us.
On closer inspection, however, we realized that the way trust is typically operationalized is remarkably close to expected gratifications.
To illustrate, the trust subdimension \emph{ability} includes items such as \enquote{The comments of other users were useful}.
In fact, in the literature trust is often operationalized as a formative construct that directly results from factors such as expected benefits (Söllner et al., 2016).
In conclusion, our results suggest that \emph{causes} of trust should not be confused with \emph{measures} of trust, for this might introduce problems of both homogeneity and/or multicollinearity.
Instead, we recommend to use general and reflective measures of trust.

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

The results do not allow for causal interpretation on the within-person level.
First, all results are based on analyses of between-person variance.
However, between-person relations often do not translate well to within-person effects (Hamaker, Kuiper, \& Grasman, 2015).
While some studies on privacy concerns online have begun to examine both sources of variance, finding that intrapersonal changes in privacy concerns are indeed related to intrapersonal changes in self-disclosure (Dietvorst, Hiemstra, Hillegers, \& Keijsers, 2017), similar analyses are still lacking for the privacy calculus.

Second, the self-reported measures were collected \emph{after} the field phase in which the dependent variable was measured.
As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.
Nevertheless, we deliberately decided to measure the self-reported variables afterward in order not to bias participants or prime our research interest.

Third, the assumption of stable unit treatment states that in experiments we should manipulate only the experimental variable while holding all others constant (Kline, 2016).
In this study, we explicitly manipulated the popularity cues.
However, because the experiment was conducted in the field several other variables could not be held constant.
This includes the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
As a result, the assumption of stable unit treatment was violated.

Although we did not find significant effects of like and dislike buttons in this study, this does not necessarily mean that they have no effect on self-disclosure and the privacy calculus in general.\\
Null-findings pose the \emph{Duhème-Quinn Problem} (Dienes, 2008), which---put somewhat crudely---states that null findings can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question.
In this case, we were not able send participants notifications when their comments were liked/disliked, which significantly decreases the popularity cues' salience.

This paper analyzes self-disclosure in the context of political participation.
Our focus was on understanding self-disclosure, which is why we deliberately excluded variables pertaining to political participation, such as informational self-efficacy (Loy, Masur, Schmitt, \& Mothes, 2018).
Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

Whereas some scholars discuss whether we should wish \enquote{Death to the privacy calculus?} (Knijnenburg et al., 2017, p. 1), we think that the privacy calculus is alive and kicking.
In this study, people who were more concerned about their privacy than others disclosed less information online, whereas people who received more gratifications from using a website than others disclosed more information online.
In addition, the results suggest that a substantial share of internet users, approximately 30\%, consciously engage in a privacy calculus by actively deliberating about whether or not to disclose information.
Popularity cues such as like and dislike buttons seem to play only a minor role in this process, especially if no means are implemented to guarantee that users are notified about others liking or disliking their communication.
In conclusion, the results thereby provide further evidence against the privacy paradox.
Internet users are at least somewhat proactive and reasonable---maybe no more or less proactive or reasonable than in other everyday situations.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-altmanPrivacyConceptualAnalysis1976}{}%
Altman, I. (1976). Privacy: A conceptual analysis. \emph{Environment and Behavior}, \emph{8}(1), 7--29. \url{https://doi.org/10.1177/001391657600800102}

\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-barnesPrivacyParadoxSocial2006}{}%
Barnes, S. B. (2006). A privacy paradox: Social networking in the United States. \emph{First Monday}, \emph{11}(9).

\leavevmode\hypertarget{ref-baruhOnlinePrivacyConcerns2017}{}%
Baruh, L., Secinti, E., \& Cemalcilar, Z. (2017). Online privacy concerns and privacy management: A meta-analytical review. \emph{Journal of Communication}, \emph{67}(1), 26--53. \url{https://doi.org/10.1111/jcom.12276}

\leavevmode\hypertarget{ref-R-quanteda}{}%
Benoit, K. (2018). \emph{Quanteda: Quantitative analysis of textual data}. \url{https://doi.org/10.5281/zenodo.1004683}

\leavevmode\hypertarget{ref-bolUnderstandingEffectsPersonalization2018}{}%
Bol, N., Dienlin, T., Kruikemeier, S., Sax, M., Boerman, S. C., Strycharz, J., \ldots{} Vreese, C. H. (2018). Understanding the effects of personalization as a privacy calculus: Analyzing self-disclosure across health, news, and commerce contexts. \emph{Journal of Computer-Mediated Communication}, \emph{23}(6), 370--388. \url{https://doi.org/10.1093/jcmc/zmy020}

\leavevmode\hypertarget{ref-boxScienceStatistics1976}{}%
Box, G. E. P. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799. \url{https://doi.org/10.1080/01621459.1976.10480949}

\leavevmode\hypertarget{ref-buchananDevelopmentMeasuresOnline2007}{}%
Buchanan, T., Paine, C., Joinson, A. N., \& Reips, U.-D. (2007). Development of measures of online privacy concern and protection for use on the Internet. \emph{Journal of the American Society for Information Science and Technology}, \emph{58}(2), 157--165. \url{https://doi.org/10.1002/asi.20459}

\leavevmode\hypertarget{ref-carrPredictingThresholdPerceived2018}{}%
Carr, C. T., Hayes, R. A., \& Sumner, E. M. (2018). Predicting a threshold of perceived Facebook post success via likes and reactions: A test of explanatory mechanisms. \emph{Communication Research Reports}, \emph{35}(2), 141--151. \url{https://doi.org/10.1080/08824096.2017.1409618}

\leavevmode\hypertarget{ref-R-pwr}{}%
Champely, S. (2018). \emph{Pwr: Basic functions for power analysis}. Retrieved from \url{https://CRAN.R-project.org/package=pwr}

\leavevmode\hypertarget{ref-chenRevisitingPrivacyParadox2018}{}%
Chen, H.-T. (2018). Revisiting the privacy paradox on social media with an extended privacy calculus model: The effect of privacy concerns, privacy self-efficacy, and social capital on privacy management. \emph{American Behavioral Scientist}, \emph{62}(10), 1392--1412. \url{https://doi.org/10.1177/0002764218792691}

\leavevmode\hypertarget{ref-cohenPowerPrimer1992}{}%
Cohen, J. (1992). A power primer. \emph{Psychological Bulletin}, \emph{112}(1), 155--159. \url{https://doi.org/10.1037/0033-2909.112.1.155}

\leavevmode\hypertarget{ref-dienesUnderstandingPsychologyScience2008}{}%
Dienes, Z. (2008). \emph{Understanding psychology as a science: An introduction to scientific and statistical inference}. New York, N.Y.: Palgrave Macmillan.

\leavevmode\hypertarget{ref-dienlinPsychologyPrivacyAnalyzing2017}{}%
Dienlin, T. (2017). \emph{The psychology of privacy: Analyzing processes of media use and interpersonal communication}. Hohenheim, Germany: University of Hohenheim.

\leavevmode\hypertarget{ref-dienlinLongitudinalAnalysisPrivacy2019}{}%
Dienlin, T., Masur, P. K., \& Trepte, S. (2019). \emph{A longitudinal analysis of the privacy paradox} (Preprint). SocArXiv. \url{https://doi.org/10.31235/osf.io/fm4h7}

\leavevmode\hypertarget{ref-dienlinExtendedPrivacyCalculus2016}{}%
Dienlin, T., \& Metzger, M. J. (2016). An extended privacy calculus model for SNSs: Analyzing self-disclosure and self-withdrawal in a representative U.S. Sample. \emph{Journal of Computer-Mediated Communication}, \emph{21}(5), 368--383. \url{https://doi.org/10.1111/jcc4.12163}

\leavevmode\hypertarget{ref-dietvorstAdolescentPerceptionsParental2017}{}%
Dietvorst, E., Hiemstra, M., Hillegers, M. H. J., \& Keijsers, L. (2017). Adolescent perceptions of parental privacy invasion and adolescent secrecy: An illustration of Simpson's paradox. \emph{Child Development}. \url{https://doi.org/10.1111/cdev.13002}

\leavevmode\hypertarget{ref-dindiaSexDifferencesSelfdisclosure1992}{}%
Dindia, K., \& Allen, M. (1992). Sex differences in self-disclosure: A meta-analysis. \emph{Psychological Bulletin}, \emph{112}(1), 106--124.

\leavevmode\hypertarget{ref-dinevExtendedPrivacyCalculus2006}{}%
Dinev, T., \& Hart, P. (2006). An extended privacy calculus model for e-commerce transactions. \emph{Information Systems Research}, \emph{17}(1), 61--80. \url{https://doi.org/10.1287/isre.1060.0080}

\leavevmode\hypertarget{ref-ellisonSocialNetworkSite2015}{}%
Ellison, N. B., \& Vitak, J. (2015). Social network site affordances and their relationship to social capital processes. In S. S. Sundar (Ed.), \emph{The handbook of the psychology of communication technology} (Vol. v.33, pp. 205--227). Chichester, MA: Wiley Blackwell.

\leavevmode\hypertarget{ref-ellisonNegotiatingPrivacyConcerns2011}{}%
Ellison, N. B., Vitak, J., Steinfield, C., Gray, R., \& Lampe, C. (2011). Negotiating privacy concerns and social capital needs in a social media environment. In S. Trepte \& L. Reinecke (Eds.), \emph{Privacy online: Perspectives on privacy and self-disclosure in the social web} (pp. 19--32). Berlin, Germany: Springer. \url{https://doi.org/10.1007/978-3-642-21521-6_3}

\leavevmode\hypertarget{ref-evansExplicatingAffordancesConceptual2017}{}%
Evans, S. K., Pearce, K. E., Vitak, J., \& Treem, J. W. (2017). Explicating affordances: A conceptual framework for understanding affordances in communication research. \emph{Journal of Computer-Mediated Communication}, \emph{22}(1), 35--52. \url{https://doi.org/10.1111/jcc4.12180}

\leavevmode\hypertarget{ref-foxDistinguishingTechnologiesSocial2017}{}%
Fox, J., \& McEwan, B. (2017). Distinguishing technologies for social interaction: The perceived social affordances of communication channels scale. \emph{Communication Monographs}, \emph{9}, 1--21. \url{https://doi.org/10.1080/03637751.2017.1332418}

\leavevmode\hypertarget{ref-gefenTrustTAMOnline2003}{}%
Gefen, D., Karahanna, E., \& Straub, D. W. (2003). Trust and TAM in online shopping: An integrated model. \emph{MIS Q}, \emph{27}(1), 5190.

\leavevmode\hypertarget{ref-gibsonEcologicalApproachVisual2015}{}%
Gibson, J. J. (2015). \emph{The ecological approach to visual perception}. New York, NY: Psychology Press.

\leavevmode\hypertarget{ref-grewalMulticollinearityMeasurementError2004}{}%
Grewal, R., Cote, J. A., \& Baumgartner, H. (2004). Multicollinearity and measurement error in structural equation models: Implications for theory testing. \emph{Marketing Science}, \emph{23}(4), 519--529. \url{https://doi.org/10.1287/mksc.1040.0070}

\leavevmode\hypertarget{ref-hamakerCritiqueCrosslaggedPanel2015}{}%
Hamaker, E. L., Kuiper, R. M., \& Grasman, R. P. P. P. (2015). A critique of the cross-lagged panel model. \emph{Psychological Methods}, \emph{20}(1), 102--116. \url{https://doi.org/10.1037/a0038889}

\leavevmode\hypertarget{ref-heirmanPredictingAdolescentsDisclosure2013}{}%
Heirman, W., Walrave, M., \& Ponnet, K. (2013). Predicting adolescents' disclosure of personal information in exchange for commercial incentives: An application of an extended theory of planned behavior. \emph{Cyberpsychology, Behavior, and Social Networking}, \emph{16}(2), 81--87. \url{https://doi.org/10.1089/cyber.2012.0041}

\leavevmode\hypertarget{ref-R-semTools}{}%
Jorgensen, D., T., Pornprasertmanit, S., Schoemann, M., A., \ldots{} Y. (2018). \emph{semTools: Useful tools for structural equation modeling}. Retrieved from \url{https://CRAN.R-project.org/package=semTools}

\leavevmode\hypertarget{ref-jourardTransparentSelf1964}{}%
Jourard, S. M. (1964). \emph{The transparent self}. New York, NY: Van Nostrand.

\leavevmode\hypertarget{ref-klinePrinciplesPracticeStructural2016}{}%
Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (Fourth). New York, NY: The Guilford Press.

\leavevmode\hypertarget{ref-knijnenburgDeathPrivacyCalculus2017}{}%
Knijnenburg, B., Raybourn, E., Cherry, D., Wilkinson, D., Sivakumar, S., \& Sloan, H. (2017). Death to the privacy calculus? \emph{SSRN Electronic Journal}. \url{https://doi.org/10.2139/ssrn.2923806}

\leavevmode\hypertarget{ref-kokolakisPrivacyAttitudesPrivacy2017}{}%
Kokolakis, S. (2017). Privacy attitudes and privacy behaviour: A review of current research on the privacy paradox phenomenon. \emph{Computers \& Security}, \emph{64}, 122--134. \url{https://doi.org/10.1016/j.cose.2015.07.002}

\leavevmode\hypertarget{ref-koohikamaliInvestigationDynamicModel2019}{}%
Koohikamali, M., French, A. M., \& Kim, D. J. (2019). An investigation of a dynamic model of privacy trade-off in use of mobile social network applications: A longitudinal perspective. \emph{Decision Support Systems}, \emph{119}, 46--59. \url{https://doi.org/10.1016/j.dss.2019.02.007}

\leavevmode\hypertarget{ref-kosinskiPrivateTraitsAttributes2013}{}%
Kosinski, M., Stillwell, D., \& Graepel, T. (2013). Private traits and attributes are predictable from digital records of human behavior. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{110}(15), 5802--5805. \url{https://doi.org/10.1073/pnas.1218772110}

\leavevmode\hypertarget{ref-krasnovaOnlineSocialNetworks2010}{}%
Krasnova, H., Spiekermann, S., Koroleva, K., \& Hildebrand, T. (2010). Online social networks: Why we disclose. \emph{Journal of Information Technology}, \emph{25}(2), 109--125. \url{https://doi.org/10.1057/jit.2010.6}

\leavevmode\hypertarget{ref-kramerMasteringChallengeBalancing2020}{}%
Krämer, N. C., \& Schäwel, J. (2020). Mastering the challenge of balancing self-disclosure and privacy in social media. \emph{Current Opinion in Psychology}, \emph{31}, 67--71. \url{https://doi.org/10.1016/j.copsyc.2019.08.003}

\leavevmode\hypertarget{ref-lakensEquivalenceTestingPsychological2018}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence testing for psychological research: A tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. \url{https://doi.org/10.1177/2515245918770963}

\leavevmode\hypertarget{ref-lauferPrivacyConceptSocial1977}{}%
Laufer, R. S., \& Wolfe, M. (1977). Privacy as a concept and a social issue: A multidimensional developmental theory. \emph{Journal of Social Issues}, \emph{33}(3), 22--42. \url{https://doi.org/10.1111/j.1540-4560.1977.tb01880.x}

\leavevmode\hypertarget{ref-liEmpiricalStudiesOnline2011}{}%
Li, Y. (2011). Empirical studies on online information privacy concerns: Literature review and an integrative framework. \emph{Communications of the Association for Information Systems}, \emph{28}, 453--496.

\leavevmode\hypertarget{ref-loyPsychologicalPredictorsPolitical2018}{}%
Loy, L. S., Masur, P. K., Schmitt, J. B., \& Mothes, C. (2018). Psychological predictors of political Internet use and political knowledge in light of the perceived complexity of political issues. \emph{Information, Communication \& Society}, \emph{45}, 1--18. \url{https://doi.org/10.1080/1369118X.2018.1450886}

\leavevmode\hypertarget{ref-masurSituationalPrivacySelfdisclosure2018}{}%
Masur, P. K. (2018). \emph{Situational privacy and self-disclosure: Communication processes in online environments}. Cham, Switzerland: Springer.

\leavevmode\hypertarget{ref-metzgerPrivacyTrustDisclosure2004}{}%
Metzger, M. J. (2004). Privacy, trust, and disclosure: Exploring barriers to electronic commerce. \emph{Journal of Computer-Mediated Communication}, \emph{9}(4). \url{https://doi.org/10.1111/j.1083-6101.2004.tb00292.x}

\leavevmode\hypertarget{ref-minHowArePeople2015}{}%
Min, J., \& Kim, B. (2015). How are people enticed to disclose personal information despite privacy concerns in social network sites? The calculus between benefit and cost. \emph{Journal of the Association for Information Science and Technology}, \emph{66}(4), 839--857. \url{https://doi.org/10.1002/asi.23206}

\leavevmode\hypertarget{ref-muchnikSocialInfluenceBias2013}{}%
Muchnik, L., Aral, S., \& Taylor, S. J. (2013). Social influence bias: A randomized experiment. \emph{Science (New York, N.Y.)}, \emph{341}(6146), 647--651. \url{https://doi.org/10.1126/science.1240466}

\leavevmode\hypertarget{ref-omarzuDisclosureDecisionModel2000}{}%
Omarzu, J. (2000). A disclosure decision model: Determining how and when individuals will self-disclose. \emph{Personality and Social Psychology Review}, \emph{4}(2), 174--185. \url{https://doi.org/10.1207/S15327957PSPR0402_5}

\leavevmode\hypertarget{ref-newyorkpublicradioPrivacyParadox2018}{}%
Radio, N. Y. P. (2018). The privacy paradox. InternetDocument, https://project.wnyc.org/privacy-paradox/.

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2018). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-R-lavaan}{}%
Rosseel, Y. (2012). lavaan: An R package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{http://www.jstatsoft.org/v48/i02/}

\leavevmode\hypertarget{ref-schererGratifikationMinuteZeitnahe2002}{}%
Scherer, H., \& Schlütz, D. (2002). Gratifikation à la minute: Die zeitnahe Erfassung von Gratifikationen. In P. Rössler (Ed.), \emph{Empirische Perspektiven der Rezeptionsforschung} (pp. 133--151). Munich, Germany: Reinhard Fischer.

\leavevmode\hypertarget{ref-sollnerWhyDifferentTrust2016}{}%
Söllner, M., Hoffmann, A., \& Leimeister, J. M. (2016). Why different trust relationships matter for information systems users. \emph{European Journal of Information Systems}, \emph{25}(3), 274--287. \url{https://doi.org/10.1057/ejis.2015.17}

\leavevmode\hypertarget{ref-stroudRecommendRespectAltering2017}{}%
Stroud, N. J., Muddiman, A., \& Scacco, J. M. (2017). Like, recommend, or respect?: Altering political behavior in news comment sections. \emph{New Media \& Society}, \emph{19}(11), 1727--1743. \url{https://doi.org/10.1177/1461444816642420}

\leavevmode\hypertarget{ref-sumnerFunctionalApproachFacebook2017}{}%
Sumner, E. M., Ruge-Jones, L., \& Alcorn, D. (2017). A functional approach to the Facebook Like button: An exploration of meaning, interpersonal functionality, and potential alternative response buttons. \emph{New Media \& Society}, \emph{20}(4), 1451--1469. \url{https://doi.org/10.1177/1461444817697917}

\leavevmode\hypertarget{ref-sunLocationInformationDisclosure2015}{}%
Sun, Y., Wang, N., Shen, X.-L., \& Zhang, J. X. (2015). Location information disclosure in location-based social network services: Privacy calculus, benefit structure, and gender differences. \emph{Computers in Human Behavior}, \emph{52}, 278--292. \url{https://doi.org/10.1016/j.chb.2015.06.006}

\leavevmode\hypertarget{ref-taddickenUsesPrivacyOnline2011}{}%
Taddicken, M., \& Jers, C. (2011). The uses of privacy online: Trading a loss of privacy for social web gratifications? In S. Trepte \& L. Reinecke (Eds.), \emph{Privacy online: Perspectives on privacy and self-disclosure in the social web} (pp. 143--158). Berlin, Germany: Springer.

\leavevmode\hypertarget{ref-trepteCrossculturalPerspectivePrivacy2017}{}%
Trepte, S., Reinecke, L., Ellison, N. B., Quiring, O., Yao, M. Z., \& Ziegele, M. (2017). A cross-cultural perspective on the privacy calculus. \emph{Social Media + Society}, \emph{3}(1). \url{https://doi.org/10.1177/2056305116688035}

\leavevmode\hypertarget{ref-treptePrivacyCalculusContextualized2020}{}%
Trepte, S., Scharkow, M., \& Dienlin, T. (2020). The privacy calculus contextualized: The influence of affordances. \emph{Computers in Human Behavior}, \emph{104}, 106115. \url{https://doi.org/10.1016/j.chb.2019.08.022}

\leavevmode\hypertarget{ref-vanhoveCollinearityIsnDisease2019}{}%
Vanhove, J. (2019). Collinearity isn't a disease that needs curing. https://janhove.github.io/analysis/2019/09/11/collinearity.

\leavevmode\hypertarget{ref-wangPowerAnalysisParameter2020}{}%
Wang, Y. A., \& Rhemtulla, M. (2020). Power analysis for parameter estimation in structural equation modeling: A discussion and tutorial. \url{https://doi.org/10.31234/osf.io/pj67b}

\leavevmode\hypertarget{ref-watzlawickPragmaticsHumanCommunication2011}{}%
Watzlawick, P., Bavelas, J. B., Jackson, D. D., \& O'Hanlon, B. (2011). \emph{Pragmatics of human communication: A study of interactional patterns, pathologies, and paradoxes}. New York, NY: W.W. Norton \& Co.

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}

\leavevmode\hypertarget{ref-zhuPrivacyCalculusIts2017}{}%
Zhu, H., Ou, C. X. J., van den Heuvel, W. J. A. M., \& Liu, H. (2017). Privacy calculus and its utility for personalization services in e-commerce: An analysis of consumer decision-making. \emph{Information \& Management}, \emph{54}(4), 427--437. \url{https://doi.org/10.1016/j.im.2016.10.001}

\leavevmode\hypertarget{ref-ziegeleDynamicsOnlineNews2017}{}%
Ziegele, M., Weber, M., Quiring, O., \& Breiner, T. (2017). The dynamics of online news discussions: Effects of news articles and reader comments on users' involvement, willingness to participate, and the civility of their contributions. \emph{Information, Communication \& Society}, \emph{7}, 1--17. \url{https://doi.org/10.1080/1369118X.2017.1324505}

\end{document}

### 2020-04-17 docs/preregistration/preregistration_changes.rmd
- initalize GitHubPages

---
title: "How Do Like and Dislike Buttons Affect Communication?"
subtitle: "Changes From Preregistration"
output: "pdf_document"
---

# Theoretical Background
## Hypotheses

 -	We changed the order of the hypotheses.
 -	We changed the wording of the hypotheses (but not the content)
    -	Before: “H1: People are more likely to communicate actively on the website, the less they are concerned about their privacy.”
    - Now: “H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.”

# Methods
## Participants
### Exclusion criteria

Initially, we planned to exclude all participants who finished the questionnaire in less than 6 minutes. However, we realized that this would lead to the deletion of participants who provided answers that seemed perfectly fine. In conclusion, we relaxed the criterion to 3 minutes, which led to the exclusion of 27 participants. Results changed only marginally and do not hinge on exclusion (see additional analyses).

# Material
## Expected Benefits

In the preregistration, we stated that we would measure expected benefits by means of 5 general items (“Using the participation platform had many benefits for me”). However, we had also designed additional items for more specific gratifications that we did not include in the preregistration (the preregistration stated that additional variables that one does not plan to analyze do not need to be preregistered). These specific measures of gratifications were hence used for exploratory analyses.

## Trust

Originally, we operationalized trust for three entities (i.e., provider, website, and other users) with four subdimensions (i.e., general trust, ability, benevolence, and integrity). Only later did we realized that the literature differentiates between general and specific trust beliefs, which we could conceptualize with the items we measured. As a result, in the paper we differentiated both dimensions.

# Results

Given that we found not apparent effects of the three websites on the privacy calculus, we did not test for indirect effects as proposed in the preregistration. We additionally also controlled for education (we probably forgot to explicitly mention it in the preregistration; results do not differ, but we think it should be included).

# Power analyses

In the preregistration, power analyses were conducted assuming 80% statistical power. However, in the meantime we have come to believe that in most cases and if logistically possible we should strive for balanced alpha and beta errors, which given an alpha of 5% leads to a desired power of 95%. As a result, we report power analyses aiming for 95% power.

# Inferences

In the preregistration, we stated that we would analyze the additional exploratory analyses using Bonferroni-Holm correction. However, in the meantime we have come to understand that formal inferences tests for exploratory analyses are debatable, for example because the number of tests one would need to account for is potentially infinite. Instead, we decided not to make strong inferences on the basis of the exploratory analyses, and report p-values / confidence intervals only descriptively as a measure of precision.

### 2020-04-17 index.Rmd
- initalize GitHubPages

---
title: "Privacy Calculus Experiment"
---

Hello world.

### 2020-04-17 index.Rmd
- updated header

@@
 
-Hello world.
+On this repository, you can find the data, analysis script, and a reproducible manuscript of the paper "How Do Like and Dislike Buttons Affect Communication?
+A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment".
+
+To view the results / additional analyses, you can either
+ - download all materials and open the file "analyses/analyses.html" in your browse
+ - or simply click on <a href="https://htmlpreview.github.io/?https://github.com/tdienlin/privacy_calc_exp/blob/master/analyses/analyses.html" target="_blank">this link</a>, and the results will open up directly in your browser.
+
+To rerun the analyses, please do the following steps:
+
+ - download all materials
+ - open the RStudio project (file "privacy_calc_exp.Rproj")
+ - run the file "analyses.rmd"
+ - please make sure that all packages are installed using their current version
+
+To reproduce the paper, please do the following steps **in addition**
+
+ - knit file "manuscript/manuscript.pdf"
+ - make sure that a current version of latex is installed

### 2020-04-17 analyses_additional.Rmd
- initialized webpage

--- 2020-04-17 docs/analyses/analyses_additional.Rmd
@@
 ---
-title: "How Do Like and Dislike Buttons Affect Communication?"
-shorttitle : "Additional Analyses"
+title: "Additional Analyses"
 output: 
@@
 
-```{r Data-Wrangling, include=F}
+```{r Data-Wrangling, include=F, cache=F}
 # load workspace
@@
 
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
+fit_likdis_lik <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
 summary(fit_likdis_lik, fit = TRUE, std = TRUE)
@@
 As stated in the preregistration, we also report the analyses including the deleted participants. Results don't change meaningfully.
+
+## Baseline model
+
+```{r}
+model_baseline <- "
+  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
+  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
+  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+  grats_par =~ GR01_07 + GR01_08 + GR01_09
+  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+  grats_ext =~ GR01_13 + GR01_14 + GR01_15
+  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+  trust_gen =~ TR01_01 + TR01_05 + TR01_09
+  trust_community =~ TR01_02 + TR01_03 + TR01_04
+  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+  trust_spec =~ trust_community + trust_provider
+  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+    SE01_01 ~~ x*SE01_02
+    SE01_03 ~~ x*SE01_04
+  self_dis_lg =~ self_dis_log
+
+  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
+"
+fit_baseline <- sem(model_baseline, data = d_all, missing = "ML")
+summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
+```
+
+```{r}
+# extract model predicted values for items & calc means
+d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
+  as.data.frame() %>% 
+  mutate(version = d_all$version, 
+         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
+         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
+         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
+         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
+         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
+         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
+         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
+  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)
+
+# combine d with d factor scores
+d_all %<>% cbind(select(d_fs, -version, -self_dis_log))
+```
 

### 2020-04-17 index.Rmd
- initialized webpage

--- 2020-04-17 index.Rmd
@@
 
-Hello world.
+On this website, you can find the companion material for the paper "How Do Like and Dislike Buttons Affect Communication?
+A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment".
+
+The material for example includes the [data](data/data.csv), [analysis script](analyses.html), and a reproducible [manuscript](manuscript.html) of the paper.
+
+This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp). You can download the material or file an issue.

### 2020-04-17 manuscript.RmD
- initialized webpage

--- 2020-04-09 manuscript/manuscript.RmD
@@
 bibliography      : 
-  - [../bibliography/r-references.bib]
-  - [../bibliography/references.bib]
+  - [bibliography/r-references.bib]
+  - [bibliography/references.bib]
 floatsintext      : yes
@@
 mask              : no
-wordcount         : "`r wordcountaddin::word_count('../manuscript/manuscript.Rmd')`"
+wordcount         : "`r wordcountaddin::word_count('manuscript/manuscript.Rmd')`"
 draft             : no
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
-# output            : papaja::apa6_word
-header-includes:
-  - \setlength{\parskip}{0em}
-  - \raggedbottom
+# to compile as pdf
+# (a) move file "_site.yml" to folder "tmp"
+# (b) uncomment the following lines
+# output            : papaja::apa6_pdf
+# header-includes:
+#   - \setlength{\parskip}{0em}
+#   - \raggedbottom
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+    toc_depth: 2
 ---
@@
 ```{r include=F}
-knitr::opts_chunk$set(cache=F)
+knitr::opts_chunk$set(cache=F, echo=F)
 ```
@@
 # create bib with r-packages
-r_refs(file = "../bibliography/r-references.bib")
+r_refs(file = "bibliography/r-references.bib")
 
 # load bib
-r_citations <- cite_r("../bibliography/r-references.bib"
+r_citations <- cite_r("bibliography/r-references.bib"
                       , footnote = FALSE
@@
 ```{r load-data, cache=T, include=F}
-load("../data/workspace.rData")
+load("data/workspace.rData")
 ```
+
+# Introduction
 
@@
 ```{r model, fig.cap="Overview of theoretical model.", fig.align='center', out.width=".8\\textwidth"}
-knitr::include_graphics("../figures/design/model.pdf")
-# knitr::include_graphics("figures/design/model.png")
+knitr::include_graphics("figures/design/model.png")
 ```
@@
 ```{r website, fig.cap="The website's homepage. (Translated to English; university logos pixelated for peer review.)", fig.align='center', out.width=".9\\textwidth"}
-knitr::include_graphics("../figures/website/website_translated.jpg")
+knitr::include_graphics("figures/website/website_translated.jpg")
 ```
@@
 ```{r comments, fig.align='center', fig.cap="Communication that took place on the website with like and dislike buttons. (Translated to English.)", out.width=".9\\textwidth"}
-knitr::include_graphics("../figures/website/comments_translated.png")
+knitr::include_graphics("figures/website/comments_translated.png")
 ```

### 2020-04-17 preregistration_changes.rmd
- initialized webpage

--- 2020-04-17 docs/preregistration/preregistration_changes.rmd
@@
 ---
-title: "How Do Like and Dislike Buttons Affect Communication?"
-subtitle: "Changes From Preregistration"
-output: "pdf_document"
+title: "Changes From Preregistration"
+output: "html_document"
 ---
+
+The preregistration can be found here. In what follows, we present where we decided to deviate from preregistration.
 

### 2020-04-20 analyses.Rmd
- initialized webpage
- updated feedback - updated website

--- 2020-04-17 docs/analyses/analyses.Rmd
@@
 ---
-title: "How Do Like and Dislike Buttons Affect Communication?"
-shorttitle : "Analyses"
+title: "Analyses"
 output: 
@@
     toc_depth: 2
-    keep_md: true
+    code_folding: hide
 ---
@@
 knitr::opts_chunk$set(
-  cache=T, comment=NA, warning=F, echo=F, error=F, 
+  cache=T, comment=NA, warning=F, echo=T, error=F, 
   message=F, prompt=F, tidy=T, fig.height=4
@@
 
-```{r r-setup, include=F}
+In what follows, you can find the analyses for the results we report in the paper. To see the underlying code, click on the button "code".
+
+# Setup
+
+We first load the packages; load and wrangle data; and extract sample characteristics and descriptives.
+
+```{r results='hide'}
+# install github packages
+# devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install
+
 # define packages
@@
               "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
-              "quanteda", "semTools", "tidyverse")
-
-# install packages # uncomment lines to install packages
-# devtools::install_github("tdienlin/td@v.0.0.2.3")
-# lapply(packages, install.packages, character.only = T, quietly = TRUE)
+              "quanteda", "semTools", "tidyverse", "td")
 
@@
 lapply(packages, library, character.only = TRUE, quietly = TRUE)
-library(td)
-```
-
-```{r Data-Wrangling, include=F}
+
 # load data
@@
   )
-```
-
-```{r include=F}
-# sample descriptives t1
-n_t1 <- nrow(d)
-age_t1_m <- mean(d$age, na.rm = TRUE)
-male_t1_m <- mean(d$male, na.rm = TRUE)
-college_t1_m <- table(d$edu)[3] / n_t1
-
-# sample descriptives t2
-n_t2 <- filter(d, !is.na(id_survey_t2)) %>% nrow()
-age_t2_m <- filter(d, !is.na(id_survey_t2))$age %>% mean()
-male_t2_m <- filter(d, !is.na(id_survey_t2))$male %>% mean(na.rm = TRUE)
-college_t2_m <- filter(d, !is.na(id_survey_t2))$edu %>% table() %>% .[3] / n_t2
-
-# descriptives users
-n_users <- filter(d, !is.na(post_count)) %>% nrow()
-
-# characteristics of posts
-n_comments <- sum(d$post_count, na.rm = TRUE)
-n_words <- sum(d$words, na.rm = TRUE)
-n_time <- sum(d$time_read_MIN, na.rm = TRUE)
-n_posts <- sum(d$post_count, na.rm = TRUE)
-
-# filter unmatched cases
-d <- filter(d, !is.na(post_count) & !is.na(id_survey_t2))  # Use only completes
-n_matched <- nrow(d)
-
-# save data file with all participants to compare results
-d_all <- d
 
@@
                       "Self-\ndisclosure")
+
+# Extract sample characteristics and descriptives.
+# sample descriptives t1
+n_t1 <- nrow(d)
+age_t1_m <- mean(d$age, na.rm = TRUE)
+male_t1_m <- mean(d$male, na.rm = TRUE)
+college_t1_m <- table(d$edu)[3] / n_t1
+
+# sample descriptives t2
+n_t2 <- filter(d, !is.na(id_survey_t2)) %>% nrow()
+age_t2_m <- filter(d, !is.na(id_survey_t2))$age %>% mean()
+male_t2_m <- filter(d, !is.na(id_survey_t2))$male %>% mean(na.rm = TRUE)
+college_t2_m <- filter(d, !is.na(id_survey_t2))$edu %>% table() %>% .[3] / n_t2
+
+# descriptives users
+n_users <- filter(d, !is.na(post_count)) %>% nrow()
+
+# characteristics of posts
+n_comments <- sum(d$post_count, na.rm = TRUE)
+n_words <- sum(d$words, na.rm = TRUE)
+n_time <- sum(d$time_read_MIN, na.rm = TRUE)
+n_posts <- sum(d$post_count, na.rm = TRUE)
+
+# filter unmatched cases
+d <- filter(d, !is.na(post_count) & !is.na(id_survey_t2))  # Use only completes
+n_matched <- nrow(d)
+
+# save data file with all participants to compare results
+d_all <- d
 ```
@@
 # Filter Participants
+
+We filtered participants who answered the questionnaire in less than three minutes, which we considered to be unreasonably fast.
 
@@
 
-We first inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.
+We inspected the data manually for cases with obvious response patterns. The following cases show extreme response patterns (alongside fast response times), and were hence removed.
 
@@
 ```{r}
-name <- "pricon"
 model <- "
@@
 ```
+
+Updated version shows good fit.
 
@@
   cbind(des[-8, ], .) %>%
-  set_rownames(var_names[-8]) %T>%
-  print()
+  set_rownames(var_names[-8])
+
+factor_val_tab %>% 
+  kable() %>% 
+  kable_styling("striped") %>% 
+  scroll_box(width = "100%")
 ```
@@
 
-```{r zds, fig.height=8, fig.width=8}
+```{r fig.height=8, fig.width=8}
 fig_fs_cor <- ggpairs(
@@
 
-```{r pwr-criteria, include=F}
+```{r include=F}
+# define pwr-criteria
 z_crit <- 1.96
@@
 
-```{r pwr-samplesize}
+```{r}
+# estimate pwr-samplesize
 pwr.r.test(r = r_sesoi, sig.level = alpha, power = power_desired, alternative = "greater") %T>%
@@
 
-```{r pwr-achieved}
+```{r}
+# compute pwr-achieved
 pwr.r.test(n = n_final, r = r_sesoi, sig.level = alpha, alternative = "greater") %T>%
@@
 
-```{r pwr-sensitivity}
+```{r}
+# estimate pwr-sensitivity
 pwr.r.test(n = n_final, power = power_desired, sig.level = alpha, alternative = "greater") %T>%
@@
 
-```{r eval=F}
+```{r eval=T}
 cooks_dis <- gCD(d, model_baseline)
@@
 
-```{r eval=F}
+```{r eval=T}
 infl_cases <- invisible(rownames(print(cooks_dis)))
@@
 
-```{r eval=F}
+```{r eval=T}
 infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
@@
         legend.title = element_blank()) +
+  coord_cartesian(ylim = c(0, 7)) +
   scale_fill_brewer(palette="Greys")
@@
 In what follows, we also report explicit statistical tests of the differences between the conditions using contrasts.
-However, please note that several models did not converge.
-This is likely because the models remain complex, while the sample size significantly decreases (i.e., only 2/3 of prior models).
+
+However, please note that several models did not converge. This is likely because the models remain complex, while the sample size significantly decreases (i.e., only 2/3 of prior models).
+
+For these models, we report less complex versions using factors scores, which converge successfully.
 
@@
 ```
+
+Now converges sucessfully.
 

### 2020-04-20 index.Rmd
- updated feedback - updated website

--- 2020-04-17 index.Rmd
@@
 
-Hello world.
+On this website, you can find the companion material for the paper _How Do Like and Dislike Buttons Affect Communication?
+A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment_.
+
+You can either read the paper [online](manuscript.html) or download it as [pdf](manuscript.pdf).
+You can also find the detailed code and summaries of the [analyses](analyses.html) that were reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.
+
+This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp).
+You can download the material and the data, file an issue, or submit a pull request.

### 2020-04-20 manuscript.RmD
- updated feedback - updated website

@@
     All authors contributed extensively to the work presented in this paper.
-TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.
+TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript, ST provided comments; ST supervised the project.
 The authors declare no competing interests.
@@
 
-  This manuscript features online supplementary material, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0).
+    This manuscript features online supplementary material, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
 abstract: |
@@
 mask              : no
-wordcount         : "`r wordcountaddin::word_count('manuscript/manuscript.Rmd')`"
+wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
 draft             : no
@@
 ```{r include=F}
-knitr::opts_chunk$set(cache=F, echo=F)
+knitr::opts_chunk$set(cache=F, echo=F, warning=F, message=F)
 ```
@@
 ```{r setup, include=F}
+# install github packages
+# devtools::install_github("tdienlin/td@v.0.0.2.3")
+
 # load packages
-pcks <- c("devtools", "jpeg", "knitr", "lavaan", "magrittr", "papaja", "png", "pwr", "semTools", "tidyverse")
+pcks <- c("devtools", "jpeg", "knitr", "lavaan", "magrittr", "papaja", "png", "pwr", "semTools", "td", "tidyverse")
 invisible(lapply(pcks, library, character.only = TRUE))
-# install_github("tdienlin/td@v.0.0.2.3")
-library(td)
 
@@
 Understanding why people disclose personal information online remains a critical question for both society and research. 
-Originally, it was claimed that self-disclosure is mostly erratic, and that self-disclosure cannot be predicted by assessing people's personal beliefs, concerns, or standpoints. 
+Originally, it was claimed that self-disclosure is erratic and that it cannot be predicted people's personal beliefs, concerns, or standpoints. 
 Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
@@
 Moreover, independent from which position one adopts, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000].
-In this study we mainly focus on communication quantity, as we consider communication quantity to be a necessary precondition and hence valid proxy for self-disclosure.
+In this study we mainly focus on communication quantity as proxy for self-disclosure.
+The relation between communication quantity and self-disclosure is not linear. 
+Impressions are formed quickly, and the more we have already expressed about ourselves the harder it becomes to self-disclose novel information.
 
@@
 
-Several attempts have already been made to expand the privacy calculus [@dinevExtendedPrivacyCalculus2006], introducing additional variables such as self-efficacy or trust. 
+Several attempts have already been made to expand the privacy calculus, introducing additional variables such as self-efficacy or trust [@dinevExtendedPrivacyCalculus2006]. 
 Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
@@
 
-Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
+The next variable, trust, can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
 It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
@@
 
-The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript (see https://osf.io/hcqat/?view_only=5db35868738d40609b11e58cc343a9b0).
+The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's online companion website (https://tdienlin.github.io/privacy_calc_exp).
 We preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
@@
 Afterward, participants were randomly assigned to one of the three websites. 
-After registration was completed, participants could discuss the topic of the terrorism threat in Germany over the course of one week (_field_). 
+After registration was completed, participants were invited (but not obliged) to discuss the topic of the terrorism threat in Germany over the course of one week (_field_). 
 Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (_T2_). 
@@
 The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
-The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already said.
+The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already expressed.
 
@@
 
-```{r popularitycues, fig.cap="Overview of the variables for the three websites.
+```{r popularitycues, fig.cap="Overview of the model-predicted values for each variable, separated for the three websites.
 Control: Website without buttons.
@@
 Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
-# knitr::include_graphics("figures/results/fig_pop.pdf")
 print(fig_fs_m)

### 2020-04-20 analyses_additional.Rmd
- updated feedback - updated website

@@
     toc_depth: 2
+    code_folding: hide
 ---
@@
 
-```{r r-setup, include=F}
+In what follows, please find the results of additional analyses. These include models, results without covariates, results with all participants (hence, including those removed due to speeding).
+
+# Set-up
+
+Load packages.
+
+```{r r-setup, results='hide'}
 # define packages
@@
 
-```{r Data-Wrangling, include=F, cache=F}
+Load data.
+
+```{r Data-Wrangling, cache=F}
 # load workspace
@@
 
-In what follows, you can find estimations of variance inflation factors to gauge multicollinearity.
+In what follows, you can find estimations of variance inflation factors, which help gauge multicollinearity.
 Generally, values above 5 or even 10 are considered problematic.
@@
 
-```{r vif, include=F}
+```{r vif}
 # Self-Efficacy
@@
 
-In what follows, you can find slightly different models that were also run.
+In what follows, you can find slightly different models that were also explored.
 

### 2020-05-14 manuscript.RmD
- included feedback from ST

@@
 Participants were randomly distributed to three different websites, on which they discussed a current political topic.
+The websites featured either (a) like buttons, (b) like and dislike button, or (c) no like/dislike buttons, and were otherwise identical.
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
@@
 The impact of the popularity cues on self-disclosure and the privacy calculus was negligible.
-In conclusion, the results suggest that privacy concerns and expected benefits are relevant when it comes to understanding self-disclosure, which together provides further evidence against the privacy paradox.
 keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
@@
 Understanding why people disclose personal information online remains a critical question for both society and research. 
-Originally, it was claimed that self-disclosure is erratic and that it cannot be predicted people's personal beliefs, concerns, or standpoints. 
+Originally, it was assumed that online self-disclosure is erratic and that it cannot be predicted by people's personal beliefs, concerns, or standpoints. 
 Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
@@
 Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020].
-However, all three of these approaches have low external validity.
-As a result, in this study we analyze actual information sharing behavior in an authentic online setting.
+However, still missing is a long-term field study, in which actual behavior is observed in an authentic context.
 

### 2020-06-15 analyses.Rmd
- implemented feedback from ST

@@
   stat_summary(fun.y = mean, geom = "bar") +
+  stat_summary(aes(label=round(..y.., 2)), fun.y = mean, geom = "text", 
+               vjust = 2, size = 3) +
   stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +

### 2020-06-15 manuscript.RmD
- implemented feedback from ST

@@
     All authors contributed extensively to the work presented in this paper.
-TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript, ST provided comments; ST supervised the project.
+TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.
+
     The authors declare no competing interests.
@@
     This research was funded by the Volkswagen Foundation, project "Transformations of privacy", which was awarded to Sandra Seubert, Sabine Trepte, Ruediger Grimm, & Christoph Gusy.
-We would like to thank all our colleagues from the project and Niklas Johannes for valuable feedback.
+We would like to thank all our colleagues from the project as well as Niklas Johannes for valuable feedback.
 
-    This manuscript features online supplementary material, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
+    This manuscript features a companion website, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
 abstract: |
@@
 So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior.
-Likewise, we still know little as to whether the privacy calculus can be influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
+Likewise, we still know little as to whether the privacy calculus is influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
 To answer these questions, we ran a preregistered one-week field experiment.
@@
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
-Although the originally preregistered model could not be confirmed, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
+Although the originally preregistered model was rejected, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
 The impact of the popularity cues on self-disclosure and the privacy calculus was negligible.
@@
 #   - \raggedbottom
+#   - \note{\clearpage}
 output:
@@
 
-# Introduction
+<!-- # Introduction -->
 
@@
 
-Somewhat surprisingly, and despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018], the privacy paradox has garnered little empirical support. 
-A recent meta-analysis revealed that the correlation between privacy concerns and self-disclosure on SNS is *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which shows that privacy concerns are indeed related to self-disclosure online.
+Somewhat surprisingly, and despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018], the privacy paradox has garnered comparatively little empirical support. 
+A recent meta-analysis reported a correlation between privacy concerns and self-disclosure on SNS of *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which shows that privacy concerns are indeed often related to self-disclosure online.
 
@@
 
-However, although the privacy calculus has gained some momentum in academic research, several important questions remain unanswered. 
+However, although the privacy calculus has gained momentum in academic research, several important questions remain unanswered. 
 First, we still know little about whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
 Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020].
-However, still missing is a long-term field study, in which actual behavior is observed in an authentic context.
+Still missing is a long-term field study in which actual behavior is observed in an authentic context.
 
@@
 
-Finally, because the privacy calculus does not take place in a vacuum, and because it is often argued that self-disclosure can be easily triggered by external circumstances, we analyze whether the privacy calculus can be affected by the design of a website.
+Finally, because the privacy calculus does not take place in a vacuum and because it is often argued that self-disclosure can be easily triggered by external circumstances, we analyze whether the privacy calculus is affected by the design of a website.
 Specifically, we investigate whether *popularity cues* such as like and dislike buttons have the power to affect the privacy calculus and to foster self-disclosure.
 
-To test our research questions, drawing from a representative sample of the German population we conducted a preregistered online field experiment.
+To test our research questions, we collected a representative sample of the German population and conducted a preregistered online field experiment.
 Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all. 
@@
 There are two different understandings of self-disclosure in the literature: 
-The first defines self-disclosure as _deliberate_ acts of sharing truthful information about the self with others [@jourardTransparentSelf1964]. 
+The first limits self-disclosure to _deliberate_ acts of sharing _truthful_ information about the self with others [@jourardTransparentSelf1964]. 
 The second considers _all_ acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information allows for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011].
@@
 
-Although privacy concerns are related to self-disclosure, one can argue that most studies report only small effects, and that there should be additional factors that also contribute to explaining self-disclosure.
-Most prominently, it has been argued that people trade a loss of privacy for a gain in gratifications such as social capital, entertainment, information, or self-presentation [@ellisonNegotiatingPrivacyConcerns2011; @taddickenUsesPrivacyOnline2011].
-By now, a large body of research has found support for this hypothesis [e.g., @krasnovaOnlineSocialNetworks2010; @minHowArePeople2015; @trepteCrossculturalPerspectivePrivacy2017].
+Although privacy concerns are related to self-disclosure, one can argue that most effects reported in the literature are only small, and that there should be additional factors explaining self-disclosure.
+For example, it has been argued that people trade a loss of privacy for a gain in gratifications [e.g., @taddickenUsesPrivacyOnline2011].
+The most prominent gratifications include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
 
@@
 
-As mentioned above, there is still a shortage of studies that explicitly analyze the decision process behind the disclosing of information---although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017].
+As mentioned above, there is still a shortage of studies explicitly analyzing the decision process behind the disclosing of information---although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017].
 This criticism is justified.
@@
 Hence, research on the privacy calculus would benefit significantly from analyzing this decision process explicitly. 
-Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which captures the extent to which individual people explicitly compare positive and negative potential outcomes before communicating with others.
+Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.
 
@@
 
-RQ1: Are people more or less likely to self-disclose on a website when they more actively deliberate about whether they should self-disclose?
+RQ1: Are people more or less likely to self-disclose on a website depending on how actively they deliberate about whether they should self-disclose?
 
@@
 
-What is the effect of the communication context on the privacy calculus and on self-disclosure? 
-First, it has often been noted that researchers should not exclusively focus on specific features of particular websites, for features are prone to change and quickly become obsolete [@foxDistinguishingTechnologiesSocial2017].
-Instead, it has been suggested to prioritize underlying latent structures, for example by analyzing so-called affordances [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. 
-The concept of affordances was developed by @gibsonEcologicalApproachVisual2015, who argued that it is not the _objective features_ of objects that determine behavior.
-Instead, more important are the _subjective perceptions_. 
-Affordances are a mental representation of how a given entity might be used; as such, they are by definition subjective. 
+How does the communication context affect the privacy calculus and self-disclosure? 
+First, it has often been noted that researchers should not exclusively focus on specific features of particular websites, for they are prone to change and to quickly become obsolete [@foxDistinguishingTechnologiesSocial2017].
+Instead, it has been suggested to prioritize the underlying latent structures by analyzing so-called affordances [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. 
+The concept of affordances was developed by @gibsonEcologicalApproachVisual2015, who argued that it is not the _objective features_ of objects that determine behavior, but our _subjective perceptions_.
+Affordances are mental representations of how objects might be used; as such, they are by definition subjective. 
 There is an ongoing debate on what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017]. 
@@
 
-As the privacy calculus states that both benefits and costs determine behavior, we suggest that popularity cues such as like and dislike buttons, which are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p.
-142], perfectly capture potential benefits and costs.
-The like button is positive. 
+As the privacy calculus states that both benefits and costs determine behavior, we suggest that popularity cues such as like and dislike buttons---which are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p.
+142]---nicely map unto the two sides of the privacy calculus.
+The like button is positive and as such a potential benefit:
 It expresses an endorsement, a compliment, a reward [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017]. 
-However, communication online is also often characterized by negative and critical debates [@ziegeleDynamicsOnlineNews2017]. 
-As the dislike button is a major means of downgrading content it is negative and represents the risk factor of the privacy calculus well. 
-In fact, its stark negative effect might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit, or stackexchange).
+The dislike button is negative and therefore a potential cost: 
+It expresses criticism and is a major means of downgrading content.
 
-Paralinguistic digital affordances and specifically popularity cues have been shown to impact behavior [@kramerMasteringChallengeBalancing2020; @treptePrivacyCalculusContextualized2020].
+Paralinguistic digital affordances and specifically popularity cues can affect behavior [@kramerMasteringChallengeBalancing2020; @treptePrivacyCalculusContextualized2020].
 For example, a large-scale field experiment in which 101,281 comments were analyzed found that comments with dislikes were more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
 @stroudRecommendRespectAltering2017 demonstrated that when users disagreed with a post, they were more likely to click on a button labeled _respect_ compared to a button labeled _like_. 
+The potentially stark negative effect of the dislike button might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit, or stackexchange).
 
-In this vein, it seems plausible that popularity cues might also impact the privacy calculus [@kramerMasteringChallengeBalancing2020].
-First, popularity cues could serve as a means of reward and punishment. 
-Being complimented with a like should encourage future self-disclosure, while being punished with a dislike should inhibit disclosure. 
-Similarly, like buttons imply being able to garner positive feedback, so implementing a like-button---similar to a compliment in the offline world---might leverage gratifications. 
-Implementing popularity cues might also bring people to more actively deliberate about whether or not it is actually worthwhile to disclose information. 
-If both like and dislike buttons are present, privacy deliberation should increase even further. 
-Finally, because people who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017], implementation of the dislike button should both stir privacy concerns and stifle self-disclosure.
+In this vein, it seems plausible that popularity cues might also impact the privacy calculus [@kramerMasteringChallengeBalancing2020], and that they serve as a means of reward and punishment. 
+Receiving a like online is similar to receiving a compliment offline. 
+Likes are positive and represent the positivity bias typical of social media [@reineckeAuthenticityWellbeingSocial2014]. 
+Introducing the option to receive likes thereby affords and emphasizes a _gain frame_
+(see also @rosoffHeuristicsBiasesCyber2013). 
+These gains can be garnered only through participation. 
+In addition, because positive outcomes are emphasized, it is likely that concerns decrease. 
+Finally, in situations where there is more to win, one needs to deliberate whether one wants to partake.
+Implementing like buttons might therefore also make people more actively deliberate about whether or not to disclose information.
 
@@
 
-H6.	Compared to people who use a website without like or dislike buttons, people who use a website with like and dislike buttons (a) self-disclose more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.
+By contrast, receiving a dislike should feel more like a punishment.
+Dislikes introduce a _loss frame_. 
+Although most communication emphasizes positive aspects, the Internet is also replete with spite, envy, and arguments.
+As a result, websites featuring both like _and_ dislike buttons should be more ambivalent compared to websites without any popularity cues.
+In online contexts, gains often outweigh losses, which is why having both types of popularity cues might still lead to more gratifications and self-disclosure.
+However, privacy concerns should not be reduced anymore:
+Because people who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017], implementing the dislike button might increase privacy concerns, thereby canceling out the positive effects of the like button.
+And because both wins and losses can accrue, participants should deliberate even more whether or not to disclose.
+
+H6.	Compared to people who use a website without like or dislike buttons, people who use a website with like _and_ dislike buttons (a) self-disclose more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.
+
+When directly comparing websites including both like and dislike buttons with website including only like buttons, building on the rationales presented above it is likely that websites including both like and dislike buttons should lead to more privacy concerns and privacy deliberation.
 
@@
 
-The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's online companion website (https://tdienlin.github.io/privacy_calc_exp).
+The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's companion website (https://tdienlin.github.io/privacy_calc_exp).
 We preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
@@
 For a full account of all changes, see OSM. 
-New analyses that were not preregistered appear in the section on exploratory analyses.
+New analyses that were not preregistered appear in the section Exploratory analyses.
 
@@
 The study was designed as an online field experiment with three different groups. 
-The first group used a website without like/dislike buttons, the second a website with only like buttons, and the third a website with both like and dislike buttons. 
+The first group used a website without like/dislike buttons, the second the same website but with only like buttons, and the third the same website but with both like and dislike buttons. 
 Participants were randomly distributed to one of the three websites in a between-subject design.
 
-We collaborated with a professional panel agency to recruit participants. 
-As incentive, participants were awarded digital points, which they could use to get special offers from other companies. 
+We collaborated with a professional market research company to recruit participants. 
+As incentive, participants were awarded digital points, which they could use to get special offers from other online commerce services. 
 Participants were above the age of 18 and lived in Germany. 
@@
 In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.[^1] 
-Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which we asked about their sociodemographics, provided more details about the study, and included a registration link for the website.
+Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which we (a) asked about their sociodemographics, (b) provided more details about the study, and (c) included a registration link for the website, which was described as "participation platform".
 Afterward, participants were randomly assigned to one of the three websites. 
@@
 
-```{r website, fig.cap="The website's homepage. (Translated to English; university logos pixelated for peer review.)", fig.align='center', out.width=".9\\textwidth"}
-knitr::include_graphics("figures/website/website_translated.jpg")
+```{r website, fig.cap="The website's homepage. (Translated to English.)", fig.align='center', out.width=".9\\textwidth"}
+knitr::include_graphics("figures/website/website_translated.png")
 ```
@@
 Our aim was to be able to detect this SESOI with a probability of at least 95%.
-Using the regular alpha level of 5%, this leads to a minimum sample size of _n_ = `r n_desired %>% format(big.mark = ",")`.
+Using the regular alpha level of 5%, basic power analyses revealed a minimum sample size of _n_ = `r n_desired %>% format(big.mark = ",")`.
 In the end, we were able to include n = `r n_final` in our analyses (see below). 
@@
 `r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1, `r n_users` participants created a user account on the website,  and `r n_t2` participants completed the survey at T2. 
-Using tokens and IP addresses, we connected the data from T1, participants' behavior on the platform, and T2 by means of objective and automated processes.
-The data for _n_ = `r n_matched` participants could be matched successfully across all three platforms. 
-We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less then three minutes, which we considered to be unreasonably fast. 
-To detect potentially corrupt data, we calculated Cook's distance.[^note]
-We excluded `r n_resp_pattern` participants because they provided clear response patterns (i.e., straight-lining). 
+Using tokens and IP addresses, we connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
+Unfortunately, the data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
+In the end, the data of _n_ = `r n_matched` participants could be matched successfully.
+We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which we considered to be unreasonably fast.[^note] 
+To detect potentially corrupt data, we calculated Cook's distance.
+We excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
 The final sample included `r n_final` participants.
@@
 One participant did not report his or her sex.
-<!-- Despite the dropout and although somewhat higher-educated, also T2 can hence be considered a largely representative sample of the German population. -->
 
@@
 However, this led to the exclusion of too many data points of high quality, which is why we relaxed this criterion.
-In the OSM, we report the results using all participants.
+In the OSM, we report also the results using all participants.
 
@@
 Wherever possible, we operationalized the variables using established measures.
-Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which we pretested concerning their legibility and understandability.
+Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which we pretested concerning legibility and understandability.
 To assess factor validity we ran confirmatory factor analyses (CFA). 
@@
 All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale. 
-Answer options were as follows: -3 (_strongly disagree_), -2 (_disagree_), -1 (_slightly disagree_), 0 (_neutral_), +1 (_slightly agree_), +2 (_agree_), +3 (_strongly agree_). 
+Answer options were visualized as follows: -3 (_strongly disagree_), -2 (_disagree_), -1 (_slightly disagree_), 0 (_neutral_), +1 (_slightly agree_), +2 (_agree_), +3 (_strongly agree_). 
+For the analyses, answers were coded from 1 to 7.
 In the questionnaire, all items measuring a variable were presented on the same page in randomized order.
@@
 
-Self-efficacy was captured with six self-designed items, which measured whether participants felt that they had sufficient self-efficacy to write a comment on the platform. 
+Self-efficacy was captured with six self-designed items, which measured whether participants felt that they had sufficient self-efficacy to write a comment on the website. 
 For example, we asked "I felt technically competent enough to write a comment." 
@@
 Because the dependent variable self-disclosure was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
-As recommended by @klinePrinciplesPracticeStructural2016, we report the following global fit indices: $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
+As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit we report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
 Because sociodemographic variables are often related to self-disclosure and other privacy-related variables [@dindiaSexDifferencesSelfdisclosure1992], we controlled all variables for the influence of sex, age, and education.
@@
 
-It is important to note that the bivariate results showed three very large correlations: First, between specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% .[2, 1] %>% my_round("std")`); second, between privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`); third, between specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`).
+It is important to note that the bivariate results showed three large correlations: First, between specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% .[2, 1] %>% my_round("std")`); second, between privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`); third, between specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`).
 As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.
@@
 
-However, these results should be treated with caution, because they indeed exhibit problems typical of multicollinearity, such as "wrong" signs of the predictors [@grewalMulticollinearityMeasurementError2004].
+However, these results should be treated with caution, because they indeed exhibited problems typical of multicollinearity, such as large standard errors or "wrong" signs of the predictors [@grewalMulticollinearityMeasurementError2004].
 For example, in the multiple regression trust had a _negative_ relation with self-disclosure, whereas in the bivariate analysis it was _positive_.
-
-<!-- As a result, specific trust and general gratifications should not be analyzed within the same model, as the two concepts are empirically too close to one another. -->
 
@@
 Combining variables was not an option in our case, because both trust and expected benefits are theoretically distinct constructs.
-Because several variables were closely related to one another, we therefore decided to fit a simple privacy calculus model, which contains only privacy concerns and specific gratifications.
+And because _several_ variables were closely related to one another, we therefore decided to fit a simple privacy calculus model containing only privacy concerns and specific gratifications.
 
@@
 print(fig_coeffs)
-# print(fig_fs_m)
 ```
@@
 In a next step, we analyzed the potential effects of the popularity cues. 
-Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables. 
-For an illustration, see Figure \@ref(fig:popularitycues), which displays the model-predicted values for each variable (using the baseline model) and shows that the confidence intervals of all preregistered variables overlap.
-For the results of the specific inference tests using contrasts, see the OSM.
+We for example expected that websites with like buttons would lead to more self-disclosure, gratifications, and privacy deliberation and to less privacy concerns.
+Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables whatsoever.
+For an illustration, see Figure \@ref(fig:popularitycues), which displays the model-predicted values for each variable (using the baseline model).
+The results show that the confidence intervals of all preregistered variables overlap, illustrating that there were no statistically significant differences across websites.
+For the detailed results of the specific inference tests using contrasts, see the OSM.
 
@@
 We additionally asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons. 
-The data came from a representative sample of the German population and were analyzed using structural equation modeling with latent variables.
+The data stem from a representative sample of the German population and were analyzed using structural equation modeling with latent variables.
 
@@
 The preregistered extended privacy calculus model was therefore not supported by the data.
-However, the model showed problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a more basal privacy calculus model, which included only privacy concerns and specific gratifications.
+However, the model showed problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a simple privacy calculus model, which included only privacy concerns and specific gratifications.
 
@@
 Determining whether this figure is large or small is a normative question.
-Because although the effect is substantial, one could argue that it should be higher and that we as society should still more actively deliberate about our self-disclosure practices online. 
+Although the effect seems substantial, one could argue that it should be higher and that more people in our society should actively deliberate about their self-disclosure practices online. 
 Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables.
@@
 Users still disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons, potentially highlighting the agency of users.
+This is of course not to say that popularity cues have no impact on the privacy calculus in general. 
+Instead, the results only suggest that there exist certain situations and instances in which the influence of popularity cues is negligible.
 
@@
 Interestingly, multicollinearity might not even be a problem per se, but rather a helpful warning sign. 
-Because from a _statistical_ perspective, strongly correlated predictors only mean that standard errors become larger [@vanhoveCollinearityIsnDisease2019]. 
+From a _statistical_ perspective, strongly correlated predictors only mean that standard errors become larger [@vanhoveCollinearityIsnDisease2019]. 
 In other words, when predictors are strongly correlated we can be less certain about the effects we obtain, because there is less unique variance [@vanhoveCollinearityIsnDisease2019]. 
-As a remedy, researchers could simply collect larger samples, which would allow to achieve sufficient statistical power. 
+As a remedy, researchers could simply collect larger samples, which would increase statistical power and precision.
 Fortunately, using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated/collinear predictors [@wangPowerAnalysisParameter2020].
@@
 
-<!-- Explaining self-disclosure online by means of a basal privacy calculus model instead has the charm of offering a more parsimonious model while still being capable of explaining a substantial part of self-disclosure online.
--->
-
-Furthermore, we found a remarkably strong correlation between specific trust and expected gratifications (i.e., _r_ = .79).
+Furthermore, we found a surprisingly strong correlation between specific trust and expected gratifications (i.e., _r_ = .79).
 At first glance, this strong relation seemed somewhat peculiar to us. 
@@
 Instead, we recommend to use general and reflective measures of trust.
-<!-- , which are less closely related to expected gratifications. -->
-
-<!-- As suggested in literature (), we operationalized trust by measuring how much expertise, benevolence, and reliability participants associated with users, the website, and the providers.
-It seems that these three measures do not measure trust per se, but rather those aspects that cause trust.
-In other words, not trust but antecedents of trust.
-We hence recommend to use measures than focus on the actual psychological experience of trust.
--->
-
-<!-- Finally, this study offers some implications on a meta-level.
-At a time when the social sciences are experiencing an excruciating replication crisis [e.g., @Camerer.2018; @Camerer.2016; @McEwan.2018], it has become increasingly important to further improve the way we go about doing science.
-In this preregistration, we have tried to implement several mechanisms proposed by @Munafo.2017.
-In doing so, we had the chance to learn several important aspects: For example, in the future we will be more hesitant to formulate concrete hypotheses when treading on novel ground.
-Moreover, instead of selling model adaptions as a priori rationales (a practice known as harking; i.e., hypothesizing after results are known), we reported them as additional analyses; we hope to have shown that this does not decrease a paper's value, but instead offers several interesting insights (e.g., that it might be expedient to formulate gratifications specifically rather than generally, or that gratifications and trust are highly correlated).
--->
 
@@
 However, between-person relations often do not translate well to within-person effects [@hamakerCritiqueCrosslaggedPanel2015]. 
-While some studies on privacy concerns online have begun to examine both sources of variance, finding that intrapersonal changes in privacy concerns are indeed related to intrapersonal changes in self-disclosure [@dietvorstAdolescentPerceptionsParental2017], similar analyses are still lacking for the privacy calculus.
+While some studies on privacy concerns online have begun to examine both sources of variance [@dietvorstAdolescentPerceptionsParental2017], similar analyses are still lacking for the privacy calculus.
 
@@
 As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.
-Nevertheless, we deliberately decided to measure the self-reported variables afterward in order not to bias participants or prime our research interest.
+Nevertheless, we deliberately decided to measure the self-reported variables afterward in order not to bias participants.
 
@@
 
-Although we did not find significant effects of like and dislike buttons in this study, this does not necessarily mean that they have no effect on self-disclosure and the privacy calculus in general.
+Again, although we did not find significant effects of like and dislike buttons in this study, this does not mean they have no effect on the privacy calculus in general.
 Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely---states that null findings can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question.
-In this case, we were not able send participants notifications when their comments were liked/disliked, which significantly decreases the popularity cues' salience.
-
-<!-- One can make the case that gratifications should not be measured as reflective constructs but rather as formative constructs.
-However, we have not been able to specify a formative model with adequate fit as of yet.
--->
+In this case, we were not able send participants notifications when their comments were liked/disliked, which significantly decreased the popularity cues' salience.
 
@@
 Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.
-<!-- and, as mentioned above, in times of big data, every piece of communication allows for increasingly accurate inferences about one's personality. -->
 
@@
 In addition, the results suggest that a substantial share of internet users, approximately 30%, consciously engage in a privacy calculus by actively deliberating about whether or not to disclose information.
-Popularity cues such as like and dislike buttons seem to play only a minor role in this process, especially if no means are implemented to guarantee that users are notified about others liking or disliking their communication.
-In conclusion, the results thereby provide further evidence against the privacy paradox.
+Popularity cues such as like and dislike buttons seem to play only a minor role in this process. 
+In conclusion, the results provide further evidence against the privacy paradox.
 Internet users are at least somewhat proactive and reasonable---maybe no more or less proactive or reasonable than in other everyday situations.

### 2020-06-15 preregistration_changes.rmd
- updated feedback - updated website
- implemented feedback from ST

@@
 
-The preregistration can be found here. In what follows, we present where we decided to deviate from preregistration.
+The preregistration can be found [here](https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859). In what follows, we present where we decided to deviate from the preregistration.
 
@@
 
- -	We changed the order of the hypotheses.
- -	We changed the wording of the hypotheses (but not the content)
+ -	We've changed the order of the hypotheses.
+ -	We've changed the wording of the hypotheses (but not the content)
     -	Before: “H1: People are more likely to communicate actively on the website, the less they are concerned about their privacy.”
     - Now: “H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.”
+ -  We've changed the enumeration of the hypotheses (but not the overall number). 
+    - Before, hypotheses were enumerated from 1-13.
+    - Now, it's 1, 2, 3, 4, 5a, 5b, 5c, 5d, 6a, 6b, 6c, 7a, 7b.
 
@@
 In the preregistration, we stated that we would measure expected benefits by means of 5 general items (“Using the participation platform had many benefits for me”).
-However, we had also designed additional items for more specific gratifications that we did not include in the preregistration (the preregistration stated that additional variables that one does not plan to analyze do not need to be preregistered).
+However, we had also designed additional items for more specific gratifications that we did not include in the preregistration (the preregistration manual stated that additional variables that one does not plan to analyze do not need to be preregistered).
 These specific measures of gratifications were hence used for exploratory analyses.
@@
 
-Originally, we operationalized trust for three entities (i.e., provider, website, and other users) with four subdimensions (i.e., general trust, ability, benevolence, and integrity).
-Only later did we realized that the literature differentiates between general and specific trust beliefs, which we could conceptualize with the items we measured.
-As a result, in the paper we differentiated both dimensions.
+Originally, we operationalized trust for three entities (i.e., provider, website, and other users) using four subdimensions (i.e., general trust, ability, benevolence, and integrity).
+Only later did we realize that the literature differentiates between general and specific trust beliefs, which we could conceptualize with the items we measured.
+As a result, in the paper we now differentiate both dimensions.
 
@@
 Given that we found not apparent effects of the three websites on the privacy calculus, we did not test for indirect effects as proposed in the preregistration.
-We additionally also controlled for education (we probably forgot to explicitly mention it in the preregistration; results do not differ, but we think it should be included).
+We additionally also controlled for education (we forgot to explicitly mention this control variable in the preregistration; results do not differ, but we think it should be included, which is why we did).
 
@@
 In the preregistration, we stated that we would analyze the additional exploratory analyses using Bonferroni-Holm correction.
-However, in the meantime we have come to understand that formal inferences tests for exploratory analyses are debatable, for example because the number of tests one would need to account for is potentially infinite.
+However, in the meantime we have come to understand that formal inferences tests for exploratory analyses are debatable, for example because the number of tests one could potentially account for is infinite.
 Instead, we decided not to make strong inferences on the basis of the exploratory analyses, and report p-values / confidence intervals only descriptively as a measure of precision.

### 2020-06-16 index.Rmd
- changed title

@@
 
-On this website, you can find the companion material for the paper _How Do Like and Dislike Buttons Affect Communication?
-A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment_.
+On this website, you can find the companion material for the paper _How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment_.
 
-You can either read the paper [online](manuscript.html) or download it as [pdf](manuscript.pdf).
-You can also find the detailed code and summaries of the [analyses](analyses.html) that were reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.
+You can either read the paper [in your browser](manuscript.html) or download it as [pdf](manuscript.pdf).
+You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.
 

### 2020-06-16 manuscript.RmD
- changed title

@@
 ---
-title             : "How Do Like and Dislike Buttons Affect Communication? A Privacy Calculus Approach to Understanding Self-Disclosure Online in a One-Week Field Experiment"
+title             : "How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment"
 shorttitle        : "Popularity cues and the privacy calculus"
@@
 
-    This manuscript features a companion website, which includes the data, code, additional analyses, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
+    This manuscript features a companion website, which includes the data, code, additional analyses, the preregistration, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
 abstract: |
@@
 
-<!-- # Introduction -->
+# Introduction
 
@@
 Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020].
-Still missing is a long-term field study in which actual behavior is observed in an authentic context.
+Still missing is a more long-term field study in which actual behavior is observed in an authentic context.
 
@@
 The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient evidence for an explicit weighing process.
-Hence, research on the privacy calculus would benefit significantly from analyzing this decision process explicitly. 
+Hence, research on the privacy calculus would benefit from analyzing this decision process explicitly. 
 Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.
@@
 Several attempts have already been made to expand the privacy calculus, introducing additional variables such as self-efficacy or trust [@dinevExtendedPrivacyCalculus2006]. 
-Self-efficacy in the context of the privacy calculus captures whether people believe in their own capability to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
-These privacy behaviors refer to either self-_disclosure_ (e.g., publishing a blog post) or self-_withdrawal_ (e.g., deleting inappropriate content).
+Self-efficacy in the context of the privacy calculus captures whether people believe in their own capacity to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
+These privacy behaviors refer to either _self-disclosure_ (e.g., publishing a blog post) or _self-withdrawal_ (e.g., deleting inappropriate content).
 People who report more privacy self-efficacy also engage in more self-withdrawal  [@chenRevisitingPrivacyParadox2018].
-In light of our focus on active communication, in this study we investigate the influence of self-_disclosure_ self-efficacy.
+In light of our focus on active communication, in this study we investigate the influence of _self-disclosure_ self-efficacy.
 
@@
 55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added].
-Whereas specific trust focuses on the causes of trust, general trust emphasized the experience of trust.
+Whereas specific trust focuses on the causes of trust, general trust emphasizes the experience of trust.
 @gefenTrustTAMOnline2003 prioritize specific trust (p. 60). 
@@
 Likes are positive and represent the positivity bias typical of social media [@reineckeAuthenticityWellbeingSocial2014]. 
-Introducing the option to receive likes thereby affords and emphasizes a _gain frame_
+Introducing the option to receive likes mighty thereby afford and emphasize a _gain frame_
 (see also @rosoffHeuristicsBiasesCyber2013). 
 These gains can be garnered only through participation. 
-In addition, because positive outcomes are emphasized, it is likely that concerns decrease. 
-Finally, in situations where there is more to win, one needs to deliberate whether one wants to partake.
-Implementing like buttons might therefore also make people more actively deliberate about whether or not to disclose information.
+In addition, because like buttons emphasize positive outcomes, it is likely that concerns decrease. 
+Finally, in situations where there is more to win, people should more actively deliberate about whether or not to disclose information.
 
@@
 We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on a smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
-In other words, we defined a minimum effect size that we would consider sufficiently large enough to support our hypotheses. 
-Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be _r_ = `r r_sesoi %>% my_round("std")`.
+In other words, we defined a minimum effect size that we considered sufficiently large enough to support our hypotheses. 
+Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with standardized small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be _r_ = `r r_sesoi %>% my_round("std")`.
 Our aim was to be able to detect this SESOI with a probability of at least 95%.
@@
 Using tokens and IP addresses, we connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
-Unfortunately, the data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
+The data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
 In the end, the data of _n_ = `r n_matched` participants could be matched successfully.
 We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which we considered to be unreasonably fast.[^note] 
-To detect potentially corrupt data, we calculated Cook's distance.
+To detect potentially problematic data, we calculated Cook's distance.
 We excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
@@
 
-In what follows, we present the materials we used to measure our variables. 
+In what follows, we present the materials we used to measure the variables. 
 Wherever possible, we operationalized the variables using established measures.
@@
 One example item was "When using the participation platform, I had concerns about my privacy". 
-One item had to be deleted due to poor psychometric properties.
+One item was deleted due to poor psychometric properties.
 
@@
 
-We differentiated between two separate types of gratification. 
+We differentiated between two separate types of gratifications. 
 _General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
@@
 
-Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two. 
+Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two (preregistered).
 The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
@@
 For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
-Worth noting, specific gratifications and general trust predicted self-disclosure better than general gratifications and specific trust (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
-_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
+Worth noting, specific gratifications predicted self-disclosure better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
+_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
 The mean of privacy deliberation was _m_ = `r des_pridel$m %>% round(2)`. Altogether, `r pridel_active %>% round(0)`% of participants reported having actively deliberated about their privacy.
@@
 
-When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (`r rsquare_fit_adapted * 100` %), followed by the preregistered model (`r rsquare_fit_prereg * 100` %), and the simple privacy calculus model (`r rsquare_fit_simple * 100` %).
+When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (`r round(rsquare_fit_adapted * 100, 2)` %), followed by the preregistered model (`r round(rsquare_fit_prereg * 100, 2)` %), and the simple privacy calculus model (`r round(rsquare_fit_simple * 100, 2)` %).
 At the same time, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
@@
 However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases.
-This is theoretically implausible. 
+This seems theoretically implausible. 
 As a result, we also fit the above-mentioned simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure.
-Taken together, the results support the privacy calculus framework and suggest that self-disclosure online is not erratic and that it can be explained by several psychological variables.
+Taken together, the results support the privacy calculus framework and suggest that---at least in specific contexts---self-disclosure online is not erratic and that it can be explained by several psychological variables.
 
@@
 Determining whether this figure is large or small is a normative question.
-Although the effect seems substantial, one could argue that it should be higher and that more people in our society should actively deliberate about their self-disclosure practices online. 
+Although the effect seems substantial to us, one could argue that it should be higher and that more people should actively deliberate about their self-disclosure practices online. 
 Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables.
@@
 This is of course not to say that popularity cues have no impact on the privacy calculus in general. 
-Instead, the results only suggest that there exist certain situations and instances in which the influence of popularity cues is negligible.
+Instead, the results only suggest that there exist certain contexts in which the influence of popularity cues is negligible.
 
@@
 For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure _while holding trust constant_.
-Theoretically, however, it is more plausible to assume that increasing gratifications also fosters trust [@sollnerWhyDifferentTrust2016].
-In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy, measures which are all strongly correlated.
-In short, the effects we found could even be correct, but the interpretation is much more difficult, artificial, and thereby of little theoretical and practical value.
+Theoretically, however, it is more plausible to assume that increasing gratifications also automatically increases trust [@sollnerWhyDifferentTrust2016].
+In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---measures which are all strongly correlated.
+In short, the effects we found could even be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value.
 

### 2020-07-15 manuscript.RmD
- changed use time from min to h - added explanations to power analyses

@@
 We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). 
-Participants used the website actively: Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(60) %>% round(0) %>% format(big.mark = ",")` minutes online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and left `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
+Participants used the website actively: Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(3600) %>% round(0) %>% format(big.mark = ",")` hours online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and clicked on `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
 Notably, we did not find any instances of people providing meaningless text. 

### 2020-07-15 test.R

@@ -1,0 +1,43 @@
+library(tidyverse)
+
+set.seed(42)
+
+results <- tibble(
+  iteration = c(),
+  raw_cor = c(),
+  raw_p = c(),
+  div_cor = c(),
+  div_p = c()
+)
+
+for (run in 1:1e4){
+  dat <- 
+    tibble(
+      pp = 1:323,
+      estimated = rnorm(323),
+      actual = rnorm(323),
+      divergence = abs(actual - estimated)
+    )
+  
+  raw_correlation <- with(dat, cor.test(actual, estimated))
+  
+  divergence_correlation <- with(dat, cor.test(actual, divergence))
+  
+  run_results <- 
+    tibble(
+      iteration = run,
+      raw_cor = raw_correlation$estimate,
+      raw_p = raw_correlation$p.value,
+      div_cor = divergence_correlation$estimate,
+      div_p = divergence_correlation$p.value
+    )
+  
+  results <- 
+    bind_rows(
+      results,
+      run_results
+    )
+}
+
+mean(results$div_p < .05)
+mean(results$raw_p < .05)

### 2021-07-14 analyses.Rmd
- changed use time from min to h - added explanations to power analyses
- implemented major changes after feedback from reviewers

--- 2020-04-20 analyses.Rmd
@@
 # devtools::install_github("tdienlin/td@v.0.0.2.3")  # uncomment to install
+# devtools::install_github("tdienlin/td")  # uncomment to install
 
 # define packages
-packages <- c("cowplot", "devtools", "faoutlier", "GGally", "gganimate",
+packages <- c("brms", "cowplot", "devtools", "faoutlier", "GGally", "gganimate",
               "kableExtra", "knitr", "lavaan", "magrittr", "MVN", "psych", "pwr", 
@@
     # contrasts
+    like = recode(version, "Control" = 0, "Like" = 1, "Like & Dislike" = 0),
+    likedislike = recode(version, "Control" = 0, "Like" = 0, "Like & Dislike" = 1),
+    control = recode(version, "Control" = 1, "Like" = 0, "Like & Dislike" = 0),
     lik_ctrl = recode(version, "Control" = 0, "Like" = 1),
@@
     # behavioral data
-    words = replace_na(.$words, 0),
+    COMM = replace_na(.$words, 0),
     self_dis = words + (reactions * 2),
@@
     words_log = log1p(.$words),
+    COMM_log = log1p(COMM),
     self_dis_log = log1p(self_dis)
@@
                "Specific trust",
-               "Self-disclosure")
+               "Communication log")
 
@@
                       "Specific\ntrust",
-                      "Self-\ndisclosure")
+                      "Communi-\ncation (log)")
 
@@
  2. ... concerns about disclosing information about myself.
- 3. ... no concerns.
+ 3. ... no concerns. (reversed)
  4. ... concerns that others could discover my real identity (i.e. my last and first name).
@@
 "
-fit <- sem(model = model, data = d, estimator = "MLR", missing = "ML")
+fit <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
 ```
@@
 As it's an inverted item that's not surprising.
-Also from a theoretic perspective it's suboptional, because it doesn't explicitly focus on privacy, but just concerns in general.
+Also from a theoretic perspective it's suboptimal, because it doesn't explicitly focus on privacy, but just concerns in general.
 Will be deleted.
@@
  4. I found it easy to express my opinion regarding the topic.
- 5. I found it complicated to write a comment.
- 6. I was overburdened to write a comment.
+ 5. I found it complicated to write a comment. (reversed)
+ 6. I was overburdened to write a comment. (reversed)
 
@@
 Adapted version shows better and adequate fit.
+
+## Communication
+### Density plot
+
+```{r}
+ggplot(gather(select(d, COMM)), 
+       mapping = aes(x = value)) +
+  geom_density() +
+  facet_wrap(~key, nrow=1) + 
+  theme_bw()
+```
+
+We see that Communication is severely skewed. Will hence be log-scaled for SEMs.
+
+## Communication Logged
+
+```{r}
+ggplot(gather(select(d, COMM_log)), 
+       mapping = aes(x = value)) +
+  geom_density() +
+  facet_wrap(~key, nrow=1) + 
+  theme_bw()
+```
 
@@
     SE01_03 ~~ x*SE01_04
-  self_dis_lg =~ self_dis_log
-
-  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
-"
-fit_baseline <- sem(model_baseline, data = d, missing = "ML")
+  comm_log =~ COMM_log
+
+ comm_log ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
+"
+
+fit_baseline <- lavaan::sem(model_baseline, data = d, missing = "ML")
 summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
@@
          self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
-  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)
+  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, COMM_log)
 
 # combine d with d factor scores
-d %<>% cbind(select(d_fs, -version, -self_dis_log))
+d %<>% cbind(select(d_fs, -version, -COMM_log))
+
+# add centered predictors for interaction analyses later
+d %<>%
+  mutate(pri_con_fs_c = scale(pri_con_fs, scale = FALSE),
+         grats_spec_fs_c = scale(grats_spec_fs, scale = FALSE),
+         pri_del_fs_c = scale(pri_del_fs, scale = FALSE),
+         trust_gen_fs_c = scale(trust_gen_fs, scale = FALSE),
+         self_eff_fs_c = scale(self_eff_fs, scale = FALSE),
+         con_x_del = pri_con_fs_c * pri_del_fs_c,
+         grats_x_del = grats_spec_fs_c * pri_del_fs_c)
 
@@
                         trust_spec_factor_val) %$%
-  cbind(des[-8, ], .) %>%
-  set_rownames(var_names[-8])
+  cbind(des[-c(8), ], .) %>%
+  set_rownames(var_names[-c(8)])
 
@@
 
-```{r fig.height=8, fig.width=8}
-fig_fs_cor <- ggpairs(
-  select(d_fs, -version),
-  upper = list(continuous = "cor"),
+```{r fig.height=9, fig.width=9}
+corr_plot <- ggpairs(select(d_fs, -version),
+                     upper = list(continuous = cor_plot),
                      lower = list(continuous = wrap(td::scat_plot, coords = c(1, 7, 0, 7)))) + 
   theme_bw()
-print(fig_fs_cor)
+print(corr_plot)
+ggsave("figures/results/cor_plot.png")
 ```
@@
 # Power analyses
+
+In what follows, we report power analyses for our study.
+Please note that we conduct a rudimentary power-analysis, assuming bivariate correlations.
+To explain, at the time we were not yet aware of the existence of power analyses for multivariate structural equation models.
 
@@
 # create subset of data with all items that were used
-d_sub <- d[, c("self_dis_log", "GR02_01", "GR02_02", "GR02_03", "GR02_04", "GR02_05", "PC01_01", "PC01_02", "PC01_04", "PC01_05", "PC01_06", "PC01_07", "TR01_02", "TR01_03", "TR01_04", "TR01_06", "TR01_07", "TR01_08", "TR01_10", "TR01_11", "TR01_12", "PD01_01", "PD01_02", "PD01_03", "PD01_04", "PD01_05", "SE01_01", "SE01_02", "SE01_03", "SE01_04", "male", "age", "edu")]
+d_sub <- d[, c("COMM", "GR02_01", "GR02_02", "GR02_03", "GR02_04", "GR02_05", "PC01_01", "PC01_02", "PC01_04", "PC01_05", "PC01_06", "PC01_07", "TR01_02", "TR01_03", "TR01_04", "TR01_06", "TR01_07", "TR01_08", "TR01_10", "TR01_11", "TR01_12", "PD01_01", "PD01_02", "PD01_03", "PD01_04", "PD01_05", "SE01_01", "SE01_02", "SE01_03", "SE01_04", "male", "age", "edu")]
 
@@
 
-In what follows we test for influential cases in baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.
-
-```{r eval=T}
+[Note: These lines stopped working after some time, potentially due to changes in package.]
+
+In what follows we test for influential cases in the baseline model, to detect potentially corrupt data (e.g., people who provided response patterns). Specifically, we compute Cook's distance.
+
+```{r eval=F}
 cooks_dis <- gCD(d, model_baseline)
@@
 
-```{r eval=T}
+```{r eval=F}
 infl_cases <- invisible(rownames(print(cooks_dis)))
@@
 
-```{r eval=T}
+```{r eval=F}
 infl_cases_tokens <- d[infl_cases, "case_token"] %>% as_vector()
@@
 
-self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
+COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
 
 # Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
+COMM_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+
+# Covariances
+male ~~ age + edu
+age ~~ edu
+"
+fit_prereg <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
 summary(fit_prereg, fit = TRUE, std = TRUE)
-rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
-```
+rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
+```
+
+Results show that there's only one significant predictor of Communication, being self-efficacy.
+The other predictors are in the direction as planned, albeit not significant.
+Trust, however, shows the inverse relation as effect, that is, more trust, less communication.
 
@@
 
-self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
+COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
 
 # Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
+COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 + TR01_01 + TR01_05 + TR01_09 ~ male + age + edu
+
+# Covariances
+male ~~ age + edu
+age ~~ edu
+"
+fit_adapted <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
 summary(fit_adapted, fit = TRUE, std = TRUE)
-rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
-```
+rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
+```
+
+Effects become a bit larger and significant, which seems to make sense. However, this also includes trust, which is a significant negative predictor of communication.
+
+### Model "Interaction"
+
+We now estimate an interaction model, as suggested by an anomymous reviewer. To estimate the interaction we'll use factor scores.
+
+```{r}
+model <- "
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_gen =~ TR01_01 + TR01_05 + TR01_09
+
+COMM_log ~ a1*pri_con_fs_c + b1*grats_spec_fs_c + c1*pri_del_fs_c + con_x_del + grats_x_del + d1*self_eff + e1*trust_gen
+
+# Covariates
+COMM_log + SE01_01 + SE01_02 + SE01_03 + SE01_04 + TR01_01 + TR01_05 + TR01_09 + pri_con_fs_c + grats_spec_fs_c + pri_del_fs_c + con_x_del ~ male + age + edu
+
+# Covariances
+pri_con_fs_c ~~ grats_spec_fs_c + pri_del_fs_c + con_x_del + grats_x_del + self_eff + trust_gen
+grats_spec_fs_c ~~ pri_del_fs_c + con_x_del + grats_x_del + self_eff + trust_gen
+pri_del_fs_c ~~ con_x_del + grats_x_del + self_eff + trust_gen
+con_x_del ~~ grats_x_del + self_eff + trust_gen
+grats_x_del ~~ self_eff + trust_gen
+self_eff ~~ trust_gen
+male ~~ age + edu
+age ~~ edu
+"
+
+fit_inter <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
+summary(fit_inter, fit = TRUE, std = TRUE)
+rsquare_fit_inter <- inspect(fit_inter, what = "rsquare")["comm"]
+```
+
+Results are interesting.
+Both interaction effects are significant.
+If Deliberation increases, the effect of concerns on communication increase (net effect).
+If Deliberation increases, the effect of gratifications on communication decrease.
+Hence, could imply that if people think more, concerns more relevant than benefits.
 
@@
 
-We now use only variables, that is specific gratifications and privacy concerns.
+We now use only two variables, namely specific gratifications and privacy concerns.
 
@@
 
-self_dis_log ~ a1*pri_con + b1*grats_spec
+COMM_log ~ a1*pri_con + b1*grats_spec
 
 # Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
+COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
+
+# Covariances
+male ~~ age + edu
+age ~~ edu
+"
+fit_simple <- lavaan::sem(model, data = d, estimator = "MLR", missing = "ML")
 summary(fit_simple, fit = TRUE, std = TRUE)
-rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
-```
+rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
+```
+
+Works as hypothesized.
 
@@
         text = element_text(size = 12)) +
-  coord_cartesian(xlim = c(-1.5, 1.5))
-
+  coord_cartesian(xlim = c(-1.3, 1.3))
+ggsave("figures/results/coeffs.png")
 fig_coeffs
+```
+
+### Model "BRMS"
+
+Because the dependent variable is a zero-inflated Poisson distribution, we'll also run Bayesian models, which can explicitly account for this distribution.
+
+#### Adapted Model
+
+```{r}
+fit_brms <- brm(COMM ~ pri_con_fs + grats_spec_fs + pri_del_fs + self_eff_fs + trust_gen_fs, data = d, family = zero_inflated_poisson())
+d_predicted <- predict(fit_brms) %>% as.data.frame()
+summary(fit_brms)
+```
+
+Shows very similar results compared to SEM. Again, trust a negative predictor.
+
+##### Plot predicted values
+
+Let's also look at how values are predicted to see how model performs.
+
+```{r}
+d_predicted <- predict(fit_brms) %>% as.data.frame()
+ggplot(d_predicted, aes(Estimate)) + 
+  geom_density()
+```
+
+Let's also plot actual values.
+
+```{r}
+# plot actual values
+ggplot(d, aes(COMM)) + 
+  geom_density()
+```
+
+Model-predicted values don't closely match actual values.
+
+#### Without Trust
+
+Because trust has a negative coefficient, which seems generally implausible, we also run a model without trust.
+
+```{r}
+fit_brms <- brm(COMM ~ pri_con_fs + grats_spec_fs + pri_del_fs + self_eff_fs, data = d, family = zero_inflated_poisson())
+d_predicted <- predict(fit_brms) %>% as.data.frame()
+summary(fit_brms)
+```
+
+Seems to make sense. Self-Efficacy a strong predictor of behavior.
+
+#### Simple model
+
+```{r}
+fit_brms_simple <- brm(COMM ~ pri_con_fs + grats_spec_fs, data = d, family = zero_inflated_poisson())
+summary(fit_brms_simple)
+```
+
+Also works, showing somewhat stronger effects.
+
+#### Simple hurdle model
+
+```{r}
+fit_brms_simple_hurdle <- brm(bf(COMM ~ pri_con_fs + grats_spec_fs, hu ~ pri_con_fs + grats_spec_fs), data = d, family = hurdle_poisson())
+summary(fit_brms_simple_hurdle)
+```
+
+Results don't differ markedly.
+
+#### Interaction model
+
+```{r}
+fit_brms <- brm(COMM ~ pri_con_fs_c * grats_spec_fs_c, data = d, family = zero_inflated_poisson())
+summary(fit_brms)
+```
+
+The effect of concerns on communication become weaker if gratifications increase.
+
+#### Interaction model including deliberation
+
+```{r}
+fit_brms <- brm(COMM ~ pri_con_fs_c * grats_spec_fs_c + pri_con_fs_c * pri_del_fs_c + grats_spec_fs_c * pri_del_fs_c, data = d, family = zero_inflated_poisson())
+summary(fit_brms)
 ```
@@
 The easiest way to assess the effect of the experimental manipulation on the variables is by visualizing their means.
-If 95% confidence intervals don't overlap, the variables differ significantly across the conditions.
+If 83% confidence intervals don't overlap, the variables differ significantly across the conditions.
 One can quickly see that there aren't any major effects.
@@
 ```{r}
+# violin plot
 fig_fs_m <- ggplot(
@@
   aes(x = version, y = value, fill = version)) +
-  stat_summary(fun.y = mean, geom = "bar") +
-  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
+  geom_violin(trim = TRUE) +
+  stat_summary(fun.y = mean, geom = "point") +
+  #  stat_summary(aes(label = round(..y.., 2)), fun.y = mean, geom = "text", 
+  #              vjust = 0, size = 3
+  #              ) +
+  #  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .5) +
+  stat_summary(fun.data = mean_se, fun.args = list(mult = 1.39), geom = "errorbar", width = .5) + 
   facet_wrap(~ variable, nrow = 2) + 
@@
         axis.title.x = element_blank(),
-        axis.text.x = element_blank(),
+        # axis.text.x = element_blank(),
         plot.title = element_text(hjust = .5),
@@
         text = element_text(size = 12),
-        legend.position="bottom",
+        legend.position="none",
         legend.title = element_blank()) +
   coord_cartesian(ylim = c(0, 7)) +
-  scale_fill_brewer(palette="Greys")
+  scale_fill_brewer(palette = "Greys")
+ggsave("figures/results/violin_plot.png")
 fig_fs_m
+
+# barplot
+# fig_fs_m <- ggplot(
+#   gather(d_fs, variable, value, -version) %>% 
+#     mutate(variable = factor(variable, levels = var_names_breaks)),
+#   aes(x = version, y = value, fill = version)) +
+#   stat_summary(fun.y = mean, geom = "bar") +
+#   stat_summary(aes(label=round(..y.., 2)), fun.y = mean, geom = "text", 
+#                vjust = 2, size = 3) +
+#   stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .75) +
+#   facet_wrap(~ variable, nrow = 2) + 
+#   theme_bw() +
+#   theme(axis.title.y = element_blank(),
+#         axis.title.x = element_blank(),
+#         axis.text.x = element_blank(),
+#         plot.title = element_text(hjust = .5),
+#         panel.spacing = unit(.9, "lines"),
+#         text = element_text(size = 12),
+#         legend.position="bottom",
+#         legend.title = element_blank()) +
+#   coord_cartesian(ylim = c(0, 7)) +
+#   scale_fill_brewer(palette="Greys")
+# fig_fs_m
 ```
@@
 
-However, please note that several models did not converge. This is likely because the models remain complex, while the sample size significantly decreases (i.e., only 2/3 of prior models).
-
-For these models, we report less complex versions using factors scores, which converge successfully.
-
-#### Like vs. Control
+#### Like & Like-Dislike vs. Control
 
@@
 
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
+pri_con + grats_gen + pri_delib + self_eff + trust_spec + COMM ~ like + likedislike
+
+# pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ like + likedislike
+# COMM ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*like + g*likedislike
 
 # Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
+# COMM + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_lik_ctrl <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
 summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
@@
 
-Model did not converge. It's likely too complex given the reduced number of participants. The trust subdimension "provider" seems to cause trouble. Will hence be substituted with factor score.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
-```
-
-Now converges sucessfully.
-
-#### Like & Dislike vs. Control
+No significant effects of popularity cues on privacy calculus.
+
+#### Like-Dislike & Control vs. Like
 
@@
 
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
+pri_con + grats_gen + pri_delib + self_eff + trust_spec + COMM ~ likedislike + control
+
+# pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ like + likedislike
+# COMM ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*like + g*likedislike
 
 # Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-Again, does not converge; will use `Trust Specific` as factor score.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_lik, fit = TRUE, std = TRUE)
-```
-
-This time, does converge, no need to change model.
+# COMM + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_lik_ctrl <- lavaan::sem(model = model, data = d, estimator = "MLR", missing = "ML")
+summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
+```
+
+No significant effects of popularity cues on privacy calculus.
 
@@
      fit_baseline, fit_prereg, fit_adapted, fit_simple,
-     fig_fs_m, fig_fs_cor, fig_coeffs,
+     fig_fs_m, fig_coeffs,
      des_pridel,

### 2021-07-14 analyses_additional.Rmd
- implemented major changes after feedback from reviewers

@@
 
-# Additional analyses
+# Communication
 
-In what follows, you can find slightly different models that were also explored.
+In what follows, we report the results for the not-logged, that is the regular measure of communication.
 
-## Privacy calculus
-### Model 1
+## Model "Peregistered"
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
+grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_community =~ TR01_02 + TR01_03 + TR01_04
+trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+trust_spec =~ trust_community + trust_provider
+
+COMM ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
+
+# Covariates
+COMM + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
+summary(fit_prereg, fit = TRUE, std = TRUE)
+rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
+```
+
+## Model "Adapted"
+
+Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_gen =~ TR01_01 + TR01_05 + TR01_09
+
+COMM ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
+
+# Covariates
+COMM + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
+summary(fit_adapted, fit = TRUE, std = TRUE)
+rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
+```
+
+## Model "Simple"
+
+We now use only variables, that is specific gratifications and privacy concerns.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+
+COMM ~ a1*pri_con + b1*grats_spec
+
+# Covariates
+COMM + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
+"
+fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
+summary(fit_simple, fit = TRUE, std = TRUE)
+rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
+```
+
+# Preregistered Model
+
+We first analyze the same models as before, but analyzing self-disclosure instead of communication. This was how we initially preregistered the study.
+
+## Model "Peregistered"
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
+grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_community =~ TR01_02 + TR01_03 + TR01_04
+trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+trust_spec =~ trust_community + trust_provider
+
+self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
+
+# Covariates
+self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
+summary(fit_prereg, fit = TRUE, std = TRUE)
+rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["self_dis_log"]
+```
+
+## Model "Adapted"
+
+Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_gen =~ TR01_01 + TR01_05 + TR01_09
+
+self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
+
+# Covariates
+self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
+summary(fit_adapted, fit = TRUE, std = TRUE)
+rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["self_dis_log"]
+```
+
+## Model "Simple"
+
+We now use only variables, that is specific gratifications and privacy concerns.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+
+self_dis_log ~ a1*pri_con + b1*grats_spec
+
+# Covariates
+self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
+"
+fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
+summary(fit_simple, fit = TRUE, std = TRUE)
+rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["self_dis_log"]
+```
 
@@
 
-### Model 2
+# Results without covariates
+
+As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain virtually the same.
+
+### Model "Peregistered"
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
+grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_community =~ TR01_02 + TR01_03 + TR01_04
+trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+trust_spec =~ trust_community + trust_provider
+
+COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
+"
+fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
+summary(fit_prereg, fit = TRUE, std = TRUE)
+rsquare_fit_prereg <- inspect(fit_prereg, what = "rsquare")["comm"]
+```
+
+### Model "Adapted"
+
+Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_gen =~ TR01_01 + TR01_05 + TR01_09
+
+COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
+"
+fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
+summary(fit_adapted, fit = TRUE, std = TRUE)
+rsquare_fit_adapted <- inspect(fit_adapted, what = "rsquare")["comm"]
+```
+
+### Model "Simple"
+
+We now use only variables, that is specific gratifications and privacy concerns.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+
+COMM_log ~ a1*pri_con + b1*grats_spec
+"
+fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
+summary(fit_simple, fit = TRUE, std = TRUE)
+rsquare_fit_simple <- inspect(fit_simple, what = "rsquare")["comm"]
+```
+
+# Results including removed participants
+
+As stated in the preregistration, we also report the analyses including the deleted participants. Results don't change meaningfully.
+
+## Baseline model
+
+```{r}
+model_baseline <- "
+  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
+  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
+  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+  grats_par =~ GR01_07 + GR01_08 + GR01_09
+  grats_ide =~ GR01_10 + GR01_11 + GR01_12
+  grats_ext =~ GR01_13 + GR01_14 + GR01_15
+  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+  trust_gen =~ TR01_01 + TR01_05 + TR01_09
+  trust_community =~ TR01_02 + TR01_03 + TR01_04
+  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+  trust_spec =~ trust_community + trust_provider
+  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+    SE01_01 ~~ x*SE01_02
+    SE01_03 ~~ x*SE01_04
+  comm_log =~ COMM_log
+
+  COMM_log ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
+"
+fit_baseline <- sem(model_baseline, data = d_all, missing = "ML")
+summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
+```
+
+```{r}
+# extract model predicted values for items & calc means
+d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
+  as.data.frame() %>% 
+  mutate(version = d_all$version, 
+         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
+         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
+         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
+         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
+         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
+         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
+         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
+  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, COMM_log)
+
+# combine d with d factor scores
+d_all %<>% cbind(select(d_fs, -version, -COMM_log))
+```
+
+## Privacy calculus
+## Model "Peregistered"
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
+grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_community =~ TR01_02 + TR01_03 + TR01_04
+trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
+trust_spec =~ trust_community + trust_provider
+
+COMM_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
+
+# Covariates
+COMM_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_prereg <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
+summary(fit_prereg, fit = TRUE, std = TRUE)
+```
+
+## Model "Adapted"
+
+Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
+self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
+  SE01_01 ~~ x*SE01_02
+  SE01_03 ~~ x*SE01_04
+trust_gen =~ TR01_01 + TR01_05 + TR01_09
+
+COMM_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
+
+# Covariates
+COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
+"
+fit_adapted <- sem(model, data = d_all, estimator = "MLR", missing = "ML", missing = "ML")
+summary(fit_adapted, fit = TRUE, std = TRUE)
+```
+
+## Model "Simple"
+
+We now use only variables, that is specific gratifications and privacy concerns.
+
+```{r}
+model <- "
+pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
+grats_inf =~ GR01_01 + GR01_02 + GR01_03 
+grats_rel =~ GR01_04 + GR01_05 + GR01_06 
+grats_par =~ GR01_07 + GR01_08 + GR01_09
+grats_ide =~ GR01_10 + GR01_11 + GR01_12 
+grats_ext =~ GR01_13 + GR01_14 + GR01_15
+grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
+
+COMM_log ~ a1*pri_con + b1*grats_spec
+
+# Covariates
+COMM_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
+"
+fit_simple <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
+summary(fit_simple, fit = TRUE, std = TRUE)
+```
+
+# Alternative Models
+
+In what follows, you can find slightly different models that were also explored.
+
+## Model 1
 
@@
 
-### Model 3
+## Model 2
 
@@
 
-### Model 4
+## Model 3
 
@@
 
-### Model 5
+## Model 4
 
@@
 ```
-
-## Effect of popularity cues
-### Like vs. control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con ~ a1*lik_ctrl
-grats_spec ~ a2*lik_ctrl
-self_dis_log ~ b1*pri_con + b2*grats_spec + c1*lik_ctrl
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_lik_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_lik_ctrl_simple, fit = TRUE, std = TRUE)
-```
-
-### Like & dislike vs. control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con + grats_spec ~ likdis_ctrl
-self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_ctrl
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_likdis_ctrl_simple <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_ctrl_simple, std = TRUE)
-```
-
-### Like & dislike vs. like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-pri_con + grats_spec ~ likdis_lik
-self_dis_log ~ a1*pri_con + b1*grats_spec + likdis_lik
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_lik, std = TRUE, fit = TRUE)
-```
-
-# Results without covariates
-
-As stated in our preregistration, we also provide the results of all analyses without controlling for covariates. The results remain the same.
-
-## Privacy calculus
-### Model "Peregistered"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
-"
-fit_prereg <- sem(model, data = d, estimator = "MLR", missing = "ML")
-summary(fit_prereg, fit = TRUE, std = TRUE)
-```
-
-### Model "Adapted"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_gen =~ TR01_01 + TR01_05 + TR01_09
-
-self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
-"
-fit_adapted <- sem(model, data = d, estimator = "MLR", missing = "ML", missing = "ML")
-summary(fit_adapted, fit = TRUE, std = TRUE)
-```
-
-### Model "Simple"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-self_dis_log ~ a1*pri_con + b1*grats_spec
-"
-fit_simple <- sem(model, data = d, estimator = "MLR", missing = "ML")
-summary(fit_simple, fit = TRUE, std = TRUE)
-```
-
-## Effects of popularity cues
-### Preregistered
-#### Like vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*lik_ctrl
-"
-fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_ctrl
-"
-fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d*self_eff + e*trust_spec + f*likdis_lik
-"
-
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_lik, fit = TRUE, std = TRUE)
-```
-
-# Results including removed participants
-
-As stated in the preregistration, we also report the analyses including the deleted participants. Results don't change meaningfully.
-
-## Baseline model
-
-```{r}
-model_baseline <- "
-  pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-  grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-  grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-  grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-  grats_par =~ GR01_07 + GR01_08 + GR01_09
-  grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-  grats_ext =~ GR01_13 + GR01_14 + GR01_15
-  grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-  pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-  trust_gen =~ TR01_01 + TR01_05 + TR01_09
-  trust_community =~ TR01_02 + TR01_03 + TR01_04
-  trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-  trust_spec =~ trust_community + trust_provider
-  self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-    SE01_01 ~~ x*SE01_02
-    SE01_03 ~~ x*SE01_04
-  self_dis_lg =~ self_dis_log
-
-  self_dis_lg ~~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec + f1*trust_gen + g1*grats_spec
-"
-fit_baseline <- sem(model_baseline, data = d_all, missing = "ML")
-summary(fit_baseline, standardized = TRUE, fit.measures = TRUE)
-```
-
-```{r}
-# extract model predicted values for items & calc means
-d_fs <- lavPredict(fit_baseline, type = "ov") %>% 
-  as.data.frame() %>% 
-  mutate(version = d_all$version, 
-         grats_gen_fs = rowMeans(select(., starts_with("GR02"))),
-         grats_spec_fs = rowMeans(select(., starts_with("GR01"))), 
-         pri_con_fs = rowMeans(select(., starts_with("PC01"))),
-         trust_gen_fs = rowMeans(select(., TR01_01, TR01_05, TR01_09)),
-         trust_spec_fs = rowMeans(select(., TR01_02: TR01_04, TR01_06 : TR01_12)),
-         pri_del_fs = rowMeans(select(., starts_with("PD01"))),
-         self_eff_fs = rowMeans(select(., starts_with("SE01")))) %>%
-  select(version, pri_con_fs, grats_gen_fs, grats_spec_fs, pri_del_fs, self_eff_fs, trust_gen_fs, trust_spec_fs, self_dis_log)
-
-# combine d with d factor scores
-d_all %<>% cbind(select(d_fs, -version, -self_dis_log))
-```
-
-## Privacy calculus
-### Model "Peregistered"
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-self_dis_log ~ a1*pri_con + b1*grats_gen + c1*pri_delib + d1*self_eff + e1*trust_spec
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_prereg <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
-summary(fit_prereg, fit = TRUE, std = TRUE)
-```
-
-### Model "Adapted"
-
-Building on the preregistered model, instead of general gratifications and specific trust, we now use specific gratifications and general trust.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_gen =~ TR01_01 + TR01_05 + TR01_09
-
-self_dis_log ~ a1*pri_con + b1*grats_spec + c1*pri_delib + d1*self_eff + e1*trust_gen
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_01 + TR01_05 + TR01_09 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_adapted <- sem(model, data = d_all, estimator = "MLR", missing = "ML", missing = "ML")
-summary(fit_adapted, fit = TRUE, std = TRUE)
-```
-
-### Model "Simple"
-
-We now use only variables, that is specific gratifications and privacy concerns.
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07  
-grats_inf =~ GR01_01 + GR01_02 + GR01_03 
-grats_rel =~ GR01_04 + GR01_05 + GR01_06 
-grats_par =~ GR01_07 + GR01_08 + GR01_09
-grats_ide =~ GR01_10 + GR01_11 + GR01_12 
-grats_ext =~ GR01_13 + GR01_14 + GR01_15
-grats_spec =~ grats_inf + grats_rel + grats_par + grats_ide + grats_ext
-
-self_dis_log ~ a1*pri_con + b1*grats_spec
-
-# Covariates
-self_dis_log + GR01_01 + GR01_02 + GR01_03 + GR01_04 + GR01_05 + GR01_06 + GR01_07 + GR01_08 + GR01_09 + GR01_10 + GR01_11 + GR01_12 + GR01_13 + GR01_14 + GR01_15 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 ~ male + age + edu
-"
-fit_simple <- sem(model, data = d_all, estimator = "MLR", missing = "ML")
-summary(fit_simple, fit = TRUE, std = TRUE)
-```
-
-## Effects of popularity cues
-### Preregistered
-
-#### Like vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ lik_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*lik_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_lik_ctrl <- sem(model = model, data = dplyr::filter(d_all, !is.na(lik_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_lik_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Control
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_spec =~ trust_spec_fs
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_ctrl
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*likdis_ctrl
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-fit_likdis_ctrl <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_ctrl)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_ctrl, fit = TRUE, std = TRUE)
-```
-
-#### Like & Dislike vs. Like
-
-```{r}
-model <- "
-pri_con =~ PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07
-grats_gen =~ GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05
-pri_delib =~ PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05
-self_eff =~ SE01_01 + SE01_02 + SE01_03 + SE01_04
-  SE01_01 ~~ x*SE01_02
-  SE01_03 ~~ x*SE01_04
-trust_community =~ TR01_02 + TR01_03 + TR01_04
-trust_provider =~ TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12
-trust_spec =~ trust_community + trust_provider
-
-pri_con + grats_gen + pri_delib + self_eff + trust_spec ~ likdis_lik
-self_dis_log ~ a*pri_con + b*grats_gen + c*pri_delib + d_all*self_eff + e*trust_spec + f*likdis_lik
-
-# Covariates
-self_dis_log + GR02_01 + GR02_02 + GR02_03 + GR02_04 + GR02_05 + PC01_01 + PC01_02 + PC01_04 + PC01_05 + PC01_06 + PC01_07 + TR01_02 + TR01_03 + TR01_04 + TR01_06 + TR01_07 + TR01_08 + TR01_10 + TR01_11 + TR01_12 + PD01_01 + PD01_02 + PD01_03 + PD01_04 + PD01_05 + SE01_01 + SE01_02 + SE01_03 + SE01_04 ~ male + age + edu
-"
-
-fit_likdis_lik <- sem(model = model, data = dplyr::filter(d_all, !is.na(likdis_lik)), estimator = "MLR", missing = "ML")
-summary(fit_likdis_lik, fit = TRUE, std = TRUE)
-```

### 2021-07-14 manuscript.RmD
- implemented major changes after feedback from reviewers

--- 2020-06-16 manuscript.RmD
@@
 ---
-title             : "How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment"
-shorttitle        : "Popularity cues and the privacy calculus"
-author:            
-  - name          : "Dienlin, Tobias"
-    email         : "tobias.dienlin@uni-hohenheim.de"
-    affiliation   : "1"
-    corresponding : yes
-    address       : "University of Hohenheim, Department of Media Psychology (540F), 70599 Stuttgart, Germany"
-  - name          : "Braeunlich, Katharina"
-    email         : "braeunlich@uni-koblenz.de"
-    affiliation   : "2"
-  - name          : "Trepte, Sabine"
-    email         : "sabine.trepte@uni-hohenheim.de"
-    affiliation   : "1"
-affiliation:
-  - id            : "1"
-    institution   : "University of Hohenheim"
-  - id            : "2"
-    institution   : "University of Koblenz-Landau"
-author_note: |
-    All authors contributed extensively to the work presented in this paper.
-TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.
-
-    The authors declare no competing interests.
-
-    This research was funded by the Volkswagen Foundation, project "Transformations of privacy", which was awarded to Sandra Seubert, Sabine Trepte, Ruediger Grimm, & Christoph Gusy.
-We would like to thank all our colleagues from the project as well as Niklas Johannes for valuable feedback.
-
-    This manuscript features a companion website, which includes the data, code, additional analyses, the preregistration, and a reproducible version of the manuscript (https://tdienlin.github.io/privacy_calc_exp).
+title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus when Communicating Online"
+shorttitle        : "Popularity cues & privacy calculus"
 abstract: |
-    According to the privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
-So far, however, most findings were based on self-reports, and little is known about whether the privacy calculus can be used to explain observations of actual behavior.
-Likewise, we still know little as to whether the privacy calculus is influenced by the design of online websites, including for example popularity cues such as like and dislike buttons.
-To answer these questions, we ran a preregistered one-week field experiment.
+    According to privacy calculus, both privacy concerns and expected gratifications explain why people communicate online.
+So far, most findings were based on self-reports or short-term experiments, and it is still largely unknown how popularity cues such as like and dislike buttons affect privacy calculus.
+To answer these questions, a preregistered one-week field experiment was conducted.
 Participants were randomly distributed to three different websites, on which they discussed a current political topic.
-The websites featured either (a) like buttons, (b) like and dislike button, or (c) no like/dislike buttons, and were otherwise identical.
+The websites featured either (a) like buttons, (b) like and dislike buttons, or (c) no like or dislike buttons, and were otherwise identical.
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
-Although the originally preregistered model was rejected, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
-The impact of the popularity cues on self-disclosure and the privacy calculus was negligible.
-keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
+Although the originally preregistered model was largely rejected, the results showed that a considerable share of actual communication could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
+The impact of the popularity cues on privacy calculus and communication was negligible.
+keywords          : "privacy calculus, communication, popularity cues, field experiment, structural equation modeling, preregistration"
 bibliography      : 
@@
 linenumbers       : yes
-mask              : no
+mask              : yes
 wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
@@
 # to compile as pdf
-# (a) move file "_site.yml" to folder "tmp"
+# (a) move file "_site.yml" to folder "archive"
 # (b) uncomment the following lines
-# output            : papaja::apa6_pdf
-# header-includes:
-#   - \setlength{\parskip}{0em}
-#   - \raggedbottom
-#   - \note{\clearpage}
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+output            : papaja::apa6_pdf
+header-includes:
+  - \setlength{\parskip}{0em}
+  - \raggedbottom
+  - \note{\clearpage}
+# output            : papaja::apa6_docx
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#     toc_depth: 2
 ---
@@
 
-Understanding why people disclose personal information online remains a critical question for both society and research. 
-Originally, it was assumed that online self-disclosure is erratic and that it cannot be predicted by people's personal beliefs, concerns, or standpoints. 
-Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
+Understanding why people share personal information online is a critical question for society and research. 
+Originally, it was assumed that the online sharing of information is erratic and that it cannot be predicted by people's personal beliefs, concerns, or attitudes. 
+Most prominently, the privacy paradox stated that people communicate vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
 
-Somewhat surprisingly, and despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018], the privacy paradox has garnered comparatively little empirical support. 
-A recent meta-analysis reported a correlation between privacy concerns and self-disclosure on SNS of *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which shows that privacy concerns are indeed often related to self-disclosure online.
+Somewhat surprisingly, and despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is ambivalent.  
+A recent meta-analysis reported a correlation between privacy concerns and self-disclosure on SNS of *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which shows that privacy concerns are indeed related to communication online.
 
-Hence, rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called _privacy-calculus_ [@lauferPrivacyConceptSocial1977], which states that self-disclosure online can be explained---at least partly---by means of expected risks *and* expected benefits [@krasnovaOnlineSocialNetworks2010].
-Specifically, by operationalizing expected risks as privacy concerns, several studies have shown that experiencing greater privacy concerns is related to disclosing less information online, whereas expecting benefits is related to disclosing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
+Rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called _privacy-calculus_ [@lauferPrivacyConceptSocial1977].
+The privacy calculus states that communication online can be explained---at least partly---by means of expected risks *and* expected benefits [@krasnovaOnlineSocialNetworks2010].
+By operationalizing expected risks as privacy concerns, several studies have shown that experiencing privacy concerns is related to sharing less information online, whereas expecting benefits is related to sharing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
 However, although the privacy calculus has gained momentum in academic research, several important questions remain unanswered.
-First, we still know little about whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
-Thus far, most research supporting the privacy calculus has used either self-reports of behavior [e.g., @krasnovaOnlineSocialNetworks2010], vignette approaches [e.g., @bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [e.g., @treptePrivacyCalculusContextualized2020].
-Still missing is a more long-term field study in which actual behavior is observed in an authentic context.
 
-Second, current research on the privacy calculus is often criticized for not explicitly focusing on the deliberation process of self-disclosure. 
-According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that concerns and gratifications both correlate with self-disclosure is not evidence for an explicit weighing process of pros and cons.
-We agree.
-In this study, we therefore explicitly focus on the privacy deliberation process. 
-Related, and on a more general level, we explore the usefulness of further extending the privacy calculus model by adding new variables such as privacy deliberation, trust, and self-efficacy.
+First, current research on the privacy calculus is often criticized for not explicitly focusing on the _deliberation process_ when communicating online. 
+According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that both concerns and gratifications correlate with communication behavior online is not sufficient evidence for an explicit weighing process.
+This study, therefore, explicitly focuses on the privacy deliberation process.
 
-Finally, because the privacy calculus does not take place in a vacuum and because it is often argued that self-disclosure can be easily triggered by external circumstances, we analyze whether the privacy calculus is affected by the design of a website.
-Specifically, we investigate whether *popularity cues* such as like and dislike buttons have the power to affect the privacy calculus and to foster self-disclosure.
+Second, in this study I approach the privacy calculus from a theoretical perspective of _bounded rationality_. 
+It is likely that other factors next to risks and benefits also determine behavior.
+I therefore extend the privacy calculus model theoretically by investigating the role and interplay of trust and self-efficacy.
 
-To test our research questions, we collected a representative sample of the German population and conducted a preregistered online field experiment.
+Third, the privacy calculus does not take place in a vacuum. 
+It is often argued that communication online can be easily triggered by external circumstances.
+I therefore analyze whether the privacy calculus is affected by the affordances of a website. 
+Specifically, I investigate whether *popularity cues* such as like and dislike buttons affect the privacy calculus and whether they foster communication online.
+
+Fourth, it is still largely unknown whether the privacy calculus can be replicated with _behavioral data_ in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
+Thus far, much research on the privacy calculus used self-reports of behavior [@krasnovaOnlineSocialNetworks2010], vignette approaches [@bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
+A long-term field study observing actual behavior in an authentic context is still missing.
+
+To test the research questions, a representative sample of the German population was collected in a preregistered online field experiment.
 Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all. 
-Over the course of one week participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany). 
+Over the course of one week, participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany). 
 Afterward, they answered a follow-up questionnaire with items measuring the privacy calculus variables.
@@
 
-Self-disclosure is a primary means of regulating privacy [e.g., @masurSituationalPrivacySelfdisclosure2018].
-It is our key variable of interest.
-There are two different understandings of self-disclosure in the literature: 
-The first limits self-disclosure to _deliberate_ acts of sharing _truthful_ information about the self with others [@jourardTransparentSelf1964]. 
-The second considers _all_ acts of sharing information---be they active or passive, deliberate or unwitting---as self-disclosure, because each piece of information allows for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011].
-In this paper we follow the latter approach, not least because the recent years have illustrated how easy it is to derive personal insights simply by analyzing exchanged communication [@kosinskiPrivateTraitsAttributes2013].
-Moreover, independent from which position one adopts, it is possible to differentiate the content of self-disclosure into three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000].
-In this study we mainly focus on communication quantity as proxy for self-disclosure.
-The relation between communication quantity and self-disclosure is not linear. 
-Impressions are formed quickly, and the more we have already expressed about ourselves the harder it becomes to self-disclose novel information.
+The key variable of interest for this study is (verbal) communication online.
+Are people willing to engage in a conversation?
+Do they express their opinion? 
+In communicating online, people share much information about themselves.
+Communication is, hence, closely related to self-disclosure, and it is a primary means of regulating privacy [e.g., @dienlinPrivacyProcessModel2014].
+<!-- Almost all types of communication allow for meaningful inferences about a person, even when we _don't_ communicate [@watzlawickPragmaticsHumanCommunication2011].  -->
+<!-- However, the recent years have illustrated vividly how much additional insights we can get about a person, simply by analyzing their digital traces of communication or their meta-data [@kosinskiPrivateTraitsAttributes2013].
+-->
+<!-- The more we communicate, the more we self-disclose. -->
 
-Privacy concerns have been defined as follows: 
-"Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [@dienlinLongitudinalAnalysisPrivacy2019, p.
-6].
-Previous research has found that people who are more concerned about their privacy than others are less likely to share personal information [@baruhOnlinePrivacyConcerns2017; @heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
+Privacy concerns were defined as follows.
+"Taken together, concerns about online privacy represent how much an individual is motivated to focus on their control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that their privacy might be threatened" [@dienlinLongitudinalAnalysisPrivacy2021, p.
+4].
 
-H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.
+In this study I adopt the theoretical perspective of the privacy calculus [@lauferPrivacyConceptSocial1977].
+The privacy calculus assumes that when communicating online people engage in a rational weighing of risks and benefits.
+Notably, I don't assume that this weighing process is flawless or that humans are perfect rational agents.
+Instead, I understand the privacy calculus from the perspective of _bounded rationality_ [@simonBoundedRationality1990].
+Bounded rationality has three tenets: 
+"(1) humans are cognitively constrained; 
+(2) these constraints impact decision making; 
+and (3) difficult problems reveal the constraints and highlight their significance." [@bendorBoundedRationality2015, p. 1303]
+Crucially, although bounded rationally upholds that human behavior is not perfectly logical, this does not meant that it is irrational [@gigerenzerBoundedRationalityAdaptive2002].
+Instead, it is a continuum.
+Humans are still trying to optimize the outcomes of their behavior according to their own best interests or values.
+It is only that their capacity to do so is bounded.
 
-Although privacy concerns are related to self-disclosure, one can argue that most effects reported in the literature are only small, and that there should be additional factors explaining self-disclosure.
-For example, it has been argued that people trade a loss of privacy for a gain in gratifications [e.g., @taddickenUsesPrivacyOnline2011].
-The most prominent gratifications include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
+Transferred to the context of online privacy, it is by now well known that several irregularities and inconsistencies between concerns and communication behavior exist.
+These differences stem from, for example, information asymmetries, present bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
+At the same time, _on average_ people do behave according to their interests, respond to incentives, or actively manage their privacy [@baruhOnlinePrivacyConcerns2017; @dienlinExtendedPrivacyCalculus2016; @soloveMythPrivacyParadox2020].
 
-H2: People are more likely to self-disclose on a website when they obtain more gratifications from using the website.
+I therefore hypothesize that people who experience more privacy concerns engage in less communication online.
+In light of bounded rationality and the existence of other competing factors that also influence online-communication (see below), the effect is likely small.
 
-As mentioned above, there is still a shortage of studies explicitly analyzing the decision process behind the disclosing of information---although this point of criticism has been leveled several times [@knijnenburgDeathPrivacyCalculus2017] and although other fields such as behavioral economics have long focused on the underlying problem [@zhuPrivacyCalculusIts2017].
-This criticism is justified.
-The observation that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient evidence for an explicit weighing process.
-Hence, research on the privacy calculus would benefit from analyzing this decision process explicitly. 
-Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence address a novel concept that might best be termed _privacy deliberation_, which captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.
+In turn, the most relevant factor driving online communication is _expected gratifications_.
+People accept a loss of privacy if they can gain something in return [e.g., @lauferPrivacyConceptSocial1977].
+The most prominent gratifications of online communication include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
+Several studies have shown, that gratifications outweigh concerns [@dienlinExtendedPrivacyCalculus2016; @bolUnderstandingEffectsPersonalization2018].
+As a result, we expect a moderate relationship.
 
-On the one hand, it seems plausible that deliberating about one's privacy would dampen subsequent self-disclosure, because refraining from regular communication---the primary means of connecting with others---requires at least a minimum of active and hence deliberate restraint.
-On the other hand, deliberating about one's privacy might also increase self-disclosure, because a person concerned about his or her privacy might arrive at the conclusion that in this situation self-disclosure is not only appropriate but expedient.
-In light of the lack of empirical studies and the plausibility of both effects, we formulate the following research question:
+H1: People who are more concerned about their privacy than others are less likely to communicate actively on a website.
 
-RQ1: Are people more or less likely to self-disclose on a website depending on how actively they deliberate about whether they should self-disclose?
+H2: People who obtain more gratifications from using a website are more likely to communicate actively on a website.
 
-Several attempts have already been made to expand the privacy calculus, introducing additional variables such as self-efficacy or trust [@dinevExtendedPrivacyCalculus2006]. 
-Self-efficacy in the context of the privacy calculus captures whether people believe in their own capacity to implement particular privacy behaviors in the future [@dienlinExtendedPrivacyCalculus2016].
-These privacy behaviors refer to either _self-disclosure_ (e.g., publishing a blog post) or _self-withdrawal_ (e.g., deleting inappropriate content).
-People who report more privacy self-efficacy also engage in more self-withdrawal  [@chenRevisitingPrivacyParadox2018].
-In light of our focus on active communication, in this study we investigate the influence of _self-disclosure_ self-efficacy.
+Privacy calculus implies that people _explicitly_ compare benefits and disadvantages before communicating online.
+Research on the privacy calculus has often ignored this aspect [@knijnenburgDeathPrivacyCalculus2017].
+Only observing that privacy concerns or expected gratifications and communication online are _related_ is insufficient to prove an explicit weighing process.
+Hence, we here analyze how much people actively deliberate about their privacy and how that might influence the privacy calculus.
 
-H3: People are more likely to self-disclose on a website when their self-efficacy about self-disclosing on the website is higher.
+We can understand the privacy calculus from two perspectives (Table \@ref(tab:PC)):
+First, is the communication behavior aligned with people's privacy concerns and expected benefits? 
+Second, is the communication process implicit or explicit?
 
-The next variable, trust, can be conceptualized in two different ways [@gefenTrustTAMOnline2003]: 
-It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p.
-55, emphasis added] or a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added].
+Here, I suggest that the privacy calculus should be discussed in light of dual process theories, which state that people either deliberately, explicitly, and centrally take decisions, or instead do so automatically, implicitly, and peripherally [@kahnemanThinkingFastSlow2011; @pettyCommunicationPersuasionCentral1986].
+Accordingly, privacy calculus would assume that people, when it comes to disclosing, engage in a central processing. 
+Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, I hence introduce and investigate a novel concept termed _privacy deliberation_.
+Privacy deliberation captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.
+
+On the one hand, deliberating about privacy could _reduce_ subsequent communication.
+Refraining from communication---the primary means of connecting with others---likely requires some active and deliberate restraint. 
+This is especially true for social media, which are designed to elicit communication and participation.
+Actively thinking about whether communicating is really worthwhile might be the first step not to participate.
+On the other hand, deliberating about privacy might also _increase_ communication.
+A person concerned about their privacy might conclude that in this situation communication is actually beneficial. 
+Deliberation could represent some kind of inner consent, providing additional affirmation.
+
+Alternatively, it could be that deliberation functions as a moderator.
+For example, if people actively deliberate about whether or not to disclose, this might reinforce the effect of concerns or gratifications.
+Reflecting about the pros and cons of communication might concerns and gratifications more salient. 
+Alternatively, it could also be that deliberating decreases the effects, for example because apparent gratifications are considered more critically, and maybe loose their appeal.
+
+I therefore formulate the following two research questions:
+
+RQ1: Do people who deliberate more actively whether they should communicate, communicate more or less online?
+
+RQ2: Do people who deliberate more actively whether they should communicate, show larger or smaller relations between concerns, gratifications and communication behavior?
+
+Bounded rationality implies that additional factors should also explain communication.
+Communication online often takes place in situations where information is limited or obscure.
+The more familiar users are with a context, the more experience, knowledge, and literacy they possess, the more likely they should be to navigate online contexts successfully.
+In other words, if users possess more _self-efficacy_ to participate, they should also communicate more.
+Related, people who report more privacy self-efficacy also engage in more self-withdrawal [@chenRevisitingPrivacyParadox2018; @dienlinExtendedPrivacyCalculus2016].
+
+H3: People are more likely to communicate on a website when their self-efficacy about self-disclosing on the website is higher.
+
+In situations where people lack experience or competence, the most relevant variable explaining behavior is, arguably, _trust_.
+Online, users often cannot control the context or the way their information is handled.
+Trust therefore plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
+People who put more trust in the providers of networks, for example, disclose more personal information [@liEmpiricalStudiesOnline2011].
+
+Trust can be conceptualized in two different ways [@gefenTrustTAMOnline2003]. 
+It either captures "_specific_ beliefs dealing primarily with the integrity, benevolence, and ability of another party" [@gefenTrustTAMOnline2003, p. 55, emphasis added].
+Alternatively, it refers to a "_general_ belief that another party can be trusted" [@gefenTrustTAMOnline2003, p.55, emphasis added]. 
 Whereas specific trust focuses on the causes of trust, general trust emphasizes the experience of trust.
-@gefenTrustTAMOnline2003 prioritize specific trust (p. 60). 
-In the online context, it is also important to differentiate among several _targets_ of trust [@sollnerWhyDifferentTrust2016]. 
-Potential targets include (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016]. 
-Trust plays a key role in online communication [@metzgerPrivacyTrustDisclosure2004]. 
-For example, people who put more trust in the providers of networks also disclose more personal information [@liEmpiricalStudiesOnline2011].
+<!-- @gefenTrustTAMOnline2003 prioritize specific trust (p. 60).  -->
+In the online context, there exist several different _targets_ of trust, including (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016].
+Because the targets can be largely different, it is often recommended to analyze them individually.
 
-H4: People are more likely to self-disclose on a website when they have greater trust in the provider, the website, and the other users.
+H4: People are more likely to communicate on a website when they have greater trust in the provider, the website, and the other users.
 
@@
 
-How does the communication context affect the privacy calculus and self-disclosure? 
-First, it has often been noted that researchers should not exclusively focus on specific features of particular websites, for they are prone to change and to quickly become obsolete [@foxDistinguishingTechnologiesSocial2017].
-Instead, it has been suggested to prioritize the underlying latent structures by analyzing so-called affordances [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. 
-The concept of affordances was developed by @gibsonEcologicalApproachVisual2015, who argued that it is not the _objective features_ of objects that determine behavior, but our _subjective perceptions_.
-Affordances are mental representations of how objects might be used; as such, they are by definition subjective. 
+So far I analyzed user-oriented factors that explain communication online.
+But how does the context, the digital infrastructure, affect the privacy calculus and communication? 
+In what follows I do not focus on specific _features_ of particular websites, which can change and quickly become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
+Instead, I address the underlying latent structures by analyzing so-called _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. 
+Developed by @gibsonEcologicalApproachVisual2015, affordances emphasize that it is not the _objective features_ of objects that determine behavior, but rather our _subjective perceptions_. 
+Affordances are mental representations of how objects might be used.
+<!-- ; as such, they are by definition subjective.  -->
 There is an ongoing debate on what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017].
@@
 
-As the privacy calculus states that both benefits and costs determine behavior, we suggest that popularity cues such as like and dislike buttons---which are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p.
-142]---nicely map unto the two sides of the privacy calculus.
-The like button is positive and as such a potential benefit:
+The privacy calculus states that both benefits and costs determine behavior.
+Popularity cues such as like and dislike buttons, which are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p.
+142], can be linked to the two sides of the privacy calculus.
+The like button is positive and a potential benefit:
 It expresses an endorsement, a compliment, a reward [@carrPredictingThresholdPerceived2018; @sumnerFunctionalApproachFacebook2017]. 
-The dislike button is negative and therefore a potential cost: 
-It expresses criticism and is a major means of downgrading content.
+The dislike button is negative and a potential cost: 
+It expresses criticism and a way to downgrade content.
 
 Paralinguistic digital affordances and specifically popularity cues can affect behavior [@kramerMasteringChallengeBalancing2020; @treptePrivacyCalculusContextualized2020].
-For example, a large-scale field experiment in which 101,281 comments were analyzed found that comments with dislikes were more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
-@stroudRecommendRespectAltering2017 demonstrated that when users disagreed with a post, they were more likely to click on a button labeled _respect_ compared to a button labeled _like_. 
+Online comments that already have several dislikes are much more likely to receive further dislikes [@muchnikSocialInfluenceBias2013]. 
+When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
 The potentially stark negative effect of the dislike button might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit, or stackexchange).
+In this vein, popularity cues likely also impact the privacy calculus [@kramerMasteringChallengeBalancing2020].
 
-In this vein, it seems plausible that popularity cues might also impact the privacy calculus [@kramerMasteringChallengeBalancing2020], and that they serve as a means of reward and punishment. 
+Specifically, _likes_ are positive and represent the positivity bias typical of social media [@reineckeAuthenticityWellbeingSocial2014]. 
 Receiving a like online is similar to receiving a compliment offline. 
-Likes are positive and represent the positivity bias typical of social media [@reineckeAuthenticityWellbeingSocial2014]. 
-Introducing the option to receive likes mighty thereby afford and emphasize a _gain frame_
-(see also @rosoffHeuristicsBiasesCyber2013). 
+Introducing like-buttons mighty afford and emphasize a _gain frame_ [@rosoffHeuristicsBiasesCyber2013].
 These gains can be garnered only through participation. 
-In addition, because like buttons emphasize positive outcomes, it is likely that concerns decrease. 
-Finally, in situations where there is more to win, people should more actively deliberate about whether or not to disclose information.
+Because like buttons emphasize positive outcomes, it is likely that concerns decrease. 
+In situations where there is more to win, people should also more actively deliberate about whether or not to disclose information.
 
-H5.	Compared to people who use a website without like or dislike buttons, people who use a website with like buttons (a) self-disclose more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.
+Receiving a _dislike_ should feel more like a punishment.
+Dislikes introduce a _loss frame_. 
+<!-- Although most communication emphasizes positive aspects, the Internet is also replete with spite, envy, and arguments. -->
+As a result, websites featuring both like _and_ dislike buttons should be more ambivalent compared to websites without any popularity cues.
+In online contexts, gains often outweigh losses.
+Having both types of popularity cues might still lead to more gratifications and communication.
+However, privacy concerns should not be reduced anymore:
+People who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017].
+Implementing the dislike button might therefore increase privacy concerns, thereby canceling out the positive effects of the like button. 
+And because there is more at stake, participants should deliberate even more whether or not to disclose.
 
-By contrast, receiving a dislike should feel more like a punishment.
-Dislikes introduce a _loss frame_. 
-Although most communication emphasizes positive aspects, the Internet is also replete with spite, envy, and arguments.
-As a result, websites featuring both like _and_ dislike buttons should be more ambivalent compared to websites without any popularity cues.
-In online contexts, gains often outweigh losses, which is why having both types of popularity cues might still lead to more gratifications and self-disclosure.
-However, privacy concerns should not be reduced anymore:
-Because people who are more concerned about their privacy are also more shy and risk averse [@dienlinPsychologyPrivacyAnalyzing2017], implementing the dislike button might increase privacy concerns, thereby canceling out the positive effects of the like button.
-And because both wins and losses can accrue, participants should deliberate even more whether or not to disclose.
+There are two potential underlying theoretical pathways:
+The _mere presence_ of popularity cues might affect whether people are willing to disclose; being able to attract likes might motivate users to communicate, while the mere option to receive dislikes might intimidate others.
+On the other hand, _actually receiving_ likes or dislikes might then affect subsequent behavior, potentially reinforcing the process.
 
-H6.	Compared to people who use a website without like or dislike buttons, people who use a website with like _and_ dislike buttons (a) self-disclose more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.
+H5.	Compared to people who use a website without like or dislike buttons, people who use a website with like buttons (a) communicate more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.
 
-When directly comparing websites including both like and dislike buttons with website including only like buttons, building on the rationales presented above it is likely that websites including both like and dislike buttons should lead to more privacy concerns and privacy deliberation.
+H6.	Compared to people who use a website without like or dislike buttons, people who use a website with like _and_ dislike buttons (a) communicate more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.
+
+<!-- When directly comparing websites including both like and dislike buttons with websites including only like buttons, building on the rationales presented above, it is likely that websites including both buttons should increase privacy concerns and privacy deliberation.
+-->
 
@@
 
-For a simplified overview of our theoretical model, see Figure \@ref(fig:model).
+For a simplified overview of the analyzed model, see Figure \@ref(fig:model).
 
-```{r model, fig.cap="Overview of theoretical model.", fig.align='center', out.width=".8\\textwidth"}
+```{r model, fig.cap="Overview of analyzed model.", fig.align='center', out.width=".8\\textwidth"}
 knitr::include_graphics("figures/design/model.png")
@@
 
-The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's companion website (https://tdienlin.github.io/privacy_calc_exp).
-We preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
-We needed to change our pre-defined plan in some cases. 
+The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's companion website (https://XMtRa.github.io/privacy_calc_exp_anon).
+I preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
+I needed to change the pre-defined plan in some cases. 
 For a full account of all changes, see OSM. 
-New analyses that were not preregistered appear in the section Exploratory analyses.
+New analyses that were not preregistered appear in the section Exploratory Analyses.
 
@@
 The study was designed as an online field experiment with three different groups. 
-The first group used a website without like/dislike buttons, the second the same website but with only like buttons, and the third the same website but with both like and dislike buttons. 
+The first group used a website without like or dislike buttons, the second the same website but with only like buttons, and the third the same website but with both like and dislike buttons. 
 Participants were randomly distributed to one of the three websites in a between-subject design.
 
-We collaborated with a professional market research company to recruit participants. 
+I collaborated with a market research company to recruit participants. 
 As incentive, participants were awarded digital points, which they could use to get special offers from other online commerce services. 
 Participants were above the age of 18 and lived in Germany. 
-In a first step, the agency sent its panel members an invitation to participate in the study (_invitation_). 
+In a first step, the company sent its panel members an invitation to participate in the study (_invitation_). 
 In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.[^1] 
-Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which we (a) asked about their sociodemographics, (b) provided more details about the study, and (c) included a registration link for the website, which was described as "participation platform".
+Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which I (a) asked about their sociodemographics, (b) provided more details about the study, and (c) included a registration link for the website, which was described as "participation platform".
 Afterward, participants were randomly assigned to one of the three websites. 
@@
 Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (_T2_). 
-Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.
+Measures were collected after and not before the field phase in order not to prime participants or reveal the primary research interest.
 
 [^1]: Although the terror attack was not of primary interest for this study, the data can and will also be used to analyze perceptions of the terrorism threat.
-Hence, no deception took place, and in the debriefing participants were informed about our additional research interest in privacy.
+Hence, no deception took place, and in the debriefing participants were informed about the additional research interest in privacy.
 
-We programmed an online website based on the open-source software _discourse_ (https://www.discourse.org/). 
-We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). 
-Participants used the website actively: Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(60) %>% round(0) %>% format(big.mark = ",")` minutes online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and left `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
-Notably, we did not find any instances of people providing meaningless text. 
+The online website was programmed based on the open-source software _discourse_ (https://www.discourse.org/). 
+I conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). 
+`r n_users %>% english::english() %>% str_to_sentence` participants created a user account on the website (see below) and used the website actively. 
+Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(3600) %>% round(0) %>% format(big.mark = ",")` hours online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and clicked on `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
+Notably, there were no instances of people providing meaningless text. 
 For an example of communication that took place, see Figure \@ref(fig:comments).
@@
 
-We ran a priori power analyses to determine how many participants to recruit. The power analysis was based on a smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
-In other words, we defined a minimum effect size that we considered sufficiently large enough to support our hypotheses. 
-Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with standardized small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be _r_ = `r r_sesoi %>% my_round("std")`.
-Our aim was to be able to detect this SESOI with a probability of at least 95%.
-Using the regular alpha level of 5%, basic power analyses revealed a minimum sample size of _n_ = `r n_desired %>% format(big.mark = ",")`.
-In the end, we were able to include n = `r n_final` in our analyses (see below). 
-This means that our study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
-Put differently, we were able to make reliable inferences (i.e., power = 95%) about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
+I ran a priori power analyses to determine sample size. 
+The power analysis was based on a smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
+Namely, I defined a minimum effect size considered sufficiently large to support the hypotheses. 
+Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with standardized small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], I set the SESOI to be _r_ = `r r_sesoi %>% my_round("std")`.
+The aim was to be able to detect this SESOI with a probability of at least 95%.
+Using the regular alpha level of 5%, basic power analyses revealed a minimum sample size of _N_ = `r n_desired %>% format(big.mark = ",")`.
+In the end, I was able to include _N_ = `r n_final` in the analyses (see below). 
+This means that the study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
+Put differently, I was able to make reliable inferences (i.e., power = 95%) about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
 
-We collected a representative sample of the German population in terms of age, sex, and federal state. 
-`r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1, `r n_users` participants created a user account on the website,  and `r n_t2` participants completed the survey at T2. 
-Using tokens and IP addresses, we connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
+A representative sample of the German population in terms of age, sex, and federal state was collected. 
+In sum, `r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1, `r n_users` participants created a user account on the website,  and `r n_t2` participants completed the survey at T2.
+Using tokens and IP addresses, I connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
 The data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
-In the end, the data of _n_ = `r n_matched` participants could be matched successfully.
-We excluded _n_ = `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which we considered to be unreasonably fast.[^note] 
-To detect potentially problematic data, we calculated Cook's distance.
-We excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
-The final sample included `r n_final` participants.
+In the end, the data of `r n_matched` participants could be matched successfully.
+I excluded `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which were considered to be unreasonably fast.[^note] 
+To detect atypical data, I calculated Cook's distance.
+I excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
+The final sample included _N_ = `r n_final` participants.
 The sample characteristics at T1 and T2 were as follows: 
-T1: Age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
-T2: Age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m * 100, 0)`%.
-One participant did not report his or her sex.
+T1: age = `r round(age_t1_m, 0)` years, sex = `r round(male_t1_m, 2)*100`% male, college degree = `r round(college_t1_m, 2)*100`%.
+T2: age = `r round(age_final_m, 0)` years, sex = `r round(male_final_m, 2)*100`% male, college degree = `r round(college_final_m * 100, 0)`%.
+One participant did not report their sex.
 
-[^note]: We preregistered to delete participants with less than 6 minutes answer time.
-However, this led to the exclusion of too many data points of high quality, which is why we relaxed this criterion.
-In the OSM, we report also the results using all participants.
+[^note]: I preregistered to delete participants with less than 6 minutes answer time.
+However, this led to the exclusion of too many data points of high quality, which is why I relaxed this criterion.
+In the OSM, I report also the results using all participants.
 
@@
 
-In what follows, we present the materials we used to measure the variables. 
-Wherever possible, we operationalized the variables using established measures.
-Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which we pretested concerning legibility and understandability.
-To assess factor validity we ran confirmatory factor analyses (CFA). 
-If the CFAs revealed insufficient fit, we deleted malfunctioning items. 
+Wherever possible, I operationalized the variables using established measures.
+Where impossible (for example, to date there exists no scale on privacy deliberation), I self-designed novel items, which were pretested concerning legibility and understandability.
+To assess factor validity I ran confirmatory factor analyses (CFA). 
+If the CFAs revealed insufficient fit, I deleted malfunctioning items. 
 All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale. 
@@
 Calculated with the model predicted values for each variable (baseline model).", fig.height=8, fig.width=8, out.width=".9\\textwidth", fig.align='center', fig.pos = "!h", warning=F}
-print(fig_fs_cor)
+knitr::include_graphics("figures/results/cor_plot.png")
 ```
@@
 
-We differentiated between two separate types of gratifications. 
+I differentiated between two separate types of gratifications. 
 _General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
@@
 _Specific gratifications_ were measured with 15 items on five different subdimensions with three items each. 
-The scaled was based on @schererGratifikationMinuteZeitnahe2002.
+The scale was based on @schererGratifikationMinuteZeitnahe2002.
 Example items were: "Using the participation platform made it possible for me to" ...
@@
 Self-efficacy was captured with six self-designed items, which measured whether participants felt that they had sufficient self-efficacy to write a comment on the website. 
-For example, we asked "I felt technically competent enough to write a comment." 
+For example, "I felt technically competent enough to write a comment." 
 Two inverted items were deleted due to poor psychometric properties.
@@
 
-We differentiated between two types of trust. 
+I differentiated between two types of trust. 
 _General trust_ was operationalized based on @sollnerWhyDifferentTrust2016, addressing three targets (i.e., provider, website, and other users) with one item each. 
-One example items was "The operators of the participation platform seemed trustworthy."
+One example item was "The operators of the participation platform seemed trustworthy."
 _Specific trust_ was operationalized for the same three targets with three subdimensions each (i.e., ability, benevolence/integrity, and reliability), which were measured with one item each. 
 Example items were "The operators of the participation platform have done a good job" (ability), "The other users had good intentions" (benevolence/integrity), "The website worked well" (reliability).
-The results showed that the provider and website targets were not sufficiently distinct, as was evidenced by a Heywood case. 
-We hence adapted the scale to combine these two targets. 
-The updated scale exhibited adequate fit.
+The results showed that the provider and website targets were not sufficiently distinct, as was evidenced by a Heywood case (i.e., standardized coefficient greater than 1). 
+I hence adapted the scale to combine these two targets. 
+The updated scale showed adequate fit.
 
-### Self-disclosure
+### Communication
 
-Self-disclosure was calculated by taking the log scale of the number of words each participant wrote in a comment, to which we added the number of likes and dislikes, which were multiplied by two (preregistered).
-The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
-The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure diminishes the more a person has already expressed.
+Communication was calculated by counting the number of words each participant wrote in a comment.
+Communication was heavily skewed.
+Many people did communicate not at all, while some communicated a lot.
+Hence, the sum of words was log-scaled.
 
@@
 All hypotheses and research questions were tested using structural equation modeling with latent variables. 
-The influence of the three websites was analyzed using contrast coding, which allows for testing the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016].
-Because the dependent variable self-disclosure was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
-As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit we report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
-Because sociodemographic variables are often related to self-disclosure and other privacy-related variables [@dindiaSexDifferencesSelfdisclosure1992], we controlled all variables for the influence of sex, age, and education.
+The influence of the three websites was analyzed using contrast coding.
+I could therefore test the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016]. 
+Because the dependent variable communication was not normally distributed, I estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
+As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit I report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
+Because sociodemographic variables are often related to communication and other privacy-related concepts [@tifferetGenderDifferencesPrivacy2019], I controlled all variables for the influence of sex, age, and education.
 Preregistered hypotheses were tested with a one-sided significance level of 5%. 
 Research questions were tested with a two-sided 5% significance level using family-wise Bonferroni-Holm correction. 
-Exploratory analyses were conducted from a descriptive perspective, which is why the reported p-values and confidence intervals should not be overinterpreted.
+Exploratory analyses were conducted from a descriptive perspective.
+The reported p-values and confidence intervals should thus not be overinterpreted.
 
-We used `r r_citations` for all our analyses.
+I used `r r_citations` for all analyses.
 
@@
 
-We first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
-The results did not reveal any relationships to be particularly curvilinear. 
-Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with self-disclosure. 
+I first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
+No relationship was particularly curvilinear. 
+Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with communication. 
 For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
-Worth noting, specific gratifications predicted self-disclosure better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
+Worth noting, specific gratifications predicted communication better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
 _r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
@@
 
-It is important to note that the bivariate results showed three large correlations: First, between specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% .[2, 1] %>% my_round("std")`); second, between privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`); third, between specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`).
+Note that the bivariate results showed three large correlations: 
+specific trust and general gratifications (_r_ = `r d_fs %>% select("Specific\ntrust", "General\ngratifications") %>% cor %>% .[2, 1] %>% my_round("std")`), 
+privacy concerns and privacy deliberation (_r_ = `r d_fs %>% select("Privacy\nconcerns", "Privacy\ndeliberation") %>% cor %>% .[2, 1] %>% my_round("std")`),
+and specific gratifications and self-efficacy (_r_ = `r d_fs %>% select("Specific\ngratifications", "Self-\nefficacy") %>% cor %>% .[2, 1] %>% my_round("std")`).
 As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.
@@
 
-First, we ran a model as specified in the preregistration. The model fit our data okay, `r fit_txt(fit_prereg, scaled = TRUE)`. 
-Regarding H1, we did not find that general gratifications predicted self-disclosure (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
-With regard to H2, privacy concerns did not significantly predict self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
-RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`; two-sided). 
-Regarding H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided). 
-Concerning H4, results showed that trust was not associated with self-disclosure (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).
+First, I ran a model as specified in the preregistration. The model fit the data okay, `r fit_txt(fit_prereg, scaled = TRUE)`. 
+Regarding H1, I did not find that general gratifications predicted communication (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
+With regard to H2, privacy concerns did not significantly predict communication (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
+RQ1 similarly revealed that privacy deliberation was not correlated with communication (`r coeffs_txt(fit_prereg, "c1")`; two-sided). 
+Regarding H3, however, I found that experiencing self-efficacy predicted communication substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided). 
+Concerning H4, results showed that trust was not associated with communication (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).
 
-However, these results should be treated with caution, because they indeed exhibited problems typical of multicollinearity, such as large standard errors or "wrong" signs of the predictors [@grewalMulticollinearityMeasurementError2004].
-For example, in the multiple regression trust had a _negative_ relation with self-disclosure, whereas in the bivariate analysis it was _positive_.
+However, these results should be treated with caution.
+I found several signs of multicollinearity, such as large standard errors or "wrong" signs of predictors [@grewalMulticollinearityMeasurementError2004]. 
+In the multiple regression trust had a _negative_ relation with communication, whereas in the bivariate analysis it was _positive_.
 
@@
 
-Thus, we slightly adapted our preregistered model on the basis of the insights described above. 
-First, instead of specific trust and general gratifications we now included _general_ trust and _specific_ gratifications, which were correlated slightly less strongly. 
-The adapted model fit our data comparatively well, `r fit_txt(fit_adapted)`.
+I slightly adapted the preregistered model on the basis of the insights described above. 
+First, instead of specific trust and general gratifications I included _general_ trust and _specific_ gratifications, which were correlated slightly less strongly. 
+The adapted model fit the data comparatively well, `r fit_txt(fit_adapted)`.
 
-In the adapted privacy calculus model, specific gratifications were positively related to self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`). 
-Furthermore, people who deliberated more about their privacy disclosed less information (`r coeffs_txt(fit_adapted, "c1")`; two-sided). 
-Self-efficacy remained substantially correlated with self-disclosure (`r coeffs_txt(fit_adapted, "d1")`; two-sided). 
-However, we again found a negative correlation between trust and self-disclosure (`r coeffs_txt(fit_adapted, "e1")`; two-sided), which again implies multicollinearity.
+In the adapted privacy calculus model, specific gratifications were positively related to communication online (`r coeffs_txt(fit_adapted, "b1")`; two-sided). 
+People who deliberated more about their privacy disclosed less information (`r coeffs_txt(fit_adapted, "c1")`; two-sided). 
+Self-efficacy remained substantially correlated with communication (`r coeffs_txt(fit_adapted, "d1")`; two-sided). 
+Notably, I found a negative correlation between trust and communication (`r coeffs_txt(fit_adapted, "e1")`; two-sided), which again implies multicollinearity.
 
@@
 (a) combining collinear variables into a single measure, or (b) keeping only one of the collinear variables.
-Combining variables was not an option in our case, because both trust and expected benefits are theoretically distinct constructs.
-And because _several_ variables were closely related to one another, we therefore decided to fit a simple privacy calculus model containing only privacy concerns and specific gratifications.
+Combining variables was not an option in this case, because both trust and expected benefits are theoretically distinct constructs.
+And because _several_ variables were closely related to one another, I therefore decided to fit a simple privacy calculus model containing only privacy concerns and specific gratifications.
 
-The simple model fit our data well, `r fit_txt(fit_simple)`. 
-First, we found that people who experienced more privacy concerns than others disclosed less information (`r coeffs_txt(fit_simple, "a1")`; two-sided). 
-Second, people who reported more specific gratifications than others self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`; two-sided). 
-Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, which implies that the they were large enough to be theoretically relevant.
+The simple model fit the data well, `r fit_txt(fit_simple)`. 
+First, I found that people who experienced more privacy concerns than others disclosed less information (`r coeffs_txt(fit_simple, "a1")`; two-sided). 
+Second, people who reported more specific gratifications than others communicated more information (`r coeffs_txt(fit_simple, "b1")`; two-sided). 
+Both effect sizes were above the predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, which implies that the they were large enough to be theoretically relevant.
 
-When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (`r round(rsquare_fit_adapted * 100, 2)` %), followed by the preregistered model (`r round(rsquare_fit_prereg * 100, 2)` %), and the simple privacy calculus model (`r round(rsquare_fit_simple * 100, 2)` %).
+When comparing the three models with one another, the adapted model explained the most variance in communication (`r round(rsquare_fit_adapted * 100, 2)` %), followed by the preregistered model (`r round(rsquare_fit_prereg * 100, 2)` %), and the simple privacy calculus model (`r round(rsquare_fit_simple * 100, 2)` %).
 At the same time, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
@@
 
-```{r plotpc, fig.cap="Predictors of self-disclosure. Displayed are the 95\\% CIs of unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=4}
-print(fig_coeffs)
+```{r plotpc, fig.cap="Predictors of communication. Displayed are the 95\\% CIs of unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=4}
+knitr::include_graphics("figures/results/coeffs.png")
 ```
@@
 
-In a next step, we analyzed the potential effects of the popularity cues. 
-We for example expected that websites with like buttons would lead to more self-disclosure, gratifications, and privacy deliberation and to less privacy concerns.
-Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables whatsoever.
+In a next step, I analyzed the potential effects of the popularity cues. 
+I for example expected that websites with like buttons would lead to more communication, gratifications, and privacy deliberation and to less privacy concerns.
+Somewhat surprisingly, I found no effects of the popularity cues on the privacy calculus variables.
 For an illustration, see Figure \@ref(fig:popularitycues), which displays the model-predicted values for each variable (using the baseline model).
@@
 Note that some differences missed statistical significance only marginally (e.g., specific gratifications for the comparison between the website with like buttons and the control website without like and dislike buttons).
-Nevertheless, we refrain from reading too much into these differences and conclude that the three websites were comparable regarding the privacy calculus variables and the amount of self-disclosure.
+Nevertheless, I refrain from reading too much into these subtle differences.
+I conclude that the three websites were comparable regarding the privacy calculus variables and the amount of communication.
 
@@
 Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
-print(fig_fs_m)
+knitr::include_graphics("figures/results/violin_plot.png")
 ```
@@
 
-In this study, we analyzed the privacy calculus using actual observed behavior in a preregistered field experiment. 
-We additionally asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons. 
-The data stem from a representative sample of the German population and were analyzed using structural equation modeling with latent variables.
+This is the first study to analyze the privacy calculus using actual observed behavior in a preregistered field experiment. 
+The data stem from a representative sample of the German population.
+I extended the theoretical privacy calculus model by explicitly testing privacy deliberation processes.
+I included self-efficacy and trust as additional variables, to better represent the theoretical premise of bounded rationality.
+I further asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons.
 
-In the bivariate analyses, all privacy calculus variables significantly predicted self-disclosure. 
-In the preregistered analyses using multiple regression, however, only self-efficacy significantly predicted self-disclosure.
+In the bivariate analyses, all privacy calculus variables significantly predicted communication activity. 
+Thus, all variables likely play an important role when it comes to understanding online-communication.
+In the preregistered analyses using multiple regression, however, only self-efficacy significantly predicted communication.
 All other variables were not significant.
+There seems to be a relevant overlap between variables, and their mutual relation is still not clear.
 The preregistered extended privacy calculus model was therefore not supported by the data.
-However, the model showed problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a simple privacy calculus model, which included only privacy concerns and specific gratifications.
+However, the model showed problems typical of multicollinearity, which is why I also explored (a) an adapted version of the preregistered model, in which I exchanged two variables, and (b) a simple privacy calculus model, which included only privacy concerns and specific gratifications.
 
-The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy disclose less, and that people who expect more specific gratifications and who feel more self-efficacious disclose more.
-However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases.
-This seems theoretically implausible. 
-As a result, we also fit the above-mentioned simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure.
-Taken together, the results support the privacy calculus framework and suggest that---at least in specific contexts---self-disclosure online is not erratic and that it can be explained by several psychological variables.
+The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy disclose less.
+People who expect more specific gratifications and who feel more self-efficacious disclose more.
+However, the model also suggests that if trust increases, while all other factors remain constant, communication decreases, which seems theoretically implausible. 
+As a result, I also fit a simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted communication. 
+Taken together, the results support the privacy calculus framework and suggest that in specific contexts communication online is not erratic and that it can be explained by several psychological variables.
+At the same time, variables such as trust and efficacy seem to play an important role, which further supports the underlying premise of bounded rationality.
 
-Aligned with this observation, the results also suggest that in new communication contexts at least one third of all Internet users _actively deliberates_ about their privacy. 
-Determining whether this figure is large or small is a normative question.
-Although the effect seems substantial to us, one could argue that it should be higher and that more people should actively deliberate about their self-disclosure practices online. 
-Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar, which was evidenced by their strong correlation with one another and their comparable correlations with other variables.
-This either implies that thinking about one's privacy increases one's concern or, conversely, that being concerned about one's privacy leads one to think about one's options more actively. 
+The results suggest that in new communication contexts at least one third of all Internet users _actively deliberates_ about their privacy. 
+Determining whether this figure is large or small is difficult.
+Although the effect seems substantial to us, one could argue that it should be higher and that more people should actively deliberate about their online communication.
+Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar.
+Both variables were strongly correlated and showed comparable correlations with other variables. 
+This either implies that thinking about privacy increases concerns or, conversely, that being concerned about privacy encourages us to ponder our options more carefully. 
 Future research might tell.
 
-The next major implication is that popularity cues do not always seem to have a strong influence on the privacy calculus and self-disclosure.
-Although some studies have found that popularity cues can substantially impact behavior [e.g., @muchnikSocialInfluenceBias2013], in our study we found the opposite.
-Users still disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons, potentially highlighting the agency of users.
-This is of course not to say that popularity cues have no impact on the privacy calculus in general. 
-Instead, the results only suggest that there exist certain contexts in which the influence of popularity cues is negligible.
+Popularity cues do not always seem to have a strong influence on the privacy calculus and communication.
+Although some studies reported that popularity cues can substantially impact behavior [@muchnikSocialInfluenceBias2013], in this study I found the opposite.
+Users disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons.
+<!-- potentially highlighting the agency of users. -->
+The results do not imply that popularity cues have no impact on the privacy calculus in general. 
+Instead, they suggest that there exist certain contexts in which the influence of popularity cues is negligible.
 
-The results also have several more fine-grained implications. 
+The results also have methodological implications. 
 First, one can question the tendency to further increase the complexity of the privacy calculus model by adding additional variables [e.g., @dienlinExtendedPrivacyCalculus2016]. 
@@
 792].
-Specifically, we have come to believe that adding self-efficacy to privacy calculus models is of limited value, because self-efficacy is often only a self-reported proxy of behavior offering little epistemic insight.
-Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to self-disclose whereas others do not. 
-In addition, although adding variables increases the amount of explained variance, it introduces further problems, for example spurious results due to multicollinearity.
+For example, it seems that adding self-efficacy to privacy calculus models is of limited theoretical value.
+Self-efficacy is often only a self-reported proxy of behavior and offers little incremental insight. 
+Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to communicate whereas others do not.
 
-Interestingly, multicollinearity might not even be a problem per se, but rather a helpful warning sign. 
-From a _statistical_ perspective, strongly correlated predictors only mean that standard errors become larger [@vanhoveCollinearityIsnDisease2019]. 
-In other words, when predictors are strongly correlated we can be less certain about the effects we obtain, because there is less unique variance [@vanhoveCollinearityIsnDisease2019]. 
-As a remedy, researchers could simply collect larger samples, which would increase statistical power and precision.
-Fortunately, using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated/collinear predictors [@wangPowerAnalysisParameter2020].
+In addition, although adding variables increases explained variance, it can also introduce multicollinearity.
+Multicollinearity is not a problem per se, but rather a helpful warning sign [@vanhoveCollinearityIsnDisease2019].
+From a _statistical_ perspective, strongly correlated predictors mean that standard errors become larger [@vanhoveCollinearityIsnDisease2019]. 
+We can be less certain about the effects, because there is less unique variance [@vanhoveCollinearityIsnDisease2019]. 
+As a remedy, researchers could collect larger samples, which would increase statistical power and precision.
+Using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated or collinear predictors [@wangPowerAnalysisParameter2020].
 
 From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
-It is our understanding that multiple regression is often used with the aim to isolate effects, to make sure that they are not simply caused by another third variable.
-However, in cases of highly correlated measures this often does not make much sense theoretically.
-For example, in our case combining trust and gratification asks how increasing benefits affects self-disclosure _while holding trust constant_.
-Theoretically, however, it is more plausible to assume that increasing gratifications also automatically increases trust [@sollnerWhyDifferentTrust2016].
-In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---measures which are all strongly correlated.
-In short, the effects we found could even be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value.
+It is my understanding that multiple regression is often used to isolate effects, to make sure that they are not caused by other third variables.
+However, in cases of highly correlated variables this often does not make much sense theoretically.
+Combining trust and gratification in a multiple regression asks how increasing benefits affects communication _while holding trust constant_.
+However, it seems more plausible to assume that increasing gratifications also automatically increases trust [@sollnerWhyDifferentTrust2016].
+In the preregistered analysis I even went further and tested whether trust increases communication while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---an unlikely scenario.
+In short, the effects I found could be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value.
 
-Furthermore, we found a surprisingly strong correlation between specific trust and expected gratifications (i.e., _r_ = .79).
-At first glance, this strong relation seemed somewhat peculiar to us. 
-On closer inspection, however, we realized that the way trust is typically operationalized is remarkably close to expected gratifications. 
+Finally, I found a surprisingly strong correlation between specific trust and expected gratifications (i.e., _r_ = .79).
+Operationalizations of trust are remarkably close to expected gratifications. 
 To illustrate, the trust subdimension _ability_ includes items such as “The comments of other users were useful”. 
-In fact, in the literature trust is often operationalized as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016]. 
-In conclusion, our results suggest that _causes_ of trust should not be confused with _measures_ of trust, for this might introduce problems of both homogeneity and/or multicollinearity.
-Instead, we recommend to use general and reflective measures of trust.
+Trust is often operationalized as a formative construct that directly results from factors such as expected benefits [@sollnerWhyDifferentTrust2016]. 
+In conclusion, it is important not to confuse _causes_ of trust with _measures_ of trust.
+<!-- Doing so can introduce problems of homogeneity and multicollinearity. -->
+I thus recommend using general and reflective measures of trust.
 
@@
 
-The results do not allow for causal interpretation on the within-person level. 
+Although I did not find significant effects of like and dislike buttons in this study, they could still affect the privacy calculus in other contexts and settings.
+All findings are limited to the context I analyzed and should not be overly generalized.
+Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008].
+They can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question. 
+In this case, it was not possible to send participants notifications when their comments were liked or disliked, which significantly decreased the popularity cues' salience.
+
+The results do not allow for causal interpretation. 
 First, all results are based on analyses of between-person variance.
-However, between-person relations often do not translate well to within-person effects [@hamakerCritiqueCrosslaggedPanel2015]. 
-While some studies on privacy concerns online have begun to examine both sources of variance [@dietvorstAdolescentPerceptionsParental2017], similar analyses are still lacking for the privacy calculus.
+However, between-person relations often do not translate to within-person effects [@hamakerCritiqueCrosslaggedPanel2015]. 
+<!-- While some studies on privacy concerns online have begun to examine both sources of variance [@dietvorstAdolescentPerceptionsParental2017], similar analyses are still lacking for the privacy calculus.
+-->
+Likewise, the mediation model is only suggestive, as I did not experimentally manipulate the mediating variables and also did not use a longitudinal design.
 
-Second, the self-reported measures were collected _after_ the field phase in which the dependent variable was measured. 
+The self-reported measures were collected _after_ the field phase in which the dependent variable was measured. 
 As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.
-Nevertheless, we deliberately decided to measure the self-reported variables afterward in order not to bias participants.
 
-Third, the assumption of stable unit treatment states that in experiments we should manipulate only the experimental variable while holding all others constant [@klinePrinciplesPracticeStructural2016].
-In this study, we explicitly manipulated the popularity cues. 
-However, because the experiment was conducted in the field several other variables could not be held constant.
-This includes the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
+The assumption of stable unit treatment states that in experiments only the experimental variable should be manipulated, while all others should be held constant [@klinePrinciplesPracticeStructural2016].
+In this study, I explicitly manipulated the popularity cues. 
+However, because the experiment was conducted in the field several other variables could not be held constant, such as the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
 As a result, the assumption of stable unit treatment was violated.
-
-Again, although we did not find significant effects of like and dislike buttons in this study, this does not mean they have no effect on the privacy calculus in general.
-Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008], which---put somewhat crudely---states that null findings can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question.
-In this case, we were not able send participants notifications when their comments were liked/disliked, which significantly decreased the popularity cues' salience.
-
-This paper analyzes self-disclosure in the context of political participation. 
-Our focus was on understanding self-disclosure, which is why we deliberately excluded variables pertaining to political participation, such as informational self-efficacy [@loyPsychologicalPredictorsPolitical2018].
-Moreover, operationalizing self-disclosure via communication quantity is, of course, only a proxy.
 
@@
 
-Whereas some scholars discuss whether we should wish "Death to the privacy calculus?" [@knijnenburgDeathPrivacyCalculus2017, p. 1], we think that the privacy calculus is alive and kicking. 
-In this study, people who were more concerned about their privacy than others disclosed less information online, whereas people who received more gratifications from using a website than others disclosed more information online.
-In addition, the results suggest that a substantial share of internet users, approximately 30%, consciously engage in a privacy calculus by actively deliberating about whether or not to disclose information.
-Popularity cues such as like and dislike buttons seem to play only a minor role in this process. 
+In this study I have found some support for the privacy calculus approach.
+People who were more concerned about their privacy disclosed less information online, whereas people who received more gratifications from using a website disclosed more information online. 
+A substantial share of internet users, approximately 30%, engaged in a privacy calculus by actively deliberating about whether or not to disclose information. 
+Popularity cues such as like and dislike buttons played only a minor role in this process. 
 In conclusion, the results provide further evidence against the privacy paradox.

### 2021-07-14 preprint.Rmd
- implemented major changes after feedback from reviewers

--- 2021-07-14 manuscript.RmD
@@
 ---
-title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus when Communicating Online"
-shorttitle        : "Popularity cues & privacy calculus"
+title             : "How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment"
+shorttitle        : "Popularity cues and privacy calculus"
+author:            
+  - name          : "Dienlin, Tobias"
+    email         : "tobias.dienlin@univie.ac.at"
+    affiliation   : "1"
+    corresponding : yes
+    address       : "University of Vienna, Department of Communication, 1090 Vienna, Austria"
+  - name          : "Braeunlich, Katharina"
+    email         : "braeunlich@uni-koblenz.de"
+    affiliation   : "2"
+  - name          : "Trepte, Sabine"
+    email         : "sabine.trepte@uni-hohenheim.de"
+    affiliation   : "3"
+affiliation:
+  - id            : "1"
+    institution   : "University of Vienna"
+  - id            : "2"
+    institution   : "University of Koblenz-Landau"
+  - id            : "3"
+    institution   : "University of Hohenheim"
+note: |
+  This preprint has been submitted to a  journal and is currently under review. Please cite carefully.
+
+authornote: |
+  Dr. Tobias Dienlin is Assistant Professor of Interactive Communication at University of Vienna. He received his Ph.D. from University of Hohenheim.
+
+  Dr. Katharina Braeunlich works at the Federal Office for Information Security in Bonn. She is an alumna from University of Koblenz-Landau, where she received her Ph.D.
+
+  Dr. Sabine Trepte is Full Professor for Media Psychology at University of Hohenheim. She received her Ph.D. from Hanover University of Music, Drama and Media.
+
+  All authors contributed extensively to the work presented in this paper.
+TD, KB, & ST designed the study; KB & TD designed the online website; TD & KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.
+
+    The authors declare no competing interests.
+
+    This research was funded by the Volkswagen Foundation, project "Transformations of privacy", which was awarded to Sandra Seubert, Sabine Trepte, Ruediger Grimm, & Christoph Gusy.
+We would like to thank all our colleagues from the project as well as Niklas Johannes for valuable feedback.
+
+    This manuscript features a companion website, which includes the data, code, additional analyses, the preregistration, and a reproducible version of the manuscript (https://XMtRa.github.io/privacy_calc_exp_anon).
 abstract: |
-    According to privacy calculus, both privacy concerns and expected gratifications explain why people communicate online.
+    According to privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online.
 So far, most findings were based on self-reports or short-term experiments, and it is still largely unknown how popularity cues such as like and dislike buttons affect privacy calculus.
-To answer these questions, a preregistered one-week field experiment was conducted.
+To answer these questions we ran a preregistered one-week field experiment.
 Participants were randomly distributed to three different websites, on which they discussed a current political topic.
@@
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
-Although the originally preregistered model was largely rejected, the results showed that a considerable share of actual communication could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
-The impact of the popularity cues on privacy calculus and communication was negligible.
-keywords          : "privacy calculus, communication, popularity cues, field experiment, structural equation modeling, preregistration"
+Although the originally preregistered model was rejected, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
+The impact of the popularity cues on self-disclosure and privacy calculus was negligible.
+keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
 bibliography      : 
@@
 linenumbers       : yes
-mask              : yes
+mask              : no
 wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
@@
 
-# Introduction
+<!-- # Introduction -->
 
-Understanding why people share personal information online is a critical question for society and research. 
-Originally, it was assumed that the online sharing of information is erratic and that it cannot be predicted by people's personal beliefs, concerns, or attitudes. 
-Most prominently, the privacy paradox stated that people communicate vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
+Understanding why people disclose personal information online is a critical question for society and research. 
+Originally, it was assumed that online self-disclosure is erratic and that it cannot be predicted by people's personal beliefs, concerns, or attitudes. 
+Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online *despite* having substantial concerns about their privacy [@barnesPrivacyParadoxSocial2006; @taddickenUsesPrivacyOnline2011].
 
-Somewhat surprisingly, and despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018], empirical support for the privacy paradox is ambivalent.  
-A recent meta-analysis reported a correlation between privacy concerns and self-disclosure on SNS of *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which shows that privacy concerns are indeed related to communication online.
+Somewhat surprisingly, and despite its popularity in the media [@newyorkpublicradioPrivacyParadox2018], the privacy paradox has garnered comparatively little empirical support. 
+A recent meta-analysis reported a correlation between privacy concerns and self-disclosure on SNS of *r* = -.13 [@baruhOnlinePrivacyConcerns2017], which shows that privacy concerns are indeed related to self-disclosure online.
 
-Rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called _privacy-calculus_ [@lauferPrivacyConceptSocial1977].
-The privacy calculus states that communication online can be explained---at least partly---by means of expected risks *and* expected benefits [@krasnovaOnlineSocialNetworks2010].
-By operationalizing expected risks as privacy concerns, several studies have shown that experiencing privacy concerns is related to sharing less information online, whereas expecting benefits is related to sharing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
+Hence, rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called _privacy-calculus_ [@lauferPrivacyConceptSocial1977].
+The privacy calculus states that self-disclosure online can be explained---at least partly---by means of expected risks *and* expected benefits [@krasnovaOnlineSocialNetworks2010].
+By operationalizing expected risks as privacy concerns, several studies have shown that experiencing privacy concerns is related to disclosing less information online, whereas expecting benefits is related to disclosing more information online [@heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
@@
 
-First, current research on the privacy calculus is often criticized for not explicitly focusing on the _deliberation process_ when communicating online. 
-According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that both concerns and gratifications correlate with communication behavior online is not sufficient evidence for an explicit weighing process.
-This study, therefore, explicitly focuses on the privacy deliberation process.
+First, current research on the privacy calculus is often criticized for not explicitly focusing on the deliberation process behind self-disclosure. 
+According to critics [e.g., @knijnenburgDeathPrivacyCalculus2017], showing that both concerns and gratifications correlate with self-disclosure is not sufficient evidence for an explicit weighing process.
+In this study, we therefore explicitly focus on the privacy deliberation process.
 
-Second, in this study I approach the privacy calculus from a theoretical perspective of _bounded rationality_. 
+Second, we approach the privacy calculus from a theoretical perspective of bounded rationality. 
 It is likely that other factors next to risks and benefits also determine behavior.
-I therefore extend the privacy calculus model theoretically by investigating the role and interplay of trust and self-efficacy.
+We therefore extend the privacy calculus model theoretically by investigating the role and interplay of trust and self-efficacy.
 
-Third, the privacy calculus does not take place in a vacuum. 
-It is often argued that communication online can be easily triggered by external circumstances.
-I therefore analyze whether the privacy calculus is affected by the affordances of a website. 
-Specifically, I investigate whether *popularity cues* such as like and dislike buttons affect the privacy calculus and whether they foster communication online.
+Third, the privacy calculus does not take place in a vacuum, and it is often argued that self-disclosure can be easily triggered by external circumstances.
+We therefore analyze whether the privacy calculus is affected by the affordances of a website. 
+Specifically, we investigate whether *popularity cues* such as like and dislike buttons affect the privacy calculus and whether they foster self-disclosure.
 
-Fourth, it is still largely unknown whether the privacy calculus can be replicated with _behavioral data_ in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
-Thus far, much research on the privacy calculus used self-reports of behavior [@krasnovaOnlineSocialNetworks2010], vignette approaches [@bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
-A long-term field study observing actual behavior in an authentic context is still missing.
+Fourth, it is still largely unknown whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting [@kokolakisPrivacyAttitudesPrivacy2017]. 
+Thus far, most research on the privacy calculus used self-reports of behavior [@krasnovaOnlineSocialNetworks2010], vignette approaches [@bolUnderstandingEffectsPersonalization2018], or one-shot experiments in the lab [@treptePrivacyCalculusContextualized2020].
+A long-term field study in which actual behavior is observed in an authentic context is still missing.
 
-To test the research questions, a representative sample of the German population was collected in a preregistered online field experiment.
+To test our research questions, we collected a representative sample of the German population and conducted a preregistered online field experiment.
 Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all. 
-Over the course of one week, participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany). 
+Over the course of one week participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany). 
 Afterward, they answered a follow-up questionnaire with items measuring the privacy calculus variables.
@@
 
-The key variable of interest for this study is (verbal) communication online.
-Are people willing to engage in a conversation?
-Do they express their opinion? 
-In communicating online, people share much information about themselves.
-Communication is, hence, closely related to self-disclosure, and it is a primary means of regulating privacy [e.g., @dienlinPrivacyProcessModel2014].
-<!-- Almost all types of communication allow for meaningful inferences about a person, even when we _don't_ communicate [@watzlawickPragmaticsHumanCommunication2011].  -->
-<!-- However, the recent years have illustrated vividly how much additional insights we can get about a person, simply by analyzing their digital traces of communication or their meta-data [@kosinskiPrivateTraitsAttributes2013].
--->
-<!-- The more we communicate, the more we self-disclose. -->
+The key variable of interest for this study is self-disclosure.
+Self-disclosure is a primary means of regulating privacy [e.g., @masurSituationalPrivacySelfdisclosure2018].
+There are two different understandings of self-disclosure: 
+The first limits self-disclosure to _deliberate_ acts of sharing _truthful_ information about the self with others [@jourardTransparentSelf1964]. 
+The second considers _all_ acts of communication---active or passive, deliberate or unintended---as self-disclosure.
+In other words, when communicating it is not possible not to self-disclose.
+In this study, we adopt the latter understanding.
+All types of communication allow for meaningful inferences about a person [@watzlawickPragmaticsHumanCommunication2011]. 
+The recent years have illustrated vividly how much we can learn about a person only by analyzing their digital traces of communication or their meta-data [@kosinskiPrivateTraitsAttributes2013]. 
+Self-disclosure has three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) [@omarzuDisclosureDecisionModel2000].
+Here, we focus on _communication quantity_.
+The more we communicate, the more we self-disclose.
+Notably, the relation is not linear: 
+Impressions are formed quickly, and the more we communicate the less likely it becomes to share new information.
 
-Privacy concerns were defined as follows.
-"Taken together, concerns about online privacy represent how much an individual is motivated to focus on their control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that their privacy might be threatened" [@dienlinLongitudinalAnalysisPrivacy2021, p.
-4].
+Privacy concerns were defined as follows: 
+"Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened" [@dienlinLongitudinalAnalysisPrivacy2019, p.
+6].
 
-In this study I adopt the theoretical perspective of the privacy calculus [@lauferPrivacyConceptSocial1977].
-The privacy calculus assumes that when communicating online people engage in a rational weighing of risks and benefits.
-Notably, I don't assume that this weighing process is flawless or that humans are perfect rational agents.
-Instead, I understand the privacy calculus from the perspective of _bounded rationality_ [@simonBoundedRationality1990].
-Bounded rationality has three tenets: 
-"(1) humans are cognitively constrained; 
-(2) these constraints impact decision making; 
-and (3) difficult problems reveal the constraints and highlight their significance." [@bendorBoundedRationality2015, p. 1303]
-Crucially, although bounded rationally upholds that human behavior is not perfectly logical, this does not meant that it is irrational [@gigerenzerBoundedRationalityAdaptive2002].
-Instead, it is a continuum.
-Humans are still trying to optimize the outcomes of their behavior according to their own best interests or values.
-It is only that their capacity to do so is bounded.
+In this study we adopt the theoretical perspective of the privacy calculus [@lauferPrivacyConceptSocial1977].
+The privacy calculus assumes that when self-disclosing people engage in a rational weighing of risks and benefits.
+We do not assume that this weighing process is flawless and that humans are perfect rational agents.
+Instead, we understand the privacy calculus from the perspective of _bounded rationality_ [@simonBoundedRationality1990].
+Although humans weigh pros and cons when disclosing, their capacity is limited, errors happen, and manipulation always possible.
 
-Transferred to the context of online privacy, it is by now well known that several irregularities and inconsistencies between concerns and communication behavior exist.
-These differences stem from, for example, information asymmetries, present bias, intangibility, illusory control, or herding [@acquistiSecretsLikesDrive2020].
-At the same time, _on average_ people do behave according to their interests, respond to incentives, or actively manage their privacy [@baruhOnlinePrivacyConcerns2017; @dienlinExtendedPrivacyCalculus2016; @soloveMythPrivacyParadox2020].
+We therefore hypothesize that experiencing privacy concerns should reduce self-disclosure.
+In light of bounded rationality and the existence of other competing factors that also influence self-disclosure, we assume that the effect is only small.
+Previous research has likewise found that people who are more concerned about their privacy than others are slightly less likely to share personal information [@baruhOnlinePrivacyConcerns2017; @heirmanPredictingAdolescentsDisclosure2013; @koohikamaliInvestigationDynamicModel2019].
 
-I therefore hypothesize that people who experience more privacy concerns engage in less communication online.
-In light of bounded rationality and the existence of other competing factors that also influence online-communication (see below), the effect is likely small.
+H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.
 
-In turn, the most relevant factor driving online communication is _expected gratifications_.
+According to privacy calculus, the most relevant competing factor explaining self-disclosure is _expected gratifications_.
 People accept a loss of privacy if they can gain something in return [e.g., @lauferPrivacyConceptSocial1977].
-The most prominent gratifications of online communication include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
-Several studies have shown, that gratifications outweigh concerns [@dienlinExtendedPrivacyCalculus2016; @bolUnderstandingEffectsPersonalization2018].
-As a result, we expect a moderate relationship.
+The most prominent gratifications include social support [@krasnovaOnlineSocialNetworks2010], social capital [@ellisonNegotiatingPrivacyConcerns2011], entertainment [@dhirUnderstandingRelationshipIntensity2017], information-seeking [@whitingWhyPeopleUse2013], and self-presentation [@minHowArePeople2015].
 
-H1: People who are more concerned about their privacy than others are less likely to communicate actively on a website.
+H2: People are more likely to self-disclose on a website when they obtain more gratifications from using the website.
 
-H2: People who obtain more gratifications from using a website are more likely to communicate actively on a website.
-
-Privacy calculus implies that people _explicitly_ compare benefits and disadvantages before communicating online.
-Research on the privacy calculus has often ignored this aspect [@knijnenburgDeathPrivacyCalculus2017].
-Only observing that privacy concerns or expected gratifications and communication online are _related_ is insufficient to prove an explicit weighing process.
-Hence, we here analyze how much people actively deliberate about their privacy and how that might influence the privacy calculus.
-
-We can understand the privacy calculus from two perspectives (Table \@ref(tab:PC)):
-First, is the communication behavior aligned with people's privacy concerns and expected benefits? 
-Second, is the communication process implicit or explicit?
-
-Here, I suggest that the privacy calculus should be discussed in light of dual process theories, which state that people either deliberately, explicitly, and centrally take decisions, or instead do so automatically, implicitly, and peripherally [@kahnemanThinkingFastSlow2011; @pettyCommunicationPersuasionCentral1986].
+Privacy calculus holds that people deliberately compare benefits and disadvantages when disclosing.
+However, that process has not been analyzed explicitly so far [@knijnenburgDeathPrivacyCalculus2017].
+Only observing that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient to prove an explicit weighing process.
+Here, we suggest that the privacy calculus should be discussed in light of dual process theories, which state that people either deliberately, explicitly, and centrally take decisions, or instead do so automatically, implicitly, and peripherally [@kahnemanThinkingFastSlow2011; @pettyCommunicationPersuasionCentral1986].
 Accordingly, privacy calculus would assume that people, when it comes to disclosing, engage in a central processing. 
-Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, I hence introduce and investigate a novel concept termed _privacy deliberation_.
+Building on @omarzuDisclosureDecisionModel2000 and @altmanPrivacyConceptualAnalysis1976, we hence introduce and investigate a novel concept termed _privacy deliberation_.
 Privacy deliberation captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.
 
-On the one hand, deliberating about privacy could _reduce_ subsequent communication.
+On the one hand, deliberating about privacy could _reduce_ subsequent self-disclosure.
 Refraining from communication---the primary means of connecting with others---likely requires some active and deliberate restraint. 
-This is especially true for social media, which are designed to elicit communication and participation.
-Actively thinking about whether communicating is really worthwhile might be the first step not to participate.
-On the other hand, deliberating about privacy might also _increase_ communication.
-A person concerned about their privacy might conclude that in this situation communication is actually beneficial. 
+On the other hand, deliberating about privacy might also _increase_ self-disclosure.
+A person concerned about their privacy might conclude that in this situation self-disclosure is actually beneficial. 
 Deliberation could represent some kind of inner consent, providing additional affirmation.
+We therefore formulate the following research question:
 
-Alternatively, it could be that deliberation functions as a moderator.
-For example, if people actively deliberate about whether or not to disclose, this might reinforce the effect of concerns or gratifications.
-Reflecting about the pros and cons of communication might concerns and gratifications more salient. 
-Alternatively, it could also be that deliberating decreases the effects, for example because apparent gratifications are considered more critically, and maybe loose their appeal.
+RQ1: Are people more or less likely to self-disclose on a website depending on how actively they deliberate about whether they should self-disclose?
 
-I therefore formulate the following two research questions:
-
-RQ1: Do people who deliberate more actively whether they should communicate, communicate more or less online?
-
-RQ2: Do people who deliberate more actively whether they should communicate, show larger or smaller relations between concerns, gratifications and communication behavior?
-
-Bounded rationality implies that additional factors should also explain communication.
-Communication online often takes place in situations where information is limited or obscure.
+Bounded rationality implies that additional factors should also explain self-disclosure.
+Self-disclosure online often takes place in situations where information is limited or obscure.
 The more familiar users are with a context, the more experience, knowledge, and literacy they possess, the more likely they should be to navigate online contexts successfully.
-In other words, if users possess more _self-efficacy_ to participate, they should also communicate more.
+In other words, if users possess more _self-efficacy_ regarding self-disclosing, they should also self-disclose more.
 Related, people who report more privacy self-efficacy also engage in more self-withdrawal [@chenRevisitingPrivacyParadox2018; @dienlinExtendedPrivacyCalculus2016].
 
-H3: People are more likely to communicate on a website when their self-efficacy about self-disclosing on the website is higher.
+H3: People are more likely to self-disclose on a website when their self-efficacy about self-disclosing on the website is higher.
 
@@
 In the online context, there exist several different _targets_ of trust, including (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users [@sollnerWhyDifferentTrust2016].
-Because the targets can be largely different, it is often recommended to analyze them individually.
 
-H4: People are more likely to communicate on a website when they have greater trust in the provider, the website, and the other users.
+H4: People are more likely to self-disclose on a website when they have greater trust in the provider, the website, and the other users.
 
@@
 
-So far I analyzed user-oriented factors that explain communication online.
-But how does the context, the digital infrastructure, affect the privacy calculus and communication? 
-In what follows I do not focus on specific _features_ of particular websites, which can change and quickly become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
-Instead, I address the underlying latent structures by analyzing so-called _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. 
-Developed by @gibsonEcologicalApproachVisual2015, affordances emphasize that it is not the _objective features_ of objects that determine behavior, but rather our _subjective perceptions_. 
+So far we analyzed user-oriented factors that explain self-disclosure.
+But how does the context, the digital infrastructure, affect the privacy calculus and self-disclosure? 
+In what follows we do not focus on specific _features_ of particular websites, which can change and quickly become obsolete [@foxDistinguishingTechnologiesSocial2017]. 
+Instead, we address the underlying latent structures by analyzing so-called _affordances_ [@ellisonSocialNetworkSite2015; @foxDistinguishingTechnologiesSocial2017]. 
+Developed by @gibsonEcologicalApproachVisual2015, affordances emphasize that it is not the _objective features_ of objects that determine behavior, but our _subjective perceptions_. 
 Affordances are mental representations of how objects might be used.
 <!-- ; as such, they are by definition subjective.  -->
-There is an ongoing debate on what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017].
+<!-- There is an ongoing debate on what exactly defines an affordance [@evansExplicatingAffordancesConceptual2017]. 
 For example, whereas @evansExplicatingAffordancesConceptual2017 propose three affordances for mediated communication (i.e., anonymity, persistence, and visibility), @foxDistinguishingTechnologiesSocial2017 suggest 10 affordances for SNSs alone (i.e., accessibility, bandwidth, social presence, privacy, network association, personalization, persistence, editability, conversation control, and anonymity).
+-->
 
@@
 Popularity cues such as like and dislike buttons, which are categorized as "paralinguistic digital affordances" [@carrPredictingThresholdPerceived2018, p.
-142], can be linked to the two sides of the privacy calculus.
+142], can be linked tp the two sides of the privacy calculus.
 The like button is positive and a potential benefit:
@@
 When users disagree with a post, they are more likely to click on a button labeled _respect_ compared to a button labeled _like_ [@stroudRecommendRespectAltering2017].
-The potentially stark negative effect of the dislike button might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit, or stackexchange).
+<!-- The potentially stark negative effect of the dislike button might also explain why to date only a handful of major websites have implemented it (e.g., youtube, reddit, or stackexchange). -->
 In this vein, popularity cues likely also impact the privacy calculus [@kramerMasteringChallengeBalancing2020].
@@
 
+H5.	Compared to people who use a website without like or dislike buttons, people who use a website with like buttons (a) self-disclose more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.
+
 Receiving a _dislike_ should feel more like a punishment.
@@
 In online contexts, gains often outweigh losses.
-Having both types of popularity cues might still lead to more gratifications and communication.
+Having both types of popularity cues might still lead to more gratifications and self-disclosure.
 However, privacy concerns should not be reduced anymore:
@@
 
-There are two potential underlying theoretical pathways:
-The _mere presence_ of popularity cues might affect whether people are willing to disclose; being able to attract likes might motivate users to communicate, while the mere option to receive dislikes might intimidate others.
-On the other hand, _actually receiving_ likes or dislikes might then affect subsequent behavior, potentially reinforcing the process.
+H6.	Compared to people who use a website without like or dislike buttons, people who use a website with like _and_ dislike buttons (a) self-disclose more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.
 
-H5.	Compared to people who use a website without like or dislike buttons, people who use a website with like buttons (a) communicate more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.
-
-H6.	Compared to people who use a website without like or dislike buttons, people who use a website with like _and_ dislike buttons (a) communicate more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.
-
-<!-- When directly comparing websites including both like and dislike buttons with websites including only like buttons, building on the rationales presented above, it is likely that websites including both buttons should increase privacy concerns and privacy deliberation.
--->
+When directly comparing websites including both like and dislike buttons with websites including only like buttons, building on the rationales presented above, it is likely that websites including both buttons should increase privacy concerns and privacy deliberation.
 
@@
 
-For a simplified overview of the analyzed model, see Figure \@ref(fig:model).
+For a simplified overview of the model we analyzed, see Figure \@ref(fig:model).
 
@@
 The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's companion website (https://XMtRa.github.io/privacy_calc_exp_anon).
-I preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
-I needed to change the pre-defined plan in some cases. 
+We preregistered the study using the registration form _OSF Prereg_, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859).
+We needed to change our pre-defined plan in some cases. 
 For a full account of all changes, see OSM. 
@@
 
-I collaborated with a market research company to recruit participants. 
+We collaborated with a market research company to recruit participants. 
 As incentive, participants were awarded digital points, which they could use to get special offers from other online commerce services. 
@@
 In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.[^1] 
-Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which I (a) asked about their sociodemographics, (b) provided more details about the study, and (c) included a registration link for the website, which was described as "participation platform".
+Members who decided to take part were subsequently sent the first questionnaire (_T1_), in which we (a) asked about their sociodemographics, (b) provided more details about the study, and (c) included a registration link for the website, which was described as "participation platform".
 Afterward, participants were randomly assigned to one of the three websites. 
@@
 Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (_T2_). 
-Measures were collected after and not before the field phase in order not to prime participants or reveal the primary research interest.
+Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.
 
 [^1]: Although the terror attack was not of primary interest for this study, the data can and will also be used to analyze perceptions of the terrorism threat.
-Hence, no deception took place, and in the debriefing participants were informed about the additional research interest in privacy.
+Hence, no deception took place, and in the debriefing participants were informed about our additional research interest in privacy.
 
-The online website was programmed based on the open-source software _discourse_ (https://www.discourse.org/). 
-I conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). 
-`r n_users %>% english::english() %>% str_to_sentence` participants created a user account on the website (see below) and used the website actively. 
-Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(3600) %>% round(0) %>% format(big.mark = ",")` hours online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and clicked on `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
-Notably, there were no instances of people providing meaningless text. 
+We programmed an online website based on the open-source software _discourse_ (https://www.discourse.org/). 
+We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \@ref(fig:website)). 
+Participants used the website actively: Overall, they spent `r sum(d_raw$time_read, na.rm = TRUE) %>% "/"(3600) %>% round(0) %>% format(big.mark = ",")` hours online, wrote `r sum(d_raw$post_count, na.rm = TRUE) %>% format(big.mark = ",")` comments, and clicked on `r sum(d_raw$reactions, na.rm = TRUE)` popularity cues.
+Notably, we did not find any instances of people providing meaningless text. 
 For an example of communication that took place, see Figure \@ref(fig:comments).
@@
 
-I ran a priori power analyses to determine sample size. 
+We ran a priori power analyses to determine sample size. 
 The power analysis was based on a smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018]. 
-Namely, I defined a minimum effect size considered sufficiently large to support the hypotheses. 
-Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with standardized small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], I set the SESOI to be _r_ = `r r_sesoi %>% my_round("std")`.
-The aim was to be able to detect this SESOI with a probability of at least 95%.
+Namely, we defined a minimum effect size that we considered sufficiently large to support our hypotheses. 
+Because small effects should be expected when researching aspects of privacy online [e.g., @baruhOnlinePrivacyConcerns2017], with standardized small effects beginning at an effect size of _r_ = .10 [@cohenPowerPrimer1992], we set our SESOI to be _r_ = `r r_sesoi %>% my_round("std")`.
+Our aim was to be able to detect this SESOI with a probability of at least 95%.
 Using the regular alpha level of 5%, basic power analyses revealed a minimum sample size of _N_ = `r n_desired %>% format(big.mark = ",")`.
-In the end, I was able to include _N_ = `r n_final` in the analyses (see below). 
-This means that the study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
-Put differently, I was able to make reliable inferences (i.e., power = 95%) about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
+In the end, we were able to include _N_ = `r n_final` in our analyses (see below). 
+This means that our study had a probability (power) of `r power_achieved * 100`% to find an effect at least as large as _r_ = `r r_sesoi %>% my_round("std")`. 
+Put differently, we were able to make reliable inferences (i.e., power = 95%) about effects at least as big as _r_ = `r r_sensitive %>% my_round("std")`.
 
-A representative sample of the German population in terms of age, sex, and federal state was collected. 
+We collected a representative sample of the German population in terms of age, sex, and federal state. 
 In sum, `r n_t1 %>% format(big.mark = ",")` participants completed the survey at T1, `r n_users` participants created a user account on the website,  and `r n_t2` participants completed the survey at T2.
-Using tokens and IP addresses, I connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
+Using tokens and IP addresses, we connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
 The data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
 In the end, the data of `r n_matched` participants could be matched successfully.
-I excluded `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which were considered to be unreasonably fast.[^note] 
-To detect atypical data, I calculated Cook's distance.
-I excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
+We excluded `r n_speeding` participants who finished the questionnaire at T2 in less than three minutes, which we considered to be unreasonably fast.[^note] 
+To detect atypical data, we calculated Cook's distance.
+We excluded `r english::english(n_resp_pattern)` participants who provided clear response patterns (i.e., straight-lining). 
 The final sample included _N_ = `r n_final` participants.
@@
 
-[^note]: I preregistered to delete participants with less than 6 minutes answer time.
-However, this led to the exclusion of too many data points of high quality, which is why I relaxed this criterion.
-In the OSM, I report also the results using all participants.
+[^note]: We preregistered to delete participants with less than 6 minutes answer time.
+However, this led to the exclusion of too many data points of high quality, which is why we relaxed this criterion.
+In the OSM, we report also the results using all participants.
 
@@
 
-Wherever possible, I operationalized the variables using established measures.
-Where impossible (for example, to date there exists no scale on privacy deliberation), I self-designed novel items, which were pretested concerning legibility and understandability.
-To assess factor validity I ran confirmatory factor analyses (CFA). 
-If the CFAs revealed insufficient fit, I deleted malfunctioning items. 
+Wherever possible, we operationalized the variables using established measures.
+Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which were pretested concerning legibility and understandability.
+To assess factor validity we ran confirmatory factor analyses (CFA). 
+If the CFAs revealed insufficient fit, we deleted malfunctioning items. 
 All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale. 
@@
 
-I differentiated between two separate types of gratifications. 
+We differentiated between two separate types of gratifications. 
 _General gratifications_ were measured with five items based on @sunLocationInformationDisclosure2015.
@@
 
-I differentiated between two types of trust. 
+We differentiated between two types of trust. 
 _General trust_ was operationalized based on @sollnerWhyDifferentTrust2016, addressing three targets (i.e., provider, website, and other users) with one item each. 
@@
 The results showed that the provider and website targets were not sufficiently distinct, as was evidenced by a Heywood case (i.e., standardized coefficient greater than 1). 
-I hence adapted the scale to combine these two targets. 
+We hence adapted the scale to combine these two targets. 
 The updated scale showed adequate fit.
 
-### Communication
+### Self-disclosure
 
-Communication was calculated by counting the number of words each participant wrote in a comment.
-Communication was heavily skewed.
-Many people did communicate not at all, while some communicated a lot.
-Hence, the sum of words was log-scaled.
+Self-disclosure was calculated by log-scaling of the number of words each participant wrote in a comment plus the double-weighted number of likes and dislikes (preregistered). 
+The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence “I like” and dislike buttons “I dislike”.
+The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure decreases the more a person communicates (see above).
 
@@
 The influence of the three websites was analyzed using contrast coding.
-I could therefore test the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016]. 
-Because the dependent variable communication was not normally distributed, I estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
-As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit I report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
-Because sociodemographic variables are often related to communication and other privacy-related concepts [@tifferetGenderDifferencesPrivacy2019], I controlled all variables for the influence of sex, age, and education.
+We could therefore test the effects of experimental manipulations within a theoretical framework while using latent variables [@klinePrinciplesPracticeStructural2016]. 
+Because the dependent variable self-disclosure was not normally distributed, we estimated the model using robust maximum likelihood [@klinePrinciplesPracticeStructural2016]. 
+As recommended by @klinePrinciplesPracticeStructural2016, to assess global fit we report the model's $\chi^2$, RMSEA (90% CI), CFI, and SRMR. 
+Because sociodemographic variables are often related to self-disclosure and other privacy-related concepts [@tifferetGenderDifferencesPrivacy2019], we controlled all variables for the influence of sex, age, and education.
 Preregistered hypotheses were tested with a one-sided significance level of 5%. 
@@
 
-I used `r r_citations` for all analyses.
+We used `r r_citations` for all our analyses.
 
@@
 
-I first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
+We first measured and plotted all bivariate relations between the study variables (see Figure \@ref(fig:corrplot)). 
 No relationship was particularly curvilinear. 
-Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with communication. 
+Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with self-disclosure. 
 For example, people who were more concerned about their privacy disclosed less information (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "pri_con" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
-Worth noting, specific gratifications predicted communication better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
+Worth noting, specific gratifications predicted self-disclosure better than general gratifications (_r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_spec" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")` vs.
 _r_ `r parameterestimates(fit_baseline, standardized = TRUE) %>%  filter(op == "~~" & lhs == "grats_gen" & rhs == "self_dis_lg") %>% select(std.all) %>%  my_round("std_txt")`).
@@
 
-First, I ran a model as specified in the preregistration. The model fit the data okay, `r fit_txt(fit_prereg, scaled = TRUE)`. 
-Regarding H1, I did not find that general gratifications predicted communication (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
-With regard to H2, privacy concerns did not significantly predict communication (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
-RQ1 similarly revealed that privacy deliberation was not correlated with communication (`r coeffs_txt(fit_prereg, "c1")`; two-sided). 
-Regarding H3, however, I found that experiencing self-efficacy predicted communication substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided). 
-Concerning H4, results showed that trust was not associated with communication (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).
+First, we ran a model as specified in the preregistration. The model fit our data okay, `r fit_txt(fit_prereg, scaled = TRUE)`. 
+Regarding H1, we did not find that general gratifications predicted self-disclosure (`r coeffs_txt(fit_prereg, "a1", one_sided=T)`; one-sided). 
+With regard to H2, privacy concerns did not significantly predict self-disclosure (`r coeffs_txt(fit_prereg, "b1", one_sided=T)`; one-sided). 
+RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (`r coeffs_txt(fit_prereg, "c1")`; two-sided). 
+Regarding H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (`r coeffs_txt(fit_prereg, "d1", one_sided=T)`; one-sided). 
+Concerning H4, results showed that trust was not associated with self-disclosure (`r coeffs_txt(fit_prereg, "e1", one_sided=T)`; one-sided).
 
 However, these results should be treated with caution.
-I found several signs of multicollinearity, such as large standard errors or "wrong" signs of predictors [@grewalMulticollinearityMeasurementError2004]. 
-In the multiple regression trust had a _negative_ relation with communication, whereas in the bivariate analysis it was _positive_.
+We found several signs of multicollinearity, such as large standard errors or "wrong" signs of predictors [@grewalMulticollinearityMeasurementError2004]. 
+In the multiple regression trust had a _negative_ relation with self-disclosure, whereas in the bivariate analysis it was _positive_.
 
@@
 
-I slightly adapted the preregistered model on the basis of the insights described above. 
-First, instead of specific trust and general gratifications I included _general_ trust and _specific_ gratifications, which were correlated slightly less strongly. 
-The adapted model fit the data comparatively well, `r fit_txt(fit_adapted)`.
+We slightly adapted our preregistered model on the basis of the insights described above. 
+First, instead of specific trust and general gratifications we included _general_ trust and _specific_ gratifications, which were correlated slightly less strongly. 
+The adapted model fit our data comparatively well, `r fit_txt(fit_adapted)`.
 
-In the adapted privacy calculus model, specific gratifications were positively related to communication online (`r coeffs_txt(fit_adapted, "b1")`; two-sided). 
+In the adapted privacy calculus model, specific gratifications were positively related to self-disclosure online (`r coeffs_txt(fit_adapted, "b1")`; two-sided). 
 People who deliberated more about their privacy disclosed less information (`r coeffs_txt(fit_adapted, "c1")`; two-sided). 
-Self-efficacy remained substantially correlated with communication (`r coeffs_txt(fit_adapted, "d1")`; two-sided). 
-Notably, I found a negative correlation between trust and communication (`r coeffs_txt(fit_adapted, "e1")`; two-sided), which again implies multicollinearity.
+Self-efficacy remained substantially correlated with self-disclosure (`r coeffs_txt(fit_adapted, "d1")`; two-sided). 
+Notably, we found a negative correlation between trust and self-disclosure (`r coeffs_txt(fit_adapted, "e1")`; two-sided), which again implies multicollinearity.
 
@@
 (a) combining collinear variables into a single measure, or (b) keeping only one of the collinear variables.
-Combining variables was not an option in this case, because both trust and expected benefits are theoretically distinct constructs.
-And because _several_ variables were closely related to one another, I therefore decided to fit a simple privacy calculus model containing only privacy concerns and specific gratifications.
+Combining variables was not an option in our case, because both trust and expected benefits are theoretically distinct constructs.
+And because _several_ variables were closely related to one another, we therefore decided to fit a simple privacy calculus model containing only privacy concerns and specific gratifications.
 
-The simple model fit the data well, `r fit_txt(fit_simple)`. 
-First, I found that people who experienced more privacy concerns than others disclosed less information (`r coeffs_txt(fit_simple, "a1")`; two-sided). 
-Second, people who reported more specific gratifications than others communicated more information (`r coeffs_txt(fit_simple, "b1")`; two-sided). 
-Both effect sizes were above the predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, which implies that the they were large enough to be theoretically relevant.
+The simple model fit our data well, `r fit_txt(fit_simple)`. 
+First, we found that people who experienced more privacy concerns than others disclosed less information (`r coeffs_txt(fit_simple, "a1")`; two-sided). 
+Second, people who reported more specific gratifications than others self-disclosed more information (`r coeffs_txt(fit_simple, "b1")`; two-sided). 
+Both effect sizes were above our predefined SESOI of _r_ = `r r_sesoi %>% my_round("std")`, which implies that the they were large enough to be theoretically relevant.
 
-When comparing the three models with one another, the adapted model explained the most variance in communication (`r round(rsquare_fit_adapted * 100, 2)` %), followed by the preregistered model (`r round(rsquare_fit_prereg * 100, 2)` %), and the simple privacy calculus model (`r round(rsquare_fit_simple * 100, 2)` %).
+When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (`r round(rsquare_fit_adapted * 100, 2)` %), followed by the preregistered model (`r round(rsquare_fit_prereg * 100, 2)` %), and the simple privacy calculus model (`r round(rsquare_fit_simple * 100, 2)` %).
 At the same time, the simple privacy calculus model was the most parsimonious one (BIC = `r model_comp_tab["simple", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["simple", "aic"] %>% round(0) %>% format(big.mark = ",")`), followed by the preregistered model (BIC = `r model_comp_tab["preregistered", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["preregistered", "aic"] %>% round(0) %>% format(big.mark = ",")`), and the adapted model (BIC = `r model_comp_tab["adapted", "bic"] %>% round(0) %>% format(big.mark = ",")`, AIC = `r model_comp_tab["adapted", "aic"] %>% round(0) %>%  format(big.mark = ",")`).
@@
 
-```{r plotpc, fig.cap="Predictors of communication. Displayed are the 95\\% CIs of unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=4}
+```{r plotpc, fig.cap="Predictors of self-disclosure. Displayed are the 95\\% CIs of unstandardized effects.", out.width = "\\textwidth", fig.pos = "!h", fig.height=4}
 knitr::include_graphics("figures/results/coeffs.png")
@@
 
-In a next step, I analyzed the potential effects of the popularity cues. 
-I for example expected that websites with like buttons would lead to more communication, gratifications, and privacy deliberation and to less privacy concerns.
-Somewhat surprisingly, I found no effects of the popularity cues on the privacy calculus variables.
+In a next step, we analyzed the potential effects of the popularity cues. 
+We for example expected that websites with like buttons would lead to more self-disclosure, gratifications, and privacy deliberation and to less privacy concerns.
+Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables.
 For an illustration, see Figure \@ref(fig:popularitycues), which displays the model-predicted values for each variable (using the baseline model).
@@
 Note that some differences missed statistical significance only marginally (e.g., specific gratifications for the comparison between the website with like buttons and the control website without like and dislike buttons).
-Nevertheless, I refrain from reading too much into these subtle differences.
-I conclude that the three websites were comparable regarding the privacy calculus variables and the amount of communication.
+Nevertheless, we refrain from reading too much into these subtle differences.
+We conclude that the three websites were comparable regarding the privacy calculus variables and the amount of self-disclosure.
 
@@
 Like \\& Dislike: Website with like and dislike buttons.", out.width = "\\textwidth", fig.pos = "!h"}
-knitr::include_graphics("figures/results/violin_plot.png")
+knitr::include_graphics("figures/results/bar_plot.png")
 ```
@@
 The data stem from a representative sample of the German population.
-I extended the theoretical privacy calculus model by explicitly testing privacy deliberation processes.
-I included self-efficacy and trust as additional variables, to better represent the theoretical premise of bounded rationality.
-I further asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons.
+We extended the theoretical privacy calculus model by explicitly testing privacy deliberation processes.
+We included self-efficacy and trust as additional variables, to better represent our theoretical premise of bounded rationality.
+We further asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons.
 
-In the bivariate analyses, all privacy calculus variables significantly predicted communication activity. 
-Thus, all variables likely play an important role when it comes to understanding online-communication.
-In the preregistered analyses using multiple regression, however, only self-efficacy significantly predicted communication.
+In the bivariate analyses, all privacy calculus variables significantly predicted self-disclosure. 
+Thus, all variables likely play an important role when it comes to understanding online-processes.
+In the preregistered analyses using multiple regression, however, only self-efficacy significantly predicted self-disclosure.
 All other variables were not significant.
@@
 The preregistered extended privacy calculus model was therefore not supported by the data.
-However, the model showed problems typical of multicollinearity, which is why I also explored (a) an adapted version of the preregistered model, in which I exchanged two variables, and (b) a simple privacy calculus model, which included only privacy concerns and specific gratifications.
+However, the model showed problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a simple privacy calculus model, which included only privacy concerns and specific gratifications.
 
@@
 People who expect more specific gratifications and who feel more self-efficacious disclose more.
-However, the model also suggests that if trust increases, while all other factors remain constant, communication decreases, which seems theoretically implausible. 
-As a result, I also fit a simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted communication. 
-Taken together, the results support the privacy calculus framework and suggest that in specific contexts communication online is not erratic and that it can be explained by several psychological variables.
+However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases, which seems theoretically implausible. 
+As a result, we also fit a simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure. 
+Taken together, the results support the privacy calculus framework and suggest that in specific contexts self-disclosure online is not erratic and that it can be explained by several psychological variables.
 At the same time, variables such as trust and efficacy seem to play an important role, which further supports the underlying premise of bounded rationality.
@@
 Determining whether this figure is large or small is difficult.
-Although the effect seems substantial to us, one could argue that it should be higher and that more people should actively deliberate about their online communication.
+Although the effect seems substantial to us, one could argue that it should be higher and that more people should actively deliberate about their online self-disclosure.
 Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar.
@@
 
-Popularity cues do not always seem to have a strong influence on the privacy calculus and communication.
-Although some studies reported that popularity cues can substantially impact behavior [@muchnikSocialInfluenceBias2013], in this study I found the opposite.
+Popularity cues do not always seem to have a strong influence on the privacy calculus and self-disclosure.
+Although some studies reported that popularity cues can substantially impact behavior [@muchnikSocialInfluenceBias2013], in our study we found the opposite.
 Users disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons.
@@
 Self-efficacy is often only a self-reported proxy of behavior and offers little incremental insight. 
-Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to communicate whereas others do not.
+Instead, it might be more interesting to find out _why_ some people feel sufficiently efficacious to self-disclose whereas others do not.
 
@@
 From a _theoretical_ perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
-It is my understanding that multiple regression is often used to isolate effects, to make sure that they are not caused by other third variables.
+It is our understanding that multiple regression is often used to isolate effects, to make sure that they are not caused by other third variables.
 However, in cases of highly correlated variables this often does not make much sense theoretically.
-Combining trust and gratification in a multiple regression asks how increasing benefits affects communication _while holding trust constant_.
+Combining trust and gratification in a multiple regression asks how increasing benefits affects self-disclosure _while holding trust constant_.
 However, it seems more plausible to assume that increasing gratifications also automatically increases trust [@sollnerWhyDifferentTrust2016].
-In the preregistered analysis I even went further and tested whether trust increases communication while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---an unlikely scenario.
-In short, the effects I found could be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value.
+In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---an unlikely scenario.
+In short, the effects we found could be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value.
 
-Finally, I found a surprisingly strong correlation between specific trust and expected gratifications (i.e., _r_ = .79).
+Finally, we found a surprisingly strong correlation between specific trust and expected gratifications (i.e., _r_ = .79).
 Operationalizations of trust are remarkably close to expected gratifications. 
@@
 <!-- Doing so can introduce problems of homogeneity and multicollinearity. -->
-I thus recommend using general and reflective measures of trust.
+We thus recommend using general and reflective measures of trust.
 
@@
 
-Although I did not find significant effects of like and dislike buttons in this study, they could still affect the privacy calculus in other contexts and settings.
-All findings are limited to the context I analyzed and should not be overly generalized.
+This paper operationalized self-disclosure via communication quantity.
+Other understandings of self-disclosure exist that are more narrow, and that would require a qualitative analysis of exchanged communication.
+However, additional qualitative analyses were beyond the scope of this paper and not aligned with our theoretical understanding of self-disclosure.
+
+Although we did not find significant effects of like and dislike buttons in this study, they could still affect the privacy calculus in other contexts and settings.
+Our findings are limited to the context we analyzed and should not be overly generalized.
 Null-findings pose the *Duhème-Quinn Problem* [@dienesUnderstandingPsychologyScience2008].
 They can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question. 
-In this case, it was not possible to send participants notifications when their comments were liked or disliked, which significantly decreased the popularity cues' salience.
+In this case, we were not able send participants notifications when their comments were liked or disliked, which significantly decreased the popularity cues' salience.
 
@@
 -->
-Likewise, the mediation model is only suggestive, as I did not experimentally manipulate the mediating variables and also did not use a longitudinal design.
+Likewise, the mediation model is only suggestive, as we did not experimentally manipulate the mediating variables and also did not use a longitudinal design.
 
@@
 The assumption of stable unit treatment states that in experiments only the experimental variable should be manipulated, while all others should be held constant [@klinePrinciplesPracticeStructural2016].
-In this study, I explicitly manipulated the popularity cues. 
+In this study, we explicitly manipulated the popularity cues. 
 However, because the experiment was conducted in the field several other variables could not be held constant, such as the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
@@
 
-In this study I have found some support for the privacy calculus approach.
+In this study we have found some support for the privacy calculus approach.
 People who were more concerned about their privacy disclosed less information online, whereas people who received more gratifications from using a website disclosed more information online. 

### 2021-07-14 preprint.tex
- implemented major changes after feedback from reviewers

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment},
  pdfauthor={Dienlin, Tobias1, Braeunlich, Katharina2, \& Trepte, Sabine3},
  pdflang={en-EN},
  pdfkeywords={privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Popularity cues and privacy calculus}
\keywords{privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration\newline\indent Word count: 6073}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\setlength{\parskip}{0em}
\raggedbottom
\note{\clearpage}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{How Do Like and Dislike Buttons Affect Communication? Testing the Privacy Calculus in a Preregistered One-Week Field Experiment}
\author{Dienlin, Tobias\textsuperscript{1}, Braeunlich, Katharina\textsuperscript{2}, \& Trepte, Sabine\textsuperscript{3}}
\date{}

\note{

This preprint has been submitted to a journal and is currently under review. Please cite carefully.

}

\authornote{

Dr.~Tobias Dienlin is Assistant Professor of Interactive Communication at University of Vienna. He received his Ph.D.~from University of Hohenheim.

Dr.~Katharina Braeunlich works at the Federal Office for Information Security in Bonn. She is an alumna from University of Koblenz-Landau, where she received her Ph.D.

Dr.~Sabine Trepte is Full Professor for Media Psychology at University of Hohenheim. She received her Ph.D.~from Hanover University of Music, Drama and Media.

All authors contributed extensively to the work presented in this paper. TD, KB, \& ST designed the study; KB \& TD designed the online website; TD \& KB administered the data collection and importation; TD wrote the code, ran the models, and analyzed the output data; TD wrote the manuscript and ST provided comments; ST supervised the project.

The authors declare no competing interests.

This research was funded by the Volkswagen Foundation, project ``Transformations of privacy,'' which was awarded to Sandra Seubert, Sabine Trepte, Ruediger Grimm, \& Christoph Gusy. We would like to thank all our colleagues from the project as well as Niklas Johannes for valuable feedback.

This manuscript features a companion website, which includes the data, code, additional analyses, the preregistration, and a reproducible version of the manuscript (\url{https://XMtRa.github.io/privacy_calc_exp_anon}).

Correspondence concerning this article should be addressed to Dienlin, Tobias, University of Vienna, Department of Communication, 1090 Vienna, Austria. E-mail: \href{mailto:tobias.dienlin@univie.ac.at}{\nolinkurl{tobias.dienlin@univie.ac.at}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Vienna\\\textsuperscript{2} University of Koblenz-Landau\\\textsuperscript{3} University of Hohenheim}

\abstract{
According to privacy calculus, both privacy concerns and expected gratifications explain self-disclosure online. So far, most findings were based on self-reports or short-term experiments, and it is still largely unknown how popularity cues such as like and dislike buttons affect privacy calculus. To answer these questions we ran a preregistered one-week field experiment. Participants were randomly distributed to three different websites, on which they discussed a current political topic. The websites featured either (a) like buttons, (b) like and dislike buttons, or (c) no like or dislike buttons, and were otherwise identical. The final sample consisted of NOT AVAILABLE participants. Although the originally preregistered model was rejected, the results showed that a considerable share of actual self-disclosure could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy. The impact of the popularity cues on self-disclosure and privacy calculus was negligible.
}

\begin{document}
\maketitle

Understanding why people disclose personal information online is a critical question for society and research.
Originally, it was assumed that online self-disclosure is erratic and that it cannot be predicted by people's personal beliefs, concerns, or attitudes.
Most prominently, the privacy paradox stated that people self-disclose vast amounts of personal information online \emph{despite} having substantial concerns about their privacy (Barnes, 2006; Taddicken \& Jers, 2011).

Somewhat surprisingly, and despite its popularity in the media (New York Public Radio, 2018), the privacy paradox has garnered comparatively little empirical support.
A recent meta-analysis reported a correlation between privacy concerns and self-disclosure on SNS of \emph{r} = -.13 (Baruh, Secinti, \& Cemalcilar, 2017), which shows that privacy concerns are indeed related to self-disclosure online.

Hence, rather than further pursuing the privacy paradox, a large share of current day research builds on the so-called \emph{privacy-calculus} (Laufer \& Wolfe, 1977).
The privacy calculus states that self-disclosure online can be explained---at least partly---by means of expected risks \emph{and} expected benefits (Krasnova, Spiekermann, Koroleva, \& Hildebrand, 2010).
By operationalizing expected risks as privacy concerns, several studies have shown that experiencing privacy concerns is related to disclosing less information online, whereas expecting benefits is related to disclosing more information online (Heirman, Walrave, \& Ponnet, 2013; Koohikamali, French, \& Kim, 2019).

However, although the privacy calculus has gained momentum in academic research, several important questions remain unanswered.

First, current research on the privacy calculus is often criticized for not explicitly focusing on the deliberation process behind self-disclosure.
According to critics (e.g., Knijnenburg et al., 2017), showing that both concerns and gratifications correlate with self-disclosure is not sufficient evidence for an explicit weighing process.
In this study, we therefore explicitly focus on the privacy deliberation process.

Second, we approach the privacy calculus from a theoretical perspective of bounded rationality.
It is likely that other factors next to risks and benefits also determine behavior.
We therefore extend the privacy calculus model theoretically by investigating the role and interplay of trust and self-efficacy.

Third, the privacy calculus does not take place in a vacuum, and it is often argued that self-disclosure can be easily triggered by external circumstances.
We therefore analyze whether the privacy calculus is affected by the affordances of a website.
Specifically, we investigate whether \emph{popularity cues} such as like and dislike buttons affect the privacy calculus and whether they foster self-disclosure.

Fourth, it is still largely unknown whether the privacy calculus can be replicated with behavioral data in an authentic long-term setting (Kokolakis, 2017).
Thus far, most research on the privacy calculus used self-reports of behavior (Krasnova, Spiekermann, Koroleva, \& Hildebrand, 2010), vignette approaches (Bol et al., 2018), or one-shot experiments in the lab (Trepte, Scharkow, \& Dienlin, 2020).
A long-term field study in which actual behavior is observed in an authentic context is still missing.

To test our research questions, we collected a representative sample of the German population and conducted a preregistered online field experiment.
Participants were randomly distributed to one of three different websites, which either included a like button, both a like and a dislike button, or no buttons at all.
Over the course of one week participants had the chance to discuss a topical issue (i.e., prevention of terrorist attacks in Germany).
Afterward, they answered a follow-up questionnaire with items measuring the privacy calculus variables.

\hypertarget{the-privacy-calculus}{%
\subsection{The Privacy Calculus}\label{the-privacy-calculus}}

The key variable of interest for this study is self-disclosure.
Self-disclosure is a primary means of regulating privacy (e.g., Masur, 2018).
There are two different understandings of self-disclosure:
The first limits self-disclosure to \emph{deliberate} acts of sharing \emph{truthful} information about the self with others (Jourard, 1964).
The second considers \emph{all} acts of communication---active or passive, deliberate or unintended---as self-disclosure.
In other words, when communicating it is not possible not to self-disclose.
In this study, we adopt the latter understanding.
All types of communication allow for meaningful inferences about a person (Watzlawick, Bavelas, Jackson, \& O'Hanlon, 2011).
The recent years have illustrated vividly how much we can learn about a person only by analyzing their digital traces of communication or their meta-data (Kosinski, Stillwell, \& Graepel, 2013).
Self-disclosure has three different dimensions: breadth (i.e., number of topics covered), depth (i.e., intimacy of topics covered), and length (i.e., quantity of disclosure) (Omarzu, 2000).
Here, we focus on \emph{communication quantity}.
The more we communicate, the more we self-disclose.
Notably, the relation is not linear:
Impressions are formed quickly, and the more we communicate the less likely it becomes to share new information.

Privacy concerns were defined as follows:
``Concerns about online privacy represent how much an individual is motivated to focus on his or her control over a voluntary withdrawal from other people or societal institutions on the Internet, accompanied by an uneasy feeling that his or her privacy might be threatened'' (Dienlin, Masur, \& Trepte, 2019, p. 6).

In this study we adopt the theoretical perspective of the privacy calculus (Laufer \& Wolfe, 1977).
The privacy calculus assumes that when self-disclosing people engage in a rational weighing of risks and benefits.
We do not assume that this weighing process is flawless and that humans are perfect rational agents.
Instead, we understand the privacy calculus from the perspective of \emph{bounded rationality} (Simon, 1990).
Although humans weigh pros and cons when disclosing, their capacity is limited, errors happen, and manipulation always possible.

We therefore hypothesize that experiencing privacy concerns should reduce self-disclosure.
In light of bounded rationality and the existence of other competing factors that also influence self-disclosure, we assume that the effect is only small.
Previous research has likewise found that people who are more concerned about their privacy than others are slightly less likely to share personal information (Baruh, Secinti, \& Cemalcilar, 2017; Heirman, Walrave, \& Ponnet, 2013; Koohikamali, French, \& Kim, 2019).

H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.

According to privacy calculus, the most relevant competing factor explaining self-disclosure is \emph{expected gratifications}.
People accept a loss of privacy if they can gain something in return (e.g., Laufer \& Wolfe, 1977).
The most prominent gratifications include social support (Krasnova, Spiekermann, Koroleva, \& Hildebrand, 2010), social capital (Ellison, Vitak, Steinfield, Gray, \& Lampe, 2011), entertainment (Dhir \& Tsai, 2017), information-seeking (Whiting \& Williams, 2013), and self-presentation (Min \& Kim, 2015).

H2: People are more likely to self-disclose on a website when they obtain more gratifications from using the website.

Privacy calculus holds that people deliberately compare benefits and disadvantages when disclosing.
However, that process has not been analyzed explicitly so far (Knijnenburg et al., 2017).
Only observing that privacy concerns and expected gratifications are related to self-disclosure is by itself not sufficient to prove an explicit weighing process.
Here, we suggest that the privacy calculus should be discussed in light of dual process theories, which state that people either deliberately, explicitly, and centrally take decisions, or instead do so automatically, implicitly, and peripherally (Kahneman, 2011; Petty \& Cacioppo, 1986).
Accordingly, privacy calculus would assume that people, when it comes to disclosing, engage in a central processing.
Building on Omarzu (2000) and Altman (1976), we hence introduce and investigate a novel concept termed \emph{privacy deliberation}.
Privacy deliberation captures the extent to which individual people explicitly compare potential positive and negative outcomes before communicating with others.

On the one hand, deliberating about privacy could \emph{reduce} subsequent self-disclosure.
Refraining from communication---the primary means of connecting with others---likely requires some active and deliberate restraint.
On the other hand, deliberating about privacy might also \emph{increase} self-disclosure.
A person concerned about their privacy might conclude that in this situation self-disclosure is actually beneficial.
Deliberation could represent some kind of inner consent, providing additional affirmation.
We therefore formulate the following research question:

RQ1: Are people more or less likely to self-disclose on a website depending on how actively they deliberate about whether they should self-disclose?

Bounded rationality implies that additional factors should also explain self-disclosure.
Self-disclosure online often takes place in situations where information is limited or obscure.
The more familiar users are with a context, the more experience, knowledge, and literacy they possess, the more likely they should be to navigate online contexts successfully.
In other words, if users possess more \emph{self-efficacy} regarding self-disclosing, they should also self-disclose more.
Related, people who report more privacy self-efficacy also engage in more self-withdrawal (Chen, 2018; Dienlin \& Metzger, 2016).

H3: People are more likely to self-disclose on a website when their self-efficacy about self-disclosing on the website is higher.

In situations where people lack experience or competence, the most relevant variable explaining behavior is, arguably, \emph{trust}.
Online, users often cannot control the context or the way their information is handled.
Trust therefore plays a key role in online communication (Metzger, 2004).
People who put more trust in the providers of networks, for example, disclose more personal information (Li, 2011).

Trust can be conceptualized in two different ways (Gefen, Karahanna, \& Straub, 2003).
It either captures ``\emph{specific} beliefs dealing primarily with the integrity, benevolence, and ability of another party'' (Gefen, Karahanna, \& Straub, 2003, p. 55, emphasis added).
Alternatively, it refers to a ``\emph{general} belief that another party can be trusted'' (Gefen, Karahanna, \& Straub, 2003, p. 55, emphasis added).
Whereas specific trust focuses on the causes of trust, general trust emphasizes the experience of trust.
In the online context, there exist several different \emph{targets} of trust, including (a) the information system, (b) the provider, (c) the Internet, and (d) the community of other users (Söllner, Hoffmann, \& Leimeister, 2016).

H4: People are more likely to self-disclose on a website when they have greater trust in the provider, the website, and the other users.

\hypertarget{the-effect-of-popularity-cues}{%
\subsection{The Effect of Popularity Cues}\label{the-effect-of-popularity-cues}}

So far we analyzed user-oriented factors that explain self-disclosure.
But how does the context, the digital infrastructure, affect the privacy calculus and self-disclosure?
In what follows we do not focus on specific \emph{features} of particular websites, which can change and quickly become obsolete (Fox \& McEwan, 2017).
Instead, we address the underlying latent structures by analyzing so-called \emph{affordances} (Ellison \& Vitak, 2015; Fox \& McEwan, 2017).
Developed by Gibson (2015), affordances emphasize that it is not the \emph{objective features} of objects that determine behavior, but our \emph{subjective perceptions}.
Affordances are mental representations of how objects might be used.

The privacy calculus states that both benefits and costs determine behavior.
Popularity cues such as like and dislike buttons, which are categorized as ``paralinguistic digital affordances'' (Carr, Hayes, \& Sumner, 2018, p. 142), can be linked tp the two sides of the privacy calculus.
The like button is positive and a potential benefit:
It expresses an endorsement, a compliment, a reward (Carr, Hayes, \& Sumner, 2018; Sumner, Ruge-Jones, \& Alcorn, 2017).
The dislike button is negative and a potential cost:
It expresses criticism and a way to downgrade content.

Paralinguistic digital affordances and specifically popularity cues can affect behavior (Krämer \& Schäwel, 2020; Trepte, Scharkow, \& Dienlin, 2020).
Online comments that already have several dislikes are much more likely to receive further dislikes (Muchnik, Aral, \& Taylor, 2013).
When users disagree with a post, they are more likely to click on a button labeled \emph{respect} compared to a button labeled \emph{like} (Stroud, Muddiman, \& Scacco, 2017).
In this vein, popularity cues likely also impact the privacy calculus (Krämer \& Schäwel, 2020).

Specifically, \emph{likes} are positive and represent the positivity bias typical of social media (Reinecke \& Trepte, 2014).
Receiving a like online is similar to receiving a compliment offline.
Introducing like-buttons mighty afford and emphasize a \emph{gain frame} (Rosoff, Cui, \& John, 2013).
These gains can be garnered only through participation.
Because like buttons emphasize positive outcomes, it is likely that concerns decrease.
In situations where there is more to win, people should also more actively deliberate about whether or not to disclose information.

H5. Compared to people who use a website without like or dislike buttons, people who use a website with like buttons (a) self-disclose more, (b) obtain more gratifications, (c) are less concerned about their privacy, and (d) deliberate more about whether they should communicate online.

Receiving a \emph{dislike} should feel more like a punishment.
Dislikes introduce a \emph{loss frame}.
As a result, websites featuring both like \emph{and} dislike buttons should be more ambivalent compared to websites without any popularity cues.
In online contexts, gains often outweigh losses.
Having both types of popularity cues might still lead to more gratifications and self-disclosure.
However, privacy concerns should not be reduced anymore:
People who are more concerned about their privacy are also more shy and risk averse (Dienlin, 2017).
Implementing the dislike button might therefore increase privacy concerns, thereby canceling out the positive effects of the like button.
And because there is more at stake, participants should deliberate even more whether or not to disclose.

H6. Compared to people who use a website without like or dislike buttons, people who use a website with like \emph{and} dislike buttons (a) self-disclose more, (b) obtain more gratifications, and (c) deliberate more about whether they should communicate online.

When directly comparing websites including both like and dislike buttons with websites including only like buttons, building on the rationales presented above, it is likely that websites including both buttons should increase privacy concerns and privacy deliberation.

H7. Compared to people who use a website with only like buttons, people who use a website with like and dislike buttons (a) are more concerned about their privacy, and (b) deliberate more about whether they should communicate online.

For a simplified overview of the model we analyzed, see Figure \ref{fig:model}.

\begin{figure}

{\centering \includegraphics[width=.8\textwidth]{figures/design/model}

}

\caption{Overview of analyzed model.}\label{fig:model}
\end{figure}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{open-science}{%
\subsection{Open Science}\label{open-science}}

The online supplementary material (OSM) of this study includes the data, research materials, analyses scripts, and a reproducible version of this manuscript, which can be found on the manuscript's companion website (\url{https://XMtRa.github.io/privacy_calc_exp_anon}).
We preregistered the study using the registration form \emph{OSF Prereg}, which includes the hypotheses, sample size, research materials, analyses, and exclusion criteria (see \url{https://osf.io/a6tzc/?view_only=5d0ef9fe5e1745878cd1b19273cdf859}).
We needed to change our pre-defined plan in some cases.
For a full account of all changes, see OSM.
New analyses that were not preregistered appear in the section Exploratory Analyses.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

The study was designed as an online field experiment with three different groups.
The first group used a website without like or dislike buttons, the second the same website but with only like buttons, and the third the same website but with both like and dislike buttons.
Participants were randomly distributed to one of the three websites in a between-subject design.

We collaborated with a market research company to recruit participants.
As incentive, participants were awarded digital points, which they could use to get special offers from other online commerce services.
Participants were above the age of 18 and lived in Germany.
In a first step, the company sent its panel members an invitation to participate in the study (\emph{invitation}).
In this invitation, panel members were asked to participate in a study analyzing the current threat posed by terrorist attacks in Germany.\footnote{Although the terror attack was not of primary interest for this study, the data can and will also be used to analyze perceptions of the terrorism threat. Hence, no deception took place, and in the debriefing participants were informed about our additional research interest in privacy.}
Members who decided to take part were subsequently sent the first questionnaire (\emph{T1}), in which we (a) asked about their sociodemographics, (b) provided more details about the study, and (c) included a registration link for the website, which was described as ``participation platform.''
Afterward, participants were randomly assigned to one of the three websites.
After registration was completed, participants were invited (but not obliged) to discuss the topic of the terrorism threat in Germany over the course of one week (\emph{field}).
Subsequently, participants received a follow-up questionnaire in which the self-reported measures were collected (\emph{T2}).
Measures were collected after and not before the field phase in order not to prime participants or reveal our primary research interest.

We programmed an online website based on the open-source software \emph{discourse} (\url{https://www.discourse.org/}).
We conducted several pretests with students from the local university to make sure the website had an authentic feel (see Figure \ref{fig:website}).
Participants used the website actively: Overall, they spent 162 hours online, wrote 1,171 comments, and clicked on 560 popularity cues.
Notably, we did not find any instances of people providing meaningless text.
For an example of communication that took place, see Figure \ref{fig:comments}.

\begin{figure}

{\centering \includegraphics[width=.9\textwidth]{figures/website/website_translated}

}

\caption{The website's homepage. (Translated to English.)}\label{fig:website}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=.9\textwidth]{figures/website/comments_translated}

}

\caption{Communication that took place on the website with like and dislike buttons. (Translated to English.)}\label{fig:comments}
\end{figure}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

We ran a priori power analyses to determine sample size.
The power analysis was based on a smallest effect size of interest {[}SESOI; Lakens, Scheel, and Isager (2018){]}.
Namely, we defined a minimum effect size that we considered sufficiently large to support our hypotheses.
Because small effects should be expected when researching aspects of privacy online (e.g., Baruh, Secinti, \& Cemalcilar, 2017), with standardized small effects beginning at an effect size of \emph{r} = .10 (Cohen, 1992), we set our SESOI to be \emph{r} = .10.
Our aim was to be able to detect this SESOI with a probability of at least 95\%. Using the regular alpha level of 5\%, basic power analyses revealed a minimum sample size of \emph{N} = 1,077.
In the end, we were able to include \emph{N} = 559 in our analyses (see below).
This means that our study had a probability (power) of 77\% to find an effect at least as large as \emph{r} = .10.
Put differently, we were able to make reliable inferences (i.e., power = 95\%) about effects at least as big as \emph{r} = .14.

We collected a representative sample of the German population in terms of age, sex, and federal state.
In sum, 1,619 participants completed the survey at T1, 960 participants created a user account on the website, and 982 participants completed the survey at T2.
Using tokens and IP addresses, we connected the data from T1, participants' behavior on the website, and T2 by means of objective and automated processes.
The data of several participants could not be matched for technical reasons, for example because they used different devices for the respective steps.
In the end, the data of 590 participants could be matched successfully.
We excluded 29 participants who finished the questionnaire at T2 in less than three minutes, which we considered to be unreasonably fast.\footnote{We preregistered to delete participants with less than 6 minutes answer time. However, this led to the exclusion of too many data points of high quality, which is why we relaxed this criterion. In the OSM, we report also the results using all participants.}
To detect atypical data, we calculated Cook's distance.
We excluded two participants who provided clear response patterns (i.e., straight-lining).
The final sample included \emph{N} = 559 participants.
The sample characteristics at T1 and T2 were as follows:
T1: age = 45 years, sex = 49\% male, college degree = 22\%.
T2: age = 46 years, sex = 49\% male, college degree = 29\%.
One participant did not report their sex.

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

Wherever possible, we operationalized the variables using established measures.
Where impossible (for example, to date there exists no scale on privacy deliberation), we self-designed novel items, which were pretested concerning legibility and understandability.
To assess factor validity we ran confirmatory factor analyses (CFA).
If the CFAs revealed insufficient fit, we deleted malfunctioning items.
All items were formulated as statements to which participants indicated their (dis-)agreement on a bipolar 7-point scale.
Answer options were visualized as follows: -3 (\emph{strongly disagree}), -2 (\emph{disagree}), -1 (\emph{slightly disagree}), 0 (\emph{neutral}), +1 (\emph{slightly agree}), +2 (\emph{agree}), +3 (\emph{strongly agree}).
For the analyses, answers were coded from 1 to 7.
In the questionnaire, all items measuring a variable were presented on the same page in randomized order.

For an overview of the means, standard deviations, factorial validity, and reliability, see Table \ref{tab:CFA}.
For an overview of the variables' distributions, see Figure \ref{fig:corrplot}.
For the exact wording of all items and their individual distributions, see OSM.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:CFA}Psychometric Properties, Factorial Validity, and Reliability of Measures}

\footnotesize{

\begin{tabular}{llllllllllll}
\toprule
 & \multicolumn{1}{c}{m} & \multicolumn{1}{c}{sd} & \multicolumn{1}{c}{chisq} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{pvalue} & \multicolumn{1}{c}{cfi} & \multicolumn{1}{c}{tli} & \multicolumn{1}{c}{rmsea} & \multicolumn{1}{c}{srmr} & \multicolumn{1}{c}{omega} & \multicolumn{1}{c}{ave}\\
\midrule
Privacy concerns & 3.21 & 1.51 & 11.04 & 9.00 & 0.27 & 1.00 & 1.00 & 0.02 & 0.01 & 0.96 & 0.80\\
General gratifications & 4.76 & 1.22 & 34.03 & 5.00 & 0.00 & 0.98 & 0.95 & 0.10 & 0.02 & 0.93 & 0.74\\
Specific gratifications & 4.71 & 1.02 & 269.77 & 85.00 & 0.00 & 0.94 & 0.93 & 0.06 & 0.05 & 0.95 & 0.59\\
Privacy deliberation & 3.93 & 1.29 & 15.55 & 5.00 & 0.01 & 0.98 & 0.96 & 0.06 & 0.02 & 0.85 & 0.53\\
Self-efficacy & 5.25 & 1.12 & 3.23 & 1.00 & 0.07 & 0.99 & 0.96 & 0.06 & 0.01 & 0.83 & 0.59\\
General trust & 5.21 & 1.04 & 2.07 & 1.00 & 0.15 & 1.00 & 0.99 & 0.04 & 0.01 & 0.87 & 0.70\\
Specific trust & 5.08 & 0.94 & 99.48 & 26.00 & 0.00 & 0.96 & 0.94 & 0.07 & 0.04 & 0.93 & 0.62\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} omega = Raykov's composite reliability coefficient omega; avevar = average variance extracted.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}[!h]

{\centering \includegraphics[width=.9\textwidth]{figures/results/cor_plot}

}

\caption{Above diagonal: zero-order correlation matrix; diagonal: density plots for each variable; below diagonal: bivariate scatter plots for zero-order correlations. Solid regression lines represent linear regressions, dotted regression lines represent quadratic regressions. Calculated with the model predicted values for each variable (baseline model).}\label{fig:corrplot}
\end{figure}

\hypertarget{privacy-concerns}{%
\subsubsection{Privacy concerns}\label{privacy-concerns}}

Privacy concerns were measured with seven items based on Buchanan, Paine, Joinson, and Reips (2007).
One example item was ``When using the participation platform, I had concerns about my privacy.''
One item was deleted due to poor psychometric properties.

\hypertarget{gratifications}{%
\subsubsection{Gratifications}\label{gratifications}}

We differentiated between two separate types of gratifications.
\emph{General gratifications} were measured with five items based on Sun, Wang, Shen, and Zhang (2015).
One example item was ``Using the participation platform has paid off for me.''
\emph{Specific gratifications} were measured with 15 items on five different subdimensions with three items each.
The scale was based on Scherer and Schlütz (2002).
Example items were: ``Using the participation platform made it possible for me to'' \ldots{} ``learn things I would not have noticed otherwise'' (information), ``react to a subject that is important to me'' (relevance), ``engage politically'' (political participation), ``try to improve society'' (idealism), and ``soothe my guilty consciences'' (extrinsic benefits).

\hypertarget{privacy-deliberation}{%
\subsubsection{Privacy deliberation}\label{privacy-deliberation}}

Privacy deliberation was measured with five self-designed items. One example item was ``While using the participation platform I have weighed the advantages and disadvantages of writing a comment.''

\hypertarget{self-efficacy}{%
\subsubsection{Self-efficacy}\label{self-efficacy}}

Self-efficacy was captured with six self-designed items, which measured whether participants felt that they had sufficient self-efficacy to write a comment on the website.
For example, ``I felt technically competent enough to write a comment.''
Two inverted items were deleted due to poor psychometric properties.

\hypertarget{trust}{%
\subsubsection{Trust}\label{trust}}

We differentiated between two types of trust.
\emph{General trust} was operationalized based on Söllner, Hoffmann, and Leimeister (2016), addressing three targets (i.e., provider, website, and other users) with one item each.
One example item was ``The operators of the participation platform seemed trustworthy.''
\emph{Specific trust} was operationalized for the same three targets with three subdimensions each (i.e., ability, benevolence/integrity, and reliability), which were measured with one item each.
Example items were ``The operators of the participation platform have done a good job'' (ability), ``The other users had good intentions'' (benevolence/integrity), ``The website worked well'' (reliability).
The results showed that the provider and website targets were not sufficiently distinct, as was evidenced by a Heywood case (i.e., standardized coefficient greater than 1).
We hence adapted the scale to combine these two targets.
The updated scale showed adequate fit.

\hypertarget{self-disclosure}{%
\subsubsection{Self-disclosure}\label{self-disclosure}}

Self-disclosure was calculated by log-scaling of the number of words each participant wrote in a comment plus the double-weighted number of likes and dislikes (preregistered).
The number of likes and dislikes were multiplied by two because, rudimentarily, like buttons abbreviate the sentence ``I like'' and dislike buttons ``I dislike.''
The sum of words and likes/dislikes was log-scaled because the relative amount of self-disclosure decreases the more a person communicates (see above).

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

All hypotheses and research questions were tested using structural equation modeling with latent variables.
The influence of the three websites was analyzed using contrast coding.
We could therefore test the effects of experimental manipulations within a theoretical framework while using latent variables (Kline, 2016).
Because the dependent variable self-disclosure was not normally distributed, we estimated the model using robust maximum likelihood (Kline, 2016).
As recommended by Kline (2016), to assess global fit we report the model's \(\chi^2\), RMSEA (90\% CI), CFI, and SRMR.
Because sociodemographic variables are often related to self-disclosure and other privacy-related concepts (Tifferet, 2019), we controlled all variables for the influence of sex, age, and education.
Preregistered hypotheses were tested with a one-sided significance level of 5\%.
Research questions were tested with a two-sided 5\% significance level using family-wise Bonferroni-Holm correction.
Exploratory analyses were conducted from a descriptive perspective.
The reported p-values and confidence intervals should thus not be overinterpreted.

We used R {[}Version 4.0.3; R Core Team (2018){]} and the R-packages \emph{lavaan} {[}Version 0.6.8; Rosseel (2012){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2018){]}, \emph{pwr} {[}Version 1.3.0; Champely (2018){]}, \emph{quanteda} {[}Version 2.1.2; Benoit (2018){]}, \emph{semTools} {[}Version 0.5.4; Jorgensen et al. (2018){]}, and \emph{tidyverse} {[}Version 1.3.1; Wickham (2017){]} for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{descriptive-analyses}{%
\subsection{Descriptive Analyses}\label{descriptive-analyses}}

We first measured and plotted all bivariate relations between the study variables (see Figure \ref{fig:corrplot}).
No relationship was particularly curvilinear.
Furthermore, all variables referring to the privacy calculus demonstrated the expected relationships with self-disclosure.
For example, people who were more concerned about their privacy disclosed less information (\emph{r} ).
Worth noting, specific gratifications predicted self-disclosure better than general gratifications (\emph{r} vs.~\emph{r} ).
The mean of privacy deliberation was \emph{m} = 3.93. Altogether, 32\% of participants reported having actively deliberated about their privacy.

Note that the bivariate results showed three large correlations:
specific trust and general gratifications (\emph{r} = .79),
privacy concerns and privacy deliberation (\emph{r} = .61),
and specific gratifications and self-efficacy (\emph{r} = .55). As all six variables were later analyzed within a single multiple regression, problems of multicollinearity might occur.

\hypertarget{privacy-calculus}{%
\subsection{Privacy Calculus}\label{privacy-calculus}}

\hypertarget{preregistered-analyses}{%
\subsubsection{Preregistered analyses}\label{preregistered-analyses}}

First, we ran a model as specified in the preregistration. The model fit our data okay, \(\chi^2\)(388) = 954.97, \emph{p} \textless{} .001, CFI = .94, RMSEA = .05, 90\% CI {[}.05, .05{]}, SRMR = .05.
Regarding H1, we did not find that general gratifications predicted self-disclosure (\(\beta\) = -.04, \textit{b} = -0.05, 95\% CI {[}-0.21, 0.11{]}, \textit{z} = -0.64, \textit{p} = .260; one-sided).
With regard to H2, privacy concerns did not significantly predict self-disclosure (\(\beta\) = .04, \textit{b} = 0.08, 95\% CI {[}-0.25, 0.41{]}, \textit{z} = 0.47, \textit{p} = .318; one-sided).
RQ1 similarly revealed that privacy deliberation was not correlated with self-disclosure (\(\beta\) = -.10, \textit{b} = -0.16, 95\% CI {[}-0.34, 0.03{]}, \textit{z} = -1.68, \textit{p} = .093; two-sided).
Regarding H3, however, we found that experiencing self-efficacy predicted self-disclosure substantially (\(\beta\) = .39, \textit{b} = 0.81, 95\% CI {[}0.51, 1.10{]}, \textit{z} = 5.38, \textit{p} \textless{} .001; one-sided).
Concerning H4, results showed that trust was not associated with self-disclosure (\(\beta\) = -.10, \textit{b} = -0.25, 95\% CI {[}-0.80, 0.29{]}, \textit{z} = -0.92, \textit{p} = .178; one-sided).

However, these results should be treated with caution.
We found several signs of multicollinearity, such as large standard errors or ``wrong'' signs of predictors (Grewal, Cote, \& Baumgartner, 2004).
In the multiple regression trust had a \emph{negative} relation with self-disclosure, whereas in the bivariate analysis it was \emph{positive}.

\hypertarget{exploratory-analyses}{%
\subsubsection{Exploratory analyses}\label{exploratory-analyses}}

We slightly adapted our preregistered model on the basis of the insights described above.
First, instead of specific trust and general gratifications we included \emph{general} trust and \emph{specific} gratifications, which were correlated slightly less strongly.
The adapted model fit our data comparatively well, \(\chi^2\)(507) = 1495.15, \emph{p} \textless{} .001, CFI = .93, RMSEA = .06, 90\% CI {[}.06, .06{]}, SRMR = .06.

In the adapted privacy calculus model, specific gratifications were positively related to self-disclosure online (\(\beta\) = .14, \textit{b} = 0.40, 95\% CI {[}\textgreater{} -0.01, 0.79{]}, \textit{z} = 1.96, \textit{p} = .050; two-sided).
People who deliberated more about their privacy disclosed less information (\(\beta\) = -.13, \textit{b} = -0.20, 95\% CI {[}-0.38, -0.01{]}, \textit{z} = -2.09, \textit{p} = .037; two-sided).
Self-efficacy remained substantially correlated with self-disclosure (\(\beta\) = .35, \textit{b} = 0.72, 95\% CI {[}0.44, 1.00{]}, \textit{z} = 4.99, \textit{p} \textless{} .001; two-sided).
Notably, we found a negative correlation between trust and self-disclosure (\(\beta\) = -.16, \textit{b} = -0.48, 95\% CI {[}-0.92, -0.05{]}, \textit{z} = -2.16, \textit{p} = .031; two-sided), which again implies multicollinearity.

When confronted with multicollinearity, two responses are typically recommended (Grewal, Cote, \& Baumgartner, 2004):
(a) combining collinear variables into a single measure, or (b) keeping only one of the collinear variables.
Combining variables was not an option in our case, because both trust and expected benefits are theoretically distinct constructs.
And because \emph{several} variables were closely related to one another, we therefore decided to fit a simple privacy calculus model containing only privacy concerns and specific gratifications.

The simple model fit our data well, \(\chi^2\)(202) = 710.65, \emph{p} \textless{} .001, CFI = .95, RMSEA = .07, 90\% CI {[}.06, .07{]}, SRMR = .05.
First, we found that people who experienced more privacy concerns than others disclosed less information (\(\beta\) = -.13, \textit{b} = -0.19, 95\% CI {[}-0.31, -0.07{]}, \textit{z} = -3.14, \textit{p} = .002; two-sided).
Second, people who reported more specific gratifications than others self-disclosed more information (\(\beta\) = .22, \textit{b} = 0.63, 95\% CI {[}0.35, 0.92{]}, \textit{z} = 4.37, \textit{p} \textless{} .001; two-sided).
Both effect sizes were above our predefined SESOI of \emph{r} = .10, which implies that the they were large enough to be theoretically relevant.

When comparing the three models with one another, the adapted model explained the most variance in self-disclosure (NA \%), followed by the preregistered model (NA \%), and the simple privacy calculus model (NA \%).
At the same time, the simple privacy calculus model was the most parsimonious one (BIC = 44,140, AIC = 43,500), followed by the preregistered model (BIC = 55,931, AIC = 55,040), and the adapted model (BIC = 64,411, AIC = 63,403).
For a visual overview of all results, see Figure \ref{fig:plotpc}.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{figures/results/coeffs} \caption{Predictors of self-disclosure. Displayed are the 95\% CIs of unstandardized effects.}\label{fig:plotpc}
\end{figure}

\hypertarget{popularity-cues}{%
\subsection{Popularity Cues}\label{popularity-cues}}

\hypertarget{preregistered-analyses-1}{%
\subsubsection{Preregistered analyses}\label{preregistered-analyses-1}}

In a next step, we analyzed the potential effects of the popularity cues.
We for example expected that websites with like buttons would lead to more self-disclosure, gratifications, and privacy deliberation and to less privacy concerns.
Somewhat surprisingly, we found no effects of the popularity cues on the privacy calculus variables.
For an illustration, see Figure \ref{fig:popularitycues}, which displays the model-predicted values for each variable (using the baseline model).
The results show that the confidence intervals of all preregistered variables overlap, illustrating that there were no statistically significant differences across websites.
For the detailed results of the specific inference tests using contrasts, see the OSM.

\hypertarget{exploratory-analyses-1}{%
\subsubsection{Exploratory analyses}\label{exploratory-analyses-1}}

The picture remained the same also when analyzing variables not included in the preregistration.
Note that some differences missed statistical significance only marginally (e.g., specific gratifications for the comparison between the website with like buttons and the control website without like and dislike buttons).
Nevertheless, we refrain from reading too much into these subtle differences.
We conclude that the three websites were comparable regarding the privacy calculus variables and the amount of self-disclosure.

\begin{figure}[!h]
\includegraphics[width=\textwidth]{figures/results/bar_plot} \caption{Overview of the model-predicted values for each variable, separated for the three websites. Control: Website without buttons. Like: Website with like buttons. Like \& Dislike: Website with like and dislike buttons.}\label{fig:popularitycues}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

This is the first study to analyze the privacy calculus using actual observed behavior in a preregistered field experiment.
The data stem from a representative sample of the German population.
We extended the theoretical privacy calculus model by explicitly testing privacy deliberation processes.
We included self-efficacy and trust as additional variables, to better represent our theoretical premise of bounded rationality.
We further asked whether the privacy calculus is affected by popularity cues such as like and dislike buttons.

In the bivariate analyses, all privacy calculus variables significantly predicted self-disclosure.
Thus, all variables likely play an important role when it comes to understanding online-processes.
In the preregistered analyses using multiple regression, however, only self-efficacy significantly predicted self-disclosure.
All other variables were not significant.
There seems to be a relevant overlap between variables, and their mutual relation is still not clear.
The preregistered extended privacy calculus model was therefore not supported by the data.
However, the model showed problems typical of multicollinearity, which is why we also explored (a) an adapted version of the preregistered model, in which we exchanged two variables, and (b) a simple privacy calculus model, which included only privacy concerns and specific gratifications.

The adapted model suggests that also when holding all other variables constant, people who deliberate more about their privacy disclose less.
People who expect more specific gratifications and who feel more self-efficacious disclose more.
However, the model also suggests that if trust increases, while all other factors remain constant, self-disclosure decreases, which seems theoretically implausible.
As a result, we also fit a simple privacy calculus model, which showed that both privacy concerns and obtained gratifications significantly and meaningfully predicted self-disclosure.
Taken together, the results support the privacy calculus framework and suggest that in specific contexts self-disclosure online is not erratic and that it can be explained by several psychological variables.
At the same time, variables such as trust and efficacy seem to play an important role, which further supports the underlying premise of bounded rationality.

The results suggest that in new communication contexts at least one third of all Internet users \emph{actively deliberates} about their privacy.
Determining whether this figure is large or small is difficult.
Although the effect seems substantial to us, one could argue that it should be higher and that more people should actively deliberate about their online self-disclosure.
Interestingly, results showed that privacy deliberation and privacy concerns were remarkably similar.
Both variables were strongly correlated and showed comparable correlations with other variables.
This either implies that thinking about privacy increases concerns or, conversely, that being concerned about privacy encourages us to ponder our options more carefully.
Future research might tell.

Popularity cues do not always seem to have a strong influence on the privacy calculus and self-disclosure.
Although some studies reported that popularity cues can substantially impact behavior (Muchnik, Aral, \& Taylor, 2013), in our study we found the opposite.
Users disclosed the same amount of personal information regardless of whether or not a website included like or dislike buttons.
The results do not imply that popularity cues have no impact on the privacy calculus in general.
Instead, they suggest that there exist certain contexts in which the influence of popularity cues is negligible.

The results also have methodological implications.
First, one can question the tendency to further increase the complexity of the privacy calculus model by adding additional variables (e.g., Dienlin \& Metzger, 2016).
``Since all models are wrong the scientist cannot obtain a''correct" one by excessive elaboration. {[}\ldots{]} Just as the ability to devise simple but evocative models is the signature of the great scientist so overelaboration and overparameterization is often the mark of mediocrity" (Box, 1976, p. 792).
For example, it seems that adding self-efficacy to privacy calculus models is of limited theoretical value.
Self-efficacy is often only a self-reported proxy of behavior and offers little incremental insight.
Instead, it might be more interesting to find out \emph{why} some people feel sufficiently efficacious to self-disclose whereas others do not.

In addition, although adding variables increases explained variance, it can also introduce multicollinearity.
Multicollinearity is not a problem per se, but rather a helpful warning sign (Vanhove, 2019).
From a \emph{statistical} perspective, strongly correlated predictors mean that standard errors become larger (Vanhove, 2019).
We can be less certain about the effects, because there is less unique variance (Vanhove, 2019).
As a remedy, researchers could collect larger samples, which would increase statistical power and precision.
Using accessible statistical software it is now possible to run a priori power analyses that explicitly account for correlated or collinear predictors (Wang \& Rhemtulla, 2020).

From a \emph{theoretical} perspective, multicollinearity could also suggest that the underlying theoretical model is ill-configured.
It is our understanding that multiple regression is often used to isolate effects, to make sure that they are not caused by other third variables.
However, in cases of highly correlated variables this often does not make much sense theoretically.
Combining trust and gratification in a multiple regression asks how increasing benefits affects self-disclosure \emph{while holding trust constant}.
However, it seems more plausible to assume that increasing gratifications also automatically increases trust (Söllner, Hoffmann, \& Leimeister, 2016).
In the preregistered analysis we even went further and tested whether trust increases self-disclose while holding constant gratifications, privacy concerns, privacy deliberations, and self-efficacy---an unlikely scenario.
In short, the effects we found could be correct, but the interpretation is more difficult, potentially artificial, and thereby of little theoretical and practical value.

Finally, we found a surprisingly strong correlation between specific trust and expected gratifications (i.e., \emph{r} = .79).
Operationalizations of trust are remarkably close to expected gratifications.
To illustrate, the trust subdimension \emph{ability} includes items such as ``The comments of other users were useful.''
Trust is often operationalized as a formative construct that directly results from factors such as expected benefits (Söllner, Hoffmann, \& Leimeister, 2016).
In conclusion, it is important not to confuse \emph{causes} of trust with \emph{measures} of trust.
We thus recommend using general and reflective measures of trust.

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

This paper operationalized self-disclosure via communication quantity.
Other understandings of self-disclosure exist that are more narrow, and that would require a qualitative analysis of exchanged communication.
However, additional qualitative analyses were beyond the scope of this paper and not aligned with our theoretical understanding of self-disclosure.

Although we did not find significant effects of like and dislike buttons in this study, they could still affect the privacy calculus in other contexts and settings.
Our findings are limited to the context we analyzed and should not be overly generalized.
Null-findings pose the \emph{Duhème-Quinn Problem} (Dienes, 2008).
They can either result from an actual non-existence of effects or, instead, from a poor operationalization of the research question.
In this case, we were not able send participants notifications when their comments were liked or disliked, which significantly decreased the popularity cues' salience.

The results do not allow for causal interpretation.
First, all results are based on analyses of between-person variance.
However, between-person relations often do not translate to within-person effects (Hamaker, Kuiper, \& Grasman, 2015).
Likewise, the mediation model is only suggestive, as we did not experimentally manipulate the mediating variables and also did not use a longitudinal design.

The self-reported measures were collected \emph{after} the field phase in which the dependent variable was measured.
As a result, the coefficients might overestimate the actual relations, because demand effects might have led participants to artificially align their theoretical answers with their practical behavior.

The assumption of stable unit treatment states that in experiments only the experimental variable should be manipulated, while all others should be held constant (Kline, 2016).
In this study, we explicitly manipulated the popularity cues.
However, because the experiment was conducted in the field several other variables could not be held constant, such as the content of communication by other users, the unfolding communication dynamics, and the characteristics of other users.
As a result, the assumption of stable unit treatment was violated.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

In this study we have found some support for the privacy calculus approach.
People who were more concerned about their privacy disclosed less information online, whereas people who received more gratifications from using a website disclosed more information online.
A substantial share of internet users, approximately 30\%, engaged in a privacy calculus by actively deliberating about whether or not to disclose information.
Popularity cues such as like and dislike buttons played only a minor role in this process.
In conclusion, the results provide further evidence against the privacy paradox.
Internet users are at least somewhat proactive and reasonable---maybe no more or less proactive or reasonable than in other everyday situations.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-altmanPrivacyConceptualAnalysis1976}{}%
Altman, I. (1976). Privacy: {A} conceptual analysis. \emph{Environment and Behavior}, \emph{8}(1), 7--29. \url{https://doi.org/10.1177/001391657600800102}

\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2018). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-barnesPrivacyParadoxSocial2006}{}%
Barnes, S. B. (2006). A privacy paradox: {Social} networking in the {United} {States}. \emph{First Monday}, \emph{11}(9). Retrieved from \href{https://www.firstmonday.org/issues/issue11_9/barnes/index.html}{www.firstmonday.org/issues/issue11\_9/barnes/index.html}

\leavevmode\hypertarget{ref-baruhOnlinePrivacyConcerns2017}{}%
Baruh, L., Secinti, E., \& Cemalcilar, Z. (2017). Online privacy concerns and privacy management: {A} meta-analytical review. \emph{Journal of Communication}, \emph{67}(1), 26--53. \url{https://doi.org/10.1111/jcom.12276}

\leavevmode\hypertarget{ref-R-quanteda}{}%
Benoit, K. (2018). \emph{Quanteda: Quantitative analysis of textual data}. \url{https://doi.org/10.5281/zenodo.1004683}

\leavevmode\hypertarget{ref-bolUnderstandingEffectsPersonalization2018}{}%
Bol, N., Dienlin, T., Kruikemeier, S., Sax, M., Boerman, S. C., Strycharz, J., \ldots{} Vreese, C. H. (2018). Understanding the effects of personalization as a privacy calculus: {Analyzing} self-disclosure across health, news, and commerce contexts. \emph{Journal of Computer-Mediated Communication}, \emph{23}(6), 370--388. \url{https://doi.org/10.1093/jcmc/zmy020}

\leavevmode\hypertarget{ref-boxScienceStatistics1976}{}%
Box, G. E. P. (1976). Science and statistics. \emph{Journal of the American Statistical Association}, \emph{71}(356), 791--799. \url{https://doi.org/10.1080/01621459.1976.10480949}

\leavevmode\hypertarget{ref-buchananDevelopmentMeasuresOnline2007}{}%
Buchanan, T., Paine, C., Joinson, A. N., \& Reips, U.-D. (2007). Development of measures of online privacy concern and protection for use on the {Internet}. \emph{Journal of the American Society for Information Science and Technology}, \emph{58}(2), 157--165. \url{https://doi.org/10.1002/asi.20459}

\leavevmode\hypertarget{ref-carrPredictingThresholdPerceived2018}{}%
Carr, C. T., Hayes, R. A., \& Sumner, E. M. (2018). Predicting a threshold of perceived {Facebook} post success via likes and reactions: {A} test of explanatory mechanisms. \emph{Communication Research Reports}, \emph{35}(2), 141--151. \url{https://doi.org/10.1080/08824096.2017.1409618}

\leavevmode\hypertarget{ref-R-pwr}{}%
Champely, S. (2018). \emph{Pwr: Basic functions for power analysis}. Retrieved from \url{https://CRAN.R-project.org/package=pwr}

\leavevmode\hypertarget{ref-chenRevisitingPrivacyParadox2018}{}%
Chen, H.-T. (2018). Revisiting the privacy paradox on social media with an extended privacy calculus model: {The} effect of privacy concerns, privacy self-efficacy, and social capital on privacy management. \emph{American Behavioral Scientist}, \emph{62}(10), 1392--1412. \url{https://doi.org/10.1177/0002764218792691}

\leavevmode\hypertarget{ref-cohenPowerPrimer1992}{}%
Cohen, J. (1992). A power primer. \emph{Psychological Bulletin}, \emph{112}(1), 155--159. \url{https://doi.org/10.1037/0033-2909.112.1.155}

\leavevmode\hypertarget{ref-dhirUnderstandingRelationshipIntensity2017}{}%
Dhir, A., \& Tsai, C.-C. (2017). Understanding the relationship between intensity and gratifications of {Facebook} use among adolescents and young adults. \emph{Telematics and Informatics}, \emph{34}(4), 350--364. \url{https://doi.org/10.1016/j.tele.2016.08.017}

\leavevmode\hypertarget{ref-dienesUnderstandingPsychologyScience2008}{}%
Dienes, Z. (2008). \emph{Understanding psychology as a science: {An} introduction to scientific and statistical inference}. New York, N.Y.: Palgrave Macmillan.

\leavevmode\hypertarget{ref-dienlinPsychologyPrivacyAnalyzing2017}{}%
Dienlin, T. (2017). \emph{The psychology of privacy: {Analyzing} processes of media use and interpersonal communication}. Hohenheim, Germany: University of Hohenheim. Retrieved from \url{http://opus.uni-hohenheim.de/volltexte/2017/1315/}

\leavevmode\hypertarget{ref-dienlinLongitudinalAnalysisPrivacy2019}{}%
Dienlin, T., Masur, P. K., \& Trepte, S. (2019). \emph{A longitudinal analysis of the privacy paradox} (preprint). SocArXiv. \url{https://doi.org/10.31235/osf.io/fm4h7}

\leavevmode\hypertarget{ref-dienlinExtendedPrivacyCalculus2016}{}%
Dienlin, T., \& Metzger, M. J. (2016). An extended privacy calculus model for {SNSs}: {Analyzing} self-disclosure and self-withdrawal in a representative {U}.{S}. sample. \emph{Journal of Computer-Mediated Communication}, \emph{21}(5), 368--383. \url{https://doi.org/10.1111/jcc4.12163}

\leavevmode\hypertarget{ref-ellisonSocialNetworkSite2015}{}%
Ellison, N. B., \& Vitak, J. (2015). Social network site affordances and their relationship to social capital processes. In S. S. Sundar (Ed.), \emph{The handbook of the psychology of communication technology} (Vol. v.33, pp. 205--227). Chichester, MA: Wiley Blackwell.

\leavevmode\hypertarget{ref-ellisonNegotiatingPrivacyConcerns2011}{}%
Ellison, N. B., Vitak, J., Steinfield, C., Gray, R., \& Lampe, C. (2011). Negotiating privacy concerns and social capital needs in a social media environment. In S. Trepte \& L. Reinecke (Eds.), \emph{Privacy online: {Perspectives} on privacy and self-disclosure in the social web} (pp. 19--32). Berlin, Germany: Springer. \url{https://doi.org/10.1007/978-3-642-21521-6_3}

\leavevmode\hypertarget{ref-foxDistinguishingTechnologiesSocial2017}{}%
Fox, J., \& McEwan, B. (2017). Distinguishing technologies for social interaction: {The} perceived social affordances of communication channels scale. \emph{Communication Monographs}, \emph{9}, 1--21. \url{https://doi.org/10.1080/03637751.2017.1332418}

\leavevmode\hypertarget{ref-gefenTrustTAMOnline2003}{}%
Gefen, D., Karahanna, E., \& Straub, D. W. (2003). Trust and {TAM} in online shopping: {An} integrated model. \emph{MIS Q}, \emph{27}(1), 5190. Retrieved from \url{http://dl.acm.org/citation.cfm?id=2017181.2017185}

\leavevmode\hypertarget{ref-gibsonEcologicalApproachVisual2015}{}%
Gibson, J. J. (2015). \emph{The ecological approach to visual perception}. New York, NY: Psychology Press.

\leavevmode\hypertarget{ref-grewalMulticollinearityMeasurementError2004}{}%
Grewal, R., Cote, J. A., \& Baumgartner, H. (2004). Multicollinearity and measurement error in structural equation models: {Implications} for theory testing. \emph{Marketing Science}, \emph{23}(4), 519--529. \url{https://doi.org/10.1287/mksc.1040.0070}

\leavevmode\hypertarget{ref-hamakerCritiqueCrosslaggedPanel2015}{}%
Hamaker, E. L., Kuiper, R. M., \& Grasman, R. P. P. P. (2015). A critique of the cross-lagged panel model. \emph{Psychological Methods}, \emph{20}(1), 102--116. \url{https://doi.org/10.1037/a0038889}

\leavevmode\hypertarget{ref-heirmanPredictingAdolescentsDisclosure2013}{}%
Heirman, W., Walrave, M., \& Ponnet, K. (2013). Predicting adolescents' disclosure of personal information in exchange for commercial incentives: {An} application of an extended theory of planned behavior. \emph{Cyberpsychology, Behavior, and Social Networking}, \emph{16}(2), 81--87. \url{https://doi.org/10.1089/cyber.2012.0041}

\leavevmode\hypertarget{ref-R-semTools}{}%
Jorgensen, D., T., Pornprasertmanit, S., Schoemann, M., A., \ldots{} Y. (2018). \emph{{semTools}: Useful tools for structural equation modeling}. Retrieved from \url{https://CRAN.R-project.org/package=semTools}

\leavevmode\hypertarget{ref-jourardTransparentSelf1964}{}%
Jourard, S. M. (1964). \emph{The transparent self}. New York, NY: Van Nostrand.

\leavevmode\hypertarget{ref-kahnemanThinkingFastSlow2011}{}%
Kahneman, D. (2011). \emph{Thinking, fast and slow}. New York: Farrar, Straus; Giroux.

\leavevmode\hypertarget{ref-klinePrinciplesPracticeStructural2016}{}%
Kline, R. B. (2016). \emph{Principles and practice of structural equation modeling} (4th ed.). New York, NY: The Guilford Press.

\leavevmode\hypertarget{ref-knijnenburgDeathPrivacyCalculus2017}{}%
Knijnenburg, B., Raybourn, E., Cherry, D., Wilkinson, D., Sivakumar, S., \& Sloan, H. (2017). Death to the privacy calculus? \emph{SSRN Electronic Journal}. \url{https://doi.org/10.2139/ssrn.2923806}

\leavevmode\hypertarget{ref-kokolakisPrivacyAttitudesPrivacy2017}{}%
Kokolakis, S. (2017). Privacy attitudes and privacy behaviour: {A} review of current research on the privacy paradox phenomenon. \emph{Computers \& Security}, \emph{64}, 122--134. \url{https://doi.org/10.1016/j.cose.2015.07.002}

\leavevmode\hypertarget{ref-koohikamaliInvestigationDynamicModel2019}{}%
Koohikamali, M., French, A. M., \& Kim, D. J. (2019). An investigation of a dynamic model of privacy trade-off in use of mobile social network applications: {A} longitudinal perspective. \emph{Decision Support Systems}, \emph{119}, 46--59. \url{https://doi.org/10.1016/j.dss.2019.02.007}

\leavevmode\hypertarget{ref-kosinskiPrivateTraitsAttributes2013}{}%
Kosinski, M., Stillwell, D., \& Graepel, T. (2013). Private traits and attributes are predictable from digital records of human behavior. \emph{Proceedings of the National Academy of Sciences of the United States of America}, \emph{110}(15), 5802--5805. \url{https://doi.org/10.1073/pnas.1218772110}

\leavevmode\hypertarget{ref-krasnovaOnlineSocialNetworks2010}{}%
Krasnova, H., Spiekermann, S., Koroleva, K., \& Hildebrand, T. (2010). Online social networks: {Why} we disclose. \emph{Journal of Information Technology}, \emph{25}(2), 109--125. \url{https://doi.org/10.1057/jit.2010.6}

\leavevmode\hypertarget{ref-kramerMasteringChallengeBalancing2020}{}%
Krämer, N. C., \& Schäwel, J. (2020). Mastering the challenge of balancing self-disclosure and privacy in social media. \emph{Current Opinion in Psychology}, \emph{31}, 67--71. \url{https://doi.org/10.1016/j.copsyc.2019.08.003}

\leavevmode\hypertarget{ref-lakensEquivalenceTestingPsychological2018}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence testing for psychological research: {A} tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. \url{https://doi.org/10.1177/2515245918770963}

\leavevmode\hypertarget{ref-lauferPrivacyConceptSocial1977}{}%
Laufer, R. S., \& Wolfe, M. (1977). Privacy as a concept and a social issue: {A} multidimensional developmental theory. \emph{Journal of Social Issues}, \emph{33}(3), 22--42. \url{https://doi.org/10.1111/j.1540-4560.1977.tb01880.x}

\leavevmode\hypertarget{ref-liEmpiricalStudiesOnline2011}{}%
Li, Y. (2011). Empirical studies on online information privacy concerns: {Literature} review and an integrative framework. \emph{Communications of the Association for Information Systems}, \emph{28}, 453--496.

\leavevmode\hypertarget{ref-masurSituationalPrivacySelfdisclosure2018}{}%
Masur, P. K. (2018). \emph{Situational privacy and self-disclosure: {Communication} processes in online environments}. Cham, Switzerland: Springer.

\leavevmode\hypertarget{ref-metzgerPrivacyTrustDisclosure2004}{}%
Metzger, M. J. (2004). Privacy, trust, and disclosure: {Exploring} barriers to electronic commerce. \emph{Journal of Computer-Mediated Communication}, \emph{9}(4). \url{https://doi.org/10.1111/j.1083-6101.2004.tb00292.x}

\leavevmode\hypertarget{ref-minHowArePeople2015}{}%
Min, J., \& Kim, B. (2015). How are people enticed to disclose personal information despite privacy concerns in social network sites? {The} calculus between benefit and cost. \emph{Journal of the Association for Information Science and Technology}, \emph{66}(4), 839--857. \url{https://doi.org/10.1002/asi.23206}

\leavevmode\hypertarget{ref-muchnikSocialInfluenceBias2013}{}%
Muchnik, L., Aral, S., \& Taylor, S. J. (2013). Social influence bias: {A} randomized experiment. \emph{Science (New York, N.Y.)}, \emph{341}(6146), 647--651. \url{https://doi.org/10.1126/science.1240466}

\leavevmode\hypertarget{ref-newyorkpublicradioPrivacyParadox2018}{}%
New York Public Radio. (2018). The privacy paradox. \{InternetDocument\}. Retrieved from \url{https://project.wnyc.org/privacy-paradox/}

\leavevmode\hypertarget{ref-omarzuDisclosureDecisionModel2000}{}%
Omarzu, J. (2000). A disclosure decision model: {Determining} how and when individuals will self-disclose. \emph{Personality and Social Psychology Review}, \emph{4}(2), 174--185. \url{https://doi.org/10.1207/S15327957PSPR0402_5}

\leavevmode\hypertarget{ref-pettyCommunicationPersuasionCentral1986}{}%
Petty, R., \& Cacioppo, J. (1986). \emph{Communication and {Persuasion}: {Central} and {Peripheral} {Routes} to {Attitude} {Change}}. New York: Springer-Verlag. \url{https://doi.org/10.1007/978-1-4612-4964-1}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2018). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-reineckeAuthenticityWellbeingSocial2014}{}%
Reinecke, L., \& Trepte, S. (2014). Authenticity and well-being on social network sites: {A} two-wave longitudinal study on the effects of online authenticity and the positivity bias in {SNS} communication. \emph{Computers in Human Behavior}, \emph{30}, 95--102. \url{https://doi.org/10.1016/j.chb.2013.07.030}

\leavevmode\hypertarget{ref-rosoffHeuristicsBiasesCyber2013}{}%
Rosoff, H., Cui, J., \& John, R. S. (2013). Heuristics and biases in cyber security dilemmas. \emph{Environment Systems and Decisions}, \emph{33}(4), 517--529. \url{https://doi.org/10.1007/s10669-013-9473-2}

\leavevmode\hypertarget{ref-R-lavaan}{}%
Rosseel, Y. (2012). {lavaan}: An {R} package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{http://www.jstatsoft.org/v48/i02/}

\leavevmode\hypertarget{ref-schererGratifikationMinuteZeitnahe2002}{}%
Scherer, H., \& Schlütz, D. (2002). Gratifikation à la minute: {Die} zeitnahe {Erfassung} von {Gratifikationen}. In P. Rössler (Ed.), \emph{Empirische {Perspektiven} der {Rezeptionsforschung}} (pp. 133--151). Munich, Germany: Reinhard Fischer.

\leavevmode\hypertarget{ref-simonBoundedRationality1990}{}%
Simon, H. A. (1990). Bounded {Rationality}. In J. Eatwell, M. Milgate, \& P. Newman (Eds.), \emph{Utility and {Probability}} (pp. 15--18). London: Palgrave Macmillan UK. \url{https://doi.org/10.1007/978-1-349-20568-4_5}

\leavevmode\hypertarget{ref-sollnerWhyDifferentTrust2016}{}%
Söllner, M., Hoffmann, A., \& Leimeister, J. M. (2016). Why different trust relationships matter for information systems users. \emph{European Journal of Information Systems}, \emph{25}(3), 274--287. \url{https://doi.org/10.1057/ejis.2015.17}

\leavevmode\hypertarget{ref-stroudRecommendRespectAltering2017}{}%
Stroud, N. J., Muddiman, A., \& Scacco, J. M. (2017). Like, recommend, or respect?: {Altering} political behavior in news comment sections. \emph{New Media \& Society}, \emph{19}(11), 1727--1743. \url{https://doi.org/10.1177/1461444816642420}

\leavevmode\hypertarget{ref-sumnerFunctionalApproachFacebook2017}{}%
Sumner, E. M., Ruge-Jones, L., \& Alcorn, D. (2017). A functional approach to the {Facebook} {Like} button: {An} exploration of meaning, interpersonal functionality, and potential alternative response buttons. \emph{New Media \& Society}, \emph{20}(4), 1451--1469. \url{https://doi.org/10.1177/1461444817697917}

\leavevmode\hypertarget{ref-sunLocationInformationDisclosure2015}{}%
Sun, Y., Wang, N., Shen, X.-L., \& Zhang, J. X. (2015). Location information disclosure in location-based social network services: {Privacy} calculus, benefit structure, and gender differences. \emph{Computers in Human Behavior}, \emph{52}, 278--292. \url{https://doi.org/10.1016/j.chb.2015.06.006}

\leavevmode\hypertarget{ref-taddickenUsesPrivacyOnline2011}{}%
Taddicken, M., \& Jers, C. (2011). The uses of privacy online: {Trading} a loss of privacy for social web gratifications? In S. Trepte \& L. Reinecke (Eds.), \emph{Privacy online: {Perspectives} on privacy and self-disclosure in the social web} (pp. 143--158). Berlin, Germany: Springer.

\leavevmode\hypertarget{ref-tifferetGenderDifferencesPrivacy2019}{}%
Tifferet, S. (2019). Gender differences in privacy tendencies on social network sites: {A} meta-analysis. \emph{Computers in Human Behavior}, \emph{93}, 1--12. \url{https://doi.org/10.1016/j.chb.2018.11.046}

\leavevmode\hypertarget{ref-treptePrivacyCalculusContextualized2020}{}%
Trepte, S., Scharkow, M., \& Dienlin, T. (2020). The privacy calculus contextualized: {The} influence of affordances. \emph{Computers in Human Behavior}, \emph{104}, 106115. \url{https://doi.org/10.1016/j.chb.2019.08.022}

\leavevmode\hypertarget{ref-vanhoveCollinearityIsnDisease2019}{}%
Vanhove, J. (2019). Collinearity isn't a disease that needs curing. Retrieved from \url{https://osf.io/8x4uc/}

\leavevmode\hypertarget{ref-wangPowerAnalysisParameter2020}{}%
Wang, Y. A., \& Rhemtulla, M. (2020). Power analysis for parameter estimation in structural equation modeling: {A} discussion and tutorial. \url{https://doi.org/10.31234/osf.io/pj67b}

\leavevmode\hypertarget{ref-watzlawickPragmaticsHumanCommunication2011}{}%
Watzlawick, P., Bavelas, J. B., Jackson, D. D., \& O'Hanlon, B. (2011). \emph{Pragmatics of human communication: {A} study of interactional patterns, pathologies, and paradoxes}. New York, NY: W.W. Norton \& Co.

\leavevmode\hypertarget{ref-whitingWhyPeopleUse2013}{}%
Whiting, A., \& Williams, D. (2013). Why people use social media: A uses and gratifications approach. \emph{Qualitative Market Research: An International Journal}, \emph{16}(4), 362--369. \url{https://doi.org/10.1108/QMR-06-2013-0041}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}

\end{CSLReferences}

\end{document}

### 2021-07-14 preregistration_changes.rmd
- implemented major changes after feedback from reviewers

@@
 # Theoretical Background
+
+In general, instead of analyzing _self-disclosure_, we're now analyzing communication behavior.
+Before, we tried to operationalized self-disclosure with the log of communication frequency plus likes and dislikes.
+However, we realized that this operationalization is too coarse to represent self-disclosure.
+We now analyze the mere quantity of communication, which is much less debatable.
+
 ## Hypotheses
@@
  -	We've changed the order of the hypotheses.
- -	We've changed the wording of the hypotheses (but not the content)
-    -	Before: “H1: People are more likely to communicate actively on the website, the less they are concerned about their privacy.”
-    - Now: “H1: People are more likely to self-disclose on a website when they are less concerned about their privacy.”
- -  We've changed the enumeration of the hypotheses (but not the overall number). 
+ -	We've changed the wording of the hypotheses (but not the content).
+ -  We've changed the enumeration of the hypotheses. 
     - Before, hypotheses were enumerated from 1-13.
     - Now, it's 1, 2, 3, 4, 5a, 5b, 5c, 5d, 6a, 6b, 6c, 7a, 7b.
+
+## Research Question
+
+ -  We dropped two Research Questions, because we realized that they just didn't make sense. That is, we dropped the RQ that popularity cues might affect self-efficacy and trust
 

### 2021-07-14 title_page.RmD
- implemented major changes after feedback from reviewers

---
title             : "Like or Dislike, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus in Online Self-Disclosure"
shorttitle        : "Popularity cues and privacy calculus"
author:            
  - name          : "Dienlin, Tobias"
    email         : "tobias.dienlin@univie.ac.at"
    affiliation   : "1"
    corresponding : yes
    address       : "University of Vienna, Department of Communication, 1090 Vienna, Austria"
affiliation:
  - id            : "1"
    institution   : "University of Vienna"
authornote: |
    Dr. Tobias Dienlin is Assistant Professor of Interactive Communication at University of Vienna. He received his Ph.D. from University of Hohenheim.

    The author declares no competing interests.

    This research was funded by the Volkswagen Foundation, project "Transformations of privacy", which was awarded to Sandra Seubert, Sabine Trepte, Ruediger Grimm, & Christoph Gusy. I would like to thank all colleagues from the project. I especially thank Katharina Bräunlich, who helped both design the website and administer the data collection and importation, and Sabine Trepte, who helped design the study and provided valuable comments on the manuscript. I also thank Niklas Johannes for insightful feedback on the manuscript.

    This manuscript features a companion website, which includes the data, code, additional analyses, the preregistration, and a reproducible version of the manuscript (https://XMtRa.github.io/privacy_calc_exp_anon).
keywords          : "privacy calculus, self-disclosure, popularity cues, field experiment, structural equation modeling, preregistration"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
lang              : "english"
class             : "man"
classoption       : "man, donotrepeattitle"
mask              : no
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
  - \note{\clearpage}
#  - \note{\clearpage}
editor_options: 
  chunk_output_type: inline
---
```{r knitr-set-up, include=F}
knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
```

```{r load-data, include=F, cache=T}
# Load Workspace
load("data/workspace.RData")
```

### 2023-03-02 manuscript.RmD
- updated abstract

@@
 ---
-title             : "Likes or Dislikes, Gratifications or Concerns? Analyzing Popularity Cues and Privacy Calculus when Communicating Online"
+title             : "Do Likes Buttons Increase Self-Disclosure? Analyzing how Online Communication is Affected by Popularity Cues Using the Privacy Calculus Model"
 shorttitle        : "Popularity cues & privacy calculus"
 abstract: |
-    According to privacy calculus, both privacy concerns and expected gratifications explain why people communicate online.
-So far, most findings were based on self-reports or short-term experiments, and it is still largely unknown how popularity cues such as like and dislike buttons affect privacy calculus.
-To answer these questions, a preregistered one-week field experiment was conducted.
+    How do like and dislike buttons affect online communication?
+According to the privacy calculus model, online self-disclosure is determined by privacy concerns and expected benefits.
+It seems possible that like and dislike buttons affect self-disclosure, for example because they increase expected benefits or privacy concerns.
+To find out, we conducted a preregistered one-week field experiment.
 Participants were randomly distributed to three different websites, on which they discussed a current political topic.
-The websites featured either (a) like buttons, (b) like and dislike buttons, or (c) no like or dislike buttons, and were otherwise identical.
+The websites featured either (a) like buttons, (b) like and dislike buttons, or (c) no like or dislike buttons.
 The final sample consisted of `r knitr::load_cache(label = "load-data", object = "n_matched")` participants.
-Although the originally preregistered model was largely rejected, the results showed that a considerable share of actual communication could be explained by privacy concerns, gratifications, privacy deliberation, trust, and self-efficacy.
-The impact of the popularity cues on privacy calculus and communication was negligible.
+The results showed that the mere existence of a like and dislike button did not affect online communication.
+However, self-disclosure could be predicted successfully using the privacy calculus variables.
 keywords          : "privacy calculus, communication, popularity cues, field experiment, structural equation modeling, preregistration"
